
\begin{thebibliography}{11}
\bibitem{Eppner2015}
Eppner C, Deimel R, Álvarez-Ruiz J, Maertens M, Brock O.:
Exploitation of environmental constraints in human and robotic grasping. 
The International Journal of Robotics Research 34(7), 1021-1038 (2015) 

\bibitem{Malzahn2014}
Malzahn, J.: Modeling and Control of Multi-Elastic-Link Robots under Gravity.
Ph.D. thesis, Technische Universit \"at Dortmund (2014)

\bibitem{Pellicciari2013}
Pellicciari, M., Berselli, G., Leali, F., Vergnano, A.: 
A method for reducing the energy consumption of pick-and-place industrial robots. 
Mechatronics 23(3), 326–334 (2013)

\bibitem{Paes2014}
Paes, K., Dewulf, W., Vander Elst, K., Kellens, K., Slaets, P.: 
Energy efficient trajectories for an industrial ABB robot. 
Procedia CIRP 15, 105–110 (2014)

\bibitem{Goya2012}
Goya, H., Matsusaka, K., Uemura, M., Nishioka, Y., Kawamura, S.: 
Realization of High-Energy Efficient Pick-and-Place Tasks of SCARA Robots by Resonance. 
In: 2012 IEEE/RSJ International Conference on Intelligent Robots and Systems, pp. 2730–2735 (2012)

\bibitem{Haddadin2012}
Haddadin, S., Huber, F., Albu-Sc\"affer, A.: 
Optimal control for exploiting the natural dynamics of variable stiffness robots. 
In: 2012 IEEE International Conference on Robotics and Automation, pp. 3347–3354 (2012)

\bibitem{Hirata2011}
Hirata, Y., Suzuki, K., Kosuge, K.: 
Improvement in the performance of passive motion support system with wires based on analysis of brake control. 
In: 2011 IEEE International Conference on Robotics and Automation, pp. 4272–4277 (2011)

\bibitem{Andreetto2016}
Andreetto, M., Divan, S., Fontanelli, D., Palopoli, L.: 
Passive robotic walker path following with bang-bang hybrid control paradigm. 
In: 2016 IEEE International Conference on Intelligent Robots and Systems, pp. 1054–1060 (2016)

\bibitem{Lamaury2013}
Lamaury, J., Gouttefarde, M., Chemori, A., Herve, P.E.: 
Dual-space adaptive control of redundantly actuated cable-driven parallel robots. 
In: 2013 IEEE International Conference on Intelligent Robots and Systems, pp. 4879–4886 (2013)

\bibitem{Oh2007}
Oh, S.R., Agrawal, S.: 
A control lyapunov approach for feedback control of cable-suspended robots. 
In: Proceedings 2007 IEEE International Conference on Robotics and Automation. pp. 4544 – 4549 (2007)

\bibitem{VESC}
VESC-project, \url{https://vesc-project.com/}. Last accessed 3 Jan 2023
\end{thebibliography}
