% \documentclass[12pt]{article}
% \usepackage[margin=1in]{geometry}
\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
% \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
%     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
% \markboth{\journalname, VOL. XX, NO. XX, XXXX 2023}
% {Cheng \MakeLowercase{\textit{et al.}}: Vehicle sequencing at signal-free intersections}
\input{./sections/header}

\begin{document}
\title{Vehicle Sequencing at Signal-Free Intersections: Analytical Performance Guarantees Based on PDMP Formulation}

\author{Xiangchen Cheng, Wei Tang, Ming Yang and Li Jin
\thanks{This work was in part supported by NSFC Project 62103260, SJTU UM Joint Institute and J. Wu \& J. Sun Endowment Fund.
(Corresponding author: Li Jin.)}
\thanks{C. Cheng, M. Yang and L. Jin are with the UM Joint Institute, and W. Tang, M. Yang and L. Jin are (also) with the Department of Automation, Shanghai Jiao Tong University, China (e-mails: mercer@sjtu.edu.cn,
donquixote@sjtu.edu.cn,  mingyang@sjtu.edu.cn, li.jin@sjtu.edu.cn).}%
}

\maketitle
%=======================================================================================================================
%==================================================

\begin{abstract}
Signal-free intersections are a representative application of smart and connected vehicle technologies. Although extensive results have been developed for trajectory planning and autonomous driving, the formulation and evaluation of vehicle sequencing have not been well understood.
In this paper, we consider theoretical guarantees of macroscopic performance (i.e., capacity and delay) of typical sequencing policies at signal-free intersections. We model intersection traffic as a piecewise-deterministic Markov process (PDMP). We analytically characterize the intersection capacity regions and provide upper bounds on travel delay under three typical policies, viz. first-in-first-out, min-switchover, and longer-queue-first. We obtain these results by constructing policy-specific Lyapunov functions and computing mean drift of the PDMP. We also validate the results via a series of micro-simulation-based experiments.
\end{abstract}

\noindent{\bf Keywords:}
Connected and autonomous vehicles, traffic control, piecewise-deterministic Markov processes, Lyapunov drift.

\input{./sections/10_introduction} %1.5p
\input{./sections/20_model} %2.5p
\input{./sections/30_performance} %5p
% \input{./sections/32_multi} %2p
\input{./sections/35_validation} %2p
\input{./sections/40_conclusion}
% \input{./sections/50_appx} %1p

\bibliographystyle{IEEEtran}
\bibliography{References}   %1.5p

% \input{./sections/60_bio} %.5p
\end{document} 