\documentclass[10pt,conference]{IEEEtran}

\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage[ruled,linesnumbered]{algorithm2e}
\usepackage{algorithmic}
\algsetup{linenosize=\small}
\SetKwInput{KwInput}{Input}                % Set the Input
\SetKwInput{KwOutput}{Output}              % set the Output
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{url}
\pagenumbering{arabic}
\usepackage{tcolorbox}
\usepackage{balance}
\usepackage{tcolorbox}
\usepackage[multiple]{footmisc}
\usepackage[english]{babel}
\usepackage{csquotes}
% \usepackage{emoji}
\usepackage{multirow}
% \usepackage{ulem}
\usepackage{subfigure}
\usepackage{lipsum}
\usepackage{tikz}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=2pt] (char) {#1};}}


% bowen comment toolkit
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{amsmath,amssymb}
\newcommand{\basicalert}[2]{\fbox{\bfseries\sffamily\scriptsize\color{blue} #1}{\sf\small$\blacktriangleright$\textit{\color{red} #2}$\blacktriangleleft$}}
\newcommand{\bowen}[1]{\basicalert{From Bowen}{#1}}


\usepackage{comment}
\newboolean{showcomments}
\setboolean{showcomments}{true}
\ifthenelse{\boolean{showcomments}}
{ \newcommand{\mynote}[2]{\textcolor{orange}{
			\fbox{\bfseries\sffamily\scriptsize#1}
			{\small$\blacktriangleright$\textsf{\emph{#2}}$\blacktriangleleft$}}}}
% { \newcommand{\mynote}[2]{}}

\ifthenelse{\boolean{showcomments}}
{ \newcommand{\dnote}[2]{\textcolor{red}{
			\fbox{\bfseries\sffamily\scriptsize#1}
			{\small$\blacktriangleright$\textsf{\emph{#2}}$\blacktriangleleft$}}}}
% { \newcommand{\dnote}[2]{}}

\ifthenelse{\boolean{showcomments}}
{ \newcommand{\hnote}[2]{\textcolor{blue}{
			\fbox{\bfseries\sffamily\scriptsize#1}
			{\small$\blacktriangleright$\textsf{\emph{#2}}$\blacktriangleleft$}}}}
% { \newcommand{\hnote}[2]{}}


\newcommand{\jack}[1]{\hnote{Jack}{#1}}
\newcommand{\dl}[1]{\dnote{David}{#1}}
\newcommand{\jie}[1]{\textcolor{blue}{Jie says: #1}}

\newcommand{\blue}[1]{\textcolor{blue}{#1}}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\pagestyle{plain}
\begin{document}

\newcommand{\yz}[1]{\textcolor{cyan}{{#1}}}
\newcommand{\jh}[1]{\textcolor{red}{\textbf{JH:} #1}}

\title{What Do Users Ask in Open-Source AI Repositories? An Empirical Study of GitHub Issues}

\author{
	\IEEEauthorblockN{Zhou Yang\IEEEauthorrefmark{1},
	Chenyu Wang\IEEEauthorrefmark{1},
	Jieke Shi\IEEEauthorrefmark{1},
	Thong Hoang\IEEEauthorrefmark{2},
	Pavneet Kochhar\IEEEauthorrefmark{3},
	Qinghua Lu\IEEEauthorrefmark{2},
	Zhenchang Xing\IEEEauthorrefmark{2}\IEEEauthorrefmark{4},
	David Lo\IEEEauthorrefmark{1}}
	\IEEEauthorblockA{\IEEEauthorrefmark{1}Singapore Management University, Singapore}
	\IEEEauthorblockA{\IEEEauthorrefmark{2}Data61, Eveleigh, CSIRO, Sydney, Australia}
	\IEEEauthorblockA{\IEEEauthorrefmark{3}Microsoft Research, Vancouver, Canada}
	\IEEEauthorblockA{\IEEEauthorrefmark{4}Australian National University, Canberra, Australia}
	\IEEEauthorblockA{\{zyang, chenyuwang, jkshi, davidlo\}@smu.edu.sg}
	\IEEEauthorblockA{\{James.Hoang, Qinghua.Lu, Zhenchang.Xing\}@data61.csiro.au}
	\IEEEauthorblockA{Pavneet.Kochhar@microsoft.com}
}


\maketitle


\begin{abstract}


Artificial Intelligence (AI) systems, which benefit from the availability of large-scale datasets and increasing computational power, have become effective solutions to various critical tasks, such as natural language understanding, speech recognition, and image processing. The advancement of these AI systems is inseparable from open-source software (OSS). Specifically, many benchmarks, implementations, and frameworks for constructing AI systems are made open source and accessible to the public, allowing researchers and practitioners to reproduce the reported results and broaden the application of AI systems. The development of AI systems follows a data-driven paradigm and is sensitive to hyperparameter settings and data separation. Developers may encounter unique problems when employing open-source AI repositories. 


This paper presents an empirical study that investigates the issues in the repositories of open-source AI repositories to assist developers in understanding problems during the process of employing AI systems. We collect 576 repositories from the \texttt{PapersWithCode} platform. Among these repositories, we find 24,953 issues by utilizing GitHub REST APIs. Our empirical study includes three phases. First, we manually analyze these issues to categorize the problems that developers are likely to encounter in open-source AI repositories. Specifically, we provide a taxonomy of 13 categories related to AI systems. The two most common issues are runtime errors (23.18\%) and unclear instructions (19.53\%). Second, we see that 67.5\% of issues are closed. We also find that half of these issues resolve within four days. Moreover, issue management features, e.g., label and assign, are not widely adopted in open-source AI repositories. In particular, only 7.81\% and 5.9\% of repositories label issues and assign these issues to assignees, respectively. Finally, we empirically show that employing GitHub issue management features and writing issues with detailed descriptions facilitate the resolution of issues. Based on our findings, we make recommendations for developers to help better manage the issues of open-source AI repositories and improve their quality.

\end{abstract}

\begin{IEEEkeywords}
Open Source Software, Mining Software Repository, Best Development Practices, AI Repositories
\end{IEEEkeywords}

%%% Introduction 
\input{sections/introduction.tex}
\input{sections/background.tex}
\input{sections/methodology.tex}
\input{sections/experiment.tex}
\input{sections/discussion.tex}
\input{sections/related_work.tex}

\section{Conclusion and Future Work}
\label{sec:conclusion}



This paper presents the first systematic empirical study of issues in open-source AI repositories. Using the \texttt{PapersWithCode} platform, we collected 576 open-source AI repositories hosted on GitHub and 24,953 issues from these repositories. Through manual analysis of a representative sample of issues, we developed a taxonomy of 13 categories, with the two most common being \texttt{runtime error} (23.18\%) and \texttt{unclear instructions} (19.53\%). Our findings also showed that 67.5\% of issues were closed, with half of them closed within five days. Additionally, we discovered that GitHub issue management features were not widely adopted in open-source AI repositories, with only 7.81\% and 5.9\% of repositories using labels and assignees, respectively. We empirically show that employing GitHub issue management features and writing issues with detailed descriptions (e.g., using more code blocks) can help resolve issues. Our study provides recommendations for repository maintainers to improve the management and quality of open-source AI repositories. 

In the future, we intend to conduct surveys and interviews to uncover the reasons behind the lack of widespread adoption of issue management features in open-source AI repositories and to explore ways to increase their usage. 
Additionally, we will investigate the topics of discussion surrounding the development of AI systems, such as AI testing and data management, on platforms like StackOverflow and GitHub.

\vspace*{0.2cm}
\noindent \textbf{Reproducibility.}
The code and documentation, along with the obtained data, have been made open-source for reproducibility: \textbf{\url{https://github.com/soarsmu/Mining-AI-repos-issues}}.

\section*{Acknowledgment}
This research is supported by the Ministry of Education, Singapore under its Academic Research Fund Tier 3 (Award ID: MOET32020-0004). Any opinions, findings and conclusions or recommendations expressed in this material are those of the author(s) and do not reflect the views of the Ministry of Education, Singapore.

\bibliographystyle{IEEEtran}
\balance
\bibliography{../reference}




\end{document}
