\documentclass[10pt,a4paper]{letter}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\address{Miguel Á. González-Santamarta,\\
Department of Mechanical, Computer \\
Science and Aerospace Engineering,\\
University of León,\\ 
Campus de Vegazana s/n, \\
24071, León (Spain).}
\signature{Miguel Á. González-Santamarta}
\begin{document} 

\begin{letter}{Editors-in-Chief,\\Scientific Reports.} 
\opening{Dear Editor,} 
% CONTENIDO
%The affiliation and contact information of your corresponding author 
%A brief explanation of why the work is appropriate for Scientific Reports

we would like our original research entitled ``SAILOR: Perceptual Anchoring For Robotic Cognitive Architectures'' to be considered for publication in \emph{Scientific Reports}.

We confirm that this work is original, and it has not been published elsewhere nor is currently under consideration for publication in other journals.

This paper presents SAILOR (Symbolic AnchorIng from perceptual data for rOs2-based Robots), a tool to perform symbolic anchoring in ROS 2, which means creating and maintaining the link between the real-world object and the symbolic knowledge that will be stored in a knowledge base. The tool uses color and depth images and is based on deep learning solutions, such as YOLOv8.

SAILOR is also equipped with a matching function, based on deep learning, to decide if a new object is already in the knowledge base. This matching function is trained and tested using new datasets obtained after processing the nuScenes and MOTFront datasets.

Our findings could be applied in a hybrid cognitive architecture for robotics as explained in the work. This symbolic knowledge can be utilized in the planning and reasoning processes that these architectures usually use. Moreover, the robot could obtain visual and physical, such as object labels, positions and sizes; data that can be used in other processes.


Here we propose a list of possible reviewers:

\textbf{Jose María Cañas}\\
\textit{University Rey Juan Carlos - Spain. josemaria.plaza@urjc.es}

\textbf{Miguel Cazorla}\\
\textit{University of Alicante - Spain. miguel.cazorla@ua.es}

\textbf{Luis Vicente Calderita}\\
\textit{University of Extremadura - Spain. lvcalderita@unex.es}

We have not had any prior discussions with a Scientific Reports Editorial Board Member about the work described in our manuscript.

Please address all correspondence concerning this manuscript 
to me at:\\
mogns@unileon.es

Thank you for your consideration of this manuscript.

\closing{Sincerely,} 
\end{letter} 
\end{document}