\documentclass[12pt]{article}

% DEFAULT PACKAGE SETUP

\usepackage{setspace,graphicx,epstopdf,amsmath,amsfonts,amssymb,amsthm}
\usepackage{marginnote,datetime,enumitem,subfigure,rotating,fancyvrb, booktabs}
\usepackage{float}
\usdate
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{lscape}
\usepackage{adjustbox}
%\usepackage[ruled]{algorithm2e}

% we have used too many packages for algorithm ?
 

\usepackage{pdflscape}
\usepackage{tikz}
\usepackage{mathpazo}
\usepackage{bm}
\usepackage{caption}
\usepackage{soul} 
\usepackage{color, xcolor}
% \usepackage{algorithm}  
\usepackage{amsmath}
\usepackage{algorithmicx}  
\usepackage{algpseudocode} 
\usepackage[colorlinks,linkcolor=blue,citecolor=blue]{hyperref}
\usepackage{longtable}
%\usepackage{versionPO}
%\usepackage[ left=1in,right=1in,top=1.5in,bottom=1.5in]{geometry}
%\usepackage[ left=1.25in,right=1.25in,top=1.25in,bottom=1.25in]{geometry}
\usepackage[ left=1in,right=1in,top=1.25in,bottom=1.25in]{geometry}
% These next lines allow including or excludingt versions of text
% using versionPO.sty
%\usepackage[notes,natbib,isbn=false,backend=biber]{biblatex-chicago}  
\usepackage[longnamesfirst]{natbib}
\usepackage{threeparttable}
\usepackage{authblk}
\algnewcommand\algorithmicparam{\textbf{Parameter:}}
\algnewcommand\Param{\item[\algorithmicparam]}


\newcommand{\E}{\mathbb{E}}
\newcommand{\se}{\sigma_\epsilon}
\newcommand{\sth}{\sigma_\theta}
\newcommand{\sx}{\sigma_x}
\newcommand{\lmd}{\lambda}
\newcommand{\ra}{\rightarrow}
\newcommand{\var}{\mathrm{Var}}
\newcommand{\bt}{\beta}
\newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}

\newtheorem{corollary}{Corollary}[section]
\newtheorem{conjecture}{Conjecture}[section]
%\newtheorem{con-proposition}{``Proposition''}
\newtheorem{proposition}{Proposition}[section]
\newtheorem{theorem}{Theorem}[section]
%\newtheorem{theorem_sec}{Theorem}[section]

% \newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}[section]

\newtheorem{example}{Example}[section]
\newtheorem{remark}{Remark}[section]
\newtheorem{question}{Question}%[section]

\newtheorem{assumption}{Assumption}[section]
%\newenvironment{proof}{{\noindent\it Proof}\quad}{\hfill $\square$\par}
\newtheorem*{theorem*}{Theorem}

\newtheorem*{prob}{Problem}
\numberwithin{equation}{section}


%\newtheorem{remark}{Remark}[section]
\newtheorem{prop}{Proposition}[section]
\newtheorem{define}{Definition}[section]

\newtheorem{hyp}{Hypothesis}


\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=blue,      
	urlcolor=blue,
	citecolor=blue,
}

\usepackage{cleveref}



\begin{document}

\setlist{noitemsep}    
	
\title{Artificial Intelligence and Dual Contract\footnote{I gratefully acknowledge the provision of high-performance computational resources by HeptaAI, which facilitated the training of the artificial intelligence models employed in this paper. I thank Allen Fu for research assistance.}}

\author{Qian QI\footnote{Correspondence. No.5 Yiheyuan Road Haidian District, Beijing, P.R.China 100871. Email: {\href{mailto:qiqian@pku.edu.cn}{qiqian@pku.edu.cn}}.}}

\affil[1]{Peking University}


\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\singlespacing
	
\maketitle
	
\vspace{-.2in}

\begin{abstract}
    
This paper explores the capacity of artificial intelligence (AI) algorithms to autonomously design incentive-compatible contracts in dual-principal-agent settings, a relatively unexplored aspect of algorithmic mechanism design. We develop a dynamic model where two principals, each equipped with independent Q-learning algorithms, interact with a single agent. Our findings reveal that the strategic behavior of AI principals (cooperation vs. competition) hinges crucially on the alignment of their profits. Notably, greater profit alignment fosters collusive strategies, yielding higher principal profits at the expense of agent incentives. This emergent behavior persists across varying degrees of principal heterogeneity, multiple principals, and environments with uncertainty. Our study underscores the potential of AI for contract automation while raising critical concerns regarding strategic manipulation and the emergence of unintended collusion in AI-driven systems, particularly in the context of the broader AI alignment problem.
\end{abstract}


\medskip
	
\noindent \textbf{JEL classification}: D21, D43, D83, L12, L13
	
\medskip
\noindent \textbf{Keywords}: Artificial intelligence, dual contract, principal-agent problem, algorithmic collusion, AI alignment.
	
\thispagestyle{empty}
	
\clearpage
	
\doublespacing
\setcounter{footnote}{0}
\renewcommand{\thefootnote}{\arabic{footnote}}
\setcounter{page}{1}
	
	
\newpage

\input{introduction}
\input{Qlearning}
\input{contracts}
\input{dualcontract}
\input{robustness}
\input{conclusion}
	
	

\clearpage
\bibliographystyle{jf}
\bibliography{abs}
\clearpage

\appendix
\input{appendix}

	
\end{document}
