%!TEX root = main.tex
\section{Threats to Validity}

As with all empirical research, there are threats to validity associated with our study, despite our best efforts to mitigate them.

\textbf{External:} We surveyed only ASF contributors and our research findings may not directly generalize to other OSS communities. On the other hand, ASF is very diverse in terms of contributions. It hosts 300+ projects in a wide variety of fields and has thousands of contributors from all over the world.

\textbf{Internal:} 
%is related to capturing the reality as close as possible, which in our case is accurately capturing contributors' experiences and perceptions. 
Internal validity threats might arise from a biased sampling of the ASF contributors. Although we deployed the surveys widely and received 600+ and 400+ responses, self-selection bias could have affected our results. 

\textbf{Construct:} Inaccurate measurements could result from us asking the wrong questions in our survey or interviews. To mitigate this threat, we utilized survey questions from existing studies and ASF internal survey recommended by the ASF D\&I committee \cite{2016ASFSurvey, Lee.Carver:2019}. Moreover, the final questionnaires we used for our longitudinal study were developed in collaboration with sixteen experienced ASF contributors from the D\&I committee.

\textbf{Conclusion:} This is a preliminary approach to analyzing the D\&I in OSS over time. Our longitudinal study consists of only two surveys conducted over two years. Survival bias may result in an ``optimistic'' perspective. As a result of the difference in the number of respondents from each background attribute, we may have obtained fewer results when observing proportional differences between the two survey outcomes. In addition, due to the fact that this is a preliminary study with only two years of survey data and we have an under-representation of minorities, statistical analysis can be biased. We only present the proportional differences we noticed; in the future, when we acquire more survey data, a more in-depth analysis will be required.

