\section{Conclusions}
\label{sec:conclusions}

The \HEJ Monte Carlo event generator provides accurate high-energy
descriptions for a steadily growing range of scattering
processes. The new version 2.2 adds predictions for the QCD corrections to the
production of two W bosons with the same charge together with two or
more jets, which are pivotal for experimental measurements of weak
boson fusion. A further major improvement concerns the gluon-fusion
production of a Higgs boson with jets, where for the first time final
states with only a single jet are included in the description.

While LO-matched predictions for charged lepton pair production with
jets were already available in \HEJ 2.1, the new release allows to
supplement these with LL-accurate high-energy corrections for high
multiplicities where exact LO generation may no longer be
feasible. Furthermore, \HEJ 2.2 allows NLO matching at the level
of differential distributions and facilitates a computationally more efficient
event input generation by separating off low-$p_\perp$ events with a
small contribution to the final predictions.

We have given detailed examples for the new features. The program code as
well as comprehensive documentation including options added in
previous versions are available on \url{https://hej.hepforge.org}.

\section*{Acknowledgements}
\label{sec:acknowledgements}

\HEJ uses \texttt{FastJet}~\cite{Cacciari:2011ma} and \texttt{LHAPDF}~\cite{Buckley:2014ana}.

We are grateful to the other members of the \HEJ collaboration for helpful
comments and discussions.   We are pleased to acknowledge funding from the UK Science and
Technology Facilities Council, the Royal Society, and the ERC Starting
Grant 715049 ``QCDforfuture''.  For the purpose of open access, the authors have
applied a Creative Commons Attribution (CC BY) licence to any Author Accepted
Manuscript version arising from this submission.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
