\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
\usepackage{booktabs}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{adjustbox}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Multi-Contrast MRI Super-Resolution via INR},
    pdfpagemode=FullScreen,
    }
\usepackage{orcidlink}
\usepackage{url}


\begin{document}
\title{Multi-contrast MRI Super-resolution via Implicit Neural Representations}

\titlerunning{Multi-contrast MRI Super-resolution via Implicit Neural Representations}

\input{00_authors.tex}


\maketitle              % typeset the header of the contribution

\begin{abstract}

Clinical routine and retrospective cohorts commonly include multi-parametric Magnetic Resonance Imaging; however, they are mostly acquired in different anisotropic 2D views due to signal-to-noise-ratio and scan-time constraints.
Thus acquired views suffer from poor out-of-plane resolution and affect downstream volumetric image analysis that typically requires isotropic 3D scans.
Combining different views of multi-contrast scans into high-resolution isotropic 3D scans is challenging due to the lack of a large training cohort, which calls for a subject-specific framework.
This work proposes a novel solution to this problem leveraging Implicit Neural Representations (INR).
Our proposed INR jointly learns two different contrasts of complementary views in a continuous spatial function and benefits from exchanging anatomical information between them.
Trained within minutes on a single commodity GPU, our model provides realistic super-resolution across different pairs of contrasts in our experiments with three datasets.
Using Mutual Information (MI) as a metric, we find that our model converges to an optimum MI amongst sequences, achieving anatomically faithful reconstruction.\footnote{Code is available at: \url{https://github.com/jqmcginnis/multi_contrast_inr/}}


\keywords{Implicit Neural Representations \and Multi-Contrast Super-resolution \and Mutual Information.}
\end{abstract}

\input{01_intro}
\input{02_rel_lit}
\input{03_method}
\input{04_exp}


\bibliographystyle{splncs04}
\bibliography{references}
\clearpage
\appendix
\input{05_appendics}

\end{document}
