\section{Effect of Changing from Pure Strategies to Mixed Strategies on the Emergence of Local Suboptimality}
\label{sec:suboptimal-change}

In \Cref{sec:pure,sec:mixed,sec:pure_vs_mixed}, we established sufficient and necessary conditions on the stage game $G$ for there exists some $T$ and some SPE of $G(T)$ where \phenom{} occurs for 2-player games, for cases where: 1) both players can only use pure strategies, 2) one player can only use pure strategies and the other player can use mixed strategies, and 3) both players can use mixed strategies.
Essentially, we established a complete characterization of $\glspp$, $\glsmp$, and $\glsmm$ (and therefore $\glopp$, $\glomp$, and $\glomm$).
Based on these results, in this section we study the effect of changing from pure strategies to mixed strategies on the emergence of \phenom{}. We aim to answer the following question: under what conditions on the stage game $G$ will allowing players to play mixed strategies change whether \phenom{} can ever occur in some repeated game $G(T)$?

Essentially, we aim to study the relationships between $\glspp$, $\glsmp$, and $\glsmm$. For example, are there stage games $G$ where $G\notin \glspp$ and $G\in \glsmp$, i.e., \phenom{} can never occur when both players can only use pure strategies but can occur when player 1 obtains access to mixed strategies? What is a complete characterization of such stage games? And in the other direction, are there stage games $G$ where $G\in \glspp$ and $G\notin \glsmp$? We also study the corresponding questions for the relationships between $\glsmp$ and $\glsmm$ and between $\glspp$ and $\glsmm$.

For the simplicity of descriptions, we refer to the case where both players can only use pure strategies as the {\em pure-pure} case, the case where player 1 can use mixed strategies and player 2 can only use pure strategies as the {\em mixed-pure} case, and the case where both players can use mixed strategies as the {\em mixed-mixed} case.

\subsection{Changing from Pure Strategies to Mixed Strategies when the Other Player Can Only Use Pure Strategies}
\label{sec:pp-to-mp}

We first analyze the situation for changing from the pure-pure case to the mixed-pure case, i.e., study the relationship between $\glspp$ and $\glsmp$. 

We first establish a useful theorem:

\begin{theorem}
\label{thm:spe-pp-mp}
For all 2-player stage games $G$, for all $T\in \integer^+$, for all $\vmu\in \spe^{p,p}(G,T)$, $\vmu \in \spe^{m,p}(G,T)$.
\end{theorem}

\begin{proof}
Assume in contradiction that there exists some $G^*$, $T^*$, and $\vmu^*\in \spe^{p,p}(G^*,T^*)$ where $\vmu^* \notin \spe^{m,p}(G^*,T^*)$. Let $k^*$ to be the largest $k$ where $\vmu^*_{|h(k)}$ is not an NE of $G^*(T-k)$ for some history $h(k)$ in the mixed-pure case. Then one of the players must be able to unilaterally change their strategy in the first round of $\vmu^*_{|h(k)}$ to obtain a higher total payoff in $G^*(T-k)$. Player 2 cannot do so since they can still only play pure strategies. For player 1, they cannot do so when they can only play pure strategies, which means any alternative actions in the first round of $\mu^*_{1|h(k)}$ cannot lead to a higher total payoff in $G^*(T-k)$. But this means that any alternative mixed strategies in the first round of $\mu^*_{1|h(k)}$ also cannot lead to a higher total payoff in $G^*(T-k)$. This produces a contradiction. Therefore, for all 2-player stage games $G$, for all $T\in \integer^+$, for all $\vmu\in \spe^{p,p}(G,T)$, $\vmu \in \spe^{m,p}(G,T)$.
\end{proof}

Now we present \Cref{thm:pp-to-mp-1,thm:pp-to-mp-2} and \Cref{lemma:no-use-1,lemma:no-use-2}, which together completely characterize the relationship between $\glspp$ and $\glsmp$.

\begin{theorem}
\label{thm:pp-to-mp-1}
$\glspp \subseteq \glsmp$, i.e.,
for 2-player stage games $G$, if there exists some $T$ and some SPE of $G(T)$ where \phenom{} occurs in the pure-pure case, then there exists some $T$ and some SPE of $G(T)$ where \phenom{} occurs in the mixed-pure case.
\end{theorem}

\begin{proof}
If there exists some $T$ and some SPE of $G(T)$ where \phenom{} occurs in the pure-pure case, denote $T^*$ to be such a $T$ and $\vmu^*$ to be such an SPE of $G(T^*)$. By \Cref{thm:spe-pp-mp}, $\vmu^*$ is also an SPE of $G(T^*)$ in the mixed-pure case.  Since any pure strategy profiles not in $\Nash^{p,p}(G)$ are also not in $\Nash^{m,p}(G)$, \phenom{} occurs in $\vmu^*$ in the mixed-pure case. Therefore, there exists some $T$ and some SPE of $G(T)$ where \phenom{} occurs in the mixed-pure case.
\end{proof}

\begin{lemma}
\label{lemma:no-use-1}
For all stage games $G$ where $|V_1^{p,p}| = 1$ and $|V_2^{p,p}| > 1$, if $G\notin \glspp$, then $G\notin \glsmp$.
\end{lemma}

\begin{proof}
If $|V_1^{p,p}| = 1$, $|V_2^{p,p}| > 1$, and $G\notin \glspp$, by \Cref{thm:pure}, for all $a_2\in A_2$, for all $a_1\in A_1$ that is a best response to $a_2$, $a_2$ is also a best response to $a_1$. Then for any $(\sigma_1, a_2)\in\Nash^{m,p}(G)$, for any $a_1\in S_{\sigma_1}$, $a_1$ is a best response to $a_2$, so $a_2$ is a best response to $a_1$, which means $(a_1, a_2)\in\Nash^{p,p}(G)$ and $u_1(a_1, a_2)\in V_1^{p,p}$. And since $u_1(\sigma_1, a_2) = u_1(a_1, a_2)$ for any $a_1\in S_{\sigma_1}$, $u_1(\sigma_1, a_2)\in V_1^{p,p}$. Thus, $V_1^{m,p}\subseteq V_1^{p,p}$. Furthermore, since $\Nash^{p,p}(G)\subseteq \Nash^{m,p}(G)$, $V_1^{p,p}\subseteq V_1^{m,p}$. Therefore, $|V_1^{p,p}| = |V_1^{m,p}|$. So $|V_1^{m,p}| = 1$, $|V_2^{m,p}| > 1$. We argue that there cannot exist $\hat{\sigma}_1 \in \Delta A_1, \hat{a}_2, a_2' \in A_2$ where $u_2(\hat{\sigma}_1, \hat{a}_2) < u_2(\hat{\sigma}_1, a_2')$ and $\hat{\sigma}_1$ is a best response to $\hat{a}_2$. Assuming there exists such $\hat{\sigma}_1$ and $\hat{a}_2$. Then for all $a_1\in S_{\hat{\sigma}_1}$, $a_1$ is a best response to $\hat{a}_2$, which means $\hat{a}_2$ is also a best response to $a_1$. Then $\hat{a}_2$ is also a best response to $\hat{\sigma}_1$, which produces a contradiction. Therefore, by \Cref{thm:pure-vs-mixed}, there does not exist some $T$ and some SPE of $G(T)$ where \phenom{} occurs in the mixed-pure case, so $G\notin \glsmp$.
\end{proof}

\begin{lemma}
\label{lemma:no-use-2}
For all stage games $G$ where $|V_1^{p,p}| > 1$ and $|V_2^{p,p}| > 1$, if $G\in \glsmp$, then $G\in \glspp$.
\end{lemma}

\begin{proof}
If $|V_1^{p,p}| > 1$, $|V_2^{p,p}| > 1$, and $G\in \glsmp$, since $\Nash^{p,p}(G)\subseteq \Nash^{m,p}(G)$, $|V_1^{m,p}| > 1$ and $|V_2^{m,p}| > 1$. Then since there exists some $T$ and some SPE of $G(T)$ where \phenom{} occurs in the mixed-pure case, by \Cref{thm:pure-vs-mixed}, there exists some $\hat{\sigma}_1\in \Delta A_1, \hat{a}_2\in A_2$ where $(\hat{\sigma}_1, \hat{a}_2) \notin \Nash^{m,p}(G)$. Applying \Cref{lemma:mixed-pure}, there exists some $a_1\in A_1$ and $a_2\in A_2$ where $(a_1, a_2) \notin \Nash^{p,p}(G)$. By \Cref{thm:pure}, there exists some $T$ and some SPE of $G(T)$ where \phenom{} occurs in the pure-pure case, so $G\in \glspp$.
\end{proof}

The above two lemmas show that under certain preconditions on $|V_1^{p,p}|$ and $|V_2^{p,p}|$, $\glspp = \glsmp$.
Now the question is whether $\glspp$ always equals $\glsmp$.
Here we show that this is not the case. We present example stage games $G$ where $G\in \glsmp$ but $G\notin \glspp$ for each of the remaining cases regarding the values of $|V_1^{p,p}|$ and $|V_2^{p,p}|$. This shows that $\glspp \neq \glsmp$. Combined with \Cref{thm:pp-to-mp-1}, this shows that $\glspp$ is a proper subset of $\glsmp$.

\begin{example}
\label{example:pp-mp-00}
\Cref{tab:none_to_new_ne} presents an example stage game $G$ where $|V_1^{p,p}| = 0$, $|V_2^{p,p}| = 0$, $G\in \glsmp$, and $G\notin \glspp$. When both players can only use pure strategies, there is no Nash equilibrium, so $|V_1^{p,p}| = 0$ and $|V_2^{p,p}| = 0$. By \Cref{thm:pure}, $G\notin \glspp$. When player 1 can use mixed strategies and player 2 can only use pure strategies, the set of Nash equilibria are: $(\sigma_1, b_2)$ and $(\sigma_1, c_2)$ for all $\sigma_1$ where $0.25\leq \sigma_1(a_1) \leq 0.75$. So $|V_1^{m,p}| > 1$ and $|V_2^{m,p}| = 1$. And $(b_1, a_2)$ is a strategy profile where player 1 does not play a best response and player 2 plays a best response. Therefore, the condition in \Cref{thm:pure-vs-mixed} is satisfied, so $G\in \glsmp$.

\begin{table}[ht]
    \centering
    \begin{tabular}{c|c|c|c|c|}
    & $a_2$ & $b_2$ & $c_2$ & $d_2$ \\
    \midrule
    $a_1$ & (4,0) & (1,3) & (2,3) & (0,4) \\
      \midrule
    $b_1$ & (0,4) & (1,3) & (2,3) & (4,0) \\
       \midrule
    \end{tabular}
    \caption{Example stage game in matrix form, row player is player 1, column player is player 2. When both players can only use pure strategies, there is no Nash equilibrium. When player 1 can use mixed strategies and player 2 can only use pure strategies, there are multiple Nash equilibria, and \phenom{} can occur in repeated games. }
    \label{tab:none_to_new_ne}
\end{table}
\end{example}

\begin{example}
\label{example:pp-mp-11}
\Cref{tab:new_ne} presents an example stage game $G$ where $|V_1^{p,p}| = 1$, $|V_2^{p,p}| = 1$, $G\in \glsmp$, and $G\notin \glspp$. When both players can only use pure strategies, the only Nash equilibria are $(a_1, a_2)$ and $(b_1, c_2)$, so $|V_1^{p,p}| = 1$ and $|V_2^{p,p}| = 1$. By \Cref{thm:pure}, $G\notin \glspp$. When player 1 can use mixed strategies and player 2 can only use pure strategies, $(\sigma_1, b_2)$ for all $\sigma_1$ where $0.25\leq \sigma_1(a_1) \leq 0.75$ are Nash equilibria. So $|V_1^{m,p}| > 1$ and $|V_2^{m,p}| > 1$. And $(b_1, a_2)\notin \Nash^{m,p}(G)$. Therefore, the condition in \Cref{thm:pure-vs-mixed} is satisfied, so $G\in \glsmp$.

\begin{table}[ht]
    \centering
    \begin{tabular}{c|c|c|c|}
    & $a_2$ & $b_2$ & $c_2$ \\
    \midrule
    $a_1$ & (4,4) & (1,3)  & (0,0) \\
      \midrule
    $b_1$ & (0,0) & (1,3) & (4,4) \\
       \midrule
    \end{tabular}
    \caption{Example stage game in matrix form, row player is player 1, column player is player 2. $|V_1^{p,p}| = 1$, $|V_2^{p,p}| = 1$, $|V_1^{m,p}| > 1$, and $|V_2^{m,p}| > 1$. }
    \label{tab:new_ne}
\end{table}
\end{example}

\begin{example}
\label{example:pp-mp-g1}
\Cref{tab:no_best_response} presents an example stage game $G$ where $|V_1^{p,p}| > 1$, $|V_2^{p,p}| = 1$, $G\in \glsmp$, and $G\notin \glspp$. For this game $G$, the set of pure Nash equilibria is: $(a_1, a_2)$, $(b_1, a_2)$, $(b_1, b_2)$, and $(c_1, b_2)$. Therefore, $|V_1^{p,p}| > 1$ and $|V_2^{p,p}|=1$. We can see that for all pure strategy profiles where player 2 plays a best response, player 1 also plays a best response. So the condition in \Cref{thm:pure} is not satisfied, and $G\notin \glspp$.
The strategy profile $(\sigma_1, a_2)$ where $\sigma_1(a_1) = 0.9$ and $\sigma_1(c_1) = 0.1$ is an example strategy profile where player 2 plays a best response and player 1 does not play a best response. And $u_1(a_1, a_2) - u_1(c_1, a_2)$ can be expressed as the sum of some sequence of values in $D = \condSet{u_1(\vsigma) - u_1(\vsigma')}{\vsigma,\vsigma' \in \Nash^{m,p}(G)}$. So the condition in \Cref{thm:pure-vs-mixed} is satisfied, and $G\in \glsmp$. Intuitively speaking, in the pure-pure case, although $|V_1^{p,p}| > 1$ makes player 1 potentially vulnerable to threats, there is no way to construct such a threat since there is no strategy profiles where player 1 does not play a best response but player 2 plays a best response. But in the mixed-pure case, such off-(stage-game)-Nash strategy profiles become available, which makes the threat possible.
\end{example}

Furthermore, the following theorem completely characterizes $\glsmp \setminus \glspp$, i.e., the set of 2-player stage games $G$ where 1) in the pure-pure case, \phenom{} can never occur, and 2) in the mixed-pure case, there exists some $T$ and some SPE of $G(T)$ where \phenom{} occurs.

\begin{theorem}
\label{thm:pp-to-mp-2}
For 2-player stage games $G$, $G\notin \glspp$ and $G\in \glsmp$ if and only if
\begin{enumerate}
    \item $|V_1^{p,p}| = 0$, $|V_2^{p,p}| = 0$, and the condition in \Cref{thm:pure-vs-mixed} is satisfied, OR
    \item $|V_1^{p,p}| = 1$, $|V_2^{p,p}| = 1$, and the condition in \Cref{thm:pure-vs-mixed} is satisfied, OR
    \item $|V_1^{p,p}| > 1$, $|V_2^{p,p}| = 1$, there does not exist $\hat{a}_1, a_1' \in A_1, \hat{a}_2 \in A_2$ where $u_1(\hat{a}_1, \hat{a}_2) < u_1(a_1', \hat{a}_2)$ and $\hat{a}_2$ is a best response to $\hat{a}_1$, and the condition in \Cref{thm:pure-vs-mixed} is satisfied.
\end{enumerate}
\end{theorem}

\begin{proof}
To show the above condition is sufficient, we show that each of 1, 2, and 3 is sufficient. 

\textbf{1.} $|V_1^{p,p}| = 0$ and $|V_2^{p,p}| = 0$ mean that $G$ has no pure Nash equilibrium. So in the pure-pure case, there is no SPE for any repeated game $G(T)$, therefore \phenom{} can never occur. Furthermore, the condition in \Cref{thm:pure-vs-mixed} is satisfied implies that in the mixed-pure case, there exists some $T$ and some SPE of $G(T)$ where \phenom{} occurs. 
\Cref{example:pp-mp-00} presents a example stage game $G$ that satisfies this condition.


\textbf{2.} Since $|V_1^{p,p}| = 1$ and $|V_2^{p,p}| = 1$, by \Cref{thm:pure}, in the pure-pure case, \phenom{} can never occur. And the condition in \Cref{thm:pure-vs-mixed} is satisfied implies that in the mixed-pure case, there exists some $T$ and some SPE of $G(T)$ where \phenom{} occurs. \Cref{example:pp-mp-11} presents an example stage game $G$ that satisfies this condition. 


\textbf{3.} Since $|V_1^{p,p}| > 1$, $|V_2^{p,p}| = 1$, and there does not exist $\hat{a}_1, a_1' \in A_1, \hat{a}_2 \in A_2$ where $u_1(\hat{a}_1, \hat{a}_2) < u_1(a_1', \hat{a}_2)$ and $\hat{a}_2$ is a best response to $\hat{a}_1$, by \Cref{thm:pure}, in the pure-pure case, \phenom{} can never occur. And the condition in \Cref{thm:pure-vs-mixed} is satisfied implies that in the mixed-pure case, there exists some $T$ and some SPE of $G(T)$ where \phenom{} occurs. \Cref{example:pp-mp-g1} presents an example stage game $G$ that satisfies this condition. 
\\
\\
To show the condition is necessary, we split all stage games $G$ into five disjoint cases based on $|V_1^{p,p}|$ and $|V_2^{p,p}|$:
\begin{itemize}
    \item[(a)] $|V_1^{p,p}| = 0$ and $|V_2^{p,p}| = 0$,
    \item[(b)] $|V_1^{p,p}| = 1$ and $|V_2^{p,p}| = 1$,
    \item[(c)] $|V_1^{p,p}| > 1$ and $|V_2^{p,p}| = 1$,
    \item[(d)] $|V_1^{p,p}| = 1$ and $|V_2^{p,p}| > 1$,
    \item[(e)] $|V_1^{p,p}| > 1$ and $|V_2^{p,p}| > 1$.
\end{itemize}

For cases (a), (b), and (c), a direct application of \Cref{thm:pure,thm:pure-vs-mixed} implies that our target condition is necessary. For cases (d) and (e), \Cref{lemma:no-use-1,lemma:no-use-2} show that $\glsmp \setminus \glspp$ is empty under these two cases. Therefore, our target condition is necessary.
\end{proof}


\subsection{Changing from Pure Strategies to Mixed Strategies when the Other Player Can Use Mixed Strategies}
\label{sec:mp-to-mm}

Next, we analyze the situation for changing from the mixed-pure case to the mixed-mixed case, i.e., study the relationship between $\glsmp$ and $\glsmm$. 

Following the same argument as the proof of \Cref{thm:spe-pp-mp}, we can prove the following theorem, which is useful for the results in this part.
\begin{theorem}
\label{thm:spe-mp-mm}
For all 2-player stage games $G$, for all $T\in \integer^+$, for all $\vmu\in \spe^{m,p}(G,T)$, $\vmu \in \spe^{m,m}(G,T)$.
\end{theorem}

\begin{proof}
Assume in contradiction that there exists some $G^*$, $T^*$, and $\vmu^*\in \spe^{m,p}(G^*,T^*)$ where $\vmu^* \notin \spe^{m,m}(G^*,T^*)$. Let $k^*$ to be the largest $k$ where $\vmu^*_{|h(k)}$ is not an NE of $G^*(T-k)$ for some history $h(k)$ in the mixed-mixed case. Then one of the players must be able to unilaterally change their strategy in the first round of $\vmu^*_{|h(k)}$ to obtain a higher total payoff in $G^*(T-k)$. Player 1 cannot do so since their strategy space is the same in the mixed-pure case and the mixed-mixed case. For player 2, they cannot do so when they can only play pure strategies, which means any alternative actions in the first round of $\mu^*_{2|h(k)}$ cannot lead to a higher total payoff in $G^*(T-k)$. But this means that any alternative mixed strategies in the first round of $\mu^*_{2|h(k)}$ also cannot lead to a higher total payoff in $G^*(T-k)$. This produces a contradiction. Therefore, for all 2-player stage games $G$, for all $T\in \integer^+$, for all $\vmu\in \spe^{m,p}(G,T)$, $\vmu \in \spe^{m,m}(G,T)$.
\end{proof}

Now we present \Cref{thm:mp-to-mm-1,thm:mp-to-mm-2} and \Cref{lemma:no-use-3}, which together completely characterize the relationship between $\glsmp$ and $\glsmm$.

\begin{theorem}
\label{thm:mp-to-mm-1}
$\glsmp \subseteq \glsmm$, i.e., for 2-player stage games $G$, if there exists some $T$ and some SPE of $G(T)$ where \phenom{} occurs in the mixed-pure case, then there exists some $T$ and some SPE of $G(T)$ where \phenom{} occurs in the mixed-mixed case.
\end{theorem}

\begin{proof}
If there exists some $T$ and some SPE of $G(T)$ where \phenom{} occurs in the mixed-pure case, denote $T^*$ to be such a $T$ and $\vmu^*$ to be such an SPE of $G(T^*)$. By \Cref{thm:spe-mp-mm}, $\vmu^*$ is also an SPE of $G(T^*)$ in the mixed-mixed case. For any strategy profile $(\sigma_1, a_2)$ where $\sigma_1\in \Delta A_1$ and $a_2\in A_2$, if $(\sigma_1, a_2)\notin \Nash^{m,p}(G)$, $(\sigma_1, a_2)\notin \Nash^{m,m}(G)$. So \phenom{} occurs in $\vmu^*$ in the mixed-mixed case. Therefore, there exists some $T$ and some SPE of $G(T)$ where \phenom{} occurs in the mixed-mixed case.
\end{proof}

\begin{lemma}
\label{lemma:no-use-3}
For all stage games $G$ where $|V_1^{m,p}| > 1$ and $|V_2^{m,p}| > 1$, if $G\in \glsmm$, then $G\in \glsmp$.
\end{lemma}

\begin{proof}
If $|V_1^{m,p}| > 1$, $|V_2^{m,p}| > 1$, and $G\in \glsmm$, since $\Nash^{m,p}(G)\subseteq \Nash^{m,m}(G)$, $|V_1^{m,m}| > 1$ and $|V_2^{m,m}| > 1$. Then since there exists some $T$ and some SPE of $G(T)$ where \phenom{} occurs in the mixed-mixed case, by \Cref{thm:general}, there exists some $\hat{\sigma}_1 \in \Delta A_1, \hat{\sigma}_2\in \Delta A_2$ where $(\hat{\sigma}_1, \hat{\sigma}_2) \notin \Nash^{m,m}(G)$. Applying \Cref{lemma:mixed-pure}, there exists some $a_1\in A_1$ and $a_2\in A_2$ where $(a_1, a_2) \notin \Nash^{p,p}(G)$. By \Cref{thm:pure-vs-mixed}, there exists some $T$ and some SPE of $G(T)$ where \phenom{} occurs in the mixed-pure case, so $G\in \glsmp$.
\end{proof}

The above lemma shows that under certain preconditions on $|V_1^{m,p}|$ and $|V_2^{m,p}|$, $\glsmp = \glsmm$.
Now the question is whether $\glsmp$ always equals $\glsmm$.
Here we show that this is not the case. We present example stage games $G$ where $G\in \glsmm$ but $G\notin \glsmp$ for each of the remaining cases regarding the values of $|V_1^{m,p}|$ and $|V_2^{m,p}|$. This shows that $\glsmp \neq \glsmm$. Combined with \Cref{thm:mp-to-mm-1}, this shows that $\glsmp$ is a proper subset of $\glsmm$.

\begin{example}
\label{example:mp-mm-00}
\Cref{tab:none_to_new_ne_flip} presents an example stage game $G$ where $|V_1^{m,p}| = 0$, $|V_2^{m,p}| = 0$, $G\in \glsmm$, and $G\notin \glsmp$. This game is essentially the stage game presented in \Cref{tab:none_to_new_ne} with column player being player 1 and row player being player 2. When player 1 can play mixed strategies and player 2 can only play pure strategies, there is no Nash equilibrium, so $|V_1^{m,p}| = 0$ and $|V_2^{m,p}| = 0$. By \Cref{thm:pure-vs-mixed}, $G\notin \glsmp$. When both players can use mixed strategies, $|V_1^{m,m}| = 1$ and $|V_2^{m,m}| > 1$. And $(a_1, b_2)$ is a strategy profile where player 1 plays a best response and player 2 does not play a best response. Therefore, the condition in \Cref{thm:general} is satisfied, so $G\in \glsmm$.

\begin{table}[ht]
    \centering
    \begin{tabular}{c|c|c|}
    & $a_2$ & $b_2$ \\
    \midrule
    $a_1$ & (0,4) & (4,0) \\
    \midrule
    $b_1$ & (3,1) & (3,1) \\
    \midrule
    $c_1$ & (3,2) & (3,2) \\
    \midrule
    $d_1$ & (4,0) & (0,4) \\
   \midrule
    \end{tabular}
    \caption{Example stage game in matrix form, row player is player 1, column player is player 2. When player 1 can play mixed strategies and player 2 can only play pure strategies, there is no Nash equilibrium. When both players can use mixed strategies, there are multiple Nash equilibria, and \phenom{} can occur in repeated games. }
    \label{tab:none_to_new_ne_flip}
\end{table}
\end{example}

\begin{example}
\label{example:mp-mm-11}
\Cref{tab:new_ne_flip} presents an example stage game $G$ where $|V_1^{m,p}| = 1$, $|V_2^{m,p}| = 1$, $G\in \glsmm$, and $G\notin \glsmp$. This game is essentially the stage game presented in \Cref{tab:new_ne} with column player being player 1 and row player being player 2. Following the arguments in \Cref{example:pp-mp-11}, for this game, $|V_1^{m,p}| = 1$, $|V_2^{m,p}| = 1$, $|V_1^{m,m}| > 1$, $|V_2^{m,m}| > 1$, and $(a_1, b_2)\notin \Nash^{m,m}(G)$. Therefore, by \Cref{thm:pure-vs-mixed,thm:general}, $G\in \glsmm$ and $G\notin \glsmp$.
\begin{table}[ht]
    \centering
    \begin{tabular}{c|c|c|}
    & $a_2$ & $b_2$ \\
    \midrule
    $a_1$ & (4,4) & (0,0) \\
      \midrule
    $b_1$ & (3,1) & (3,1) \\
       \midrule
   $c_1$ & (0,0) & (4,4) \\
   \midrule
    \end{tabular}
    \caption{Example stage game in matrix form, row player is player 1, column player is player 2. $|V_1^{m,p}| = 1$, $|V_2^{m,p}| = 1$, $|V_1^{m,m}| > 1$, and $|V_2^{m,m}| > 1$. }
    \label{tab:new_ne_flip}
\end{table}
\end{example}

\begin{example}
\label{example:mp-mm-g1}
\Cref{tab:no_multiset_sum} presents an example stage game $G$ where $|V_1^{m,p}| > 1$, $|V_2^{m,p}| = 1$, $G\in \glsmm$, and $G\notin \glsmp$. When player 1 can play mixed strategies and player 2 can only play pure strategies, the set of Nash equilibria is: 1) $(\sigma_{\lambda}, a_2)$ for all $0\leq \lambda\leq 1$ where $\sigma_{\lambda}(a_1)=\lambda$ and $\sigma_{\lambda}(b_1) = 1 - \lambda$, and 2) $(\sigma'_{\theta}, b_2)$ for all $0\leq \theta\leq 1$ where $\sigma'_{\theta}(b_1)=\theta$ and $\sigma'_{\theta}(c_1) = 1 - \lambda$. So $|V_1^{m,p}| > 1$ and $|V_2^{m,p}| = 1$. For any $\hat{\sigma}_1 \in \Delta A_1, \hat{a}_2 \in A_2$ where $\hat{a}_2$ is a best response to $\hat{\sigma}_1$ and $\hat{\sigma}_1$ is not a best response to $\hat{a}_2$, if $\hat{a}_2=a_2$, $S_{\hat{\sigma}_1}$ must include $c_1$ and at least one of $a_1$ and $b_1$; if $\hat{a}_2=b_2$, $S_{\hat{\sigma}_1}$ must include $a_1$ and at least one of $b_1$ and $c_1$. In all these cases, there is some $a, a'\in S_{\hat{\sigma}_1}$ where $u_1(a, \hat{a}_2) - u_1(a', \hat{a}_2)=0.5$. But $V_1 = \{2,3\}$ only contains integer elements. So such $u_1(a, \hat{a}_2) - u_1(a', \hat{a}_2)$ can never be expressed as the sum of a sequence of values from $D = \condSet{u_1(\vsigma) - u_1(\vsigma')}{\vsigma,\vsigma' \in \Nash^{m,p}(G)}$. Therefore, the condition in \Cref{thm:pure-vs-mixed} is not satisfied, whereas the condition in \Cref{thm:general} is satisfied. So $G\in \glsmm$ and $G\notin \glsmp$. Intuitively speaking, in the mixed-pure case, although $|V_1^{m,p}| > 1$ makes player 1 potentially vulnerable to threats, there is no way to construct such a threat with the available strategy profiles. But in the mixed-mixed case, as player 2 obtains access to mixed strategies, new mechanisms for constructing threats become available (as are used in the proof of \Cref{thm:general}), which enables \phenom{} to occur. 

\begin{table}[ht]
    \centering
    \begin{tabular}{c|c|c|}
    & $a_2$ & $b_2$ \\
    \midrule
     $a_1$ & (3,2)   & (1.5,1) \\
      \midrule
     $b_1$ & (3,2)   & (2,2) \\
       \midrule
     $c_1$ & (2.5,1)  & (2,2) \\
       \midrule
    \end{tabular}
    \caption{Example stage game in matrix form, row player is player 1, column player is player 2. $|V_1^{m,p}| > 1$, $|V_2^{m,p}| = 1$. \Phenom{} can never occur in the mixed-pure case, but can occur in the mixed-mixed case.}
    \label{tab:no_multiset_sum}
\end{table}
\end{example}

\begin{example}
\label{example:mp-mm-1g}
\Cref{tab:no_best_response_flip} presents an example stage game $G$ where $|V_1^{m,p}| = 1$, $|V_2^{m,p}| > 1$, $G\in \glsmm$, and $G\notin \glsmp$.
This game is essentially the stage game presented in \Cref{tab:no_best_response} with column player being player 1 and row player being player 2. The same discussion in \Cref{example:pp-mp-g1} applies here.

\begin{table}[ht]
    \centering
    \begin{tabular}{c|c|c|c|}
    & $a_2$ & $b_2$ & $c_2$ \\
    \midrule
    $a_1$ & (2,3) & (2,3) & (1,1) \\
      \midrule
    $b_1$ & (1,1) & (2,2) & (2,2) \\
       \midrule
    \end{tabular}
    \caption{Example stage game in matrix form, row player is player 1, column player is player 2. For all $a\in A_2$, for all $\sigma_1\in \Delta A_1$ that is a best response to $a$, $a$ is also a best response to $\sigma_1$. }
    \label{tab:no_best_response_flip}
\end{table}
\end{example}

Furthermore, the following theorem completely characterizes $\glsmm \setminus \glsmp$, i.e., the set of 2-player stage games $G$ where 1) in the mixed-pure case, \phenom{} can never occur, and 2) in the mixed-mixed case, there exists some $T$ and some SPE of $G(T)$ where \phenom{} occurs.

\begin{theorem}
\label{thm:mp-to-mm-2}
For 2-player stage games $G$, $G\notin \glsmp$ and $G\in \glsmm$ if and only if
\begin{enumerate}
    \item $|V_1^{m,p}| = 0$, $|V_2^{m,p}| = 0$, and the condition in \Cref{thm:general} is satisfied, OR
    \item $|V_1^{m,p}| = 1$, $|V_2^{m,p}| = 1$, and the condition in \Cref{thm:general} is satisfied, OR
    \item $|V_1^{m,p}| > 1$, $|V_2^{m,p}| = 1$, the condition in \Cref{thm:pure-vs-mixed} is not satisfied, and the condition in \Cref{thm:general} is satisfied, OR
    \item $|V_1^{m,p}| = 1$, $|V_2^{m,p}| > 1$, the condition in \Cref{thm:pure-vs-mixed} is not satisfied, and the condition in \Cref{thm:general} is satisfied.
\end{enumerate}
\end{theorem}

\begin{proof}
Same as in the proof of \Cref{thm:pp-to-mp-2}, a direct application of \Cref{thm:pure-vs-mixed,thm:general} shows that the above condition is sufficient. \Cref{example:mp-mm-00,example:mp-mm-11,example:mp-mm-1g,example:mp-mm-g1} present example stage games $G$ that belong to each of the cases 1, 2, 3, and 4.

To show the condition is necessary, we split all stage games $G$ into five disjoint cases based on $|V_1^{m,p}|$ and $|V_2^{m,p}|$:
\begin{itemize}
    \item[(a)] $|V_1^{m,p}| = 0$ and $|V_2^{m,p}| = 0$,
    \item[(b)] $|V_1^{m,p}| = 1$ and $|V_2^{m,p}| = 1$,
    \item[(c)] $|V_1^{m,p}| > 1$ and $|V_2^{m,p}| = 1$,
    \item[(d)] $|V_1^{m,p}| = 1$ and $|V_2^{m,p}| > 1$,
    \item[(e)] $|V_1^{m,p}| > 1$ and $|V_2^{m,p}| > 1$.
\end{itemize}

For cases (a), (b), (c), and (d), a direct application of \Cref{thm:pure-vs-mixed,thm:general} implies that our target condition is necessary. For case (e), \Cref{lemma:no-use-3} shows that $\glsmm \setminus \glsmp$ is empty under this case. Therefore, our target condition is necessary.
\end{proof}

\subsection{Changing Both Players from Pure Strategies to Mixed Strategies}
\label{sec:pp-to-mm}

Finally, we analyze the situation for changing from the pure-pure case to the mixed-mixed case, i.e., i.e., study the relationship between $\glspp$ and $\glsmm$. The results and example games for this situation can mostly be derived directly from the results in \Cref{sec:pp-to-mp,sec:mp-to-mm}.

\begin{theorem}
\label{thm:pp-to-mm-1}
$\glspp \subseteq \glsmm$, i.e., for 2-player stage games $G$, if there exists some $T$ and some SPE of $G(T)$ where \phenom{} occurs in the pure-pure case, then there exists some $T$ and some SPE of $G(T)$ where \phenom{} occurs in the mixed-mixed case.
\end{theorem}

\begin{proof}
\Cref{thm:pp-to-mp-1,thm:mp-to-mm-1} directly imply this result.
\end{proof}

\begin{lemma}
\label{lemma:no-use-4}
For all stage games $G$ where $|V_1^{p,p}| > 1$ and $|V_2^{p,p}| > 1$, if $G\in \glsmm$, then $G\in \glspp$.
\end{lemma}

\begin{proof}
If $|V_1^{p,p}| > 1$, $|V_2^{p,p}| > 1$, since $\Nash^{p,p}(G)\subseteq \Nash^{m,p}(G)\subseteq \Nash^{m,m}(G)$, $|V_1^{m,p}| > 1$, $|V_2^{m,p}| > 1$, $|V_1^{m,m}| > 1$ and $|V_2^{m,m}| > 1$. Therefore, by applying \Cref{lemma:no-use-2,lemma:no-use-3}, we have if $G\in \glsmm$, then $G\in \glspp$.
\end{proof}

The above lemma shows that under certain preconditions on $|V_1^{p,p}|$ and $|V_2^{p,p}|$, $\glspp = \glsmm$.
Here we present example stage games $G$ where $G\in \glsmm$ but $G\notin \glspp$ for each of the remaining cases regarding the values of $|V_1^{p,p}|$ and $|V_2^{p,p}|$. These examples are reused from \Cref{sec:pp-to-mp,sec:mp-to-mm}. This shows that $\glspp \neq \glsmm$. Combined with \Cref{thm:pp-to-mm-1}, this shows that $\glspp$ is a proper subset of $\glsmm$.

\begin{example}
\label{example:pp-mm-00}
\Cref{tab:none_to_new_ne} presents an example stage game $G$ where $|V_1^{p,p}| = 0$, $|V_2^{p,p}| = 0$, $G\in \glsmm$, and $G\notin \glspp$.
\end{example}

\begin{example}
\label{example:pp-mm-11}
\Cref{tab:new_ne} presents an example stage game $G$ where $|V_1^{p,p}| = 1$, $|V_2^{p,p}| = 1$, $G\in \glsmm$, and $G\notin \glspp$.
\end{example}

\begin{example}
\label{example:pp-mm-g1}
\Cref{tab:no_best_response} presents an example stage game $G$ where $|V_1^{p,p}| > 1$, $|V_2^{p,p}| = 1$, $G\in \glsmm$, and $G\notin \glspp$.
\end{example}

\begin{example}
\label{example:pp-mm-1g}
\Cref{tab:no_best_response_flip} presents an example stage game $G$ where $|V_1^{p,p}| = 1$, $|V_2^{p,p}| > 1$, $G\in \glsmm$, and $G\notin \glspp$.
\end{example}

The following theorem completely characterizes $\glsmm \setminus \glspp$, i.e., the set of 2-player stage games $G$ where 1) in the pure-pure case, \phenom{} can never occur, and 2) in the mixed-mixed case, there exists some $T$ and some SPE of $G(T)$ where \phenom{} occurs.

\begin{theorem}
\label{thm:pp-to-mm-2}
For 2-player stage games $G$, $G\notin \glspp$ and $G\in \glsmm$ if and only if
\begin{enumerate}
    \item $|V_1^{p,p}| = 0$, $|V_2^{p,p}| = 0$, and the condition in \Cref{thm:general} is satisfied, OR
    \item $|V_1^{p,p}| = 1$, $|V_2^{p,p}| = 1$, and the condition in \Cref{thm:general} is satisfied, OR
    \item $|V_1^{p,p}| > 1$, $|V_2^{p,p}| = 1$, the condition in \Cref{thm:pure} is not satisfied, and the condition in \Cref{thm:general} is satisfied, OR
    \item $|V_1^{p,p}| = 1$, $|V_2^{p,p}| > 1$, the condition in \Cref{thm:pure} is not satisfied, and the condition in \Cref{thm:general} is satisfied.
\end{enumerate}
\end{theorem}

\begin{proof}
Same as in the proofs of \Cref{thm:pp-to-mp-2,thm:mp-to-mm-2}, a direct application of \Cref{thm:pure,thm:general} shows that the above condition is sufficient. \Cref{example:pp-mm-00,example:pp-mm-11,example:pp-mm-1g,example:pp-mm-g1} present example stage games $G$ that belong to each of the cases 1, 2, 3, and 4.

To show the condition is necessary, again, we split all stage games $G$ into five disjoint cases based on $|V_1^{p,p}|$ and $|V_2^{p,p}|$:
\begin{itemize}
    \item[(a)] $|V_1^{p,p}| = 0$ and $|V_2^{p,p}| = 0$,
    \item[(b)] $|V_1^{p,p}| = 1$ and $|V_2^{p,p}| = 1$,
    \item[(c)] $|V_1^{p,p}| > 1$ and $|V_2^{p,p}| = 1$,
    \item[(d)] $|V_1^{p,p}| = 1$ and $|V_2^{p,p}| > 1$,
    \item[(e)] $|V_1^{p,p}| > 1$ and $|V_2^{p,p}| > 1$.
\end{itemize}
For cases (a), (b), (c), and (d), a direct application of \Cref{thm:pure,thm:general} implies that our target condition is necessary.
For case (e), \Cref{lemma:no-use-4} shows that $\glsmm \setminus \glsmp$ is empty under this case. Therefore, our target condition is necessary.
\end{proof}


\subsection{Discussion}

The central question we focus on in this section is how changing a player (or both players) from pure-strategies-only to mixed-strategies-allowed can affect the emergence of \phenom{}.
We present here an intuitive interpretation of the results established in this section.

First, if \phenom{} can occur before the change, then after changing any player (or both players) from pure-strategies-only to mixed-strategies-allowed, \phenom{} can still occur (\Cref{thm:pp-to-mp-1,thm:mp-to-mm-1,thm:pp-to-mm-1}). So allowing players to play mixed strategies can never prohibit the emergence of \phenom{}.

On the other hand, it is possible that \phenom{} can never occur before the change, but after changing one player (or both players) from pure-strategies-only to mixed-strategies-allowed, \phenom{} can occur. Such phenomena can happen through two different mechanisms. The first one is through the introduction of new stage-game Nash equilibria. Before the change, there might be no stage-game NE, or there is only one payoff value attainable at stage-game NEs for each player ($V_1=V_2=1$), which makes neither of the players vulnerable to potential threats that force them to play locally suboptimally. After allowing one (or both) player(s) to play mixed strategies, a new set of stage-game NEs becomes available. This makes some $|V_i| > 1$, making that player vulnerable to potential threats. Cases 1 and 2 in \Cref{thm:pp-to-mp-2,thm:mp-to-mm-2,thm:pp-to-mm-2} and \Cref{example:pp-mp-00,example:pp-mp-11,example:mp-mm-00,example:mp-mm-11,example:pp-mm-00,example:pp-mm-11} belong to this type.

For the second mechanism, before the change, some player already have $|V_i| > 1$, which means they are potentially vulnerable to threats. However, there is no way of constructing such a threat in any SPE given the available strategy profiles, so \phenom{} cannot occur. After allowing one (or both) player(s) to play mixed strategies, with the newly available strategy profiles, it becomes possible to construct such a threat, which makes it possible for \phenom{} to occur. We show that this can happen in the following cases:
\begin{itemize}
    \item The player that is potentially vulnerable to threats before the change (i.e., $|V_i|>1$) changes from pure-strategies-only to mixed-strategies-allowed. This change can open up vulnerabilities for themselves, regardless of whether the opponent has access to mixed strategies or not. Case 3 in \Cref{thm:pp-to-mp-2} ($|V_1^{p,p}| > 1$, $|V_2^{p,p}| = 1$, player 1 changes from pure to mixed, player 2 can only play pure), case 4 in \Cref{thm:mp-to-mm-2} ($|V_1^{m,p}| = 1$, $|V_2^{m,p}| > 1$, player 2 changes from pure to mixed, player 1 can play mixed), and the corresponding example games \Cref{example:pp-mp-g1,example:mp-mm-1g} demonstrate this type.
    \item A player changes from pure-strategies-only to mixed-strategies-allowed when their opponent is potentially vulnerable to threats before the change (i.e., $|V_i|>1$). Here, only if their opponent has access to mixed strategies will such change be useful to create threats that were not possible before the change. Case 3 in \Cref{thm:mp-to-mm-2} and the corresponding example game \Cref{example:mp-mm-g1} demonstrate this situation. Importantly, if their opponent only has access to pure strategies, changing from pure-strategies-only to mixed-strategies-allowed will not enable a player to construct threats if it was impossible to create threats before the change. This is shown in \Cref{lemma:no-use-1}.
\end{itemize}
