\section{The Pure Strategy Against Mixed Strategy Case}
\label{sec:pure_vs_mixed}

To complete the picture, we also analyze the case where one player can only use pure strategies while the other player can use mixed strategies. Without loss of generality, we consider the case where player 1 can use mixed strategies and player 2 can only use pure strategies in both the stage game and the repeated games. 
%We use $\Nash^{m,p}(G)$ to denote the set of Nash equilibria of the stage game $G$ when player 1 can use mixed strategies and player 2 can only use pure strategies, and $V_i^{m,p} = \condSet{u_i(\vsigma)}{\vsigma\in\Nash^{m,p}(G)}$ to denote the set of payoff values attainable at stage game Nash equilibria for player $i$ when player 1 can use mixed strategies and player 2 can only use pure strategies. 
We use $\Nash^{m,p}(G)$, $\spe^{m,p}(G,T)$, and $V_i^{m,p}$ to denote the corresponding concepts of $\Nash(G)$, $\spe(G,T)$, and $V_i$ when player 1 can use mixed strategies and player 2 can only use pure strategies.
We use $\glsmp$ and $\glomp$ to denote the partition of the set of all stage games $\mathcal{G}$ when player 1 can use mixed strategies and player 2 can only use pure strategies. For stage games $G$ where $\Nash^{m,p}(G) = \emptyset$, there is no SPE in the repeated game $G(T)$ for any $T$, so we categorize such stage games $G$ to $\glomp$ since \phenom{} can never occur. The following theorem presents a complete mathematical characterization of $\glsmp$. As we will see, the sufficient and necessary condition for \phenom{} to occur in this case is different from both the pure strategy case and the general case.


\begin{theorem}[2-player, pure strategy against mixed strategy]
\label{thm:pure-vs-mixed}
For 2-player games where player 1 can use mixed strategies and player 2 can only use pure strategies, a sufficient and necessary condition on the stage game $G$ for there exists some $T$ and some SPE of $G(T)$ where \phenom{} occurs is:
\begin{enumerate}
    \item $|V_1^{m,p}| > 1$, $|V_2^{m,p}| > 1$, and there exists some $\hat{\sigma}_1\in \Delta A_1, \hat{a}_2\in A_2$ where $(\hat{\sigma}_1, \hat{a}_2) \notin \Nash^{m,p}(G)$, OR
    \item $|V_1^{m,p}| > 1$, $|V_2^{m,p}| = 1$, and there exists $\hat{\sigma}_1 \in \Delta A_1, a_1' \in A_1, \hat{a}_2 \in A_2$ where
    \begin{enumerate}
        \item $u_1(\hat{\sigma}_1, \hat{a}_2) < u_1(a_1', \hat{a}_2)$, and
        \item $\hat{a}_2$ is a best response to $\hat{\sigma}_1$, and
        \item if $\hat{\sigma}_1$ has more than one support (not a pure strategy), denote the set of possible differences in $u_1$ between pairs of NEs in the stage game as $D = \condSet{u_1(\vsigma) - u_1(\vsigma')}{\vsigma,\vsigma' \in \Nash^{m,p}(G)}$, there exists an action $a$ from the support of $\hat{\sigma}_1$, i.e., $a\in S_{\hat{\sigma}_1}$, such that, for every $a'\in S_{\hat{\sigma}_1}\setminus a$, there exists some integer $n_{a'}\geq 0$ and $d_k^{a'}\in D$, $k=1,\dots,n_{a'}$ such that $u_1(a, \hat{a}_2) - u_1(a', \hat{a}_2) = \sum_{k=1}^{n_{a'}} d_k^{a'}$,
    \end{enumerate} OR
    \item $|V_1^{m,p}| = 1$, $|V_2^{m,p}| > 1$, and there exists $\hat{\sigma}_1 \in \Delta A_1, \hat{a}_2, a_2' \in A_2$ where $u_2(\hat{\sigma}_1, \hat{a}_2) < u_2(\hat{\sigma}_1, a_2')$ and $\hat{\sigma}_1$ is a best response to $\hat{a}_2$.
\end{enumerate}
\end{theorem}

We first establish a useful lemma.

\begin{lemma}
\label{lemma:spe_payoff}
For 2-player stage game $G$ and $T$-round repeated game $G(T)$ where player 1 can use mixed strategies and player 2 can only use pure strategies, for any SPE $\vmu$ of $G(T)$ where the strategy profile at each round forms a stage-game NE, player 1's total payoff in the repeated game $U_1(\vmu) = \sum_{k=1}^{T} c_k$ for some $c_k\in V_1^{m,p}$, $k=1,\dots,T$, i.e., player 1's total payoff in the repeated game equals the sum of some sequence of stage-game NE payoffs.
\end{lemma}

\begin{proof}
We prove by induction on $T$. The proposition trivially holds for $T=1$. Given that the proposition holds for $T=K-1$, consider $T=K$. For any SPE $\vmu$ of $G(K)$ where the strategy profile at each round forms a stage-game NE, denote the first round strategy profile as $(\hat{\sigma}_1, \hat{a}_2)$ where $\hat{\sigma}_1\in \Delta A_1$, $\hat{a}_2\in A_2$. Since $(\hat{\sigma}_1, \hat{a}_2)\in \Nash^{m,p}(G)$, for all $a, a'\in S_{\hat{\sigma}_1}$, $u_1(a, \hat{a}_2) = u_1(a', \hat{a}_2) = u_1(\hat{\sigma}_1, \hat{a}_2)$. Denote $\vmu_{|(a_1, a_2)}$ as the strategy profile starting from round 2 given that players play $(a_1, a_2)$ in the first round, for $\vmu$ to be a Nash equilibrium of the root game, we have for all $a, a'\in S_{\hat{\sigma}_1}$, $u_1(a, \hat{a}_2) + U_1(\vmu_{|(a, \hat{a}_2)}) = u_1(a', \hat{a}_2) + U_1(\vmu_{|(a', \hat{a}_2)}) = U_1(\vmu)$. By the induction hypothesis, for any $a\in S_{\hat{\sigma}_1}$, $U_1(\vmu_{|(a, \hat{a}_2)}) = \sum_{k=1}^{K-1} c_k$ for some $c_k\in V_1^{m,p}$, $k=1,\dots,K-1$. Therefore, $U_1(\vmu) = u_1(a, \hat{a}_2) + U_1(\vmu_{|(a, \hat{a}_2)}) = u_1(\hat{\sigma}_1, \hat{a}_2) + U_1(\vmu_{|(a, \hat{a}_2)}) = \sum_{k=1}^{K} c_k$ for some $c_k\in V_1^{m,p}$, $k=1,\dots,K$. This completes the induction step. 
\end{proof}



\begin{proof}[Proof of \Cref{thm:pure-vs-mixed}]

First we show the condition is sufficient, by showing if the condition is satisfied, we can construct some $T$ and some SPE where \phenom{} occurs. If the condition is satisfied, at least one of (1),(2),(3) must be satisfied. We consider each case here.

If (1) is satisfied, we can use the same construction that is used for the proofs of the pure strategy case and the general case (see the proofs of \Cref{thm:pure,thm:general}, the parts that handle the case where (1) is satisfied). If (3) is satisfied, we can use the same construction that is used for the proof of the pure strategy case (see the proofs of \Cref{thm:pure}, the parts that handle the case where (2) is satisfied).

If (2) is satisfied, then there exists $\hat{\sigma}_1 \in \Delta A_1, a_1' \in A_1, \hat{a}_2 \in A_2$ where (a), (b), and (c) are satisfied. If $|S_{\hat{\sigma}_1}|=1$, i.e., $\hat{\sigma}_1$ is a pure strategy, we can use the same construction that is used for the proof of the pure strategy case (see the proofs of \Cref{thm:pure}, the parts that handle the case where (2) is satisfied). If $|S_{\hat{\sigma}_1}|>1$, i.e., $\hat{\sigma}_1$ is not a pure strategy, we know from (c) that there exists an action $a\in S_{\hat{\sigma}_1}$ such that, for every $a'\in S_{\hat{\sigma}_1}\setminus a$, there exists some integer $n_{a'}\geq 0$ and $d_k^{a'}\in D$, $k=1,\dots,n_{a'}$ such that $u_1(a, \hat{a}_2) - u_1(a', \hat{a}_2) = \sum_{k=1}^{n_{a'}} d_k^{a'}$. Let $a$, $n_{a'}$ for every $a'\in S_{\hat{\sigma}_1}\setminus a$, $d_k^{a'}\in D$ for every $a'\in S_{\hat{\sigma}_1}\setminus a$ and $k=1,\dots,n_{a'}$ be such a set of assignments. We consider a game with $T= 1 + \sum_{a'\in S_{\hat{\sigma}_1}\setminus a} n_{a'} + n_{\bot}$ where $n_{\bot}$ is a large enough integer.
We construct an SPE $\vmu^*$ consisting of segments. Denote $\vmu^t$ as all the $t$-th round behavior strategy profiles in $\vmu^*$ and $\vmu^{t_1:t_2}$ as all the behavior strategy profiles between the $t_1$-th round and the $t_2$-th round in $\vmu^*$. $\vmu^*$ is divided into segments: $\vmu^1, \vmu^{2:T_1}, \vmu^{T_1+1:T_2},\dots, \vmu^{T_{|S_{\hat{\sigma}_1}|-1}+1:T_{|S_{\hat{\sigma}_1}|}}$. Each segment ending at $T_i$ for $i=1,\dots,|S_{\hat{\sigma}_1}|-1$ corresponds to one of $a'\in S_{\hat{\sigma}_1}\setminus a$. We denote the segment corresponding to $a'$ as $\vmu^{a'}$ for every $a'\in S_{\hat{\sigma}_1}\setminus a$; $\vmu^{a'}$ has $n_{a'}$ rounds. We denote the final segment as $\vmu^{\bot}$, which has $n_{\bot}$ rounds. Each $\vmu^{a'}$ for every $a'\in S_{\hat{\sigma}_1}\setminus a$ and $\vmu^{\bot}$ only depend on the play in the first round, not depending on any later rounds. 
we construct $\vmu^*$ as follows:
\begin{itemize}
    \item In the first round, play $\vmu^1 = (\hat{\sigma}_1, \hat{a}_2)$.
    \item For segment $\vmu^{a'}$ for each $a'\in S_{\hat{\sigma}_1}\setminus a$, if player 1's first round play is $a'$, play the sequence of stage-game NEs $\Sigma_1 = (\vsigma_1^1,\dots, \vsigma_1^{n_{a'}})$; otherwise, play the sequence of stage-game NEs $\Sigma_0 = (\vsigma_0^1,\dots, \vsigma_0^{n_{a'}})$. The sequences $\Sigma_1$ and $\Sigma_0$ are chosen according to $u_1(\vsigma_1^k) - u_1(\vsigma_0^k) = d_k^{a'}$ for all $k=1,\dots,n_{a'}$.
    \item Let $\vsmin, \vsmax\in \Nash^{m,p}(G)$ such that $u_1(\vsmin) = \min (V_1^{m,p})$ and $u_1(\vsmax) = \max (V_1^{m,p})$, so $u_1(\vsmax) > u_1(\vsmin)$. For segment $\vmu^{\bot}$, if player 1's first round play is some $a\in S_{\hat{\sigma}_1}$, play $(\vsmax, \vsmax,\dots)$; if player 1's first round play is some $a\notin S_{\hat{\sigma}_1}$, play $(\vsmin, \vsmin,\dots)$.
\end{itemize}
This construction ensures that: 1) player 1 choosing any action $a\in S_{\hat{\sigma}_1}$ in the first round results in the same total payoff in $G(T)$, and 2) player 1 choosing any action $a\notin S_{\hat{\sigma}_1}$ in the first round results in a lower total payoff in $G(T)$ as long as $n_{\bot}$ is large enough. This ensures that such $\vmu^*$ is an SPE of $G(T)$ and the first round play does not form a stage-game NE.
\\
\\
To prove this condition is necessary, we prove that if the condition is not satisfied, then for any $T$ and any SPE $\vmu$ of $G(T)$, \phenom{} does not occur, i.e., the strategy profile at each round must form an NE of the stage game. The condition is not satisfied means all of (1),(2),(3) are false. This can be divided into the following disjoint cases.

\textbf{1. $|V_1^{m,p}| = 0$, $|V_2^{m,p}|=0$.} Here, $\Nash^{m,p}(G) = \emptyset$, so there is no SPE in the repeated game $G(T)$ for any $T$. Therefore, \phenom{} can never occur.

\textbf{2. $|V_1^{m,p}| = 1$, $|V_2^{m,p}|=1$.} 
Using backward induction, we know that in any SPE, the strategy profile at each round must form an NE of the stage game.

\textbf{3. $|V_1^{m,p}| > 1$, $|V_2^{m,p}|>1$.}
Since (1) is false, there does not exist $\hat{\sigma}_1\in \Delta A_1, \hat{a}_2\in A_2$ where $(\hat{\sigma}_1, \hat{a}_2)\notin \Nash^{m,p}(G)$. Therefore, it trivially follows that in any SPE of $G(T)$, the strategy profile at each round must form an NE of the stage game.

\textbf{4. $|V_1^{m,p}| = 1$, $|V_2^{m,p}|>1$. }
Since (3) is false, there does not exist $\hat{\sigma}_1 \in \Delta A_1, \hat{a}_2, a_2' \in A_2$ where $u_2(\hat{\sigma}_1, \hat{a}_2) < u_2(\hat{\sigma}_1, a_2')$ and $\hat{\sigma}_1$ is a best response to $\hat{a}_2$. This means that for any $\hat{\sigma}_1 \in \Delta A_1, \hat{a}_2\in A_2$ where $\hat{\sigma}_1$ is a best response to $\hat{a}_2$, $\hat{a}_2$ is a best response to $\hat{\sigma}_1$, and thus $(\hat{\sigma}_1, \hat{a}_2) \in \Nash^{m,p}(G)$. Now we can use the same backward induction argument as in the proof of \Cref{thm:pure} (the part that proves the condition is necessary, case 4) to prove that in any SPE, the strategy profile at each round must form an NE of the stage game. 

\textbf{5. $|V_1^{m,p}| > 1$, $|V_2^{m,p}| = 1$. } 
Since (2) is false, we know that:
\begin{itemize}
    \item[($\ast$)] For all pure strategy $a_1\in A_1$ and $a_2\in A_2$, if $a_2$ is a best response to $a_1$, then $a_1$ is also a best response to $a_2$, i.e., $(a_1, a_2)\in \Nash^{m,p}(G)$.
    \item[($\ast\ast$)] For all $\sigma_1\in \Delta A_1$ and $a_2\in A_2$ where $a_2$ is a best response to $\sigma_1$ and $\sigma_1$ is not a best response to $a_2$ and $\sigma_1$ is not a pure strategy, denote the set of possible differences in $u_1$ between pairs of NEs in the stage game as $D = \condSet{u_1(\vsigma) - u_1(\vsigma')}{\vsigma,\vsigma' \in \Nash^{m,p}(G)}$, then there does not exist an action from the support of $\sigma_1$ $a\in S_{\sigma_1}$ such that, for every $a'\in S_{\sigma_1}\setminus a$, there exists some integer $n_{a'}\geq 0$ and $d_k^{a'}\in D$, $k=1,\dots,n_{a'}$ such that $u_1(a, a_2) - u_1(a', a_2) = \sum_{k=1}^{n_{a'}} d_k^{a'}$.
\end{itemize}

Now we can use backward induction to prove that in any SPE, the strategy profile at each round must form an NE of the stage game. The strategy profiles in the last round must form stage-game NEs. Given that the strategy profiles in the last $k$ rounds must all form stage-game NEs, consider the $(k+1)$-to-last round. Denote the strategies played in this round as $(\hat{\sigma}_1, \hat{a}_2)$. $\hat{a}_2$ must be a best response to $\hat{\sigma}_1$, since player 2's play in this round does not affect the total payoff they get in the final $k$ rounds. If $\hat{\sigma}_1$ is a pure strategy, then according to ($\ast$), $(\hat{\sigma}_1, \hat{a}_2)$ forms a stage-game NE, which completes the induction step. 

If $\hat{\sigma}_1$ is a mixed strategy (more than one support), assume on the contrary that the strategy profile at this round does not form a stage-game NE, then $\hat{\sigma}_1$ is not a best response to $\hat{a}_2$. By ($\ast\ast$), there does not exist an action from the support of $\hat{\sigma}_1$ $a\in S_{\hat{\sigma}_1}$ such that, for every $a'\in S_{\hat{\sigma}_1}\setminus a$, there exists some integer $n_{a'}\geq 0$ and $d_k^{a'}\in D$, $k=1,\dots,n_{a'}$ such that $u_1(a, \hat{a}_2) - u_1(a', \hat{a}_2) = \sum_{k=1}^{n_{a'}} d_k^{a'}$. Denote $\vmu_{|(a_1, a_2)}^{-k:}$ as the strategy profile in the last $k$ rounds given players played $(a_1, a_2)$ in the first round. For $(\hat{\sigma}_1, \hat{a}_2)$ to be part of a Nash equilibrium of the $(k+1)$-round repeated game, we have for all $a,a'\in S_{\hat{\sigma}_1}$, $u_1(a, \hat{a}_2) + U_1(\vmu_{|(a, \hat{a}_2)}^{-k:}) = u_1(a', \hat{a}_2) + U_1(\vmu_{|(a', \hat{a}_2)}^{-k:})$. By \Cref{lemma:spe_payoff}, for each $a\in S_{\hat{\sigma}_1}$, $U_1(\vmu_{|(a, \hat{a}_2)}^{-k:}) = \sum_{t=1}^k c_t^a$ for some $c_t^a\in V_1^{m,p}$, $t=1,\dots,k$. Therefore, taking an arbitrary $a\in S_{\hat{\sigma}_1}$, for every $a'\in S_{\hat{\sigma}_1}\setminus a$, $u_1(a, \hat{a}_2) - u_1(a', \hat{a}_2) = U_1(\vmu_{|(a', \hat{a}_2)}^{-k:}) - U_1(\vmu_{|(a, \hat{a}_2)}^{-k:}) = \sum_{t=1}^k c_t^{a'} - \sum_{t=1}^k c_t^a = \sum_{t=1}^k d_t^{a'}$, where $d_t^{a'} = c_t^{a'} - c_t^a \in D$. This produces a contradiction. Therefore, the strategy profile at the $(k+1)$-to-last round also forms a stage-game NE. This completes the induction step.

\end{proof}

Again, we can obtain the following corollary regarding the value of $T$ above which \phenom{} can occur if the condition in \Cref{thm:pure-vs-mixed} is satisfied:

\begin{corollary}
For 2-player games where player 1 can use mixed strategies and player 2 can only use pure strategies, given a stage game $G$:
\begin{enumerate}
    \item If $|V_1^{m,p}| > 1$, $|V_2^{m,p}| > 1$, and there exists some $\hat{\sigma}_1\in \Delta A_1, \hat{a}_2\in A_2$ where $(\hat{\sigma}_1, \hat{a}_2) \notin \textrm{Nash}(G)$, then by \Cref{lemma:mixed-pure}, there exists $\hat{a}_1\in A_1$ and $\hat{a}_2\in A_2$ where $(\hat{a}_1, \hat{a}_2) \notin \Nash^{m,p}(G)$, for all $T \geq 2\cdot \max\Big( \frac{\delta_1}{\max (V_1^{m,p})-\min (V_1^{m,p})}, \frac{\delta_2}{\max (V_2^{m,p})- \min (V_2^{m,p})} \Big) +1$ where $\delta_1 = \max_{a_1\in A_1} u_1(a_1, \hat{a}_2) - u_1(\hat{a}_1, \hat{a}_2)$ and $\delta_2 = \max_{a_2\in A_2} u_2(\hat{a}_1, a_2) - u_2(\hat{a}_1, \hat{a}_2)$, there exists some SPE of $G(T)$ where \phenom{} occurs.
    \item If $|V_1^{m,p}| > 1$, $|V_2^{m,p}| = 1$, and there exists $\hat{\sigma}_1 \in \Delta A_1, a_1' \in A_1, \hat{a}_2 \in A_2$ where 
    \begin{enumerate}
        \item $u_1(\hat{\sigma}_1, \hat{a}_2) < u_1(a_1', \hat{a}_2)$, and
        \item $\hat{a}_2$ is a best response to $\hat{\sigma}_1$, and
        \item if $\hat{\sigma}_1$ has more than one support (not a pure strategy), denote the set of possible differences in $u_1$ between pairs of NEs in the stage game as $D = \condSet{u_1(\vsigma) - u_1(\vsigma')}{\vsigma,\vsigma' \in \Nash^{m,p}(G)}$, there exists an action from the support of $\hat{\sigma}_1$ $a\in S_{\hat{\sigma}_1}$ such that, for every $a'\in S_{\hat{\sigma}_1}\setminus a$, there exists some integer $n_{a'}\geq 0$ and $d_k^{a'}\in D$, $k=1,\dots,n_{a'}$ such that $u_1(a, \hat{a}_2) - u_1(a', \hat{a}_2) = \sum_{k=1}^{n_{a'}} d_k^{a'}$,
    \end{enumerate}
    then if $\hat{\sigma}_1$ is a pure strategy, i.e., $|S_{\hat{\sigma}_1}|=1$, for all $T\geq \frac{\max_{a_1\in A_1} u_1(a_1, \hat{a}_2) - u_1(\hat{\sigma}_1, \hat{a}_2)}{\max (V_1^{m,p})-\min (V_1^{m,p})} + 1$, there exists some SPE of $G(T)$ where \phenom{} occurs; if $|S_{\hat{\sigma}_1}|>1$, for all $T\geq 2 + \sum_{a'\in S_{\hat{\sigma}_1}\setminus a} n_{a'} + \frac{\max_{i, i'\in A_1} u_1(i, \hat{a}_2) - u_1(i', \hat{a}_2) }{\max(V_1^{m,p}) - \min(V_1^{m,p})}$, where $a$ and $n_{a'}$ for every $a'\in S_{\hat{\sigma}_1}\setminus a$ are given in (c), there exists some SPE of $G(T)$ where \phenom{} occurs.
    
    \item If $|V_1^{m,p}| = 1$, $|V_2^{m,p}| > 1$, and there exists $\hat{\sigma}_1 \in \Delta A_1, \hat{a}_2, a_2' \in A_2$ where $u_2(\hat{\sigma}_1, \hat{a}_2) < u_2(\hat{\sigma}_1, a_2')$ and $\hat{\sigma}_1$ is a best response to $\hat{a}_2$, then for all $T\geq \frac{\max_{a_2\in A_2} u_2(\hat{\sigma}_1, a_2) - u_2(\hat{\sigma}_1, \hat{a}_2)}{\max (V_2^{m,p})-\min (V_2^{m,p})} + 1$, there exists some SPE of $G(T)$ where \phenom{} occurs.
\end{enumerate}
\end{corollary}