Systematic uncertainties 
arise from the tracking inefficiency, unfolding procedure, unfolding model dependence, UE subtraction procedure, and residual effects from combinatorial jets.
The tracking-inefficiency uncertainty is determined by repeating the analysis with an RM based on a track sample with 4\% of all tracks randomly rejected. This number corresponds to the uncertainty in the tracking efficiency, determined by varying the track selection parameters and ITS$\textendash$TPC matching criteria.

The unfolding-procedure uncertainty is determined by extending the lower and upper bounds of the \pTchjet{} spectrum by 5 \GeVc, changing the detector-level \DeltaR{} binning, changing the number of unfolding iterations, and scaling the prior distribution. The four categories of variations are carried out individually and combined into an unfolding uncertainty using their standard deviation.
The uncertainty from the model dependence in the unfolding is determined by repeating the analysis with response matrices based on different event generators including Herwig~7~\cite{Gieseke:2012ft} and JEWEL~\cite{Zapp:2013vla} with and without the inclusion of medium partons recoiling after interactions with the jet.

Potential bias introduced by the event-wide UE subtraction~\cite{Berta:2014eza,Berta:2019hnj} is quantified as the maximum difference between the nominal result and the results obtained by repeating the procedure with parameters $\Delta R^{\rm max}= 0.05$ (0.1), which lead to an under-subtraction, and $\Delta R^{\rm max}= 0.5$ (0.7), which lead to an over-subtraction of the background, for jets of $R=0.2$ (0.4).
Deviations between the generator-level and unfolded distributions due to residual combinatorial jets are determined with a closure test. PYTHIA~8 events are embedded into background events with no jets and analyzed identically to the measured data. Deviations between the unfolded and PYTHIA~8 generator-level spectra are assigned as the uncertainty.

The systematic uncertainties are added in quadrature. The total systematic uncertainty is in the range of 2\textendash{}61\% depending on \DeltaR{} and \pTchjet.
The large variation comes primarily from the background subtraction procedure at low \pTchjet{} (where background effects are largest). It is small at low values of \DeltaR, and smoothly grows in the tails of the distributions. 
See the supplemental materials~\cite{JA:sup} for details.