\section{Conclusion}
\label{sec:conclusion}

We have studied the reliability of recent segmentation models---in terms of \textbf{robustness} and \textbf{uncertainty estimation} under natural domain shifts. Overall, while no single model family is better in all scenarios, recent models are remarkably more robust to domain shifts than ResNet baselines. Yet, this does not translate into better \textit{calibration}---severely degraded out of domain. Thus, it is crucial to find methods to improve model calibration in \ood settings. 
%
To this end, we have explored state-of-the-art methods and found that Local Temperature Scaling \cite{ding2021local}, although originally devised for \id settings, is a promising 
technique.
% avenue for future work. 

Furthermore, we have explored \textit{misclassification} and \textit{\ood detection}---two other important tasks regarding uncertainty estimation. We have shown that recent and more robust models tend to perform better at misclassification under strong domain shifts, 
% however 
but yet
they underperform ResNet baselines \id. On the other hand, \ood detection under domain shifts is negatively correlated with the mIoU, which translates into a trade-off between robustness and uncertainty. 
% This might suggest it would be more effective to design light-weight, underperforming models which might be used in tandem with larger, more robust models. 
Finally, we find that adaptive temperature scaling techniques can help beyond calibration and improve \ood detection and misclassification in some settings. 

All in all,
% ---instead of focusing on \id performance only.
% , in place of merely focusing on \iid performance. 
although we appear to be \textit{on the right track} for what concerns robustness, our findings motivate the need to improve reliability of segmentation models in other dimensions, where results are not equally postive. In that regard, we identify several promising directions which we hope may encourage future research on this important topic.

% and identify several promising directions for future work.