% WACV 2025 Paper Template
% based on the WACV 2024 template, which is
% based on the CVPR 2023 template (https://media.icml.cc/Conferences/CVPR2023/cvpr2023-author_kit-v1_1-1.zip) with 2-track changes from the WACV 2023 template (https://github.com/wacv-pcs/WACV-2023-Author-Kit)
% based on the CVPR template provided by Ming-Ming Cheng (https://github.com/MCG-NKU/CVPR_Template)
% modified and extended by Stefan Roth (stefan.roth@NOSPAMtu-darmstadt.de)

\documentclass[10pt,twocolumn,letterpaper]{article}

%%%%%%%%% PAPER TYPE  - PLEASE UPDATE FOR FINAL VERSION
% \usepackage[review,algorithms]{wacv}      % To produce the REVIEW version for the algorithms track
% \usepackage[review,applications]{wacv}      % To produce the REVIEW version for the applications track
% \usepackage{wacv}              % To produce the CAMERA-READY version
\usepackage[pagenumbers]{wacv} % To force page numbers, e.g. for an arXiv version

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}

% My packages
\usepackage{multirow}
\usepackage{multicol}
\usepackage{dblfloatfix}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{enumitem}
\usepackage{lipsum} % for dummy text
\usepackage{wrapfig} % for wrapping text around figures
\usepackage[dvipsnames]{xcolor}
\usepackage{color, colortbl}
\usepackage{makecell}
\usepackage{pifont}
\usepackage{amsmath}
% \usepackage{natbib}
% \usepackage[accsupp]{axessibility} 

\newcommand{\TB}[1]{\textcolor{red}{\textbf{TB:} #1}}
\newcommand{\CB}[1]{\textcolor{blue}{\textbf{CB:} #1}}
\newcommand{\AlgoName}{CODIP }
\newcommand{\AlgoNameNoSpace}{CODIP}
\newcommand{\AlgoNameTop}{$\text{CODIP}_{\text{Top-}k}$ }
\newcommand{\AlgoNameTopNoSpace}{$\text{CODIP}_{\text{Top-}k}$}
\definecolor{gray}{RGB}{0, 0, 0}
\definecolor{golden}{RGB}{255, 215, 0}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

% It is strongly recommended to use hyperref, especially for the review version.
% hyperref with option pagebackref eases the reviewers' job.
% Please disable hyperref *only* if you encounter grave issues, e.g. with the
% file validation for the camera-ready version.
%
% If you comment hyperref and then uncomment it, you should delete
% ReviewTempalte.aux before re-running LaTeX.
% (Or just hit 'q' on the first LaTeX run, let it finish, and you
%  should be clear).
\usepackage[pagebackref,breaklinks,colorlinks]{hyperref}


% Support for easy cross-referencing
\usepackage[capitalize]{cleveref}
\crefname{section}{Sec.}{Secs.}
\Crefname{section}{Section}{Sections}
\Crefname{table}{Table}{Tables}
\crefname{table}{Tab.}{Tabs.}


%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\wacvPaperID{282} % *** Enter the WACV Paper ID here
\def\confName{WACV}
\def\confYear{2025}


\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Class-Conditioned Transformation for Enhanced Robust Image Classification}

\author{
    Tsachi Blau\textsuperscript{\dag}\thanks{\texttt{tsachiblau@campus.technion.ac.il}} \quad 
    Roy Ganz\textsuperscript{\dag} \quad 
    Chaim Baskin\textsuperscript{\ddag} \quad 
    Michael Elad\textsuperscript{\dag} \quad 
    Alex M. Bronstein\textsuperscript{\dag}
}


% \author{First Author\\
% Institution1\\
% Institution1 address\\
% {\tt\small firstauthor@i1.org}
% % For a paper whose authors are all at the same institution,
% % omit the following lines up until the closing ``}''.
% % Additional authors and addresses can be added with ``\and'',
% % just like the second author.
% % To save space, use either the email address or home page, not both
% \and
% Second Author\\
% Institution2\\
% First line of institution2 address\\
% {\tt\small secondauthor@i2.org}
% }
\maketitle

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\footnotetext[2]{Department of Computer Science Technion - Israel Institute of Technology}
\footnotetext[3]{School of Electrical and Computer Engineering - Ben-Gurion University of the Negev}

%%%%%%%%% ABSTRACT
\begin{abstract}
    Robust classification methods predominantly concentrate on algorithms that address a specific threat model, resulting in ineffective defenses against other threat models. Real-world applications are exposed to this vulnerability, as malicious attackers might exploit alternative threat models. In this work, we propose a novel test-time threat model agnostic algorithm that enhances Adversarial-Trained (AT) models. Our method operates through COnditional image transformation and DIstance-based Prediction (CODIP) and includes two main steps: First, we transform the input image into each dataset class, where the input image might be either clean or attacked. Next, we make a prediction based on the shortest transformed distance. The conditional transformation utilizes the perceptually aligned gradients property possessed by AT models and, as a result, eliminates the need for additional models or additional training. Moreover, it allows users to choose the desired balance between clean and robust accuracy without training. The proposed method achieves state-of-the-art results demonstrated through extensive experiments on various models, AT methods, datasets, and attack types. Notably, applying CODIP leads to substantial robust accuracy improvement of up to $+23\%$, $+20\%$, $+26\%$, and $+22\%$ on CIFAR10, CIFAR100, ImageNet and Flowers datasets, respectively.   
    \\For more details, visit the \href{https://github.com/tsachiblau/Class-Conditioned-Transformation-for-Enhanced-Robust-Image-Classification}{project page}.
\end{abstract}



\input{sections/introduction}
\input{sections/related_work}
\input{sections/our_method}
\input{sections/experiments}
\input{sections/ablations}
\input{sections/conclusion}
\input{sections/acknowledgments}


%%%%%%%%% REFERENCES
{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}

% \clearpage
% \input{appendix}

\end{document}
