%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Preamble version 08.09.22
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt,a4paper,oneside]{amsart}
% \usepackage[a4paper]{geometry} % Changing page shape
% \geometry{left=2.5cm,right=2.5cm,top=3cm,bottom=3cm}

% Comments

\newcounter{commentcounter}
\newcommand{\commentSH}[1]{\stepcounter{commentcounter}\textbf{Comment \arabic{commentcounter} (by Sam)}: {\textcolor{blue}{#1}}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Packages
\usepackage{amsmath} % Lots of maths functionality
\usepackage{amssymb} % Maths symbols
\usepackage{amsthm} % Maths environments: \begin{proof}, etc.
\usepackage{stmaryrd} % [[ brackets
%\usepackage[toc,page]{appendix} % Nice formatting for appendices
\usepackage[english]{babel} % Language and hyphenation.
\usepackage[font=small,justification=centering]{caption} % More flexibility for captioning figures
%\usepackage{csquotes} % Quotation environment
\usepackage[nodayofweek]{datetime}
%\usepackage{empheq} % Allows grouping of equations with empheq environment
\usepackage[shortlabels]{enumitem} % Change enumeration labelling with \begin{enumerate}[a)] etc.
%\usepackage{float} % For placing graphics, allows \begin{figure}[H] etc.
\usepackage[T1]{fontenc} % For font encoding, to allow accents, copy & paste, inequality signs, etc. to all work nicely.
%\usepackage{graphicx} % Add images to the document
\usepackage[utf8]{inputenc} % To be loaded after fontenc, also for encoding.
\usepackage{ifthen} % For Dani's \begin{com} environment and \numberedtheorem
\usepackage{mathabx} % Contains \pnest symbol and more. Clashes with accents for \ring
\usepackage{mathtools} % Uses amsmath, fixes quirks and adds functionality.
\usepackage[dvipsnames]{xcolor} % Allow links to have colour. Needs to be before hyperref and tikz-cd
\usepackage[pdftex,  colorlinks=true]{hyperref} % Makes references and citations into links
    \hypersetup{urlcolor=RoyalBlue, linkcolor=RoyalBlue,  citecolor=black}
%\usepackage{setspace} % Allows \onehalfspacing etc. for changing gaps between lines
%\onehalfspacing
\usepackage{tikz-cd} % Commutative diagrams
\usepackage{xfrac} % Nicer quotients 
\usepackage[capitalize]{cleveref} % use \Cref{} for instead of X~\ref{} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Subject class
\makeatletter
\@namedef{subjclassname@1991}{Mathematical subject classification 1991}
\@namedef{subjclassname@2000}{Mathematical subject classification 2000}
\@namedef{subjclassname@2010}{Mathematical subject classification 2010}
\@namedef{subjclassname@2020}{Mathematical subject classification 2020}
\makeatother


% Theorem Counters
\newtheorem{thm}{Theorem}[section]
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{corollary}[thm]{Corollary}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{conjecture}[thm]{Conjecture}
\newtheorem{claim}[thm]{Claim}
\newtheorem{addendum}[thm]{Addendum}
\newtheorem{assumption}[thm]{Assumption}
\newtheorem{question}[thm]{Question}



% "letter-numbered" theorems
\newtheorem{thmx}{Theorem}
\newtheorem{corx}[thmx]{Corollary}
\newtheorem{propx}[thmx]{Proposition}
\renewcommand{\thethmx}{\Alph{thmx}}
\renewcommand{\thecorx}{\Alph{corx}}


% Definition environment style 
\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\newtheorem{remark}[thm]{Remark}
\newtheorem{remarks}[thm]{Remarks}
\newtheorem{construction}[thm]{Construction}
\newtheorem{setup}[thm]{Setup}
\newtheorem{example}[thm]{Example}
\newtheorem{examples}[thm]{Examples}

\theoremstyle{plain}
\newtheorem*{ConjSinger}{The Singer Conjecture}


    \newtheoremstyle{TheoremNum}
        {\topsep}{\topsep} %%% space between body and thm
        {\itshape} %%% Thm body font
        {-0.25cm} %%% Indent amount (empty = no indent)
        {\bfseries} %%% Thm head font
        {.} %%% Punctuation after thm head
        { }  %%% Space after thm head
        {\thmname{#1}\thmnote{ \bfseries #3}}%%% Thm head spec
    \theoremstyle{TheoremNum}
    \newtheorem{duplicate}{}



\newcommand*{\claimproofname}{My proof}
\newenvironment{claimproof}[1][\claimproofname]{\begin{proof}[#1]\renewcommand*{\qedsymbol}{\(\blacksquare\)}}{\end{proof}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Large asterisks created by Ian Leary with some help from Boris Okun
\DeclareMathOperator*{\Aster}{\text{\LARGE{\textasteriskcentered}}}
\DeclareMathOperator{\aster}{\text{\LARGE{\textasteriskcentered}}}


% Sets
\DeclareMathOperator{\Aut}{\mathrm{Aut}}
\DeclareMathOperator{\Out}{\mathrm{Out}}
\DeclareMathOperator{\Inn}{\mathrm{Inn}}
\DeclareMathOperator{\Ker}{\mathrm{Ker}}
\DeclareMathOperator{\coker}{\mathrm{Coker}}
\DeclareMathOperator{\Coker}{\mathrm{Coker}}
\DeclareMathOperator{\Hom}{\mathrm{Hom}}
\DeclareMathOperator{\Ext}{\mathrm{Ext}}
\DeclareMathOperator{\Tor}{\mathrm{Tor}}
\DeclareMathOperator{\tr}{\mathrm{tr}}
\DeclareMathOperator{\im}{\mathrm{im}}
\DeclareMathOperator{\Fix}{\mathrm{Fix}}
\DeclareMathOperator{\orb}{\mathrm{Orb}}
\DeclareMathOperator{\End}{\mathrm{End}}
\DeclareMathOperator{\Irr}{\mathrm{Irr}}
\DeclareMathOperator{\Comm}{\mathrm{Comm}}
\DeclareMathOperator{\Isom}{\mathrm{Isom}}
\DeclareMathOperator{\Min}{\mathrm{Min}}
\DeclareMathOperator{\Core}{\mathrm{Core}}
\DeclareMathOperator{\bigset}{Big}
\DeclareMathOperator{\cay}{Cay}
\DeclareMathOperator{\diam}{diam}
\DeclareMathOperator{\hull}{hull}
\DeclareMathOperator{\link}{Lk}
\DeclareMathOperator{\map}{Map}
\DeclareMathOperator{\sym}{Sym}
\DeclareMathOperator{\lat}{\mathrm{Lat}}
\DeclareMathOperator{\dom}{\mathrm{dom}}

% mathcal
\newcommand{\cala}{{\mathcal{A}}}
\newcommand{\calb}{{\mathcal{B}}}
\newcommand{\calc}{{\mathcal{C}}}
\newcommand{\cald}{{\mathcal{D}}}
\newcommand{\cale}{{\mathcal{E}}}
\newcommand{\calf}{{\mathcal{F}}}
\newcommand{\calg}{{\mathcal{G}}}
\newcommand{\calh}{{\mathcal{H}}}
\newcommand{\cali}{{\mathcal{I}}}
\newcommand{\calj}{{\mathcal{J}}}
\newcommand{\calk}{{\mathcal{K}}}
\newcommand{\call}{{\mathcal{L}}}
\newcommand{\calm}{{\mathcal{M}}}
\newcommand{\caln}{{\mathcal{N}}}
\newcommand{\calo}{{\mathcal{O}}}
\newcommand{\calp}{{\mathcal{P}}}
\newcommand{\calq}{{\mathcal{Q}}}
\newcommand{\calr}{{\mathcal{R}}}
\newcommand{\cals}{{\mathcal{S}}}
\newcommand{\calt}{{\mathcal{T}}}
\newcommand{\calu}{{\mathcal{U}}}
\newcommand{\calv}{{\mathcal{V}}}
\newcommand{\calw}{{\mathcal{W}}}
\newcommand{\calx}{{\mathcal{X}}}
\newcommand{\caly}{{\mathcal{Y}}}
\newcommand{\calz}{{\mathcal{Z}}}

% mathfrak
\newcommand*{\frakg}{\mathfrak{G}}
\newcommand*{\fraks}{\mathfrak{S}}
\newcommand*{\frakt}{\mathfrak{T}}

% underline
\newcommand{\ulE}{\underline{E}}
\newcommand{\ulEG}{\underline{E}\Gamma}
\newcommand{\Efin}{E_{\mathcal{FIN}})}
\newcommand{\EfinG}{E_{\mathcal{FIN}}\Gamma}

% Categories
\newcommand{\grp}{\mathbf{Grp}}
\newcommand{\set}{\mathbf{Set}}
\newcommand{\gtop}{\mathbf{Top}_\Gamma}
\newcommand{\orbf}{\mathbf{Or}_\calf(\Gamma)}
\newcommand{\bfE}{\mathbf{E}}
\newcommand{\Top}{\mathbf{Top}}

% Spectra
\newcommand{\spectra}{\mathbf{Spectra}}
\newcommand{\ko}{\mathbf{ko}}
\newcommand{\KO}{\mathbf{KO}}

% Families
\newcommand{\TRV}{\mathcal{TRV}}
\newcommand{\FIN}{\mathcal{FIN}}
\newcommand{\VC}{\mathcal{VC}}
\newcommand{\ALL}{\mathcal{ALL}}

% Functors
\newcommand{\hocolim}{{\rm hocolim}}
\newcommand{\colim}{{\rm colim}}
\newcommand{\ind}{{\rm ind}}
\newcommand{\res}{{\rm res}}
\newcommand{\coind}{{\rm coind}}

% Groups
\newcommand{\GL}{\mathrm{GL}}
\newcommand{\PGL}{\mathrm{PGL}}
\newcommand{\PGammaL}{\mathrm{P\Gamma L}}
\newcommand{\SL}{\mathrm{SL}}
\newcommand{\PSL}{\mathrm{PSL}}
\newcommand{\GU}{\mathrm{GU}}
\newcommand{\PGU}{\mathrm{PGU}}
\newcommand{\UU}{\mathrm{U}}
\newcommand{\SU}{\mathrm{SU}}
\newcommand{\PSU}{\mathrm{PSU}}
\newcommand{\Sp}{\mathrm{Sp}}
\newcommand{\PSp}{\mathrm{PSp}}
\newcommand{\OO}{\mathrm{O}}
\newcommand{\SO}{\mathrm{SO}}
\newcommand{\PSO}{\mathrm{PSO}}
\newcommand{\PGO}{\mathrm{PGO}}
\newcommand{\AGL}{\mathrm{AGL}}
\newcommand{\ASL}{\mathrm{ASL}}
\newcommand{\He}{\mathrm{He}}

\newcommand{\PSLp}{\mathrm{PSL}_2(\ZZ[\frac{1}{p}])}
\newcommand{\SLp}{\mathrm{SL}_2(\ZZ[\frac{1}{p}])}
\newcommand{\SLm}{\mathrm{SL}_2(\ZZ[\frac{1}{m}])}
\newcommand{\GLp}{\mathrm{GL}_2(\ZZ[\frac{1}{p}])}

\newcommand{\LM}{\mathrm{LM}}
\newcommand{\HLM}{\mathrm{HLM}}
\newcommand{\CAT}{\mathrm{CAT}}

% HHG relations
\newcommand*{\lhalf}[1]{\overleftarrow{#1}}
\newcommand*{\rhalf}[1]{\overrightarrow{#1}}
\newcommand*{\sgen}[1]{\langle#1\rangle}
\newcommand*{\nest}{\sqsubseteq}
\newcommand*{\pnest}{\sqsubset}
\newcommand*{\conest}{\sqsupset}
\newcommand*{\pconest}{\sqsupsetneq}
\newcommand*{\trans}{\pitchfork}

%Misc
\DeclareMathOperator{\Ad}{\mathrm{Ad}}
\DeclareMathOperator{\id}{id}
\newcommand{\onto}{\twoheadrightarrow}
\def\iff{if and only if }

% Symmetric spaces
\newcommand{\EE}{\mathbb{E}}
\newcommand{\KH}{\mathbb{K}\mathbf{H}} % Hyperbolic space over K
\newcommand{\RH}{\mathbb{R}\mathbf{H}} % Real hyperbolic space
\newcommand{\CH}{\mathbb{C}\mathbf{H}} % Complex hyperbolic space
\newcommand{\HH}{\mathbb{H}\mathbf{H}} % Quaternion hyperbolic space
\newcommand{\OH}{\mathbb{O}\mathbf{H}^2} % Cayley hyperbolic space
\newcommand{\Ffour}{\mathrm{F}_4^{-20}} % The other rank one group

% Projective spaces
\newcommand{\KP}{\mathbb{K}\mathbf{P}} % Projective plane over K
\newcommand{\RP}{\mathbb{R}\mathbf{P}} % Real projective plane
\newcommand{\CP}{\mathbb{C}\mathbf{P}} % Complex projective plane
\newcommand{\OP}{\mathbb{O}\mathbf{P}^2} % Cayley projective plane


% Invariants
\newcommand{\Covol}{\mathrm{Covol}}
\newcommand{\Vol}{\mathrm{Vol}}
\newcommand{\rank}{\mathrm{rank}}
\newcommand{\gd}{\mathrm{gd}}
\newcommand{\cd}{\mathrm{cd}}
\newcommand{\vcd}{\mathrm{vcd}}
\newcommand{\hd}{\mathrm{hd}}
\newcommand{\vhd}{\mathrm{vhd}}
\newcommand{\betti}{b^{(2)}}
\DeclareMathOperator{\lcm}{\mathrm{lcm}}
\DeclareMathOperator{\Char}{\mathrm{Char}}

% Spaces
\newcommand{\flag}{{\rm Flag}}
\newcommand{\wtX}{\widetilde{X}}
\newcommand{\wtXj}{\widetilde{X_J}}
\newcommand{\ulG}{\underline{\Gamma}}

% Rings
\newcommand{\MM}{\mathbf{M}}
\newcommand{\repr}{\calr_\RR}
\newcommand{\repc}{\calr_\CC}
\newcommand{\reph}{\calr_\HH}
%\newcommand{\gg}{\mathfrak{g}}
%\newcommand{\hh}{\mathfrak{h}}
%\newcommand{\gl}{\mathfrak{gl}}
%\renewcommand{\sl}{\mathfrak{sl}}
%\newcommand{\so}{\mathfrak{so}}
%\newcommand{\nov}[3]{{\mathrm{Nov}({#1 #2, #3}})}
\newcommand{\nov}[3]{{\widehat{#1 #2}^{#3}}}
\newcommand{\cgr}[2]{#1 \llbracket #2 \rrbracket} %completed group ring
\def\Z{\mathbb{Z}}


% Fields
\newcommand{\NN}{\mathbb{N}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\QQ}{\mathbb{Q}}
\newcommand{\FF}{\mathbb{F}}
\newcommand{\KK}{\mathbb{K}}

%ODEs and PDEs
\newcommand{\ode}{\mathrm{d}}
\newcommand*{\pde}[3][]{\ensuremath{\frac{\partial^{#1} #2}{\partial #3}}}


%tikz
\usepackage{tikz}
\usetikzlibrary{arrows,quotes}
\tikzstyle{blackNode}=[fill=black, draw=black, shape=circle]


\newcommand{\dn}{\mathcal{D}N}
\newcommand{\ione}{(i_1)_{*}}
\newcommand{\itwo}{(i_2)_{*}}


\title[Exotic subgroups of hyperbolic groups]{A note on arithmetic lattices in Isom$(\mathbb{H}^n)$ and exotic subgroups of hyperbolic groups}
\author{Monika Kudlinska}
\address{Mathematical Institute, Andrew Wiles Building, Observatory Quarter, University of Oxford, Oxford OX2 6GG, UK}
\email{monika.kudlinska@maths.ox.ac.uk}
\date{\today}

\subjclass[2020]{Primary 20F67; Secondary 20E07, 20J05, 57M07}


\begin{document}

\maketitle

\begin{abstract}
    We construct the first known infinite family of quasi-isometry classes of subgroups of hyperbolic groups which are not hyperbolic and are of type $\mathrm{FP}(\mathbb{Q})$. We give a simple criterion for producing many non-hyperbolic subgroups of hyperbolic groups with strong finiteness properties. We also observe that local hyperbolicity and algebraic fibring are mutually exclusive in higher dimensions.
\end{abstract}

\section{Introduction}

Let $R$ be a ring. A group $G$ is said to be of type $\mathrm{FP}_n(R)$ if there exists a projective resolution
\[\cdots \to P_{n+1} \to P_n \to \cdots \to P_0 \to M \to 0,\]
where each $P_i$ is a left $RG$-module which is finitely generated whenever $i \leq n,$ and $M$ is the trivial $RG$-module. We say that $G$ is of type $\mathrm{FP}_{\infty}(R)$, if it is of type $\mathrm{FP}_n(R)$ for all $n \geq 1$, and that it is of type $\mathrm{FP}(R)$ if there exists a finite projective resolution of $M$ by finitely generated $RG$-modules. The \emph{cohomological dimension} $\mathrm{cd}_R(G)$ of $G$ over $R$ is the minimal $d$ such that the trivial $RG$-module $R$ has a projective resolution of length $d$ by $RG$-modules. We write $\mathrm{cd}(G)$ to denote the cohomological dimension of $G$ over $\mathbb{Z}$.%A group $G$ is said to be of type $F_n$ if there exists a $K(G,1)$ with a finite $n$-skeleton, and it is said to be of type $F$ if it admits a finite $K(G,1)$.

The existence of the Rips complex shows that every torsion-free Gromov hyperbolic group is of type $\mathrm{F}$ and hence of type $\mathrm{\mathrm{FP}}(R)$, for any ring $R$ \cite[p.468]{BridsonHaefliger1999}. This gives a useful necessary criterion for hyperbolicity and, moreover, one which does not pass to subgroups.

In this vein, Rips constructed the first examples of finitely generated subgroups of hyperbolic groups which are not finitely presented \cite{Rips1982}. Then Brady produced a subgroup of a hyperbolic group which is finitely presented but not of type $\mathrm{FP}_3(\mathbb{Z})$ \cite{Brady1999}. The existence of subgroups of hyperbolic groups with higher finiteness properties was observed by \cite{IsenrichMartelliPy2021} and \cite{Fisher2021}. Most recently, Isenrich--Py, using methods from complex geometry, produced non-hyperbolic subgroups of hyperbolic groups of type $\mathrm{F}_n$ but not $\mathrm{F}_{n+1},$ for every $n\geq 1$ \cite{IsenrichPy2022}. 

A natural question that follows is whether one can obtain subgroups of hyperbolic groups which are not hyperbolic but are of type $\mathrm{FP}(R)$.  Italiano--Martelli--Migliorini \cite{ItalianoMartelliMigliorini2023} recently obtained the first such known example, which is moreover of type $\mathrm{F}$. To do so, they constructed a topological fibring of a finite-volume hyperbolic 5-manifold $M$; the resulting fibre is a finite-volume 4-manifold $N$ such that the outer automorphism group $\mathrm{Out}\,\pi_1(N)$ is infinite. They argue further that one can fill the cusps in $M$ to obtain a negatively curved pseudo-manifold $M'$ which still fibres, and such that the new fibre $N'$ is aspherical and has $\mathrm{Out}\, \pi_1(N')$ infinite. If $\pi_1(N')$ were to be Gromov hyperbolic, Paulin's theorem \cite{Paulin1991} would imply that $\pi_1(N')$ splits over an infinite cyclic subgroup. However, a simple Mayer-Vietoris argument shows that $\pi_1(N')$ cannot split over $\Z$.

Our method for producing exotic examples of subgroups of hyperbolic groups which are themselves not hyperbolic is also based on the study of kernels of maps to $\Z$.

\begin{thm}\label{main2}
    Let $G$ be a torsion-free hyperbolic virtually special group with $\mathrm{cd}_{\mathbb{Q}}(G) \geq 4$. Suppose that the $L^2$-Betti numbers of $G$ satisfy $b_{i}^{(2)}(G) = 0$ for all $i \leq n.$ Then $G$ contains a non-hyperbolic subgroup $N \leq G$ of type $\mathrm{FP}_n(\mathbb{Q})$ and $\mathrm{cd}_{\mathbb{Q}}(N) \in \{\mathrm{cd}_{\mathbb{Q}}(G) -1, \mathrm{cd}_{\mathbb{Q}}(G) \}$. Moreover, if $\mathrm{cd}_{\mathbb{Q}}(G) \leq n$ then $\mathrm{cd}_{\mathbb{Q}}(N) =  \mathrm{cd}_{\mathbb{Q}}(G) -1$.
\end{thm}
The proof of Theorem~\ref{main2} crucially uses the main result of Fisher in \cite{Fisher2021}. We note that it was already observed by Fisher \cite{Fisher2021} and Isenrich--Martelli--Py \cite{IsenrichMartelliPy2021} that such an approach can be used to construct subgroups of hyperbolic groups of type $\mathrm{FP}_n(\mathbb{Q})$ but not $\mathrm{FP}_{n+1}(\mathbb{Q})$ 

\begin{thm}\label{examples}
    For every integer $n\geq 2$, there exists a non-hyperbolic subgroup $N$ of a torsion-free hyperbolic group, such that $N$ is of type $\mathrm{FP}(\mathbb{Q})$ and $\mathrm{cd}(N) = 2n$. 
\end{thm}

Let $\mathcal{F}$ denote the family of discrete countable groups with finite cohomological dimension over $\mathbb{Z}$. By the work of Sauer \cite{Sauer2006}, cohomological dimension over $\mathbb{Z}$ is a quasi-isometry invariant amongst groups in $\mathcal{F}$. Hence we get the following corollary: 

\begin{corollary}\label{corollary}
    There exists infinitely many quasi-isometry classes of finitely generated subgroups of hyperbolic groups which are of type $\mathrm{FP}(\mathbb{Q})$ and which are not hyperbolic. 
\end{corollary}

Recall that a group $G$ is said to be \emph{locally hyperbolic} if every finitely generated subgroup of $G$ is hyperbolic. As a consequence of our method, we show that local hyperbolicity and algebraic fibring are mutually exclusive phenomena in higher dimensional groups: 

\begin{corollary}
    Let $G$ be a finitely generated, locally hyperbolic, torsion-free group. Suppose that $G$ fibres algebraically. Then 
    \[G \simeq (F_n \ast \Sigma_1 \ast \ldots \ast \Sigma_k) \rtimes \mathbb{Z},\]
    where $F_n$ is a free group of rank $n$, and each $\Sigma_i$ is a closed surface group. In particular, $\mathrm{cd}_{\mathbb{Q}}(G) \leq 3$.
    
    Furthermore, if $\mathrm{cd}_{\mathbb{Q}}(G) = 3$ then $G$ contains a closed surface subgroup.
\end{corollary}

\subsection*{Acknowledgements}

The author would like to thank her supervisors Martin Bridson and Dawid Kielak for their invaluable support and guidance; moreover, Martin for pointing out the examples of arithmetic lattices of simplest type. Finally, thanks go to Marco Linton for pointing out a more general version of Theorem~\ref{main}.

This work has received funding from an Engineering and Physical Sciences Research Council studentship (Project Reference 2422910). 

\section{Main results}

\begin{lemma}\label{one-ended} Let $H$ be a one-ended torsion-free hyperbolic group. If $H$ is not the fundamental group of a surface then $H \rtimes \mathbb{Z}$ contains a subgroup isomorphic to $\mathbb{Z}^2$. 
\end{lemma}

\begin{proof}

    Let $G = H \rtimes_{\phi} \langle t \rangle$ be one-ended, torsion-free hyperbolic. If $H$ does not split over $\mathbb{Z}$, then by \cite{Paulin1991} the outer automorphism group $\mathrm{Out}(H)$ of $H$ is finite. In particular, there exists $m \geq 1$ such that $\phi^m$ is an inner automorphism of $H$. Hence there exists some $x\in G$ such that $\langle H, xt^m\rangle \simeq H  \times \mathbb{Z}$. 
    
   Suppose now that $H$ splits over $\mathbb{Z}$. Since $H$ is not a surface group, it admits a non-trivial JSJ decomposition \cite{Sela1997}. The JSJ splitting is canonical, and thus $\phi$ permutes the conjugacy classes of edge stabilisers. Hence, for every edge of the splitting, there exists some $x \in G$ and $m \geq 1$ such that the generator of the edge stabiliser commutes with $t^mx$.
\end{proof}

\begin{thm}\label{main} Let $G$ be a group with no $\mathbb{Z}^2$-subgroups. Suppose that $G$ fits into the short exact sequence 
\[1 \to H \to G \to Q \to 1,\]
where $Q$ is infinite. If $H$ is torsion-free hyperbolic then it is isomorphic to a free product of finitely many hyperbolic surface groups of finite type.
\end{thm}

\begin{proof}
 By \cite{Mosher1996}, $Q$ is hyperbolic and thus contains an element of infinite order. Let $\gamma$ denote the lift of such an element to $G$. Then $G$ contains a subgroup $\langle H , \gamma \rangle \simeq H \rtimes \Z$. If $H$ is one-ended then the result follows by Lemma~\ref{one-ended}. If $H$ is two-ended then it is isomorphic to the infinite cyclic group, and $G \simeq \Z \rtimes \Z$ is virtually $\Z^2$ and thus it is not hyperbolic. 

Suppose that $H$ is infinitely-ended. Let $H = H_1 \ast \ldots \ast H_n \ast F_k$ be the Grushko decomposition of $H$. Fix a lift $t\in G$ of a generator of the infinite cyclic group. Let $\phi \in \mathrm{Aut}(H)$ be the automorphism of $H$ induced by the conjugation action of $t$ on $H$ in $G$. Then $\phi$ permutes the conjugacy classes of the subgroups $H_i$. Hence for all $i$, there exists $x_i \in G$ such that \[\langle H_i, t^mx_i \rangle \simeq H_i \rtimes_{\iota_{x_i} \phi^m} \mathbb{Z},\] 
where $\iota_{x_i}$ denotes the inner automorphism of $G$ with respect to $x_i$. Note that each $H_i$ is one-ended, torsion-free hyperbolic. If there exists some $H_i$ which is not a surface group, then by Lemma~\ref{one-ended} $G$ is not hyperbolic. The result follows.
\end{proof}

We note that the special case of Theore~\ref{main} when $Q \simeq \Z$ was already observed by Peter Brinkmann in his thesis \cite{BrinkmannThesis2000}. The author would like to thank Daniel Groves for point this out. 

\begin{proof}[Proof of Theorem~\ref{main2}]
    If $G$ is torsion-free hyperbolic, then $G$ is of type $\mathrm{FP}_{\infty}(\mathbb{Q})$. Hence by Fisher \cite{Fisher2021}, the hypothesis on the vanishing of the $L^2$-Betti numbers of $G$ implies that there exists a finite index subgroup $G' \leq G$ such that $G'$ fibres algebraically with kernel $N$ of type $\mathrm{FP}_k(\mathbb{Q})$ for $k \leq n$. Furthermore, the cohomological dimension of $N$ satisfies
  \begin{equation}\label{eq:1}\begin{split} \mathrm{cd}_{\mathbb{Q}}(N) &\geq \mathrm{cd}_{\mathbb{Q}}(G') - 1  \\
    &= \mathrm{cd}_{\mathbb{Q}}(G) - 1 \geq 3. \end{split}\end{equation} 
Hence, it follows by Theorem~\ref{main} that $N$ is not hyperbolic. 

If $\mathrm{cd}_{\mathbb{Q}}(G) \leq n$ then $\mathrm{cd}_{\mathbb{Q}}(N) \leq n$ and since $N$ is of type $FP_n(\mathbb{Q})$, we conclude that $N$ is of type $FP(\mathbb{Q})$. Thus by a result of Feldman \cite{Feldman1971} the first inequality in \eqref{eq:1} is an equality.  \end{proof}

\section{Constructing exotic examples}

Dodziuk shows that it is possible to obtain information about the $L^2$-cohomology of a manifold $M$ from studying the $L^2$-harmonic forms on $M$ \cite{Dodziuk1977}. His explicit calculation of the $L^2$-harmonic forms for hyperbolic manifolds yields the following:

\begin{thm}[\cite{Dodziuk1979}]
Let $n \geq 1$ be odd. If $G$ is the fundamental group of a closed oriented hyperbolic $n$-manifold, then for all $i \geq 0$, 
\[b_i^{(2)}(G) = 0.\]
\end{thm}

Hence, any odd-dimensional closed hyperbolic $n$-manifold with $n \geq 4$, whose fundamental group is virtually special, will contain a subgroup as in Theorem~\ref{examples}. Such examples can be obtained from the work of Bergeron--Haglund--Wise, who prove that in every dimension $n$ there exist cocompact arithmetic lattices in $SO(n,1)$ which are virtually special \cite{BergeronHaglundWise2011}. After passing to a subgroup of finite index, we may assume that the lattice $G$ is torsion-free and special. Note that in this case it is also possible to see that the kernel $K$ of an algebraic fibration is non-hyperbolic if it is of type $FP_{n-1}(\mathbb{Q})$, since by \cite[Theorem~1.19]{Hillman2002} it is an $(n-1)$-dimensional Poincar\'{e} Duality group  (over $\mathbb{Q}$), and thus a Mayer--Vietoris argument shows that it cannot split over $\Z$. Then, one argues as in the proof of Lemma~\ref{one-ended} to conclude that $K$ is not Gromov hyperbolic.

Finally, we note that it would be interesting to construct such examples which do not arise from the world of manifolds. One potential avenue to do so is through the work of Arenas \cite{Arenas2022}, whose cubical Rips construction is a new tool for constructing higher dimensional Gromov hyperbolic groups which fibre algebraically.

\bibliographystyle{alpha}
\bibliography{main.bib}

\end{document}
