\documentclass[twocolumn,10pt]{IEEEtran}
%
\usepackage[mathscr]{eucal}
\usepackage{ifpdf}
\usepackage{cite}
\usepackage{graphicx}
\usepackage[cmex10]{amsmath}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{placeins}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{algorithmic}
\usepackage{units}
\usepackage{setspace}
\usepackage{algorithm}
\usepackage{array}
\usepackage{booktabs}
\usepackage{amsthm}
\usepackage{multirow}
\usepackage{enumerate}
\usepackage{color}
\usepackage{mathtools}
\usepackage{caption}
\usepackage[labelformat=simple]{subcaption}
\usepackage{tabularx}
\usepackage{tcolorbox}
\usepackage{supertabular}
\usepackage{tikz}
\usepackage{bm}
\usepackage{xcolor,colortbl}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xfrac}
%\usepackage{dblfloatfix}
%\usepackage{float}
\usepackage{stfloats}
\usetikzlibrary{arrows.meta, positioning,patterns}

\renewcommand\thesubfigure{(\alph{subfigure})}

\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

\newcounter{assume}
\def\theassume{A\arabic{assume}}
\setcounter{assume}{0}
%\newcommand{\inp}[1]{\textcolor{blue}{#1}}
\newcommand{\resl}[1]{}
\newcommand{\tosl}[1]{}
\newcommand{\cosl}[1]{}
\newcommand{\insl}[1]{#1}

\definecolor{mygreen}{RGB}{143, 188, 187}
\definecolor{green1}{RGB}{147, 196, 125}
\definecolor{red1}{RGB}{213,88,88}

\begin{document}
\title{Domain Generalization in Machine
Learning Models for Wireless Communications: Concepts, State-of-the-Art, and Open Issues}
\author{
\IEEEauthorblockN{Mohamed Akrout, Amal Feriani, Faouzi Bellili, \textit{Member, IEEE},\\ Amine Mezghani, \textit{Member, IEEE}, and Ekram Hossain, \textit{Fellow, IEEE}}
}
%
\maketitle
%
%----------------------------------------------Abstract---------------------------------------------
\begin{abstract}
Data-driven machine learning (ML) is promoted as one potential technology to be used in next-generations wireless systems. This led to a large body of research work that applies ML techniques to solve problems in different layers of the wireless transmission link. However, most of these applications rely on supervised learning which assumes that the source (training) and target (test) data are independent and identically distributed (i.i.d). This assumption is often violated in the real world due to domain or distribution shifts between the source and the target data. Thus, it is important to ensure that these algorithms generalize to out-of-distribution (OOD) data. In this context, domain generalization (DG) tackles the OOD-related issues by learning models on different and distinct source domains/datasets with generalization capabilities to unseen new domains without additional finetuning. Motivated by the importance of DG requirements for wireless applications, we present a comprehensive overview of the recent developments in DG and the different sources of domain shift. We also summarize the existing DG methods and review their applications in selected wireless communication problems, and conclude with insights and open questions.

\let\thefootnote\relax\footnotetext{The authors are with the Department of Electrical 
and Computer Engineering, University of Manitoba, Winnipeg, MB, Canada (e-mails: 
\{akroutm,feriania\}@myumanitoba.ca, \{faouzi.bellili, amine.mezghani, ekram.hossain\}@umanitoba.ca). The work was supported by a Discovery Grant from the Natural Sciences and Engineering Research Council of Canada (NSERC).}
\end{abstract}
%
{\em Keywords}: ML-aided wireless networks, Out-of-distribution generalization, Domain generalization

%----------------------------------------------Chapters-----------------------------------------

\input{chapters/introduction}
\input{chapters/background}
\input{chapters/data_manipulation.tex}
\input{chapters/representation_learning.tex}
\input{chapters/learning.tex}
\input{chapters/applications.tex}
\input{chapters/future_directions.tex}
\input{chapters/conclusion.tex}

%----------------------------------------------Bibliography-------------------------------------------
%\clearpage
\bibliographystyle{ieeetr}
\bibliography{refs}
%---------------------------------------------------------------------------------------------------

\end{document}
