\documentclass[a4paper,12pt,openright]{book}

\usepackage{amsmath,amsthm,amssymb,bm,braket}
\usepackage[dvips,dvipdfmx]{graphicx} %\usepackage[dvips]{graphicx}
\usepackage{cite,caption}
\usepackage{wrapfig}
\usepackage{setspace}
\usepackage{fancybox,fancyhdr}
\usepackage{geometry}
\geometry{left=18truemm, right=18truemm, top=30truemm, bottom=24truemm}

%\pagestyle{plain}
%\pagestyle{headings}
\pagestyle{fancy}
  \fancyhead{} %reset headings
  \fancyhead[LE,RO]{\leftmark}
  \renewcommand{\chaptermark}[1]{\markboth{Chapter~\thechapter\; \; #1}{}}
%  \fancyhead[RO]{\rightmark}
%  \renewcommand{\sectionmark}[1]{\markright{\thesection\; #1}{}}
  \cfoot{\thepage}

%------------------------------------------------------------------------

\begin{document}

\renewcommand{\figurename}{Figure}
%\renewcommand{\thefigure}{\Roman{figure}}
\renewcommand{\tablename}{Table}
\renewcommand{\thetable}{\arabic{table}}

\newcommand{\bi}[1]{\ensuremath{ \boldsymbol{#1} }}
\newcommand{\oprt}[1]{\ensuremath{ \hat{\mathcal{#1}} }}
\newcommand{\abs}[1]{\ensuremath{ \left| #1 \right| }}
\newcommand{\cgc}[2]{\ensuremath{ \mathcal{C}^{#1}_{#2} }}
\newcommand{\cmd}[1]{\texttt{\symbol{"5C}#1}}
%\newcommand{\unit}[1]{\ensuremath{ \mathrm{#1} }}
%\newcommand{\mybraket}[1]{\ensuremath{ \left< #1 \right> }}

%\newcommand{\Schr}{Schr\"odinger }
\def \Schr{Schr\"odinger }
%\newcommand{\CG}{Clebsch-Gordan }
\def \CG{Clebsch-Gordan }

\def \beq{\begin{equation}}
\def \eeq{\end{equation}}
\def \beqa{\begin{eqnarray}}
\def \eeqa{\end{eqnarray}}

\def \twop{2{\it p}}
\def \bis{\bi{s}}
\def \bir{\bi{r}}
\def \ubir{\bar{\bi{r}}}
\def \bip{\bi{p}}
\def \ubip{\bar{\bi{r}}}


\renewcommand{\include}[1]{} %annul ``include'' command.
\renewcommand{\documentclass}[2][]{} %annul ``\documentclass'' command.

%\title{}
%\author{}
%\date{}
%\maketitle
%----------------------------------------------------------------
\begingroup \thispagestyle{empty}
\begin{center}
{\Huge Doctoral Thesis} \\
\vspace{20truemm}
\begin{spacing}{3.0} {\Huge \bf Diproton Correlation and Two-Proton Emission from Proton-Rich Nuclei} \end{spacing} 
\vspace{60truemm}
{\Large Tomohiro Oishi} \\
\vspace{20truemm}
{\Large A Dissertation Submitted for the Degree of \\ Doctor of 
Science at Tohoku University} \\
\vspace{20truemm}
{\Large March, 2014}
\end{center}
\endgroup
%----------------------------------------------------------------

\newpage
{\bf ABSTRACT}

This is the open-print version of my dissertation thesis in 2014 \cite{2014Oishi}.
In this open-print version, several Figures were inevitably eliminated, because of the copyright and/or file-size problems.
Those figures are indicated with the message ``(Figure is hidden in open-print version.)'',
whereas original files could be available from T. OISHI when requested.
Several minor corrections have been also done, but without changing the scientific discussions, results, and conclusions from the original version \cite{2014Oishi}.


In this thesis, I investigate the two-proton emission in proton-rich nuclei.
The aim of study is to discuss the relation between the observables of this emission and the diproton correlation with quantum entanglement, which is one characteristic phenomenon due to the nuclear pairing interaction.

The pairing correlation between two nucleons plays 
an essential role in nuclear structure. 
Especially, two nucleons near the Fermi surface in nuclei have been 
predicted to make the ``diproton'' and ``dineutron'' correlations. 
These correlations mean 
the spatial localization of two nucleons, associated with 
the dominance of the spin-singlet configuration with entanglement. 
%This is a characteristic prediction of the modern theory of nuclear structures, and to investigate this property is expected to enhance the predictive powers of that theory. 
Especially, the dineutron correlation has been actively studied 
recently with a strong connection to the exotic features of neutron-rich nuclei. 
These nuclei far from the beta-stability line have attracted 
novel interests in nuclear physics, and their basic information 
have been extensively investigated for the past few decades. 
On the other hand, the diproton correlation in proton-rich nuclei has been less studied. 

In the former half of this thesis, 
I discuss the universality of the diproton and dineutron correlations, 
with a theoretical study of the $^{17,18}$Ne and $^{18}$O nuclei. 
This study is based on a three-body model, which provides a 
semi-microscopic description for the two nucleons inside nuclei. 
I demonstrate that a diproton correlation exists in the ground state of $^{17,18}$Ne, similarly to a dineutron
correlation in $^{18}$O. 
It is also shown that the Coulomb repulsive force between 
the two protons does not affect significantly this correlation. 
Consequently, the nuclear pairing interaction plays an important 
role to occur the dinucleon correlations inside nuclei. 

The later half of this thesis focuses on the relation 
between the diproton correlation and the two-proton emission. 
Even with theoretical predictions, for the dinucleon correlations, 
there have been no direct experimental evidences, 
because of a difficulty to access the intrinsic structures of nuclei. 
Recently, on the other hand, 
``two-proton emission'' has been focused as a direct 
probe into the diproton correlation with entanglement.
Namely, via this process, a pair of protons is emitted directly from the parent nuclei.
The emitted two protons are expected to provide information about 
the nuclear pairing interaction and the diproton correlation. 
In order to extract such information, one has to consider both the quantum meta-stability and the many-body 
properties in an unified framework. 
For this purpose, I develop a time-dependent three-body model. 
By applying this model to the $^6$Be nucleus, which is the 
lightest two-proton emitter, I investigate several novel 
properties about the role of pairing correlations in the meta-stable state. 
It has been shown that, by considering the Cooper pairing in the initial state of the two protons,
(i) the experimental decay width of $^6$Be is well reproduced, and 
(ii) the two protons are emitted mainly 
as a diproton-like cluster with the spin-singlet configuration, in the early stage of the emission. 
These results strongly suggest the diproton correlation during the emission process.
Namely, the two-proton emission can be an efficient tool to access the diproton correlation with a strong entanglement.

Despite these important theoretical findings, in order to extract the information on the diproton correlation 
from the experimental data, 
there still remain several points to be improved. 
The most important one is to take the final-state interactions into account sufficiently. 
For the two-proton emission from the $^6$Be nucleus, 
my result for the early stage of the emission predicts 
a dominant diproton-like configuration. 
On the other hand, there is only little signal of 
such a configuration in the experimental data of 
the energy-angular correlation pattern, 
which correspond to the late stage of the emission. 
This discrepancy is due to a strong disruption of the diproton 
correlation in the late stage, caused by the final-state 
interactions among all the particles. 
In order to establish the agreement between 
the calculated result and the experimental data, 
I need to expand the model-space so that a longer time-evolution can be carried out. 


As a summary of this thesis, the first step 
to investigate the diproton correlation by means of the two-proton 
emission has been established. 
The time-dependent method based on the three-body model 
has provided an intuitive way to 
describe the quantum dynamics of the entangled fermionic pair, with an advantage to understand the role of pairing correlations. 
I expect that the improved time-dependent method will be 
a powerful tool for two-proton emissions, and also for other 
quantum meta-stable processes. 
After further investigations, 
the obtained knowledge of the pairing correlations and the 
meta-stable processes will be an important result 
not only for nuclear physics 
but also for atomic, molecular, condensed matter and 
quantum informative physics. 



\tableofcontents

\input{ch1.tex}%DONE
\input{ch2.tex}%DONE
\input{ch3.tex}%DONE
\input{ch4.tex}%Skipped
\input{ch5.tex}%DONE
\input{ch6.tex}%DONE
\input{ch71.tex}%Skipped
\input{ch72.tex}%DONE
\input{ch9.tex}%DONE
\input{ack.tex}%DONE

\appendix
\pagestyle{fancy}
  \fancyhead{} %reset headings
  \fancyhead[LE,RO]{\leftmark}
  \renewcommand{\chaptermark}[1]{\markboth{Appendix~\thechapter\; \; #1}{}}
  \cfoot{\thepage}
\input{apA.tex}%DONE
\input{apM.tex}%DONE
\input{apP.tex}%DONE
\input{apS.tex}%DONE
\input{apT.tex}%DONE
%\input{bibli.tex}
\input{root.bbl}


\end{document}

