\section*{Appendix}

\section*{Outline}
In this Appendix, we elaborate on the following aspects that are not presented in the submission due to the space limit: 
\begin{itemize}[leftmargin=*]

    \item \textbf{Section \ref{sec:dataset-details} -- Details of the two benchmarks} tested in the experiments: the Visual Domain Decathlon (VDD)~\cite{vdd} benchmark (Section~\ref{sec:vdd}) and the 5-Datasets~\cite{adversarial-continual-learning} benchmark (Section~\ref{sec:5datasets}).

    \item \textbf{Section \ref{sec:base-vit-model} -- The base model and its training details}: the Vision Transformer (ViT) model specification (ViT-B/8) and how it is initially training on the ImageNet in our experiments. 

    \item \textbf{Section \ref{sec:training-details} -- Experimental settings and training hyperparameters in our implementation} on the VDD benchmark and  the 5-dataset benchmark.

      
    \item \textbf{Section \ref{sec:other-architectures} -- More examples of learned CHEEM} by our proposed hierarchical exploration-exploitation (HEE) sampling scheme and by the vanilla pure exploration (PE) sampling scheme.
    
  
    
    \item \textbf{Section \ref{sec:ablations} - Ablation Studies}: 
    \begin{itemize}
        \item \textbf{Section \ref{sec:CHEEM-components} -- How about other components in ViTs as CHEEM?}: We compare with the Query/Key/Value layer and the FFN layer, and verify the effectiveness of the proposed identification in the main paper.
        \item \textbf{Section \ref{sec:hybrid-adapter} -- How is the {\tt Adapt} operation implemented?}: We elaborate two implementation methods of the {\tt Adapt} operation and compare their performance.
        \item \textbf{Section \ref{sec:task_orders} - Effects of task orders.}
    \end{itemize}
    
    
    \item \textbf{Section \ref{sec:baseline}} -  Details of Modifying Baseline Methods on the VDD Benchmark:
    \begin{itemize}
        \item \textbf{Section \ref{sec:task-inc-l2p-sprompt} -- Modifying S-Prompts and Learn to Prompt (L2P)} to leverage task ID in inference.
        
        \item  \textbf{Section \ref{sec:modification-t2t} -- Modifying SupSup, EFT and LL} to work with ViTs.   
    \end{itemize}
    
       
    
    
     
\end{itemize}

\newpage