\documentclass[10pt,conference,hidelinks]{IEEEtran}

\usepackage{url}
\usepackage{subfig}
\usepackage{graphicx}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}
%\usepackage{subcaption}
\usepackage{listings}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{comment}
\usepackage{listings,newtxtt}
\lstset{basicstyle=\ttfamily, keywordstyle=\bfseries}

\usepackage{tikz}
\usepackage{xcolor}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,fill,inner sep=1pt] (char) {\textcolor{white}{#1}};}}


\usepackage{pbox}
\usepackage{comment}
\usepackage{csvsimple}
\usepackage{fancyhdr}
\usepackage{mathtools}
\usepackage{caption}
\usepackage{amsmath}
\usepackage{makecell}
\usepackage{tikz}
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}
%\usepackage[top=1in, bottom=1in, left=0.75in, right=0.75in]{geometry}
\usepackage{siunitx}
\sisetup{
    table-figures-decimal = 3,
    table-number-alignment=center-decimal-marker
}

\newcommand\Ayaz[1]{\textcolor{black}{#1}}
\newcommand\note[1]{\textcolor{blue}{#1}}

\begin{document}

% Use these macros to cite our tools, etc.
% This ensures consistency.
\newcommand{\gem}{gem{5}}

\title{A Cycle-level Unified DRAM Cache Controller Model for 3DXPoint Memory Systems in \gem{}}

% I don't like the title, we should find a better one
%\text{NOTE: ISPASS 2022 Submission, Currently Under Review  -- \\
%This Is a Confidential Draft -- Do NOT Distribute.}
\author{
%\normalsize{NOTE: ISPASS 2022 Submission, Currently Under Review  -- This Is a Confidential Draft -- Do NOT Distribute.}\\
\\\IEEEauthorblockN{Maryam Babaie, Ayaz Akram, Jason Lowe-Power}
\IEEEauthorblockA{Department of Computer Science,
University of California, Davis\\
Email: \{mbabaie, yazakram, jlowepower\}@ucdavis.edu}}

\maketitle

\begin{abstract}

    To accommodate the growing memory footprints of today's applications, CPU vendors have employed large DRAM caches,
    backed by large non-volatile memories like Intel Optane (e.g., Intel's Cascade Lake).
    The existing computer architecture simulators do not provide support to
    model and evaluate systems which use DRAM devices as a cache to the non-volatile main memory.
    In this work, we present a cycle-level DRAM cache model which is integrated with \gem{}.
    % a general DRAM cache protocol for the aforementioned systems.
    % We extend gem5 (widely used full-system simulator) with a unified DRAM cache and main memory controller
    % (\textit{UDCC}) to implement the DRAM cache protocol. \textit{UDCC} controls two different memory devices at the same time,
    % in which one of them caches data for the other one and data is kept consistent between the two.
    This model leverages the flexibility of \gem{}'s memory devices models and full system support to enable exploration of many different DRAM cache designs.
    We demonstrate the usefulness of this new tool by exploring the design space of a DRAM cache controller through several case studies including the impact of
    scheduling policies, required buffering, combining different memory technologies (e.g., HBM, DDR3/4/5, 3DXPoint, High latency)
    as the cache and main memory, and the effect of wear-leveling when DRAM cache is backed by NVM main memory.
    We also perform experiments with real workloads in full-system simulations to validate the proposed model
    and show the sensitivity of these workloads to the DRAM cache sizes.
    % We address the complexities involved in timing and micro-architecture details of \textit{UDCC} that are vital to support the data
    % consistency across DRAM cache and main memory and reason about the performance degradation caused by these complexities.

\end{abstract}

\begin{IEEEkeywords}
computer architecture, simulation, dram caches
\end{IEEEkeywords}


%\input{introduction}
\input{new-intro}
\input{background}
\input{design}
\input{validation}
\input{case-studies}
\input{related}

\section{Conclusion}

In this work, we described our detailed cycle-level DRAM cache
simulation model implemented and validated on \gem{}, which can enable performing a design space exploration in
DRAM cache research.
% As the applications memory footprint is scaling out and demanding larger and faster memories,
% and heterogeneous memory systems are becoming more available
% in the market to address this demand, new hardware techniques are required
% to enable efficient data management in the memory systems.
This new tool can be used to explore new unified DRAM cache and memory controller designs as part of an agile and full-system simulation platforms.
% are required to allow exploration of new techniques to address these needs.
The tool we presented in this work
can enable many interesting research work in the domain of heterogeneous memory systems.
For instance, using \textit{UDCC} we can address questions such as what is
the efficient data movement or data placement in systems composed of fast and slow memories.
Since, our tool provides full system simulation platform, also it can address the hardware and software co-design
ideas to explore design space of heterogeneous memories.

Moreover, \gem{} is highly modular and allows composing a simulated system based on a variety of components.
\textit{UDCC} can enable experimenting with different and new memory device models which might have features to be a better fit to be used as a cache to a backing memory.

%\section*{ACKNOWLEDGMENT}

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,references}

\end{document}
