\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{multirow}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\begin{document}
%
\title{Practical and Ethical Challenges of Large Language Models in Education: A Systematic Literature Review}

\titlerunning{Practical and Ethical Challenges of Large Language Models in Education}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here

\author{Lixiang Yan\inst{1}, Lele Sha\inst{1}, Linxuan Zhao\inst{1}, Yuheng Li\inst{1}, Roberto Martinez-Maldonado\inst{1}, Guanliang Chen\inst{1}, Xinyu Li\inst{1}, Yueqiao Jin\inst{1}, Dragan Gašević\inst{1} }
\institute{Centre for Learning Analytics at Monash, Faculty of Information Technology, Monash University, Clayton, Victoria, Australia}

\authorrunning{Yan et al.}

\maketitle             

\begin{abstract}

Educational technology innovations that have been developed based on large language models (LLMs) have shown the potential to automate the laborious process of generating and analysing textual content. While various innovations have been developed to automate a range of educational tasks (e.g., question generation, feedback provision, and essay grading), there are concerns regarding the practicality and ethicality of these innovations. Such concerns may hinder future research and the adoption of LLMs-based innovations in authentic educational contexts. To address this, we conducted a systematic literature review of 118 peer-reviewed papers published since 2017 to pinpoint the current state of research on using LLMs to automate and support educational tasks. The practical and ethical challenges of LLMs-based innovations were also identified by assessing their technological readiness, model performance, replicability, system transparency, privacy, equality, and beneficence. The findings were summarised into three recommendations for future studies, including updating existing innovations with state-of-the-art models (e.g., GPT-3), embracing the initiative of open-sourcing models/systems, and adopting a human-centred approach throughout the developmental process. These recommendations could support future research to develop practical and ethical innovations for supporting diverse educational tasks and benefiting students, teachers, and institutions.

\keywords{Large Language Models \and Pre-trained Language Models \and Educational Data Mining \and Artificial Intelligence \and Education \and GPT \and BERT \and ChatGPT \and Natural Language Processing .}

\end{abstract}

\section*{Practitioner notes}
What is currently known about this topic
\begin{itemize}
    \item Generating and analysing text-based educational content are time-consuming and laborious tasks.    
    \item Large language models are capable of efficiently analysing an unprecedented amount of textual content and completing complex natural language processing and generation tasks.
    \item Large language models have been increasingly used to develop educational technologies that aim to automate the generation and analysis of textual content.
\end{itemize}
What this paper adds
\begin{itemize}
    \item A comprehensive list of different educational tasks that could potentially benefit from LLMs-based innovations through automation.
    \item A structured assessment of the practicality and ethicality of existing LLMs-based innovations from seven important aspects using established frameworks. 
    \item Three recommendations that could potentially support future studies to develop LLMs-based innovations that are practical and ethical to implement in authentic educational contexts.
\end{itemize}
Implications for practitioners
\begin{itemize}
    \item Updating existing innovations with state-of-the-art models may further reduce the amount of manual effort required for adapting existing models to different educational tasks.
    %fine-turning and conducting few-shot learning with older models.
    \item The reporting standards of empirical research that aims to develop educational technologies using large language models need to be improved.
    \item Adopting a human-centred approach throughout the developmental process could contribute to resolving the practical and ethical challenges of large language models in education. 
\end{itemize}


\input{sections/1_intro}
\vspace{-10pt}
\input{sections/2_background}
\vspace{-10pt}
\input{sections/3_method}
\input{sections/4_results}
\vspace{-10pt}
\input{sections/5_discussion}
\vspace{-10pt}
\input{sections/6_conclusion}

\bibliographystyle{splncs04}
\bibliography{reference.bib}

\end{document}
