\begin{thebibliography}{100}
\providecommand{\url}[1]{{#1}}
\providecommand{\urlprefix}{URL }
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{DOI~\discretionary{}{}{}#1}\else
  \providecommand{\doi}{DOI~\discretionary{}{}{}\begingroup
  \urlstyle{rm}\Url}\fi

\bibitem{CWE-656}
{CWE-656}: Reliance on security through obscurity.
\newblock \url{https://cwe.mitre.org/data/definitions/656.html}

\bibitem{magicquadrant}
{Gartner Magic Quadrant for Network Firewalls}.
\newblock \url{https://www.gartner.com/en/documents/4007809}

\bibitem{owl2}
Owl 2 web ontology language new features and rationale (second edition).
\newblock W3c recommendation, World Wide Web Consortium (W3C), Cambridge, MA,
  US (2012).
\newblock \urlprefix\url{https://www.w3.org/TR/owl2-new-features/}

\bibitem{frost}
Global software licensing and monetization market, forecast to 2021.
\newblock Tech. Rep. 3715874, Frost \& Sullivan (2016)

\bibitem{ENISA}
{ENISA good practices for security of Smart Cars}.
\newblock Tech. rep., {European Union Agency for Cyber Security} (2019)

\bibitem{10.1145/2229156.2229157}
van~der Aalst, W.: Process mining: Overview and opportunities.
\newblock ACM Trans. Manage. Inf. Syst. \textbf{3}(2) (2012).
\newblock \doi{10.1145/2229156.2229157}

\bibitem{renewability}
Abrath, B., Coppens, B., Van~den Broeck, J., Wyseur, B., Cabutto, A., Falcarin,
  P., De~Sutter, B.: Code renewability for native software protection.
\newblock ACM Transactions on Privacy and Security \textbf{23}(4) (2020)

\bibitem{circulardebugging}
Abrath, B., Coppens, B., Nevolin, I., De~Sutter, B.: Resilient self-debugging
  software protection.
\newblock In: 2020 IEEE European Symposium on Security and Privacy Workshops,
  pp. 606--615. IEEE Computer Society (2020)

\bibitem{diabloSelfDebugging}
Abrath, B., Coppens, B., Volckaert, S., Wijnant, J., De~Sutter, B.:
  Tightly-coupled self-debugging software protection.
\newblock In: Proc.\ of the 6th Workshop on Software Security, Protection, and
  Reverse Engineering (SSPREW), pp. 7:1--7:10. ACM (2016)

\bibitem{ahmadvand2018}
Ahmadvand, M., Pretschner, A., Kelbert, F.: A taxonomy of software integrity
  protection techniques.
\newblock Advances in Computers  (2019).
\newblock \doi{https://doi.org/10.1016/bs.adcom.2017.12.007}

\bibitem{MATEtaxonomy}
Akhunzada, A., Sookhak, M., Anuar, N.B., Gani, A., Ahmed, E., Shiraz, M.,
  Furnell, S., Hayat, A., {Khurram Khan}, M.: Man-at-the-end attacks: Analysis,
  taxonomy, human aspects, motivation and future directions.
\newblock Journal of Network and Computer Applications \textbf{48}, 44--57
  (2015).
\newblock \doi{https://doi.org/10.1016/j.jnca.2014.10.009}

\bibitem{Anckaert2006}
Anckaert, B., Jakubowski, M., Venkatesan, R.: Proteus: Virtualization for
  diversified tamper-resistance.
\newblock In: Proceedings of the ACM Workshop on Digital Rights Management, p.
  47–58. ACM (2006)

\bibitem{Anckaert2007}
Anckaert, B., Madou, M., De~Sutter, B., De~Bus, B., De~Bosschere, K., Preneel,
  B.: Program obfuscation: a quantitative approach.
\newblock In: Proc.\ 2007 ACM workshop on Quality of Protection, pp. 15--20
  (2007)

\bibitem{Ban17}
Banescu, S., Collberg, C., Pretschner, A.: Predicting the resilience of
  obfuscated code against symbolic execution attacks via machine learning.
\newblock In: Proc.\ 26th USENIX Security Symposium, pp. 661--678 (2017)

\bibitem{banescu2017tutorial}
Banescu, S., Pretschner, A.: A tutorial on software obfuscation.
\newblock In: Advances in Computers, vol. 108, pp. 283--353. Elsevier (2017).
\newblock \doi{10.1016/bs.adcom.2017.09.004}

\bibitem{barakImpossibility}
Barak, B., Goldreich, O., Impagliazzo, R., Rudich, S., Sahai, A., Vadhan, S.,
  Yang, K.: On the (im)possibility of obfuscating programs.
\newblock In: J.~Kilian (ed.) Advances in Cryptology, pp. 1--18. Springer
  Berlin Heidelberg (2001)

\bibitem{basileOTP}
Basile, C., Canavese, D., d'Annoville, J., De~Sutter, B., Valenza, F.:
  Automatic discovery of software attacks via backward reasoning.
\newblock In: Proc.\ 1st Int'l Workshop on Software Protection, SPRO '15, pp.
  52--58. IEEE Press (2015)

\bibitem{D1.06}
Basile, C., Canavese, D., Regano, L.: {ASPIRE Validation}.
\newblock In: ASPIRE Project Deliverable 1.06 (2016).
\newblock
  \urlprefix\url{https://aspire-fp7.eu/sites/default/files/D1.06-ASPIRE-Validation-v1.01.pdf}

\bibitem{reganoMeta}
Basile, C., Canavese, D., Regano, L., Falcarin, P., De~Sutter, B.: A meta-model
  for software protections and reverse engineering attacks.
\newblock Journal of Systems and Software \textbf{150}, 3--21 (2019)

\bibitem{D5.11}
Basile, C., et~al.: {ASPIRE Framework Report}.
\newblock Deliverable D5.11, {ASPIRE EU FP7 Project} (2016).
\newblock
  \urlprefix\url{https://aspire-fp7.eu/sites/default/files/D5.11-ASPIRE-Framework-Report.pdf}

\bibitem{ceccato-new-one}
Berlato, S., Ceccato, M.: A large-scale study on the adoption of anti-debugging
  and anti-tampering protections in android apps.
\newblock Journal of Information Security and Applications \textbf{52}, 102,463
  (2020)

\bibitem{AESwhite}
Bringer, J., Chabanne, H., Dottax, E.: White box cryptography: Another attempt.
\newblock Cryptology ePrint Archive, Report 2006/468 (2006)

\bibitem{JENS}
Van~den Broeck, J., Coppens, B., De~Sutter, B.: Obfuscated integration of
  software protections.
\newblock Int'l Journal of Information Security \textbf{20}, 73--101 (2021)

\bibitem{brumley_apeg}
Brumley, D., Poosankam, P., Song, D., Zheng, J.: Automatic patch-based exploit
  generation is possible: Techniques and implications.
\newblock In: IEEE Symposium on Security and Privacy, pp. 143 -- 157. IEEE
  Computer Society (2008)

\bibitem{10.1145/3338503.3357722}
Brunet, P., Creusillet, B., Guinet, A., Martinez, J.M.: Epona and the
  obfuscation paradox: Transparent for users and developers, a pain for
  reversers.
\newblock In: Proceedings of the 3rd ACM Workshop on Software Protection, pp.
  41--52. Association for Computing Machinery (2019)

\bibitem{BSA}
{BSA | The Software Alliance}: {BSA Global Software Piracy Survey}.
\newblock Online at \url{https://gss.bsa.org/} (2018)

\bibitem{bsimm}
{Building Security in Maturity Model}.
\newblock \urlprefix\url{https://www.bsimm.com/}

\bibitem{mckinsey-automotive}
Burkacky, O., Deichmann, J., Klein, B., Pototzky, K., Scherf, G.: Cybersecurity
  in automotive.
\newblock Tech. rep., McKinsey \& Company (2020)

\bibitem{codeMobility}
Cabutto, A., Falcarin, P., Abrath, B., Coppens, B., De~Sutter, B.: Software
  protection with code mobility.
\newblock In: Proc.\ of the 2nd ACM Workshop on Moving Target Defense, MTD '15,
  pp. 95--103. ACM (2015)

\bibitem{reganoMetric}
Canavese, D., Regano, L., Basile, C., Viticchi{\'e}, A.: Estimating software
  obfuscation potency with artificial neural networks.
\newblock In: Security and Trust Management, pp. 193--202. Springer
  International Publishing (2017)

\bibitem{D4.06}
Ceccato, M.: {ASPIRE Security Evaluation Methodology}.
\newblock Deliverable D4.06, {ASPIRE EU FP7 Project} (2016)

\bibitem{barrierslicing}
Ceccato, M., Dalla~Preda, M., Nagra, J., Collberg, C., Tonella, P.: Barrier
  slicing for remote software trusting.
\newblock In: 7th IEEE Int'l Working Conference on Source Code Analysis and
  Manipulation (SCAM), pp. 27--36. IEEE Computer Society (2007)

\bibitem{ceccatoTaxonomy}
Ceccato, M., Tonella, P., Basile, C., Coppens, B., De~Sutter, B., Falcarin, P.,
  Torchiano, M.: How professional hackers understand protected code while
  performing attack tasks.
\newblock In: 2017 IEEE/ACM 25th International Conference on Program
  Comprehension (ICPC), pp. 154--164. IEEE Computer Society (2017)

\bibitem{emse2019}
Ceccato, M., Tonella, P., Basile, C., Falcarin, P., Torchiano, M., Coppens, B.,
  De~Sutter, B.: Understanding the behaviour of hackers while performing attack
  tasks in a professional setting and in a public challenge.
\newblock Empirical Software Engineering \textbf{24}(1), 240--286 (2019)

\bibitem{chow2002white}
Chow, S., Eisen, P., Johnson, H., van Oorschot, P.C.: A white-box {DES}
  implementation for {DRM} applications.
\newblock In: J.~Feigenbaum (ed.) Digital Rights Management, pp. 1--15.
  Springer Berlin Heidelberg (2003)

\bibitem{DSRA-evaluation-alternatives}
Cleven, A., Gubler, P., H\"{u}ner, K.M.: Design alternatives for the evaluation
  of design science research artifacts.
\newblock In: Proc.\ 4th Int'l Conf.\ on Design Science Research in Information
  Systems and Technology, DESRIST '09. Association for Computing Machinery, New
  York, NY, USA (2009).
\newblock \doi{10.1145/1555619.1555645}

\bibitem{tigress}
Collberg, C., Martin, S., Myers, J., Nagra, J.: Distributed application tamper
  detection via continuous software updates.
\newblock In: Proc.\ of the 28th Annual Computer Security Applications
  Conference, p. 319–328. ACM (2012)

\bibitem{collberg1997taxonomy}
Collberg, C., Thomborson, C., Low, D.: A taxonomy of obfuscating
  transformations.
\newblock Computer Science Technical Reports 148, Dep.\ of Computer Science,
  University of Auckland, New Zealand (1997)

\bibitem{collbergOpake}
Collberg, C., Thomborson, C., Low, D.: Manufacturing cheap, resilient, and
  stealthy opaque constructs.
\newblock In: Proc.\ 25th ACM SIGPLAN-SIGACT symposium on Principles of
  programming languages, pp. 184--196 (1998)

\bibitem{coppens2013feedback}
Coppens, B., De~Sutter, B., Maebe, J.: Feedback-driven binary code
  diversification.
\newblock ACM Transactions on Architecture and Code Optimization (TACO)
  \textbf{9}(4), 1--26 (2013)

\bibitem{D5.13}
Coppens, B., et~al.: {ASPIRE Open Source Manual}.
\newblock Deliverable D5.13, {ASPIRE EU FP7 Project} (2016).
\newblock
  \urlprefix\url{https://aspire-fp7.eu/sites/default/files/D5.13-ASPIRE-Open-Source-Manual.pdf}

\bibitem{robust}
Dawes, R.M.: The robust beauty of improper linear models in decision making.
\newblock American psychologist \textbf{34}(7), 571 (1979)

\bibitem{AESbroken}
De~Mulder, Y., Wyseur, B., Preneel, B.:
  Cryptanalysis\,of\,a\,perturbated\,white-box\,{AES}\,implementation.
\newblock In: G.~Gong, K.C. Gupta (eds.) Progress in Cryptology-INDOCRYPT 2010,
  pp. 292--310. Springer Berlin Heidelberg (2010)

\bibitem{Dagstuhl}
{De Sutter}, B., Collberg, C., {Dalla Preda}, M., Wyseur, B.: {Software
  Protection Decision Support and Evaluation Methodologies (Dagstuhl Seminar
  19331)}.
\newblock Dagstuhl Reports \textbf{9}(8), 1--25 (2019)

\bibitem{nistir8011}
{Dempsey, Kelley and Takamura, Eduardo and Eavy, Paul and Moore, George}:
  {NISTIR 8011 Vol. 4. Automation Support for Security Control Assessments:
  Software Vulnerability Management.}
\newblock Tech. rep., National Institute of Standards \& Technology,
  Gaithersburg, MD, United States (2020)

\bibitem{idesReq}
Denning, D., Neumann, P.G.: Requirements and model for ides -- a real-time
  intrusion-detection expert system.
\newblock Tech. rep., SRI International, Menlo Park, CA, USA (1985)

\bibitem{doerry2015monetizing}
Doerry, N., Sibley, M.: Monetizing risk and risk mitigation.
\newblock Naval Engineers Journal \textbf{127}, 35--46 (2015)

\bibitem{GOP}
van~der Ende, M., Hageraats, M., Poort, J., Quintais, J.P., Yagafarova, A.:
  Global online piracy study 2018.
\newblock Online at
  \url{https://www.ivir.nl/projects/global-online-piracy-study/} (2018)

\bibitem{fwExpSys}
Eronen, P., Zitting, J.: An expert system for analyzing firewall rules.
\newblock In: Proceedings of the 6th Nordic Workshop on Secure IT Systems
  (NordSec 2001), pp. 100--107 (2001)

\bibitem{gdpr1yafter}
{European Union Agency for Fundamental Rights (FRA)}: The general data
  protection regulation -- one year on.
\newblock Tech. rep., {}European Union Agency for Fundamental Rights (FRA)
  (2019)

\bibitem{Gartner-report-riskanalysis}
{Gartner, Inc.}: Risk assessment process and methodologies primer for 2019.
\newblock Online at \url{https://www.gartner.com/en/documents/3938592} (2019)

\bibitem{Gartner-report-online}
{Gartner, Inc.}: Cybersecurity labor shortage and {COVID-19}.
\newblock Online at
  \url{https://www.gartner.com/en/human-resources/research/talentneuron/cybersecurity-labor-shortage-and-covid-19}
  (2020)

\bibitem{heffner2004obfuscation}
Heffner, K., Collberg, C.: The obfuscation executive.
\newblock In: K.~Zhang, Y.~Zheng (eds.) Information Security, pp. 428--440.
  Springer Berlin Heidelberg, Berlin, Heidelberg (2004)

\bibitem{hevner2004design}
Hevner, A.R., March, S.T., Park, J., Ram, S.: Design science in information
  systems research.
\newblock MIS quarterly pp. 75--105 (2004)

\bibitem{hoffman1986risk}
Hoffman, L.J.: Risk analysis and computer security: bridging the cultural gaps.
\newblock In: Proceedings of the 9th National Computer Security Conference, pp.
  156--161. National Institute of Standards and Technology (1986)

\bibitem{obf_evaloptphaseord}
Holder, W., McDonald, J.T., Andel, T.R.: Evaluating optimal phase ordering in
  obfuscation executives.
\newblock In: Proc.\ 7th Software Security, Protection, and Reverse Engineering
  Workshop, SSPREW-7. ACM (2017)

\bibitem{horvath2020cryptographic}
Horv{\'a}th, M., Butty{\'a}n, L.: Cryptographic Obfuscation: A Survey.
\newblock Springer (2020)

\bibitem{Irdeto-report1}
Irdeto: Irdeto global connected industries cybersecurity survey.
\newblock Online at
  \url{https://go.irdeto.com/connected-industries-cybersecurity-survey-report/}
  (2020)

\bibitem{ISO27k}
{Information technology - Security techniques - Information security management
  systems - Overview and vocabulary}.
\newblock Standard, International Organization for Standardization,
  International Electrotechnical Commission, Geneva, CH (2018)

\bibitem{ISO27004}
{Information technology - Security techniques - Information security management
  - Monitoring, measurement, analysis and evaluation}.
\newblock Standard, International Organization for Standardization,
  International Electrotechnical Commission (2016)

\bibitem{nistSP800-37}
{Joint Task Force}: {SP 800-37}. risk management framework for information
  systems and organizations (revision 2).
\newblock Tech. rep., National Institute of Standards \& Technology,
  Gaithersburg, MD, United States (2018)

\bibitem{nistSP800-53}
{Joint Task Force}: {SP 800-53}. security and privacy controls for information
  systems and organizations (revision 5).
\newblock Tech. rep., National Institute of Standards \& Technology,
  Gaithersburg, MD, United States (2020)

\bibitem{nistSP800-39}
{Joint Task Force Transformation Initiative}: {SP 800-39}. managing information
  security risk: Organization, mission, and information system view.
\newblock Tech. rep., National Institute of Standards \& Technology (2011)

\bibitem{thinking}
Kahneman, D.: Thinking, fast and slow.
\newblock Macmillan (2011)

\bibitem{conditions}
Kahneman, D., Klein, G.: Conditions for intuitive expertise: a failure to
  disagree.
\newblock American psychologist \textbf{64}(6), 515 (2009)

\bibitem{intro_crypto}
Kaltz, J., Lindell, Y.: Introduction to modern cryptography: principles and
  protocols.
\newblock Chapman and Hall  (2008)

\bibitem{knapsack-book}
Kellerer, H., Pferschy, U., Pisinger, U.: Knapsack Problems.
\newblock Springer-Verlag (2004)

\bibitem{Khanmohammadi2019repacked}
Khanmohammadi, K., Hamou-Lhadj, A., Ebrahimi, N., Khoury, R.: Empirical study
  of android repackaged applications.
\newblock {Empirical Software Engineering} \textbf{24}(6), 3587--3629 (2019)

\bibitem{kimForensics}
Kim, J.S., Kim, M., Noh, B.N.: A fuzzy expert system for network forensics.
\newblock In: Computational Science and Its Applications (ICCSA), pp. 175--182.
  Springer Berlin Heidelberg (2004)

\bibitem{arxan-report}
Knight, A.: In plain sight: The vulnerability epidemic in financial mobile apps
  (April 2019)

\bibitem{CPI}
Kuznetsov, V., Szekeres, L., Payer, M., Candea, G., Sekar, R., Song, D.:
  Code-pointer integrity.
\newblock In: 11th {USENIX} Symposium on Operating Systems Design and
  Implementation, pp. 147--163. {USENIX} Association (2014)

\bibitem{liaoForensics}
Liao, N., Tian, S., Wang, T.: Network forensics based on fuzzy logic and expert
  system.
\newblock Comput. Commun. \textbf{32}(17), 1881--1892 (2009)

\bibitem{linn2003branchFunctions}
Linn, C., Debray, S.: Obfuscation of executable code to improve resistance to
  static disassembly.
\newblock In: Proceedings 10th ACM conference on Computer and communications
  security, pp. 290--299. ACM, New York, NY, USA (2003)

\bibitem{obf_optvialangmods}
Liu, H.: Towards better program obfuscation: Optimization via language models.
\newblock In: Proc.\ 38th Int'l Conference on Software Engineering Companion,
  ICSE '16, pp. 680--682. Association for Computing Machinery (2016)

\bibitem{7985664}
Liu, H., Sun, C., Su, Z., Jiang, Y., Gu, M., Sun, J.: Stochastic optimization
  of program obfuscation.
\newblock In: Proceedings of the 39th International Conference on Software
  Engineering, ICSE '17, pp. 221--231. IEEE Press (2017)

\bibitem{lukyanenko2014instantiation}
Lukyanenko, R., Evermann, J., Parsons, J.: Instantiation validity in is design
  research.
\newblock In: Advancing the Impact of Design Science: Moving from Theory to
  Practice: 9th International Conference, DESRIST 2014, Miami, FL, USA, May
  22-24, 2014. Proceedings 9, pp. 321--328. Springer (2014)

\bibitem{instantiation-validity}
Lukyanenko, R., Evermann, J., Parsons, J.: Instantiation validity in is design
  research.
\newblock In: M.C. Tremblay, D.~VanderMeer, M.~Rothenberger, A.~Gupta, V.~Yoon
  (eds.) Advancing the Impact of Design Science: Moving from Theory to
  Practice, pp. 321--328. Springer International Publishing, Cham (2014)

\bibitem{10.1007/978-3-030-55583-2_9}
Macher, G., Schmittner, C., Veledar, O., Brenner, E.: {ISO/SAE DIS 21434}
  automotive cybersecurity standard - in a nutshell.
\newblock In: Proceedings of Computer Safety, Reliability, and Security
  (SAFECOMP) Workshops: DECSoS 2020, DepDevOps 2020, USDAI 2020, and WAISE
  2020, pp. 123–--135. Springer-Verlag (2020).
\newblock \doi{10.1007/978-3-030-55583-2_9}

\bibitem{Mandiant}
Mandiant: 2020 security effectiveness: Deep dive into cyber reality.
\newblock Online at
  \url{https://content.fireeye.com/security-effectiveness/rpt-security-effectiveness-2020-deep-dive-into-cyber-reality}
  (2020)

\bibitem{ReMind}
Mantovani, A., Aonzo, S., Fratantonio, Y., Balzarotti, D.: {RE-Mind}: a first
  look inside the mind of a reverse engineer.
\newblock In: Proc. 32st Usenix Security Symposium (2022).
\newblock To appear

\bibitem{mccabe}
McCabe, T.J.: A complexity measure.
\newblock IEEE Transactions on Software Engineering \textbf{SE-2}(4), 308--320
  (1976)

\bibitem{merlo2021repackage}
Merlo, A., Ruggia, A., Sciolla, L., Verderame, L.: You shall not repackage!
  demystifying anti-repackaging on android.
\newblock Computers and Security \textbf{103}, 102,181 (2021)

\bibitem{collbergbook}
Nagra, J., Collberg, C.: Surreptitious Software: Obfuscation, Watermarking, and
  Tamperproofing for Software Protection.
\newblock Pearson Education, London, UK (2009)

\bibitem{rational}
Osbeck, L.M., Held, B.S.: Rational intuition: Philosophical roots, scientific
  investigations.
\newblock Cambridge University Press (2014)

\bibitem{owaspasvs}
{OWASP Application Security Verification Standard v4.03} (2021).
\newblock
  \urlprefix\url{https://owasp.org/www-project-application-security-verification-standard/}

\bibitem{owaspsamm}
{OWASP Software Assurance Maturity Model v2.0} (2020).
\newblock \urlprefix\url{https://owaspsamm.org/}

\bibitem{owensIDS}
Owens, S.F., Levary, R.R.: An adaptive expert system approach for intrusion
  detection.
\newblock Int. J. Secur. Netw. \textbf{1}(3/4), 206--217 (2006)

\bibitem{attack_graphs}
Phillips, C., Swiler, L.P.: A graph-based system for network-vulnerability
  analysis.
\newblock In: Proceedings of the 1998 Workshop on New Security Paradigms, NSPW
  ’98, pp. 71--79. ACM (1998)

\bibitem{Prat-taxonomy}
Prat, N., Comyn-Wattiau, I., Akoka, J.: A taxonomy of evaluation methods for
  information systems artifacts.
\newblock Journal of Management Information Systems \textbf{32}(3), 229--267
  (2015).
\newblock \doi{10.1080/07421222.2015.1099390}

\bibitem{ReganoPhd}
Regano, L.: An expert system for automatic software protection.
\newblock Ph.D. thesis, Politecnico di Torino (2019)

\bibitem{reganoL2P}
Regano, L., Canavese, D., Basile, C., Lioy, A.: Towards optimally hiding
  protected assets in software applications.
\newblock In: Proc.\ Int'l Conf.\ on Software Quality, Reliability and
  Security, pp. 374--385. IEEE Computer Society (2017)

\bibitem{reganoProlog}
Regano, L., Canavese, D., Basile, C., Viticchi{\'e}, A., Lioy, A.: Towards
  automatic risk analysis and mitigation of software applications.
\newblock In: Information Security Theory and Practice, pp. 120--135. Springer
  International Publishing (2016)

\bibitem{virtualizationAttack}
Rolles, R.: Unpacking virtualization obfuscators.
\newblock In: Proceedings of the 3rd USENIX Conference on Offensive
  Technologies, WOOT'09, pp. 1--1. USENIX Association (2009)

\bibitem{schrittwieser2016}
Schrittwieser, S., Katzenbeisser, S., Kinder, J., Merzdovnik, G., Weippl, E.:
  Protecting software through obfuscation: Can it keep pace with progress in
  code analysis?
\newblock ACM Comput. Surv. \textbf{49}(1), 4:1--4:37 (2016)

\bibitem{angr}
Shoshitaishvili, Y., Wang, R., Salls, C., Stephens, N., Polino, M., Dutcher,
  A., Grosen, J., Feng, S., Hauser, C., Kruegel, C., Vigna, G.: Sok: (state of)
  the art of war: Offensive techniques in binary analysis.
\newblock In: 2016 IEEE Symposium on Security and Privacy (SP), pp. 138--157.
  IEEE Computer Society (2016)

\bibitem{nistSP800-40}
{Souppaya, Murugiah and Scarfone, Karen}: {SP 800-40 Rev.~4. Guide to
  Enterprise Patch Management Planning: Preventive Maintenance for Technology}.
\newblock Tech. rep., National Institute of Standards \& Technology (2017)

\bibitem{Tamada2012}
Tamada, H., Fukuda, K., Yoshioka, T.: Program incomprehensibility evaluation
  for obfuscation methods with queue-based mental simulation model.
\newblock In: 13th ACIS Int'l Conf.\ on Software Engineering, Artificial
  Intelligence, Networking and Parallel Distributed Computing, pp. 498--503
  (2012)

\bibitem{standardization}
Tassey, G.: Standardization in technology-based markets.
\newblock Research policy \textbf{29}(4-5), 587--602 (2000)

\bibitem{RevEngE}
Taylor, C., Collberg, C.: Getting {RevEngE}: a system for analyzing reverse
  engineering behavior.
\newblock In: 14th International Conference on Malicious and Unwanted Software
  ({MALCON}) (2019)

\bibitem{audes}
Tsudik, G., Summers, R.C.: Audes - an expert system for security auditing.
\newblock In: Proceedings of the The Second Conference on Innovative
  Applications of Artificial Intelligence, pp. 221–--232. AAAI Press (1990)

\bibitem{architectural}
Tuma, K., Calikli, G., Scandariato, R.: Threat analysis of software systems: A
  systematic literature review.
\newblock Journal of Systems and Software \textbf{144}, 275--294 (2018)

\bibitem{Jens2}
{Van den Broeck}, J., Coppens, B., {De Sutter}, B.: Flexible software
  protection.
\newblock Computers \& Security \textbf{116}, 102,636 (2022)

\bibitem{diablo}
{Van Put}, L., Chanet, D., {De Bus}, B., {De Sutter}, B., {De Bosschere}, K.:
  {DIABLO}: a reliable, retargetable and extensible link-time rewriting
  framework.
\newblock In: Proc.\ Fifth IEEE Int'l Symposium on Signal Processing and
  Information Technology, pp. 7--12. IEEE Computer Society (2005)

\bibitem{FEDS-evaluation}
Venable, J., Pries-Heje, J., Baskerville, R.: {FEDS}: a framework for
  evaluation in design science research.
\newblock European Journal of Information Systems \textbf{25}(1), 77--89
  (2016).
\newblock \doi{10.1057/ejis.2014.36}

\bibitem{viticchie2016reactive}
Viticchi\'{e}, A., Basile, C., Avancini, A., Ceccato, M., Abrath, B., Coppens,
  B.: Reactive attestation: Automatic detection and reaction to software
  tampering attacks.
\newblock In: Proceedings of the 2016 ACM Workshop on Software PROtection, SPRO
  '16, p. 73–84. ACM (2016)

\bibitem{wangFlatteningTechReport}
Wang, C., Hill, J., Knight, J., Davidson, J.: Software tamper resistance:
  Obstructing static analysis of programs.
\newblock Tech. rep., University of Virginia, Charlottesville, VA, USA (2000)

\bibitem{petri_nets_attacks}
Wang, H., Fang, D., Wang, N., Tang, Z., Chen, F., Gu, Y.: Method to evaluate
  software protection based on attack modeling.
\newblock In: Int'l Conf.\ on High Performance Computing and Communications
  (HPCC) \& Int'l Conf.\ on Embedded and Ubiquitous Computing (EUC), pp.
  837--844. IEEE Computer Society (2013)

\bibitem{SWI-Prolog}
Wielemaker, J., Schrijvers, T., Triska, M., Lager, T.: {SWI-Prolog}.
\newblock Theory and Practice of Logic Programming \textbf{12}(1-2), 67--96
  (2012)

\bibitem{OWASPrisk}
Williams, J.: {OWASP Risk Rating Methodology}.
\newblock Online at
  \url{https://owasp.org/www-community/OWASP_Risk_Rating_Methodology} (1930)

\bibitem{wohlin00}
Wohlin, C., Runeson, P., H\"ost, M., Ohlsson, M., Regnell, B., Wessl\'en, A.:
  Experimentation in Software Engineering - An Introduction.
\newblock Kluwer Academic Publishers (2000)

\bibitem{wyseur2011white}
Wyseur, B.: White-box cryptography.
\newblock Ph.D. thesis, KU Leuven (2011)

\bibitem{D1.02}
Wyseur, B.: Assets.
\newblock In: ASPIRE Project Deliverable 1.02: Attack Model, pp. 10--12 (2014)

\bibitem{D1.02attack}
Wyseur, B.: Classification of attacks.
\newblock In: ASPIRE Project Deliverable 1.02: Attack Model, pp. 13--52 (2014)

\bibitem{DESbroken}
Wyseur, B., Michiels, W., Gorissen, P., Preneel, B.: Cryptanalysis of white-box
  {DES} implementations with arbitrary external encodings.
\newblock In: C.~Adams, A.~Miri, M.~Wiener (eds.) Selected Areas in
  Cryptography, pp. 264--277. Springer Berlin Heidelberg (2007)

\bibitem{yadegari}
Yadegari, B., Johannesmeyer, B., Whitely, B., Debray, S.: A generic approach to
  automatic deobfuscation of executable code.
\newblock In: Proc.\ Symposium on Security and Privacy, pp. 674–--691. IEEE
  Computer Society (2015)

\bibitem{Zhou2012repacked}
Zhou, Y., Jiang, X.: Dissecting android malware: Characterization and
  evolution.
\newblock In: 2012 IEEE Symposium on Security and Privacy, pp. 95--109 (2012).
\newblock \doi{10.1109/SP.2012.16}

\bibitem{Gartner}
Zumerle, D., Bhat, M.: Gartner: Market guide for application shielding (2017)

\end{thebibliography}
