We thank Vincent Boudart for making the CNN architecture plot,
the UL\`iege group from the STAR Institute, in particular Jean-Ren\'e Cudell,
Maxime Fays, Gr\'egory Baltus and Prasanta Char 
for hosting L.M.M. during a g2net (CA17137)
short term scientific mission working on this project,
Karl Wette for
valuable help with LALSuite SWIG wrappings~\cite{Wette:2020air},
Xingyu Zhong and Andrew L. Miller for initial exchanges about applying CNNs to tCWs,
Pep Covas for an interesting seminar talk on his improved short-segment detection statistic
that gave us useful inspiration on interpreting our ROC results,
and Alicia M. Sintes, Maite Mateu-Lucena and other members of the LIGO--Virgo--KAGRA
Continuous Waves working group for useful comments. This work was supported by
the Universitat de les Illes Balears (UIB); the Spanish Ministry of Science and
Innovation (MCIN) and the Spanish Agencia Estatal de Investigacio{\'o}n (AEI)
grants PID2019-106416GB-I00/MCIN/AEI/10.13039/501100011033; the MCIN with
funding from the European Union NextGenerationEU (PRTR-C17.I1); the FEDER
Operational Program 2021-2027 of the Balearic Islands; the Comunitat
Aut{\`o}noma de les Illes Balears through the Direcci{\'o} General de
Poli{\'i}tica Universitaria i Recerca with funds from the Tourist Stay Tax Law
ITS 2017-006 (PRD2018/24, PRD2020/11); the Conselleria de Fons Europeus,
Universitat i Cultura del Govern de les Illes Balears; and EU COST Actions
CA18108 and CA17137. DK is supported by the Spanish Ministerio de Ciencia,
Innovaci{\'o}n y Universidades (ref. BEAGAL 18/00148) and cofinanced by the
Universitat de les Illes Balears. RT is supported by the Spanish Ministerio de
Ciencia, Innovaci{\'o}n y Universidades (ref. FPU 18/00694). This research has
made use of data or software obtained from the Gravitational Wave Open Science
Center (gwosc.org), a service of LIGO Laboratory, the LIGO Scientific
Collaboration, the Virgo Collaboration, and KAGRA. LIGO Laboratory and Advanced
LIGO are funded by the United States National Science Foundation (NSF) as well
as the Science and Technology Facilities Council (STFC) of the United Kingdom,
the Max-Planck-Society (MPS), and the State of Niedersachsen/Germany for support
of the construction of Advanced LIGO and construction and operation of the
GEO600 detector. Additional support for Advanced LIGO was provided by the
Australian Research Council. Virgo is funded, through the European Gravitational
Observatory (EGO), by the French Centre National de Recherche Scientifique
(CNRS), the Italian Istituto Nazionale di Fisica Nucleare (INFN) and the Dutch
Nikhef, with contributions by institutions from Belgium, Germany, Greece,
Hungary, Ireland, Japan, Monaco, Poland, Portugal, Spain. KAGRA is supported by
Ministry of Education, Culture, Sports, Science and Technology (MEXT), Japan
Society for the Promotion of Science (JSPS) in Japan; National Research
Foundation (NRF) and Ministry of Science and ICT (MSIT) in Korea; Academia
Sinica (AS) and National Science and Technology Council (NSTC) in Taiwan. 
The authors are grateful for computational resources provided by the LIGO
Laboratory and supported by National Science Foundation Grants PHY-0757058 and
PHY-0823459. 
The authors gratefully acknowledge the computer resources at
Artemisa, funded by the European Union ERDF and Comunitat Valenciana as well as
the technical support provided by the Instituto de Física Corpuscular, IFIC
(CSIC-UV).

This paper has been assigned document numbers
\href{https://dcc.ligo.org/\dcc}{LIGO-\dcc}
and \href{\tdsurl}{\tds}.
