% This must be in the first 5 lines to tell arXiv to use pdfLaTeX, which is strongly recommended.
\pdfoutput=1
% In particular, the hyperref package requires pdfLaTeX in order to break URLs across lines.

\documentclass[11pt]{article}

% Remove the "review" option to generate the final version.
\usepackage{acl}

% Standard package includes
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{booktabs}


% For proper rendering and hyphenation of words containing Latin characters (including in bib files)
\usepackage[T1]{fontenc}
% For Vietnamese characters
% \usepackage[T5]{fontenc}
% See https://www.latex-project.org/help/documentation/encguide.pdf for other character sets

% This assumes your files are encoded as UTF8
\usepackage[utf8]{inputenc}


\usepackage{microtype}

\title{Salient Span Masking for Temporal Understanding}


\author{Jeremy R. Cole \qquad Aditi Chaudhary \qquad Bhuwan Dhingra \qquad Partha Talukdar \\
  Google Research \\
  \texttt{\{jrcole,aditichaud,bdhingra,partha@google.com\}}}

\begin{document}
\maketitle
\begin{abstract}
Salient Span Masking (SSM) has shown itself to be an effective strategy to improve closed-book question answering performance. SSM extends general masked language model pretraining by creating additional unsupervised training sentences that mask a single entity or date span, thus oversampling factual information.
Despite the success of this paradigm, the span types and sampling strategies are relatively arbitrary and not widely studied for other tasks. 
Thus, we investigate SSM from the perspective of temporal tasks, where learning a good representation of various temporal expressions is important. To that end, we introduce Temporal Span Masking (TSM) intermediate training.
First, we find that SSM alone improves the  downstream performance on three temporal tasks by an avg. +5.8 points. 
Further, we are able to achieve additional improvements (avg. +0.29 points) by adding the TSM task. These comprise the new best reported results on the targeted tasks. 
Our analysis suggests that the effectiveness of SSM stems from the sentences chosen in the training data rather than the mask choice: sentences with entities frequently also contain temporal expressions. Nonetheless, the additional targeted spans of TSM can still improve performance, especially in a zero-shot context.
\end{abstract}


%Improvement of SSM over best-reported baseline, avg across three tasks
%(58.52 - 52.74) = 5.78
%Improvement of SSM+TSM over SSM alone
%(86.20 - 85.88) + (100.0 - 99.73)
\input{tex/introduction}
\input{tex/methods}
\input{tab/overall}
\input{tex/results}
\input{tex/related_work}
\input{tex/conclusion}
\input{tex/limitations}

\section*{Acknowledgements}
We would like to thank Kelvin Guu and Srini Narayanan, as well as our anonymous reviewers, for their helpful feedback on a previous version of this manuscript.

\bibliography{anthology,custom}
\bibliographystyle{acl_natbib}

\clearpage

\appendix

\input{tex/training_appendix}
\input{tex/discussion_appendix}

\end{document}
