% Template for ICASSP-2021 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}
\usepackage{spconf,amsmath,amsthm,amssymb,graphicx}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage[normalem]{ulem}
\usepackage{subfigure}
\usepackage{booktabs}
\usepackage{adjustbox}
\usepackage{wrapfig,soul} %subfig
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{mathtools}
\useunder{\uline}{\ul}{}

% \pagecolor[rgb]{0.15,.15,.15} \color[rgb]{1,1,1}

\newcommand{\reminder}[1]{{\color{red}[#1]}}
\newcommand{\pt}[1]{\textcolor{blue}{[#1]}}
\newcommand{\conf}{\texttt{Conf}}
\newcommand{\lms}{\texttt{LMS}}
\newcommand{\gde}{\texttt{MA}}
\newcommand{\gdeln}{\texttt{MA}_0.02}
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newcommand\mypar[1]{\noindent \textit{#1}}

% Example definitions.
% --------------------
\def\x{{\mathbf x}}
\def\L{{\cal L}}

% Title.
% ------
\title{A Closer Look at Scoring Functions and Generalization Prediction}

\name{Puja Trivedi$^{\star}$ \qquad Danai Koutra$^{\star}$ \qquad Jayaraman J. Thiagarajan$^{\dagger}$}


\address{$^{\star}$ University of Michigan \\
$^{\dagger}$Lawrence Livermore National Laboratory\thanks{This work was performed under the auspices of the U.S. Department of Energy by the Lawrence Livermore National Laboratory under Contract No. DE-AC52-07NA27344. Supported by the ASCR Co-Design project. It was also partially supported by the National Science Foundation under CAREER Grant No.~IIS 1845491. Code available: \href{https://github.com/pujacomputes/icassp23-gengap.git}{\texttt{https://github.com/pujacomputes/icassp23-gengap.git}}}}

%
\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
Generalization error predictors (GEPs) aim to predict model performance on unseen distributions by deriving dataset-level error estimates from sample-level scores. However, GEPs often utilize disparate mechanisms (e.g., regressors, thresholding functions, calibration datasets, etc), to derive such error estimates, which can obfuscate the benefits of a particular scoring function. Therefore, in this work, we rigorously study the effectiveness of popular scoring functions (confidence, local manifold smoothness, model agreement), independent of mechanism choice. 
We find, absent complex mechanisms, that state-of-the-art confidence- and smoothness- based scores fail to outperform simple model-agreement scores when estimating error under distribution shifts and corruptions. Furthermore, on realistic settings where the training data has been compromised (e.g., label noise, measurement noise, undersampling), we find that model-agreement scores continue to perform well and that ensemble diversity is important for improving its performance. 
Finally, to better understand the limitations of scoring functions, we demonstrate that simplicity bias, or the propensity of deep neural networks to rely upon simple but brittle features, can adversely affect GEP performance.
Overall, our work carefully studies the effectiveness of popular scoring functions in realistic settings and helps to better understand their limitations. 
\end{abstract}
%
\begin{keywords}
Generalization, Data Augmentation, Out-of-Distribution  
\end{keywords}
%
\section{Introduction}
\label{sec:intro}
\input{010intro_v2.tex}

\section{Preliminaries}
% \section{Background \& Preliminaries}
% \label{sec:related}
% \input{020related}

% \section{Scoring Functions for Building GEP}
\label{sec:preliminaries}
\input{020prelim_v2.tex}

\section{A Closer Look at Scoring Functions}
\label{sec:method}
\input{030methodology_v2}
\input{simplicity_bias_table}
\section{Effect of Simplicity Bias on GEPs}
\input{040_simplicitybias}
\label{sec:simp_bias}
\vspace{-0.2pt}
\section{Conclusion}
\label{sec:concl}
\input{050_conclusions}

% \section{REFERENCES}
% \label{sec:refs}

% List and number all bibliographical references at the end of the
% paper. The references can be numbered in alphabetic order or in
% order of appearance in the document. When referring to them in
% the text, type the corresponding reference number in square
% brackets as shown at the end of this sentence \cite{C2}. An
% additional final page (the fifth page, in most cases) is
% allowed, but must contain only references to the prior
% literature.

% References should be produced using the bibtex program from suitable
% BiBTeX files (here: strings, refs, manuals). The IEEEbib.bst bibliography
% style file from IEEE produces unsorted bibliography list.
% -------------------------------------------------------------------------
\bibliographystyle{ieee}
\bibliography{icassp}

\end{document}
