\section{Real data experiment setup}
\label{sec:real-setup}

This section describes the setup for the experiments that involve real instead of synthetic data.
As noted in the introduction,
this is a face image quality assessment (FIQA) setup,
but the paper's general conclusions regarding QA algorithm evaluations using EDC curves should apply to scenarios with other biometric modalities as well.

\subsection{Used algorithms}

The real data experiments use one face detector for face image preprocessing, one face recognition system, and five (FI)QA algorithms:

\begin{itemize}
\item Face detector model: RetinaFace-R50 \cite{Deng-FaceDetection-RetinaFace-CVPR-2020}
\begin{itemize}
\item Images are excluded from the experiments when the face detection step fails.
\item The detected facial landmarks are used to preprocess the face images.
The same preprocessing approach used for ArcFace \cite{Deng-ArcFace-IEEE-CVPR-2019}
is also used for all FIQA models here, only the scaling differs since the models require different input resolutions.
Note that specialized preprocessing methods could be used for the individual models to possibly enhance their performance,
but that this work is about more general observations on the EDC, which should apply either way.
\end{itemize}
\item Face recognition feature extraction model: ArcFace-R100-MS1MV2 \cite{Deng-ArcFace-IEEE-CVPR-2019}.
\item FIQA algorithms:
\begin{itemize}
\item CR-FIQA(L) \cite{Boutros-FIQA-CRFIQA-arXiv-2022}: ResNet100 backbone trained on MS1MV2 \cite{Deng-ArcFace-IEEE-CVPR-2019}. $112\times 112$ input image size.
\item CR-FIQA(S) \cite{Boutros-FIQA-CRFIQA-arXiv-2022}: ResNet50 backbone trained on CASIA-WebFace \cite{Yi-LearningFaceRepresentationFromScratchCASIAWebFace-arXiv-2014}. $112\times 112$ input image size.
\item MagFace \cite{Meng-FRwithFQA-MagFace-CVPR-2021}: ResNet100 backbone trained on MS1MV2 \cite{Deng-ArcFace-IEEE-CVPR-2019}. $112\times 112$ input image size. %
\item PCNet \cite{Xie-FQA-PredictiveUncertaintyEstimation-BMVC-2020}: Trained on VGGFace2 \cite{Cao-VGGFace2Dataset-FGR-2018}. $224\times 224$ input image size.
\item SER-FIQ \cite{Terhorst-FQA-SERFIQ-CVPR-2020}: ``Same model'' variant using ArcFace. $112\times 112$ input image size.
\end{itemize}
\end{itemize}

The PCNet model was provided to us by one of the authors, the other models are publicly available.

\subsection{Used datasets}

Two datasets are used, LFW \cite{LFWTech} and TinyFace \cite{Cheng-TinyFace-LowResolutionFaceRecognition-ACCV-2018}:

\begin{itemize}
\item LFW (Labeled Faces in the Wild) \cite{LFWTech}
\begin{itemize}
\item Type: Web-scraped (varying quality).
\item Image width $\times$ height: $250\times 250$
\item Mean face region width $\times$ height: $94.98\times 129.63$
\item Excluded image file duplicates: 2
\item Images subsequently excluded due to failed face detection: 0
\item Images remaining: 13,231
\item Remaining subjects with only one image (implicitly excluded from mated pair set): 4,067
\item Subjects in mated comparisons: 1,680
\item Images in mated comparisons: 9,164
\item Mated comparisons used: 242,257
\end{itemize}
\item TinyFace (subsets Testing\_Set/Gallery\_Match and Testing\_Set/Probe) \cite{Cheng-TinyFace-LowResolutionFaceRecognition-ACCV-2018}
\begin{itemize}
\item Type: Web-scraped (varying quality).
\item Mean image width $\times$ height: $30.64\times 31.74$
\item Mean face region width $\times$ height: $29.22\times 31.50$
\item Excluded image file duplicates: 184
\item Images subsequently excluded due to failed face detection: 132
\item Images remaining: 7,855
\item Remaining subjects with only one image (implicitly excluded from mated pair set): 131
\item Subjects in mated comparisons: 2,434
\item Images in mated comparisons: 7,724
\item Mated comparisons used: 19,478
\end{itemize}
\end{itemize}

The number of used mated comparison pairs is the number of all possible mated pairs for the images which were not excluded.
Lists of the excluded image file duplicates are provided in supplemental material\footnote{\url{https://github.com/dasec/dataset-duplicates}}, due to the larger number of duplicates found in TinyFace.
