\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{iccv}
\pdfoutput=1
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{overpic}
\usepackage{float}
\usepackage{subfig}
\usepackage[ruled]{algorithm2e}

\newcommand{\Xiao}[1]{{\color{blue}{#1}}}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

\iccvfinalcopy % *** Uncomment this line for the final submission

\def\iccvPaperID{4628} % *** Enter the ICCV Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ificcvfinal\pagestyle{empty}\fi

\begin{document}

%%%%%%%%% TITLE
 \title{NeTO:{Ne}ural Reconstruction of {T}ransparent {O}bjects \\  with Self-Occlusion Aware Refraction-Tracing}
% NETO    Neural reconstruction of Transparent Object

% \author{First Author\\
% Institution1\\
% Institution1 address\\
% {\tt\small firstauthor@i1.org}
% % For a paper whose authors are all at the same institution,
% % omit the following lines up until the closing ``}''.
% % Additional authors and addresses can be added with ``\and'',
% % just like the second author.
% % To save space, use either the email address or home page, not both
% \and
% Second Author\\
% Institution2\\
% First line of institution2 address\\
% {\tt\small secondauthor@i2.org}
% }

\author{Zongcheng Li$^{1}$$^{\ast}$  \quad Xiaoxiao Long$^{2}$$^{\ast}$ \quad Yusen Wang$^{1}$ \quad Tuo Cao$^{1}$ \\ \quad Wenping Wang$^{3}$ \quad Fei Luo$^{1}$ \quad Chunxia Xiao$^{1}$$^{\dagger}$ \\[0.3em]\\
% $^{3}$  \quad Wenping Wang$^{4}$
 \quad $^{1}$Wuhan University \quad $^{2}$The University of Hong Kong   
\quad $^{3}$Texas A\&M University }

\maketitle

\footnotetext[1]{Equal contributions.}
\footnotetext[2]{Corresponding author.}

% Remove page # from the first page of camera-ready.
\ificcvfinal\thispagestyle{empty}\fi


\begin{abstract}

    We present a novel method, called NeTO, for capturing 3D geometry of solid transparent objects from 2D images via volume rendering. 
    Reconstructing transparent objects is a very challenging task, which is ill-suited for general-purpose reconstruction techniques due to the specular light transport phenomena.
    Although existing refraction-tracing based methods, designed specially for this task, achieve impressive results, they still suffer from unstable optimization and loss of fine details, since the explicit surface representation they adopted is difficult to be optimized, and the self-occlusion problem is ignored for refraction-tracing.
    In this paper, we propose to leverage implicit Signed Distance Function (SDF) as surface representation, and optimize the SDF field via volume rendering with a self-occlusion aware refractive ray tracing. 
    The implicit representation enables our method to be capable of reconstructing high-quality reconstruction even with a limited set of images, and the self-occlusion aware strategy makes it possible for our method to accurately reconstruct the self-occluded regions. 
    Experiments show that our method achieves faithful reconstruction results and outperforms prior works by a large margin.
    Visit our project page at \url{https://www.xxlong.site/NeTO/}.
\end{abstract}

%%%%%%%%% BODY TEXT
	
\input{sections/1_intro}
\input{sections/2_related_works}
\input{sections/3_method}
\input{sections/4_implementation}
\input{sections/5_experiments}
\input{sections/6_conclusion}
 
	
{\small
    \bibliographystyle{ieee_fullname}
    % \bibliography{NeTO/egbib}
    \input{main.bbl}
}



\end{document}