\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{iccv}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[pdftex]{xcolor}

% Include other packages here, before hyperref.
\usepackage{framed,multirow}
\usepackage{amsthm}
\usepackage{comment}
\usepackage{booktabs}
\theoremstyle{plain}
\newtheorem{pro}{Proposition}

\newcommand{\mukaigawa}[1]{\textcolor{blue}{[mukaigawa:#1]}}
\newcommand{\funa}[1]{\xspace\textcolor{olive}{[funa:#1]}}
\newcommand{\kussy}[1]{\textcolor[rgb]{1., 0.5, 0.0}{[kussy:#1]}}
\newcommand{\fujimura}[1]{\textcolor{cyan}{[fujimura:#1]}}

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

\iccvfinalcopy % *** Uncomment this line for the final submission

\def\iccvPaperID{1548} % *** Enter the ICCV Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ificcvfinal\pagestyle{empty}\fi

\begin{document}

%%%%%%%%% TITLE
\title{NLOS-NeuS: Non-line-of-sight Neural Implicit Surface}

\author{Yuki Fujimura$^1$ 
\and 
Takahiro Kushida$^1$ 
\and 
Takuya Funatomi$^1$
\and 
Yasuhiro Mukaigawa$^1$ \\
$^1$Nara Institute of Science and Technology, Japan\\
{\tt\small \{fujimura.yuki,kushida.takahiro.kh3,funatomi,mukaigawa\}@is.naist.jp}
}

\maketitle
% Remove page # from the first page of camera-ready.
\ificcvfinal\thispagestyle{empty}\fi


%%%%%%%%% ABSTRACT
\begin{abstract}
Non-line-of-sight (NLOS) imaging is conducted to infer invisible scenes from indirect light on visible objects.
The neural transient field (NeTF) was proposed for representing scenes as neural radiance fields in NLOS scenes.
We propose NLOS neural implicit surface (NLOS-NeuS), which extends the NeTF to neural implicit surfaces with a signed distance function (SDF) for reconstructing three-dimensional surfaces in NLOS scenes.
We introduce two constraints as loss functions for correctly learning an SDF to avoid non-zero level-set surfaces.
We also introduce a lower bound constraint of an SDF based on the geometry of the first-returning photons.
The experimental results indicate that these constraints are essential for learning a correct SDF in NLOS scenes.
Compared with previous methods with discretized representation, NLOS-NeuS with the neural continuous representation enables us to reconstruct smooth surfaces while preserving fine details in NLOS scenes.
To the best of our knowledge, this is the first study on neural implicit surfaces with volume rendering in NLOS scenes.
\end{abstract}

%%%%%%%%% BODY TEXT

\input{sec1} % Introduction
\input{sec2} % Related work
\input{sec3} % Method
\input{sec4} % Experiments
\input{sec5} % Conclusion

{\small
\section*{Acknowledgement}
This work was supported by the Japan Society for the Promotion of Science KAKENHI Grant Number 21K21317, 20K20629.
}

{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}

\newpage
%~
%\newpage

\input{supp} % supplementary

\end{document}