\documentclass[journal]{new-aiaa}
%\documentclass[conf]{new-aiaa} for conference papers
\usepackage[utf8]{inputenc}
\usepackage{textcomp}

% \usepackage{amsmath, amsfonts, amssymb, amscd}
\usepackage[usenames,dvipsnames]{color} 

\usepackage[capitalize]{cleveref}
\usepackage{longtable}
\usepackage{multicol}
\usepackage{pdfpages}
\usepackage[utf8]{inputenc}
\usepackage[table]{xcolor}
\usepackage[final]{changes}

\usepackage{graphics}
\usepackage{subfigure}
\usepackage{tikz}

\usepackage{pgfplots}
\usetikzlibrary{pgfplots.fillbetween}
\pgfplotsset{scaled x ticks=false}
\pgfplotsset{compat=newest}
\pgfplotsset{every axis/.append style={axis on top}}
\setlength{\unitlength}{1in} 
\usepgfplotslibrary{groupplots}

\usepackage{nomencl}
% \usepackage{enumerate}
% \usepackage[normalem]{ulem}
\usepackage{cancel}
% \usepackage{subcaption}
% \usepackage{graphicx}

\usepackage[none]{hyphenat}

\usepackage[style=ieee, url=false, doi=true]{biblatex}
\renewcommand*{\bibfont}{\footnotesize}
\addbibresource{jais.bib}

%\usepackage{lineno}
%\linenumbers

% \usepackage[version=4]{mhchem}
\usepackage{siunitx}
\usepackage{longtable,tabularx}
\usepackage{todonotes}
\setlength\LTleft{0pt} 

\title{Inferring Traffic Models in Terminal Airspace \\ from Flight Tracks and Procedures}

\author{Soyeon Jung,\footnote{Ph.D. candidate, Aeronautics and Astronautics.} Amelia Hardy,\footnote{M.S. student, Computer Science.} and Mykel J. Kochnederfer\footnote{Associate Professor, Aeronautics and Astronautics. AIAA Associate Fellow.  Corresponding author: mykel@stanford.edu.}}
\affil{Stanford University, Stanford, CA 94304 USA}

\begin{document}

\maketitle
\vspace{-1.2cm}
\begin{center}
    DOI: \href{https://doi.org/10.48550/arXiv.2303.09981}{10.48550/arXiv.2303.09981}
\end{center}

\begin{abstract}
Realistic aircraft trajectory models are useful in the design and validation of air traffic management (ATM) systems. 
Models of aircraft operated under instrument flight rules (IFR) require capturing the variability inherent in how aircraft follow standard flight procedures. The variability in aircraft behavior differs among flight stages. In this paper, we propose a simple probabilistic model that can learn this variability from procedural data and flight tracks collected from radar surveillance data. For each segment, we use a Gaussian mixture model to learn the deviations of aircraft trajectories from their procedures. Given new procedures, we generate synthetic trajectories by sampling a series of deviations from the Gaussian mixture model and reconstructing the aircraft trajectory using the deviations and the procedures. We extend this method to capture pairwise correlations between aircraft and show how a pairwise model can be used to generate traffic involving an arbitrary number of aircraft. We demonstrate the proposed models on the arrival tracks and procedures of the John F. Kennedy International Airport. Distributional similarity between the original and the synthetic trajectory dataset was evaluated using the Jensen-Shannon divergence between the empirical distributions of different variables and we provide qualitative analyses of the synthetic trajectories generated. 
\end{abstract}

% \section*{Nomenclature}

% \noindent(Nomenclature entries should have the units identified)

% {\renewcommand\arraystretch{1.0}
% \noindent\begin{longtable*}{@{}l @{\quad=\quad} l@{}}
% $A$  & amplitude of oscillation \\
% $a$ &    cylinder diameter \\
% $C_p$& pressure coefficient \\
% $Cx$ & force coefficient in the \textit{x} direction \\
% $Cy$ & force coefficient in the \textit{y} direction \\
% c   & chord \\
% d$t$ & time step \\
% $Fx$ & $X$ component of the resultant pressure force acting on the vehicle \\
% $Fy$ & $Y$ component of the resultant pressure force acting on the vehicle \\
% $f, g$   & generic functions \\
% $h$  & height \\
% $i$  & time index during navigation \\
% $j$  & waypoint index \\
% $K$  & trailing-edge (TE) nondimensional angular deflection rate\\
% $\Theta$ & boundary-layer momentum thickness\\
% $\rho$ & density\\
% \multicolumn{2}{@{}l}{Subscripts}\\
% cg & center of gravity\\
% $G$ & generator body\\
% iso	& waypoint index
% \end{longtable*}}




% \section{Introduction}
% \lettrine{T}{his} document is a \LaTeX{} template for preparation of papers for AIAA Technical Journals. If you are reading a hard-copy or .pdf version of this document, download the electronic file, new-aiaa.cls, and use it to prepare your manuscript.

% Authors using \url{https://www.overleaf.com} may simply open the AIAA template from the Overleaf gallery to work online; no local installation of any files is required. Authors using a local \LaTeX{} installation will need to open the template in Overleaf and use the ``Download as zip'' option from the project menu to download a local copy of the template files. To create your formatted manuscript, type your own text over sections of the template, or cut and paste from another document and then use the available markup styles. Note that special formatting such as subscripts, superscripts, and italics may be lost when you copy your text into the template from a Word Processing program such as Microsoft Word. See Sec. IV for more detailed formatting guidelines.

\newlength\figureheight
\newlength\figurewidth

\input{intro.tex}
\input{data.tex}
\input{single.tex}
\input{multiple.tex}
\input{experiments.tex}
\input{conclusions.tex}

\section*{Acknowledgments}
This material is based upon work supported by the Department of the Air Force under Air Force Contract FA8702-15-D-0001.
Opinions, findings, conclusions and recommendations are those of the authors and do not necessarily reflect the views of the Department of the Air Force.
The authors acknowledge the FAA and the MITRE Corporation for sharing the surveillance data.
They thank Evan Maki, Randal Guendel, and Mikhail Krichman from MIT Lincoln Laboratory for their support and assistance.
This article benefited from the work of Shane Barratt, and conversations with Rachael Tompa and Kyle Julian.

\printbibliography

\end{document}
