\section*{Response to reviewer \#1}
\rpy{(Responses are highlighted in red. Corresponding code changes are highlighted in red as well in the manuscript.)}

\subsection*{Minor comments}
\paragraph{Comment 1} 
Please fix hyperlinks. For instance, when I click on Algorithm 2.2 (line 205), the hyperlink takes me to the first page. Similar with other links in the text. Probably simple LaTeX error/compilation issue.

\rpy{Thank you for bringing this to our attention. We believe this is indeed a technical error due to an erroneous LaTex command. We have corrected it and generated a new PDF with correct hyperlinks.}


\paragraph{Comment 2} 
Line 72: "At each iteration, the Matrix Powers Kernel (MPK) performs s SpMVs on a starting normalized column vector $Q_i$" -- unclear what $i$ is/ Consider adding "at step/iteration/block iteration $i$"

\rpy{Thank you for your feedback. We have added the clarification at line 72}


\paragraph{Comment 3} 
Line 152: "Barlow showed that BCGS2 produce " $\rightarrow$ "Barlow showed that BCGS2 produces"

\rpy{Thank you for your feedback. We have corrected the typo at line 152}


\paragraph{Comment 4} 
Line 167: capitalize Algorithm.

Line 205: capitalize Algorithm.

\rpy{Thank you for your feedback. We have corrected the typo at line 167 and 205.}


\paragraph{Comment 5 (Series of comments about mismatching figure numbers)} 
Line 477: It should probably be Fig 2, not Fig 3 (Fig 3 is for 2D Laplace). Same in Line 490.

Line508: It should be Fig 3 not Fig 4. 

Line525: Should be Fig 4, not Fig 5 (based on figure captions). Same in Line 532.

Line540: Should be Fig 5, not Fig 6. Same comment, Line 560.

Line599: Should be Fig 6, not Fig 7. Also line 600 should be Fig 5.

Line607: Should be Fig 7.

Line623: Should be Fig 7.

Line642: Fig 8, not Fig 9.

Line652: Fig 9, not Fig 10.

Line664: Fig 10, not Fig 11.

Line684: Fig 10, not Fig 11.

Line699: Fig 10, not Fig 11. Also check line 703 for correct figure references.

Line718: Fig 11, not Fig 12.

Line794: Fig 12, not Fig 13. Also Line 826.

Line846: Fig 12, not Fig 13.

Line909: Fig 13, not Fig 14. Same in Lines 909, 910, 918.

Line934: Should be Fig 14, not Fig 15.

Line 935: Fig 15, not Fig 16.

Line 959: Fig 15, not FIg 16.

\rpy{Thank you for your feedback about the wrong numbering of figures and we appreciate the detailed tracking of all the wrong numbering of references. This issue was also raised by another referee. The wrong numbering has been tracked down to an erroneous LaTex command in the previous manuscript that incorrectly incremented the numbering of all figure references by 1. In other words, all references to Figure $x$ were incorrectly compiled to Figure $x+1$ in text. We apologize for the technical error. This has been fixed in the revised manuscript.}


\paragraph{Comment 6} 
Figure 11: Some matrices used are symmetric positive definite (say Thermal2) and CG can be applied (GMRES is an overkill). Others (say Delaunay\_n20, belgium\_osm) are not linear system matrices. Maybe justify your choice in the caption?

\rpy{Thank you for pointing this out. We believe there are two parts to the question here, one regarding symmetric positive definite (SPD) matrices and the other about non-linear system matrices.

Our original intention was to randomly choose several large-scale matrices ($N>10^6$) from SuiteSparse Matrix Collection for testing. During the selection process, we did not explicitly exclude SPD matrices. Although our paper is on GMRES variants, this particular section on initial step size estimator could potentially apply to adaptive s-step CG for SPD matrices since the estimator only relies on the eigenvalue distributions. For this reason, in the revised manuscript, we have 2 SPD matrices in the selection (\texttt{G3\_circuit} and \texttt{thermal2}).

On the other hand, we did make the careless mistake of including matrices that are not really linear system matrices. This was tracked down to a careless selection on the SuiteSparse website where we did not filter the field \textit{Rutherford-Boeing Type} so that binary matrices were included. This has been corrected in the revised manuscript where binary matrices are removed and only real matrices are included. We have also added additional matrices to demonstrate the robustness of our proposed estimator.

To clarify the selection of matrices, we have included a table (Table. 1) in \textit{Section 4, Test 10} to display the vast range of domains that we have tested our algorithm on. All matrices are of size $N>10^6$.}


\paragraph{Comment 7} 
Line 648: "The E20R5000 matrix with the ILU(0) preconditioner does not converge well" $\rightarrow$ it is not the matrix that converges, but the linear system with the matrix.

\rpy{Thank you for your feedback. We have added the clarification at line 645 about the linear system.}


\paragraph{Comment 8} 
Line 508: Also, in the caption of Fig 4, the size is 1.6*$10^6$ while in the text it is 1.6 * $10^5$.

\rpy{Thank you for your feedback. The correct dimension is $1.6\times10^5$ as it is generated from a $400\times 400$ 2D mesh. We have corrected the typo in the caption of Figure 4.}


\paragraph{Comment 9} 
Line 636: "Test 6: 2DLaplace" -> "Test 6: 2D Laplace" (missing space).

\rpy{Thank you for your feedback. We have corrected the typo in the parapraph header at line 633.}


\paragraph{Comment 10} 
Reference [39]: fix capitalization.

\rpy{Thank you for your feedback. We have fixed the capitalization. We also removed a redundant bibliography entry during our proofreading. The original reference [39] is now [38].}