%\documentclass[11pt]{article}
\documentclass{llncs}
%\documentclass{sn-jnl}
\usepackage{orcidlink}

\title{Satisfiability of
  Non-Linear Transcendental Arithmetic as a
  Certificate Search Problem}

%corresponding?
%emails?

\usepackage{url}
%\usepackage[toc,page]{appendix}
\usepackage{todonotes}
\usepackage{hyperref}


\usepackage{tableof}

% To disable colors, comment the following row and de-comment the next one
\usepackage{xcolor}
%\usepackage[monochrome]{xcolor}

%\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{xspace}
\usepackage{hhline}
\usepackage{makecell}
\usepackage{colortbl} %used only for coloring table in draft

\usepackage{amssymb}

\input{macros}

\begin{document}


\author{Enrico Lipparini\inst{1,2}\orcidlink{0009-0009-0428-4403}\and
	Stefan Ratschan\inst{3} \orcidlink{0000-0003-1710-1513} 
}

\institute{
	University of Genoa, Italy 	\and
	University of Cagliari, Italy \and
	Institute of Computer Science of the Czech Academy of Sciences
}


% TODO
\setlength{\marginparwidth}{4cm}
\reversemarginpar




\maketitle


\begin{abstract}

\begin{center}
\end{center}
	\noindent
	For typical first-order logical theories, satisfying assignments have a straightforward finite representation that can directly serve as a certificate that a given assignment satisfies the given formula. For non-linear real arithmetic augmented with trigonometric and exponential functions (\nta), however, there is no known direct representation of satisfying assignments that allows for a simple independent check of whether the represented numbers exist and satisfy the given formula. Hence, in this paper, we introduce a different form of satisfiability certificate for \nta, and formulate the satisfiability problem as the problem of searching for such a certificate.
	% This does not only ease the independent verification of satisfiability, but also allows the design of new algorithms that show satisfiability by systematically searching for such certificates. Moreover, it provides a basis for studying algorithmically solvable sub-classes of  the undecidable theory of non-linear real arithmetic with transcendental functions, which we characterize by providing lower and upper bounds in terms of relevant well-known classes, and for which we show the existence of a terminating procedure.
	% Computational experiments document that the resulting algorithms are able to prove satisfiability of a substantially higher number of benchmark problems than existing methods.
	This does not only ease the independent verification of satisfiability, but also allows the design of new algorithms that show satisfiability by systematically searching for such certificates.          Computational experiments document that the resulting algorithms are able to prove satisfiability of a substantially higher number of benchmark problems than existing methods.         
We also characterize the formulas  whose satisfiability can be demonstrated by such a certificate, by providing lower and upper bounds in terms of relevant well-known classes.
Finally we show the existence of a procedure for checking the satisfiability of \nta-formulas that terminates for formulas that satisfy certain robustness assumptions.        
\end{abstract}

%\setcounter{tocdepth}{5} %show more in the toc
%\tableofcontents

\input{introduction}

\input{preliminaries}

\input{goal}

\input{method}

\input{certificate_search}


\input{experiments}

\input{theoretical_considerations}


 \input{relwork}	
	

\section{Conclusions}
\label{sec:conclusions}
We introduced a form of satisfiability certificate for \smtnta and formulated the satisfiability verification problem as the problem of searching for such a certificate. We showed how to perform this search in a systematic fashion introducing new and efficient search techniques, and provided a theoretical classification providing insight into the possibilities and restrictions of such an approach. Computational experiments document that the resulting method is able to prove satisfiability of a substantially higher number of benchmark problems than existing methods. This suggests future work on the  integration of such search methods into the deduction machinery of current SMT solvers.

While in the unsatisfiable case~\cite{Barbosa:23}, proof certificates are already produced by some current SMT solvers,  and there has already been a standardization effort concerning proof formats and software infrastructure, this is still a topic for future work in the case of satisfiability of \smtnta. Finally, the extension of such techniques to even richer theories (e.g., reasoning not only about real numbers, but about real-valued functions~\cite{Ratschan:23}), is an interesting topic for future research.


%The approach described in this paper provides a unifying framework over such methods that clearly separates search from verification. 

\section*{Acknowledgments}\label{s:ack}
The work of Stefan Ratschan was supported by
the project 21-09458S of the Czech Science Foundation GA ČR
and institutional support RVO:67985807. 


\bibliographystyle{plain}
\bibliography{refs}


%\input{unused_material}
\end{document}



%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:


