\documentclass[numbers = noenddot, twoside=true, open = right, a4wide, 11pt , parskip=half, %bibtotocnumbered,
liststotocnumbered,headings=optiontohead, captions=tableheading]{scrreprt}

\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{nicefrac}
\usepackage{a4wide}
\usepackage{amsmath}
\usepackage{parskip}
\usepackage{amssymb}
\usepackage{lscape}
\usepackage{fancyhdr}
\usepackage{appendix}
\usepackage{booktabs}
\usepackage{multirow,arydshln,tabu}
\usepackage{setspace}
\usepackage[small,hang,bf]{caption}
%\usepackage{subfig}
%\usepackage{subfigure}
\usepackage{subcaption,booktabs} % for the subtables
\usepackage{array}
%\usepackage{slashbox}
\usepackage{caption}
\usepackage{url}
\usepackage{natbib}
\usepackage{listings}
\usepackage{ae,aecompl}
% \usepackage{lineno} % get rid of once not needed anymore
\usepackage[table]{xcolor}
%\usepackage{hyperref}	% Hyperlinks
\usepackage{enumitem} % to set style of \begin{description}
\usepackage{pdflscape, afterpage} % for correct placement of landscape tables
%\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,filecolor=blue,urlcolor=blue}


\setcounter{totalnumber}{5}
%\addto\captionsenglish{\renewcommand{\figurename}{Fig.}}
%\addto\captionsenglish{\renewcommand{\tablename}{Tab.}}
\parindent 0mm
\onehalfspacing
\lstset{basicstyle = \ttfamily}
% \setlength{\parindent}{0pt}

% commands that are defined in mnras.cls that my paper uses:
% (search for those when error "Undefined control sequence" appears)
\newcommand\degr{\hbox{$^\circ$}}
\newcommand\farcs{\hbox{$.\!\!^{\prime\prime}$}}
\newcommand\arcsec{\hbox{$^{\prime\prime}$}}
% Standard journal abbreviations
% Mostly as used by ADS, with a few additions for journals where MNRAS does not
% follow normal IAU style.

\newcommand\aap{A\&A}                % Astronomy and Astrophysics
\let\astap=\aap                          % alternative shortcut
\newcommand\aapr{A\&ARv}             % Astronomy and Astrophysics Review (the)
\newcommand\aaps{A\&AS}              % Astronomy and Astrophysics Supplement Series
\newcommand\actaa{Acta Astron.}      % Acta Astronomica
\newcommand\afz{Afz}                 % Astrofizika
\newcommand\aj{AJ}                   % Astronomical Journal (the)
\newcommand\ao{Appl. Opt.}           % Applied Optics
\let\applopt=\ao                         % alternative shortcut
\newcommand\aplett{Astrophys.~Lett.} % Astrophysics Letters
\newcommand\apj{ApJ}                 % Astrophysical Journal
\newcommand\apjl{ApJ}                % Astrophysical Journal, Letters
\let\apjlett=\apjl                       % alternative shortcut
\newcommand\apjs{ApJS}               % Astrophysical Journal, Supplement
\let\apjsupp=\apjs                       % alternative shortcut
% The following journal does not appear to exist! Disabled.
%\newcommand\apspr{Astrophys.~Space~Phys.~Res.} % Astrophysics Space Physics Research
\newcommand\apss{Ap\&SS}             % Astrophysics and Space Science
\newcommand\araa{ARA\&A}             % Annual Review of Astronomy and Astrophysics
\newcommand\arep{Astron. Rep.}       % Astronomy Reports
\newcommand\aspc{ASP Conf. Ser.}     % ASP Conference Series
\newcommand\azh{Azh}                 % Astronomicheskii Zhurnal
\newcommand\baas{BAAS}               % Bulletin of the American Astronomical Society
\newcommand\bac{Bull. Astron. Inst. Czechoslovakia} % Bulletin of the Astronomical Institutes of Czechoslovakia 
\newcommand\bain{Bull. Astron. Inst. Netherlands} % Bulletin Astronomical Institute of the Netherlands
\newcommand\caa{Chinese Astron. Astrophys.} % Chinese Astronomy and Astrophysics
\newcommand\cjaa{Chinese J.~Astron. Astrophys.} % Chinese Journal of Astronomy and Astrophysics
\newcommand\fcp{Fundamentals Cosmic Phys.}  % Fundamentals of Cosmic Physics
\newcommand\gca{Geochimica Cosmochimica Acta}   % Geochimica Cosmochimica Acta
\newcommand\grl{Geophys. Res. Lett.} % Geophysics Research Letters
\newcommand\iaucirc{IAU~Circ.}       % IAU Cirulars
\newcommand\icarus{Icarus}           % Icarus
\newcommand\japa{J.~Astrophys. Astron.} % Journal of Astrophysics and Astronomy
\newcommand\jcap{J.~Cosmology Astropart. Phys.} % Journal of Cosmology and Astroparticle Physics
\newcommand\jcp{J.~Chem.~Phys.}      % Journal of Chemical Physics
\newcommand\jgr{J.~Geophys.~Res.}    % Journal of Geophysics Research
\newcommand\jqsrt{J.~Quant. Spectrosc. Radiative Transfer} % Journal of Quantitiative Spectroscopy and Radiative Transfer
\newcommand\jrasc{J.~R.~Astron. Soc. Canada} % Journal of the RAS of Canada
\newcommand\memras{Mem.~RAS}         % Memoirs of the RAS
\newcommand\memsai{Mem. Soc. Astron. Italiana} % Memoire della Societa Astronomica Italiana
\newcommand\mnassa{MNASSA}           % Monthly Notes of the Astronomical Society of Southern Africa
\newcommand\mnras{MNRAS}             % Monthly Notices of the Royal Astronomical Society
\newcommand\na{New~Astron.}          % New Astronomy
\newcommand\nar{New~Astron.~Rev.}    % New Astronomy Review
\newcommand\nat{Nature}              % Nature
\newcommand\nphysa{Nuclear Phys.~A}  % Nuclear Physics A
\newcommand\pra{Phys. Rev.~A}        % Physical Review A: General Physics
\newcommand\prb{Phys. Rev.~B}        % Physical Review B: Solid State
\newcommand\prc{Phys. Rev.~C}        % Physical Review C
\newcommand\prd{Phys. Rev.~D}        % Physical Review D
\newcommand\pre{Phys. Rev.~E}        % Physical Review E
\newcommand\prl{Phys. Rev.~Lett.}    % Physical Review Letters
\newcommand\pasa{Publ. Astron. Soc. Australia}  % Publications of the Astronomical Society of Australia
\newcommand\pasp{PASP}               % Publications of the Astronomical Society of the Pacific
\newcommand\pasj{PASJ}               % Publications of the Astronomical Society of Japan
\newcommand\physrep{Phys.~Rep.}      % Physics Reports
\newcommand\physscr{Phys.~Scr.}      % Physica Scripta
\newcommand\planss{Planet. Space~Sci.} % Planetary Space Science
\newcommand\procspie{Proc.~SPIE}     % Proceedings of the Society of Photo-Optical Instrumentation Engineers
\newcommand\rmxaa{Rev. Mex. Astron. Astrofis.} % Revista Mexicana de Astronomia y Astrofisica
\newcommand\qjras{QJRAS}             % Quarterly Journal of the RAS
\newcommand\sci{Science}             % Science
\newcommand\skytel{Sky \& Telesc.}   % Sky and Telescope
\newcommand\solphys{Sol.~Phys.}      % Solar Physics
\newcommand\sovast{Soviet~Ast.}      % Soviet Astronomy (aka Astronomy Reports)
\newcommand\ssr{Space Sci. Rev.}     % Space Science Reviews
\newcommand\zap{Z.~Astrophys.}       % Zeitschrift fuer Astrophysik 

\begin{document}
\raggedbottom

\pagestyle{empty}

\input{titlepage}

 \cleardoublepage


\pagenumbering{gooble}

\pagestyle{plain}

%% Vorblatt

\begin{flushright}
 \begin{table}[!b]
 \setlength{\tabcolsep}{0pt}
  \begin{tabular}{l r}
   Gutachter der Dissertation: & Prof. Dr. Jochen Liske \\
				     & A/Prof. Dr. Aaron S. G. Robotham \\
				     & \\
   Zusammensetzung der Pr\"ufungskommission: & Prof. Dr. Jochen Liske \\  
& Prof. Dr. Robi Banerjee \\
& Prof. Dr. Peter Hauschildt \\
& Prof. Dr. Dieter Horns \\
& Prof. Dr. Johannes Haller \\
& \\
Vorsitzender der Pr\"ufungskommission: & Prof. Dr. Peter Hauschildt \\ 
& \\
Datum der Disputation: & 17.06.2022  \\ 
& \\
Vorsitzender des Fach-Promotionsausschusses PHYSIK: & Prof. Dr. Wolfgang J. Parak \\
& \\
Leiter des Fachbereichs PHYSIK: & Prof. Dr. G\"unter H. W. Sigl\\
& \\
Dekan der Fakultät MIN: & Prof. Dr. Heinrich Graener
  \end{tabular}

 \end{table}

\end{flushright}



\pagenumbering{Roman}
\chapter*{Eidesstattliche Versicherung}
\bigskip
 Hiermit versichere ich an Eides statt, die vorliegende Dissertationsschrift selbst verfasst und keine anderen als die angegebenen Hilfsmittel und Quellen benutzt zu haben. \\
 
Hamburg, den 27.04.2022
\bigskip
\bigskip

{\begin{flushright}
  (Sarah Casura) \\
 \end{flushright}
 }
 
\newpage 
 
\chapter*{Zusammenfassung}
Quantitative Strukturanalysen von Galaxien sind unerlässlich um theoretische Modelle und Simulationen einzugrenzen, welche die Entstehung und Entwicklung von Galaxien sowie des gesamten Universums beschreiben. Entsprechende Daten werden von Himmelsdurchmusterungen in hoher Qualität geliefert. Um diese vollumfänglich nutzen zu können, sind automatisierte Methoden notwendig.  
Diese Promotionsarbeit präsentiert Strukturparameter für die Komponenten einer großen Anzahl von GAMA Galaxien im nahen Universum und verbessert die Bildanalyse, die Modellierung von Galaxien sowie die Nachbearbeitung solcher Modelle zur Qualitätssicherung, im Kontext von automatisierten Galaxiezerlegungsstudien. 
Die Probe umfasst 13096 Galaxien in den GAMA II Equatorialregionen bei Rotverschiebungen $z$\,<\,0.08. Die Bilddaten stammen von den KiDS und VIKING Himmelsdurchmusterungen, welche den optischen und nah-infraroten Wellenlängenbereich abdecken ($ugriZYJHK_s$-Filter). Wir fitten die Oberflächenhelligkeitsverteilung jeder Galaxie in jedem Filter mit drei Modellen: einer S\'ersicfunktion, einer S\'ersic- plus Exponentialfunktion sowie einer Punktquelle plus Exponentialfunktion. Die Modellanpassung erfolgt mit einer vollautomatisierten Markov-Chain-Monte-Carlo-Analyse mit dem bayesschen zweidimensionalen Profilanpassungs-Code \texttt{ProFit}. Die Vorarbeit, einschlie{\ss}lich der Bildsegmentierung, Hintergrundsubtraktion, Modellierung der Punktspreizfunktion und Schätzung von Anfangswerten, wird mit dem Bildanalysen-Code \texttt{ProFound} ausgeführt. Nach der Modellierung wird eine Modellauswahl getroffen und Galaxien für welche keines der Modelle angemessen ist - z.B. asymmetrische und verschmelzende Systeme - markiert. Die Modellierungsqualität wird durch visuelle Inspektion, Vergleiche mit bestehenden Veröffentlichungen sowie zwischen unabhängigen Ergebnissen für mehrfach-Aufnahmen derselben Galaxie und mit speziell auf diese Arbeit zugeschnittenen Simulationen überprüft. Diese werden auch für eine Untersuchung von systematischen Fehlerquellen verwendet. Die Modellierungsresultate erweisen sich als verlässlich für eine große Spannbreite an verschiedenen Galaxietypen und Bildqualitäten. Es liegen nur minimale systematische Messabweichungen vor. Die systematischen Fehler sind einen Faktor von 2-3 gr\"o{\ss}er als zufällige Fehler. Die automatisierte Modellauswahl stimmt mit einer Genauigkeit von >\,90\,\% mit der visuellen Inspektion einer Teilprobe von Galaxien überein. Eine Untersuchung der $g-r$-Farben von Galaxiekomponenten und des zugehörigen Farbe-Helligkeits-Diagramms ergibt, dass diese im Einklang mit bestehenden Veröffentlichungen sind, trotz der größeren Flexibilität der Modelle dieser Arbeit. Alle Resultate sind auf der GAMA-Datenbank integriert. 

\newpage

\chapter*{Abstract}
Quantitative measurements of the structural components of the galaxy population are crucial to constrain theory and simulations, which - in turn - constrain the formation and evolution of galaxies and the universe as a whole. This requires analysing large and diverse samples of galaxies at multiple wavelengths. Corresponding high-quality data is delivered by current and future large galaxy imaging surveys. To fully exploit these, automated analysis methods need to be developed further.  
In this thesis, we derive a catalogue of robust structural parameters for the components of a large sample of nearby GAMA galaxies while at the same time contributing to the advancement of image analysis, surface brightness fitting and post-processing routines for quality assurance in the context of automated large-scale bulge-disk decomposition studies. 
The sample consists of 13096 galaxies at redshifts $z$\,<\,0.08 in the GAMA II equatorial survey regions with imaging data from the Kilo-Degree Survey (KiDS) and the VISTA Kilo-Degree INfrared Galaxy (VIKING) survey spanning the optical and near-infrared ($u, g, r, i, Z, Y, J, H$ and $K_s$ bands). We fit three models to the surface brightness distribution of each galaxy in each band individually: a single S\'ersic model, a S\'ersic plus exponential and a point source plus exponential. The fitting is performed with a fully automated Markov-chain Monte Carlo (MCMC) analysis using the Bayesian two-dimensional profile fitting code \texttt{ProFit}. All preparatory work, including image segmentation, background subtraction, point spread function estimation, and obtaining initial guesses, is carried out using the complementary image analysis package \texttt{ProFound}. After fitting the galaxies, we perform model selection and flag galaxies for which none of our models are appropriate, mainly mergers and irregular galaxies. The fit quality is assessed by visual inspections, comparison to previous works, comparison of independent fits of galaxies in the overlap regions between KiDS tiles and bespoke simulations. The latter two are also used for a detailed investigation of systematic error sources. We find that our fit results are robust across various galaxy types and image qualities with minimal biases. Errors given by the MCMC underestimate the true errors typically by factors 2-3. Automated model selection criteria are accurate to >\,90\,\% as calibrated by visual inspection of a subsample of galaxies. We also present $g-r$ component colours and the corresponding colour-magnitude diagram, consistent with previous works despite our increased fit flexibility. All results are integrated into the GAMA database.


\newpage 

\chapter*{Previous publications}
The following publications make use of results obtained in this thesis:
\begin{itemize}
\item Casura~S., Liske~J., Robotham~A.~S.~G., Brough~S., Driver~S.~P., Graham~A.~W., H{\"a}u{\ss}ler~B., et al., ``Galaxy And Mass Assembly (GAMA): Bulge-disk decomposition of KiDS data in the nearby universe", MNRAS (submitted)
\item Oh S., Colless M., D'Eugenio F., Croom S.~M., Cortese L., Groves B., Kewley L.~J., et al., ``The SAMI Galaxy Survey: the difference between ionized gas and stellar velocity dispersions", 2022, MNRAS, 512, 1765. doi:10.1093/mnras/stac509
\item H{\"a}u{\ss}ler B., Vika M., Bamford S.~P., Johnston E.~J., Brough S., Casura S., Holwerda B.~W., et al., ``Galapagos-2/Galfitm/GAMA -- multi-wavelength measurement of galaxy structure: separating the properties of spheroid and disk components in modern surveys", 2022, arXiv, arXiv:2204.05907
\item Oh S., Colless M., Barsanti S., Casura S., Cortese L., van de Sande J., Owers M.~S., et al., ``The SAMI Galaxy Survey: decomposed stellar kinematics of galaxy bulges and disks", 2020, MNRAS, 495, 4638. doi:10.1093/mnras/staa1330
\item Cluver M.~E., Jarrett T.~H., Taylor E.~N., Hopkins A.~M., Brough S., Casura S., Holwerda B.~W., et al., “Galaxy and Mass Assembly (GAMA): Demonstrating the Power of WISE in the Study of Galaxy Groups to z\,<\,0.1”, 2020, ApJ, 898, 20. doi:10.3847/1538-4357/ab9cb8
\item Robotham A.~S.~G., Davies L.~J.~M., Driver S.~P., Koushan S., Taranu D.~S., Casura S., Liske J., “ProFound: Source Extraction and Application to Modern Survey Data”, 2018, MNRAS, 476, 3137. doi:10.1093/mnras/sty440
\end{itemize}


\cleardoublepage

\pagestyle{fancy}

%\fancyhead[LE,RO]{\textsl{\rightmark}}
%\fancyhead[LO,RE]{\textsl{\leftmark}}
% \fancyfoot[C]{\thepage}

\fancyhf{}
\fancyhead[RE]{\color[gray]{0}\leftmark}
\fancyhead[LO]{\color[gray]{0}\rightmark}
\fancyfoot[RO,LE]{\thepage}

%\renewcommand{\partmark}[1]{\markboth{\thepart. #1}{}}
%\renewcommand{\chaptermark}[1]{\markright{\thechapter.\ #1}}
%\renewcommand{\sectionmark}[1]{}

\doublespacing
\tableofcontents
\onehalfspacing

\newpage
\thispagestyle{plain}




\input{chap1_intro}
\clearpage
\newpage
\input{chap2_pipeline}
\clearpage
\newpage
\input{chap3_results}
\clearpage
\newpage
\input{chap4_QC}
\clearpage
\newpage
\input{chap5_conclusion}
\clearpage
\newpage

\pagenumbering{roman}
\clearpage
\newpage
%\appendix
%\input{appendix}
%\clearpage\\

%\newpage


\bibliographystyle{thesis}

\addcontentsline{toc}{chapter}{Bibliography}
\bibliography{/home/sarah/Desktop/papers/zzzreferences}

\clearpage
 


\end{document}

  
