\documentclass{article}
\usepackage{PRIMEarxiv}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}
\usepackage{fancyhdr}       % header
\usepackage{graphicx}       % graphics
\graphicspath{{media/}}     % organize your images and other figures under media/ folder
\usepackage{multicol}
\usepackage{multirow}
\usepackage{array}
\usepackage{amssymb}
\usepackage{pifont}
\usepackage{fancyhdr}
\usepackage{authblk}

\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
%Header
\pagestyle{fancy}
\thispagestyle{empty}
\rhead{ \textit{ }} 

% Update your Headers here
\fancyhead[LO]{3D Oral Reconstruction with Neural X-ray Field from Panoramic Imaging}
% \fancyhead[RE]{Firstauthor and Secondauthor} % Firstauthor et al. if more than 2 - must use \documentclass[twoside]{article}



  
%% Title
\title{Oral-NeXF: 3D Oral Reconstruction with Neural X-ray Field from Panoramic Imaging
}

\author[1]{Weinan Song}
\author[1]{Haoxin Zheng}
\author[1]{Jiawei Yang}
\author[3]{Chengwen Liang}
\author[2,1]{Lei He}

\affil[1]{University of California, Los Angeles}
\affil[2]{Eastern Institute for Advanced Study, Ningbo, China}
\affil[3]{Hangzhou Dental Hospital, Hangzhou, China}

\begin{document}
\maketitle


\begin{abstract}
3D reconstruction of medical images from 2D images has increasingly become a challenging research topic with the advanced development of deep learning methods. Previous work in 3D reconstruction from limited (generally one or two) X-ray images mainly relies on learning from paired 2D and 3D images. In 3D oral reconstruction from panoramic imaging, the model also relies on some prior individual information, such as the dental arch curve or voxel-wise annotations, to restore the curved shape of the mandible during reconstruction. These limitations have hindered the use of single X-ray tomography in clinical applications. To address these challenges, we propose a new model that relies solely on projection data, including imaging direction and projection image, during panoramic scans to reconstruct the 3D oral structure. Our model builds on the neural radiance field by introducing multi-head prediction, dynamic sampling, and adaptive rendering, which accommodates the projection process of panoramic X-ray in dental imaging. Compared to end-to-end learning methods, our method achieves state-of-the-art performance without requiring additional supervision or prior knowledge.
\end{abstract}


% keywords can be removed
\keywords{3D Reconstruction\and Neural Radiance Field \and Dental Imaging}
\input{sections/intro}
\input{sections/method}
\input{sections/exp}
\input{sections/result}

\section{Conclusion}
In this paper, we propose Oral-NeXF, a method for reconstructing 3D oral structures from projection information in panoramic X-ray (PX) imaging. Unlike existing deep learning models, Oral-NeXF does not require extensive patient data or dense annotations to recover the 3D object. Instead, we utilize a multi-head neural field function to predict a group of voxel values at a single time given a 2D coordinate. Furthermore, we introduce a dynamic sampling strategy and an adaptive rendering method to obtain a smooth density distribution. Extensive experiments on simulated data from 100 CBCT scans demonstrate that Oral-NeXF achieves competitive performance compared to end-to-end models, both qualitatively and quantitatively. These results demonstrate the effectiveness and efficiency of our proposed method in 3D oral reconstruction.

\clearpage
%Bibliography
\bibliographystyle{unsrt}  
\bibliography{ref}  


\end{document}
