@misc{NIST,
         key = "{\relax DLMF}",
       title = "{\it NIST Digital Library of Mathematical Functions}",
howpublished = "http://dlmf.nist.gov/, Release 1.1.2 of 2021-06-15",
         url = "http://dlmf.nist.gov/",
        note = "F.~W.~J. Olver, A.~B. {Olde Daalhuis}, D.~W. Lozier, B.~I. Schneider,
                R.~F. Boisvert, C.~W. Clark, B.~R. Miller, B.~V. Saunders,
                H.~S. Cohl, and M.~A. McClain, eds."
}
@misc{Kac,
  title="{Euler-Maclaurin Formula}",
  author={Victor G. Kac and Pokman Cheung},
  year={2005},
  url = "http://people.csail.mit.edu/kuat/courses/euler-maclaurin.pdf",
  howpublished = "http://people.csail.mit.edu/kuat/courses/euler-maclaurin.pdf",
  note = "{Date accessed $02/16/2022$}"
}
@article{Riemann,
 ISSN = {00029890, 19300972},
 URL = {http://www.jstor.org/stable/10.4169/amer.math.monthly.123.4.387},
 abstract = {We present several generalizations of the Riemann–Lebesgue lemma. Our approach highlights the role of cancellation in the Riemann–Lebesgue lemma.},
 author = {Ovidiu Costin and Neil Falkner and Jeffery D. McNeal},
 journal = {The American Mathematical Monthly},
 number = {4},
 pages = {387--391},
 publisher = {Mathematical Association of America},
 title = "{Some Generalizations of the Riemann–Lebesgue Lemma}",
 urldate = {2022-06-19},
 volume = {123},
 year = {2016}
}
@article{Biermann,
   title="{Unruh and analogue Unruh temperatures for circular motion in 
3+1
 and 
2+1
 dimensions}",
   volume={102},
   ISSN={2470-0029},
   url={http://dx.doi.org/10.1103/PhysRevD.102.085006},
   DOI={10.1103/physrevd.102.085006},
   number={8},
   journal={Physical Review D},
   publisher={American Physical Society (APS)},
   author={Biermann, Steffen and Erne, Sebastian and Gooding, Cisco and Louko, Jorma and Schmiedmayer, Jörg and Unruh, William G. and Weinfurtner, Silke},
   year={2020},
   month={Oct}
}
@article{Fewster,
   title="{Waiting for Unruh}",
   volume={33},
   ISSN={1361-6382},
   url={http://dx.doi.org/10.1088/0264-9381/33/16/165003},
   DOI={10.1088/0264-9381/33/16/165003},
   number={16},
   journal={Classical and Quantum Gravity},
   publisher={IOP Publishing},
   author={Fewster, Christopher J and Juárez-Aubry, Benito A and Louko, Jorma},
   year={2016},
   month={Jul},
   pages={165003}
}
@book{G+R,
  author = {Gradshteyn, I. S. and Ryzhik, I. M.},
  edition = {Seventh},
  pages = {xlviii+1171},
  publisher = {Elsevier/Academic Press, Amsterdam},
  title = {Table of integrals, series, and products},
  year = 2007
}
@article{RotatingVacuum,
       author = {{Davies}, Paul C.~W. and {Dray}, Tevian and {Manogue}, Corinne A.},
        title = "{Detecting the rotating quantum vacuum}",
      journal = {Physical Review D},
     keywords = {04.62.+v, Quantum field theory in curved spacetime, General Relativity and Quantum Cosmology},
         year = 1996,
        month = apr,
       volume = {53},
       number = {8},
        pages = {4382-4387},
          doi = {10.1103/PhysRevD.53.4382},
archivePrefix = {arXiv},
       eprint = {gr-qc/9601034},
 primaryClass = {gr-qc},
       adsurl = {https://ui.adsabs.harvard.edu/abs/1996PhRvD..53.4382D},
      adsnote = {Provided by the SAO/NASA Astrophysics Data System}
}
@book{NumericalRecipes,
  author = {Press, William H. and Teukolsky, Saul A. and Vetterling, William T. and Flannery, Brian H.},
  edition = {Third},
  publisher = {Cambridge University Press},
  title = {Numerical Recipes: The Art of Scientific Computation},
  year = 2007
}
@article{Unruh,
  title = {Notes on black-hole evaporation},
  author = {Unruh, W. G.},
  journal = {Phys. Rev. D},
  volume = {14},
  issue = {4},
  pages = {870--892},
  numpages = {0},
  year = {1976},
  month = {Aug},
  publisher = {American Physical Society},
  doi = {10.1103/PhysRevD.14.870},
  url = {https://link.aps.org/doi/10.1103/PhysRevD.14.870}
}
@book{birrell, place={Cambridge}, series={Cambridge Monographs on Mathematical Physics}, title={Quantum Fields in Curved Space}, DOI={10.1017/CBO9780511622632}, publisher={Cambridge University Press}, author={Birrell, N. D. and Davies, P. C. W.}, year={1982}, collection={Cambridge Monographs on Mathematical Physics}}
@article{Upton,
    author = "Louko, Jorma and Upton, Samuel D.",
    title = "{Low energy Lorentz violation from high energy modified dispersion in inertial and circular motion}",
    eprint = "1710.06954",
    archivePrefix = "arXiv",
    primaryClass = "gr-qc",
    doi = "10.1103/PhysRevD.97.025008",
    journal = "Phys. Rev. D",
    volume = "97",
    number = "2",
    pages = "025008",
    year = "2018"
}
@misc{Maple,
  title = {Maple},
  howpublished = {\url{https://www.maplesoft.com/}},
}
@article{Einstein,
    author = "Einstein, Albert",
    title = "{Zur Quantentheorie der Strahlung}",
    journal = "Phys. Z.",
    volume = "18",
    pages = "121--128",
    year = "1917"
}
@article{QuantumVacuum,
    author = "Davies, Paul C. W. and Dray, Tevian and Manogue, Corinne A.",
    title = "{The rotating quantum vacuum}",
    eprint = "gr-qc/9601034",
    archivePrefix = "arXiv",
    reportNumber = "ADP-95-43-M-36-REV, ADP-95-43-M-36",
    doi = "10.1103/PhysRevD.53.4382",
    journal = "Phys. Rev. D",
    volume = "53",
    pages = "4382--4387",
    year = "1996"
}
@article{Fulling,
  title = "{Nonuniqueness of Canonical Field Quantization in Riemannian Space-Time}",
  author = {Fulling, Stephen A.},
  journal = {Phys. Rev. D},
  volume = {7},
  issue = {10},
  pages = {2850--2862},
  numpages = {0},
  year = {1973},
  month = {May},
  publisher = {American Physical Society},
  doi = {10.1103/PhysRevD.7.2850},
  url = {https://link.aps.org/doi/10.1103/PhysRevD.7.2850}
}
@article{Davies1975,
	doi = {10.1088/0305-4470/8/4/022},
	url = {https://doi.org/10.1088/0305-4470/8/4/022},
	year = 1975,
	month = {apr},
	publisher = {{IOP} Publishing},
	volume = {8},
	number = {4},
	pages = {609--616},
	author = {P C W Davies},
	title = "{Scalar production in Schwarzschild and Rindler metrics}",
	journal = {Journal of Physics A: Mathematical and General},
}
@article{Takagi,
    author = {Takagi, Shin},
    title = "{Vacuum Noise and Stress Induced by Uniform Acceleration: Hawking-Unruh Effect in Rindler Manifold of Arbitrary Dimension}",
    journal = {Progress of Theoretical Physics Supplement},
    volume = {88},
    pages = {1-142},
    year = {1986},
    month = {03},
    issn = {0375-9687},
    doi = {10.1143/PTP.88.1},
    url = {https://doi.org/10.1143/PTP.88.1},
    eprint = {https://academic.oup.com/ptps/article-pdf/doi/10.1143/PTP.88.1/5461184/88-1.pdf},
}
@article{Crispino_2008,
   title="{The Unruh effect and its applications}",
   volume={80},
   ISSN={1539-0756},
   url={http://dx.doi.org/10.1103/RevModPhys.80.787},
   DOI={10.1103/revmodphys.80.787},
   number={3},
   journal={Reviews of Modern Physics},
   publisher={American Physical Society (APS)},
   author={Crispino, Luís C. B. and Higuchi, Atsushi and Matsas, George E. A.},
   year={2008},
   month={Jul},
   pages={787–838}
}
@article{Gooding,
    author = "Gooding, Cisco and Biermann, Steffen and Erne, Sebastian and Louko, Jorma and Unruh, William G. and Schmiedmayer, Joerg and Weinfurtner, Silke",
    title = "{Interferometric Unruh detectors for Bose-Einstein condensates}",
    eprint = "2007.07160",
    archivePrefix = "arXiv",
    primaryClass = "gr-qc",
    doi = "10.1103/PhysRevLett.125.213603",
    journal = "Phys. Rev. Lett.",
    volume = "125",
    number = "21",
    pages = "213603",
    year = "2020"
}
@article{Hodgkinson,
    author = "Hodgkinson, Lee and Louko, Jorma and Ottewill, Adrian C.",
    title = "{Static detectors and circular-geodesic detectors on the Schwarzschild black hole}",
    eprint = "1401.2667",
    archivePrefix = "arXiv",
    primaryClass = "gr-qc",
    doi = "10.1103/PhysRevD.89.104002",
    journal = "Phys. Rev. D",
    volume = "89",
    number = "10",
    pages = "104002",
    year = "2014"
}
@book{Pitaevskii, 
series={International Series of Monographs on Physics}, title={Bose-Einstein Condensation}, 
publisher={Clarendon Press}, 
author={Pitaevskii, Lev and Stringari, Sandro}, 
year={2003}, 
collection={International Series of Monographs on Physics}
}
@book{Prudnikov, 
title={Integrals and Series, Volume 2: Special Functions}, 
publisher={Gordon and Breach Science Publishers}, 
author={Prudnikov, A.P. and Brychkov, Yu. A. and Marichev, O.I.}, 
year={1986},
}
@Book{AS,
 author    = "Milton {Abramowitz} and Irene A. {Stegun}",
 title     = "Handbook of Mathematical Functions with
              Formulas, Graphs, and Mathematical Tables",
 publisher = "Dover",
 year      =  1964,
 address   = "New York City",
 edition   = "ninth Dover printing, tenth GPO printing"
}
@article{Roche,
title = {Measurement of the surface tension of superfluid {sup 4}He at low temperature by capillary wave resonances},
author = {Roche, P and Deville, G and Appleyard, N J and Williams, F I.B.},
doi = {10.1007/BF02395922},
url = {https://www.osti.gov/biblio/530542}, journal = {Journal of Low Temperature Physics},
volume = 106,
place = {United States},
year = {1997},
month = {3}
}
@article{Analogue,
    author = "Barcelo, Carlos and Liberati, Stefano and Visser, Matt",
    title = "{Analogue gravity}",
    eprint = "gr-qc/0505065",
    archivePrefix = "arXiv",
    doi = "10.12942/lrr-2005-12",
    journal = "Living Rev. Rel.",
    volume = "8",
    pages = "12",
    year = "2005"
}
@article{Unruh1981,
  title = {Experimental Black-Hole Evaporation?},
  author = {Unruh, W. G.},
  journal = {Phys. Rev. Lett.},
  volume = {46},
  issue = {21},
  pages = {1351--1353},
  numpages = {0},
  year = {1981},
  month = {May},
  publisher = {American Physical Society},
  doi = {10.1103/PhysRevLett.46.1351},
  url = {https://link.aps.org/doi/10.1103/PhysRevLett.46.1351}
}
@article{Liberati,
    author = "Barcelo, Carlos and Liberati, Stefano and Visser, Matt",
    title = "{Analogue gravity}",
    eprint = "gr-qc/0505065",
    archivePrefix = "arXiv",
    doi = "10.12942/lrr-2005-12",
    journal = "Living Rev. Rel.",
    volume = "8",
    pages = "12",
    year = "2005"
}
@book{HeliumUniverse,
  title={The Universe in a Helium Droplet},
  author={Volovik, G.E.},
  series={International series of monographs on physics},
  url={https://books.google.co.uk/books?id=VuLJrQEACAAJ},
  year={2009},
  publisher={Oxford University Press}
}
@ARTICLE{BEC1,
       author = {Retzker, A. and Cirac, J.~I. and Plenio, M.~B. and Reznik, B.},
        title = "{Methods for Detecting Acceleration Radiation in a Bose-Einstein Condensate}",
     keywords = {03.75.Nt, 03.65.-w, 03.67.-a, Other Bose-Einstein condensation phenomena, Quantum mechanics, Quantum information, Quantum Physics},
         year = 2008,
        month = sep,
        journal = {\PRL},
       volume = {101},
       number = {11},
          eid = {110402},
        pages = {110402},
          doi = {10.1103/PhysRevLett.101.110402},
archivePrefix = {arXiv},
       eprint = {0709.2425},
 primaryClass = {quant-ph},
       adsurl = {https://ui.adsabs.harvard.edu/abs/2008PhRvL.101k0402R}
}
@ARTICLE{BEC2,
       author = {{Rodr{\'\i}guez-Laguna}, Javier and {Tarruell}, Leticia and {Lewenstein}, Maciej and {Celi}, Alessio},
        title = "{Synthetic Unruh effect in cold atoms}",
      journal = {\PR A},
     keywords = {Condensed Matter - Quantum Gases, General Relativity and Quantum Cosmology, High Energy Physics - Theory, Quantum Physics},
         year = 2017,
        month = jan,
       volume = {95},
       number = {1},
          eid = {013627},
        pages = {013627},
          doi = {10.1103/PhysRevA.95.013627},
archivePrefix = {arXiv},
       eprint = {1606.09505},
 primaryClass = {cond-mat.quant-gas},
       adsurl = {https://ui.adsabs.harvard.edu/abs/2017PhRvA..95a3627R},
      adsnote = {Provided by the SAO/NASA Astrophysics Data System}
}
@ARTICLE{BEC3,
       author = {{Kosior}, Arkadiusz and {Lewenstein}, Maciej and {Celi}, Alessio},
        title = "{Unruh effect for interacting particles with ultracold atoms}",
      journal = {SciPost Physics},
     keywords = {Condensed Matter - Quantum Gases, General Relativity and Quantum Cosmology, High Energy Physics - Theory, Quantum Physics},
         year = 2018,
        month = dec,
       volume = {5},
       number = {6},
          eid = {061},
        pages = {061},
          doi = {10.21468/SciPostPhys.5.6.061},
archivePrefix = {arXiv},
       eprint = {1804.11323},
 primaryClass = {cond-mat.quant-gas},
       adsurl = {https://ui.adsabs.harvard.edu/abs/2018ScPP....5...61K},
      adsnote = {Provided by the SAO/NASA Astrophysics Data System}
}
@article{BellLeinaas,
title = {Electrons as accelerated thermometers},
journal = {Nuclear Physics B},
volume = {212},
number = {1},
pages = {131-150},
year = {1983},
issn = {0550-3213},
doi = {https://doi.org/10.1016/0550-3213(83)90601-6},
url = {https://www.sciencedirect.com/science/article/pii/0550321383906016},
author = {J.S. Bell and J.M. Leinaas},
abstract = {The possibility of using accelerated electrons to exhibit the quantum field theoretic relation between acceleration and temperature is considered. In principle, the depolarization of electrons in a magnetic field could be used to give temperature reading. The effect is examined for linearly accelerated electrons, but the result is that the relevant orders of magnitude are too small for real experiments in linear accelerators. For electrons in storage rings sufficiently large accelerations can be obtained, and the residual depolarization which has been found theoretically and experimentally is shown to be an effect closely related to the thermal effect of linearly accelerated electrons.}
}
@article{Hawking:1975vcx,
    author = "Hawking, S. W.",
    editor = "Gibbons, G. W. and Hawking, S. W.",
    title = "{Particle Creation by Black Holes}",
    doi = "10.1007/BF02345020",
    journal = "Commun. Math. Phys.",
    volume = "43",
    pages = "199--220",
    year = "1975",
    note = "[Erratum: Commun.Math.Phys. 46, 206 (1976)]"
}
@article{Parker:1969au,
    author = "Parker, Leonard",
    title = "{Quantized fields and particle creation in expanding universes. 1.}",
    doi = "10.1103/PhysRev.183.1057",
    journal = "Phys. Rev.",
    volume = "183",
    pages = "1057--1068",
    year = "1969"
}
@book{Mukhanov:2007zz,
    author = "Mukhanov, Viatcheslav and Winitzki, Sergei",
    title = "{Introduction to quantum effects in gravity}",
    isbn = "978-0-521-86834-1, 978-1-139-78594-5",
    publisher = "Cambridge University Press",
    month = "6",
    year = "2007"
}
@article{Letaw,
  title = {Stationary world lines and the vacuum excitation of noninertial detectors},
  author = {Letaw, John R.},
  journal = {Phys. Rev. D},
  volume = {23},
  issue = {8},
  pages = {1709--1714},
  numpages = {0},
  year = {1981},
  month = {Apr},
  publisher = {American Physical Society},
  doi = {10.1103/PhysRevD.23.1709},
  url = {https://link.aps.org/doi/10.1103/PhysRevD.23.1709}
}
@article{Korsbakken:2004bv,
    author = "Korsbakken, Jan Ivar and Leinaas, Jon Magne",
    title = "{The Fulling-Unruh effect in general stationary accelerated frames}",
    eprint = "hep-th/0406080",
    archivePrefix = "arXiv",
    reportNumber = "OSLO-TP-1-04",
    doi = "10.1103/PhysRevD.70.084016",
    journal = "Phys. Rev. D",
    volume = "70",
    pages = "084016",
    year = "2004"
}
@article{LetawPfautsch,
  title = {Quantized scalar field in rotating coordinates},
  author = {Letaw, John R. and Pfautsch, Jonathan D.},
  journal = {Phys. Rev. D},
  volume = {22},
  issue = {6},
  pages = {1345--1351},
  numpages = {0},
  year = {1980},
  month = {Sep},
  publisher = {American Physical Society},
  doi = {10.1103/PhysRevD.22.1345},
  url = {https://link.aps.org/doi/10.1103/PhysRevD.22.1345}
}
@article{Good:2020hav,
    author = "Good, Michael and Ju\'arez-Aubry, Benito A. and Moustos, Dimitris and Temirkhan, Maksat",
    title = "{Unruh-like effects: Effective temperatures along stationary worldlines}",
    eprint = "2004.08225",
    archivePrefix = "arXiv",
    primaryClass = "gr-qc",
    doi = "10.1007/JHEP06(2020)059",
    journal = "JHEP",
    volume = "06",
    pages = "059",
    year = "2020"
}
@incollection{DeWitt:1980hx,
    author = "DeWitt, Bryce S.",
    title = "{Quantum Gravity: The New Synthesis}",
    booktitle = "{General Relativity}: {An Einstein Centenary Survey}",
    editor = "Hawking, S. W. and Israel, W.",
    address = "Cambridge", 
    pages = "680--745",
    year = "1979", 
    publisher = "Cambridge University Press"
}
@article{Lin:2006jw,
    author = "Lin, Shih-Yuin and Hu, B. L.",
    title = "{Backreaction and the Unruh effect: New insights from exact solutions of uniformly accelerated detectors}",
    eprint = "gr-qc/0611062",
    archivePrefix = "arXiv",
    doi = "10.1103/PhysRevD.76.064008",
    journal = "Phys. Rev. D",
    volume = "76",
    pages = "064008",
    year = "2007"
}

@misc{Weinfurther-private-2023,
  author       = "{Weinfurtner, S}",
  howpublished = "private communication",
  year         = 2022,
}
