\section{Introduction}\label{sec:intro}
Grasping unknown objects from a cluttered environment is a fundamental problem for autonomous robotic manipulation, arising in a wide range of applications such as industrial automation (e.g., bin-picking, quality inspection, and warehouse automation), commercial places (e.g., book picking or placing in a library and healthcare) and household (e.g., folding laundry, playing billiards, and fetching a beer in a refrigerator). Despite the exciting progress in pose prediction and object manipulation for parallel-jaw grippers~\cite{DBLP:conf/cvpr/FangWGL20,jiang2011efficient,DBLP:journals/ijrr/PasGSP17,DBLP:conf/iccv/MousavianEF19,DBLP:conf/icra/MuraliMEPF20,DBLP:conf/icra/SundermeyerMTF21}, robotic grasping for multi-finger hands with high DoFs remains challenging. Parallel-jaw grippers have relatively low complexity in manipulation due to their one DoF structure. However, their structures also limit their deployment in more complicated scenarios with relatively big, irregular, or spherical objects.

Unlike parallel-jaw grippers, multi-finger dexterous hands significantly improve adaptability for object shapes due to higher DoFs and flexibility.
However, the difficulties in finding valid hand configurations and grasp poses for multi-finger robotic hands are greatly increased due to high-dimensional search space and discontinuous grasp space~\cite{ciocarlie2007dexterous,DBLP:conf/rss/LiuP0GM20,DBLP:conf/iros/HangSK14}.


To handle these issues, previous work for multi-finger grasping can be divided into two categories.
\emph{Traditional analytical methods}~\cite{ciocarlie2007dexterous,DBLP:conf/icra/GoldfederALP07,DBLP:conf/iros/HangSK14,DBLP:conf/icra/MillerKCA03,DBLP:conf/icra/PelossofMAJ04} explore the potential grasping space through stochastic search and sampling.
These algorithms are often computationally expensive, typically requiring tens or even hundreds of iterations per object. Moreover, they heavily rely on precise object representation, thus not applicable to unknown objects in a cluttered environment.
\emph{Data-driven approaches} have attracted attention in recent years.
%
Lu~\etal proposed a grasp planner and grasp evaluator based on an efficient deep neural network~\cite{DBLP:conf/iros/BrahmbhattHHF19}. This work still assumes the object models are known.
%
Lundell~\etal proposed a coarse-to-fine model to predict grasps~\cite{DBLP:conf/icra/LundellCLVWRMK21}. This work targets a single object instead of many objects in a cluttered environment.
Li \etal presented an end-to-end network~\cite{DBLP:conf/icra/LiWL0LZ22} that can predict grasp poses and configurations. It simply discretizes and classifies multi-finger hand configurations manually.
%


In this paper, we propose a novel approach to grasp unknown objects in a cluttered environment. Our contribution includes:
\begin{itemize}
\item A new grasp representation that projects 10-DoFs grasps to only 6-DoFs based on contact points. This significantly reduces the potential grasping search space, facilitates the process of learning and improves the grasping quality.
\item Based on this novel representation, we propose an end-to-end deep neural network, CMG-Net, which outputs multi-finger hand configurations and grasp poses for an input single-shot viewpoint in a cluttered scene.
\item To demonstrate the benefits using CMG-Net, we build a synthetic grasping dataset, consisting of 5000 cluttered scenes with 80 object classes and 20 million grasp annotations (i.e., hand poses and hand configurations).
\item Our experimental results show that CMG-Net outperforms the state-of-the-art in terms of both grasping success rate and grasping quality. Moreover, we also demonstrate that CMG-Net works very well for robotic grasping in a real-world environment.
\end{itemize}

