\pdfoutput=1
\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage[accsupp]{axessibility}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{float}
\usepackage{cuted}
\usepackage{capt-of}
\usepackage{multirow}
\usepackage{bbding}

\usepackage[pagebackref,breaklinks,colorlinks]{hyperref}

\usepackage[capitalize]{cleveref}


\crefname{section}{Sec.}{Secs.}
\Crefname{section}{Section}{Sections}
\Crefname{table}{Table}{Tables}
\crefname{table}{Tab.}{Tabs.}

\def\ie{\emph{i.e.}}
\def\etal{{\em et al.}}

\newcommand{\sota}{state-of-the-art}
\newcommand{\forwardwarp}{\overrightarrow{\mathcal{W}}}
\newcommand{\backwardwarp}{\overleftarrow{\mathcal{W}}}
\newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}

\def\cvprPaperID{1448}
\def\confName{CVPR}
\def\confYear{2023}

\begin{document}
\title{A Dynamic Multi-Scale Voxel Flow Network for Video Prediction}
\author{Xiaotao Hu$^{1,2}$
		~~~~
		Zhewei Huang$^{2}$
        ~~~~
		Ailin Huang$^{2,3}$
        ~~~~
            Jun Xu$^{4,}$\thanks{Corresponding authors.}
        ~~~~
            Shuchang Zhou$^{2,}$\samethanks{}\\
		$^{1}$College of Computer Science, Nankai University~~~~$^{2}$Megvii Technology\\ $^{3}$Wuhan University~~~~
        $^{4}$School of Statistics and Data Science, Nankai University\\
		{\tt\small \{huxiaotao, huangzhewei, huangailin, zhoushuchang\}@megvii.com}\tt\small, nankaimathxujun@gmail.com\\
  \url{https://huxiaotaostasy.github.io/DMVFN/}
	}
	\maketitle
 
%%%%%%%%% ABSTRACT
\begin{abstract}
The performance of video prediction has been greatly boosted by advanced deep neural networks.
%
However, most of the current methods suffer from large model sizes and require extra inputs, \eg, semantic/depth maps, for promising performance.
% 
For efficiency consideration, in this paper, we propose a Dynamic Multi-scale Voxel Flow Network (DMVFN) to achieve better video prediction performance at lower computational costs with only RGB images, than previous methods.
%
The core of our DMVFN is a differentiable routing module that can effectively perceive the motion scales of video frames.
% 
Once trained, our DMVFN selects adaptive sub-networks for different inputs at the inference stage.
%
Experiments on several benchmarks demonstrate that our DMVFN is an order of magnitude faster than Deep Voxel Flow~\cite{dvf} and surpasses the state-of-the-art iterative-based OPT~\cite{wu2022optimizing} on generated image quality.
%
% 
	\end{abstract}
	%%%%%%%%% BODY TEXT
	\input{chapter/introduction}
	\input{chapter/relatedwork}
	\input{chapter/method}
	\input{chapter/exp}
	\input{chapter/conclution}
        \clearpage
	{\small
		\bibliographystyle{ieee_fullname}    
		\bibliography{egbib}
	}
        \clearpage
        \onecolumn
        \input{chapter/appendix}
	\clearpage
\end{document}
