\subsection{Proof of \Cref{thm:nonobv_pga_bound}}\label{apx:nonobv-proof}
In this section, we demonstrate how to adapt the PGA bound in \cref{thm:pga_bound} to the Boosted PGA setting. For the proof we use the slightly more general form of the non-oblivious function in \cite{zhang2022stochastic} which also works for weakly submodular functions with parameter $\gamma$:
\begin{align}
    F'(\x) := \int_0^1 \frac{e^{\gamma(s-1)}}{s}F(s*\x) ds \\
    \nabla F'(\x) := \int_0^1 e^{\gamma(s-1)}F(s*\x) ds
\end{align}
The noisy gradient estimate of this auxiliary function is now:
\begin{align}\label{eq:nonobv-noisy}
    \nabla \tilde{F}'(\x_t) := \frac{1-e^{-\gamma}}{\gamma}\nabla \tilde{F}(s_t*\x_t).
\end{align}
Here $s_t$ is independently sampled from a distribution with cdf: $\mathbb{P}(\pmb{S}\leq s) = \int_0^s \frac{\gamma^{\gamma(u-1)}}{1-e^{-\gamma}} \mathds{1}(u\in[0,1])du$, where $\mathds{1}$ is the indicator function.\\
We now begin with a slightly stricter version of proposition 1 from \cite{zhang2022stochastic}.

\begin{lemma}[Proposition 1, Zhang et al. 2022]\label{prop:nonobv-martingale}
If $z_t$ is sampled according to the distribution in Eq. \eqref{eq:nonobv-noisy}, then given Assumptions \ref{ass:x_bound},\ref{ass:g_lip},\ref{ass:g_bound} are satisfied (i.e. Lipschitz-smooth function along with bounded domain and gradient noise), we have
\begin{align}
    \mathbb{E}\left(\frac{1-e^{-\gamma}}{\gamma}\nabla \tilde{F}(s_t*\x_t)\right) = \nabla F'(\x) \\
    \norm{\nabla F'(\x) - \nabla \tilde{F}'(\x)}^2 \leq M_{\gamma}^2
\end{align}
where $M_\gamma := (M+2 LD)\left(\frac{1-e^{-\gamma}}{\gamma}\right)$.
\end{lemma}
The first equality statement is unchanged from the original proposition, while the second inequality is modified to bound the squared norm error instead of the variance. We provide a short proof of the second inequality below:
\begin{proof}

\begin{align}
    \norm{\nabla F'(\x) - \nabla \tilde{F}'(\x)} &\leq \norm{\frac{1-e^{-\gamma}}{\gamma}(\nabla \tilde{F}(z*\x)- \nabla F(z*\x))} + \norm{\frac{1-e^{-\gamma}}{\gamma}\nabla F(z*\x) - \nabla F'(x)} \nonumber \\
    & \leq \left(\frac{1-e^{-\gamma}}{\gamma}\right) M + \norm{\frac{1-e^{-\gamma}}{\gamma}\nabla F(z*\x) - \nabla F'(x)}
\end{align}
We use the definition of $\nabla \tilde{F}'(\x)$, as well as the triangle inequality in the first step. In the second step, we use the assumption that the noise of our gradient oracle is bounded by $M$. Finally to bound the second term:
\begin{align}
    \norm{\frac{1-e^{-\gamma}}{\gamma}\nabla F(z*\x) - \nabla F'(x))} &= \norm{\int_0^1 e^{\gamma(u-1)}(\nabla F(z*\x)-\nabla F(u*\x) du} \nonumber \\
    &\leq \left(\int_0^1 e^{\gamma(u-1)}|z-u| L \norm{\x}|\right) \nonumber \\
    &\leq 2LD\left(\int_0^1 e^{\gamma(u-1)}du\right) = 2LD\left(\frac{1-e^{-\gamma}}{\gamma}\right)
\end{align}
We use the Lipschitz smoothness constraint and Cauchy-Schwarz in the first inequality, and $|z-u|<2$ in the second. 
\end{proof}
Now equipped with Lemma \ref{prop:nonobv-martingale}, we can proceed using the same proof structure as in Theorem \ref{thm:pga_bound}:
\begin{proof}
 Starting from $\langle \y-\x, \nabla F'(\x)\rangle \geq (1-e^{-\gamma})F(\y)-F(\x)$ evaluated at $\y=\x^*$, we can show using steps analogous to \cref{eq:proof1-step1,eq:proof1-step2,eq:proof1-step3} the following inequality:
 \begin{align}
     (1-e^{-\gamma})F(\y)-F(\x) &\leq \frac{\eta_t}{2}\norm{\nabla\tilde{F}'(\x_t)}^2 + \frac{1}{2\eta_t} \left(\norm{\x_t-\x^*}^2 - \norm{\x_{t+1}-\x^*}^2 \right) - \langle \x^*-\x_t,\nabla\tilde{F}'(\x_t)- \nabla F'(\x_t)\rangle \nonumber \\
     &\leq \frac{\eta_t}{2}(L_\gamma D + M_\gamma)^2 + \frac{1}{2\eta_t} \left(\norm{\x_t-\x^*}^2 - \norm{\x_{t+1}-\x^*}^2 \right) - \langle \x^*-\x_t,\nabla\tilde{F}'(\x_t)- \nabla F'(\x_t)\rangle 
 \end{align}
 From \cite{zhang2022stochastic} we know that $F'$ is $L_\gamma$-smooth with $L_\gamma = L \frac{\gamma+e^{-\gamma}-1}{\gamma^2}$, giving us the second inequality above. Using $\eta_t = 1/\sqrt{t}$ and applying the bound iteratively produces the parallel equation to \cref{eq:proof1-combine-step}:
 \begin{align}
     (1-e^{-\gamma})OPT-\frac{1}{T}F(\x_t) \leq \frac{1}{\sqrt{T}}(L_\gamma D + M_\gamma)^2 + \frac{\norm{\x^*-\x_1}^2}{8\sqrt{T}} + \frac{1}{2T}\sum_{t=1}^T \langle \x^*-\x_t,\nabla\tilde{F}'(\x_t)- \nabla F'(\x_t)\rangle
 \end{align}
From Lemma \ref{prop:nonobv-martingale} we can treat the summation of $\langle \x^*-\x_t,\nabla\tilde{F}'(\x_t)- \nabla F'(\x_t)\rangle$ terms as a c-lipschitz Martingale with constant:
\begin{equation}
    |\langle \x^*-\x_t,\nabla\tilde{F}'(\x_t)- \nabla F'(\x_t)\rangle| \leq \norm{\x^*-\x_t}\norm{\nabla\tilde{F}'(\x_t)- \nabla F'(\x_t)} \leq DM_{\gamma} =: c
\end{equation}
Therefore, the analogous bound to \cref{thm:pga_bound} for non-oblivious PGA is:
\begin{equation}
    (1-e^{-\gamma})OPT-\frac{1}{T}F(\x_t) \leq \frac{1}{\sqrt{T}} \left(\frac{8(L_\gamma D + M_\gamma)^2+D^2}{8}\right) + \sqrt{\frac{\log(\frac{1}{\delta})}{2T}}DM_\gamma
\end{equation}
 With probability $p>1-\delta$. By substituting $\gamma=1$, we recover the bound for the fully submodular setting.
 
\end{proof}
