\pdfoutput=1
%
%
\documentclass[sigconf]{acmart}
%
%
%
%
%
%
\settopmatter{printacmref=true}
%
%
%
%
%
%
%


%
\newif\ifshortVersion
\shortVersionfalse %
%

\usepackage{xr}

%
\ifshortVersion
    \externaldocument{appendices}
\fi

\newcommand{\appendixRef}[1]{%
  \hspace{1sp}%
  \ifshortVersion%
    \cite[#1]{full-version}%
  \else%
    {#1}%
  \fi%
}

%
%
%
%
%
%
%
%

%
%
%
%
%


\copyrightyear{2024}
\acmYear{2024}
\setcopyright{acmlicensed}\acmConference[CCS '24]{Proceedings of the 2024 ACM SIGSAC Conference on Computer and Communications Security}{October 14--18, 2024}{Salt Lake City, UT, USA}
\acmBooktitle{Proceedings of the 2024 ACM SIGSAC Conference on Computer and Communications Security (CCS '24), October 14--18, 2024, Salt Lake City, UT, USA}
\acmDOI{10.1145/3658644.3670347}
\acmISBN{979-8-4007-0636-3/24/10}



\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10002978.10003006.10003013</concept_id>
       <concept_desc>Security and privacy~Distributed systems security</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
 </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Security and privacy~Distributed systems security}


\usepackage{import}
\import{./lib/}{boilerplate_pdflatex.tex}
\import{./lib/}{colors.tex}
\import{./lib/}{tikzpgfplot.tex}
\import{./lib/}{tikzpgfplot_parulalinestyles.tex}
\import{./lib/}{tikzpgfplot_plotstyles.tex}
\import{./lib/}{tikzpgfplot_blockchainstructures.tex}
\import{./lib/}{tables.tex}
\import{./lib/}{algorithms.tex}
%
\import{./lib/}{lateplate_pdflatex.tex}

\usepackage{color}
\renewcommand\UrlFont{\color{blue}\rmfamily}

\input{custom_commands}



%

%
%
%
%
%





%
%
%
%
%
%
%


%
%
%
%
%
%
%
%
%
%
%
%
%
%


%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
\title[Nakamoto Consensus under Bounded Processing Capacity]{Nakamoto Consensus under Bounded Processing Capacity}
%



%
%

%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%



\author{Lucianna Kiffer}
\orcid{0000-0003-2022-7993}
\affiliation{%
    \institution{ETH Z\"urich}%
    \city{Zurich}%
    \country{Switzerland}%
}
\email{lkiffer@ethz.ch}
%
\author{Joachim Neu}
\orcid{0000-0002-9777-6168}
\affiliation{%
    \institution{Stanford University}%
    \city{Stanford}%
    \state{CA}%
    \country{USA}%
}
\email{jneu@stanford.edu}
%
\author{Srivatsan Sridhar}
\orcid{0000-0002-1880-570X}
\affiliation{%
    \institution{Stanford University}%
    \city{Stanford}%
    \state{CA}%
    \country{USA}%
}
\email{svatsan@stanford.edu}
%
\author{Aviv Zohar}
\orcid{0000-0001-8539-9222}
\affiliation{%
    \institution{The Hebrew University}%
    \city{Jerusalem}%
    \country{Israel}%
}
\email{avivz@cs.huji.ac.il}
%
\author{David Tse}
\orcid{0000-0003-1460-5900}
\affiliation{%
    \institution{Stanford University}%
    \city{Stanford}%
    \state{CA}%
    \country{USA}%
}
\email{dntse@stanford.edu}

\thanks{LK, JN, SS and AZ are listed alphabetically.
\ifshortVersion%
    Full version with appendices: \cite{full-version}%
\fi}


%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%


%
\newcommand{\gitSourceUrl}[0]{\url{https://github.com/avivz/finitebwlc}}
%

%
%

%


%
\makeatletter
\def\ps@headings{%
\def\@oddhead{\mbox{}\scriptsize\rightmark \hfil \thepage}%
\def\@evenhead{\scriptsize\thepage \hfil \leftmark\mbox{}}}
\makeatother
\pagestyle{headings}



%
%
%
%

%
%

%
%
%
%

%
%
%

%
%
%
%
%


%
%

%
\setcounter{secnumdepth}{3}
\renewcommand\thesubsubsection{\thesubsection.\arabic{subsubsection}}
\crefname{section}{Sec.}{Secs.}
\Crefname{section}{Sec.}{Secs.}
\crefname{appendix}{App.}{Apps.}
\Crefname{appendix}{App.}{Apps.}
\crefname{subsection}{Sec.}{Secs.}
\Crefname{subsection}{Sec.}{Secs.}
\crefname{subappendix}{App.}{Apps.}
\Crefname{subappendix}{App.}{Apps.}
\crefname{subsubsection}{Sec.}{Secs.}
\Crefname{subsubsection}{Sec.}{Secs.}
\crefname{subsubappendix}{App.}{Apps.}
\Crefname{subsubappendix}{App.}{Apps.}
\crefname{subsubsubsection}{Sec.}{Secs.}
\Crefname{subsubsubsection}{Sec.}{Secs.}
\crefname{subsubsubappendix}{App.}{Apps.}
\Crefname{subsubsubappendix}{App.}{Apps.}

%
\newcommand{\myparagraph}[1]{\smallskip\noindent\textbf{#1.}~~}

%
%
%
%
%
%
%
%
%
%
%
%
%
%
%

%
%
%
%
%

%
%
%

%
\setcounter{tocdepth}{4}

%
\usepackage{thmtools}

%
\newcommand\blfootnote[1]{%
  \begingroup%
  \renewcommand\thefootnote{}\footnote{#1}%
  \addtocounter{footnote}{-1}%
  \endgroup%
}




\begin{document}
%
\begin{abstract}
    For Nakamoto's longest-chain consensus protocol, whose proof-of-work (PoW) and proof-of-stake (PoS) variants power major blockchains such as Bitcoin and Cardano, we revisit the classic problem of the security--performance tradeoff:
    Given a network of nodes with finite 
    communication- and computation-resources, against what fraction of adversary power is Nakamoto consensus (NC) secure for a given block production rate?
    %
    State-of-the-art analyses of NC fail to answer this question, because their \emph{bounded-delay} model does not capture the rate limits to nodes' processing of blocks, which cause congestion when blocks are released in quick succession.
    %
    We develop a new analysis technique to prove a refined security--performance tradeoff for PoW NC in a \emph{bounded-capacity} model.
    In this model, we show that, in contrast to the classic bounded-delay model, Nakamoto's private attack is no longer the worst attack, and a new attack we call the \emph{\teaserattack}, that exploits congestion, is strictly worse.
    %
    In PoS, equivocating blocks can exacerbate congestion, making  traditional PoS NC insecure except at very low block production rates.
    To counter such equivocation spamming, we present a variant of PoS NC we call \emph{\ProtMid} (\emph{\ProtShort}), which achieves the \emph{same resilience} as PoW NC.
\end{abstract}
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%



\keywords{Nakamoto; consensus; blockchain; capacity; bandwidth; spamming.}


\maketitle
%
%
%
%
%

\input{01_introduction.tex}
\input{02_attacks.tex}
\input{03_modelprotocol.tex}
\input{04_analysis_00.tex}
\input{05_pos_blanc.tex}
\input{05b_pos_predictable_validity.tex}
\input{06_outlook.tex}


\section*{Acknowledgment}
%
We thank
%
Lei Yang, Mohammad Alizadeh,
Sundararajan Renganathan, David Mazières,
Ertem Nusret Tas,
Ghassan Karame,
Florian Tschorsch,
and
George Danezis
for fruitful discussions.
The work of LK, JN, and AZ
was conducted in part
during Dagstuhl Seminar \#22421.
LK is supported by the
armasuisse Science and Technology CYD Distinguished Postdoctoral Fellowship.
JN is supported by the Protocol Labs PhD Fellowship.
JN and SS are supported by a gift from
the Ethereum Foundation and by a research hub funded by Input Output Global Inc.
SS is suported by NSF grant CCF-1563098.
AZ is supported by grant \#1443/21 from the Israel Science Foundation.
%


%
%
%

%
%

%
%
\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

\ifshortVersion
    \appendix
    
    \section*{Appendices}
    Full version with appendices: \cite{full-version}.

    \nocite{doi:10.1080/01621459.1963.10500830,duchi-hoeffding,stackexchange-math-rwreturnto0,poisson_tail}
\else
    \nocite{full-version}
    \input{appendices.tex}
\fi

%
%
%


%
%
%
%



%

%
%
%
%
%
%
%
%
%


\end{document}
