\abstract{Emerging events, such as the COVID pandemic and the Ukraine Crisis, require a time-sensitive comprehensive understanding of the situation to allow for appropriate decision-making and effective action response. Automated generation of situation reports can significantly reduce the time, effort, and cost for domain experts when preparing their official human-curated reports. However, AI research toward this goal has been very limited, and no successful trials have yet been conducted to automate such report generation. %Since
Pre-existing natural language processing methods, large language model based text generation, and information retrieval techniques are insufficient to identify, locate, and summarize important information,
% for generating good-quality intelligence reports, 
and lack detailed, structured, and strategic awareness. 
We propose \textbf{SmartBook}, a novel task formulation targeting situation report generation, which consumes large volumes of news data to produce a structured situation report with multiple hypotheses (claims) summarized and grounded with rich links to factual evidence. %\heng{elaborate a little more on why our framework is innovative and better, there are other reasons: our data sources are in multilingual multimedia, we construct claim-claim networks, each claim is associated with knowledge elements.}
We realize SmartBook for the Ukraine-Russia crisis by automatically generating intelligence analysis reports to assist expert analysts. The machine-generated reports are structured in the form of timelines, with each timeline organized by major events (or chapters), corresponding strategic questions (or sections) and their grounded summaries (or section content).
%\heng{I remember Brad only deleted 2\% tokens, which means the information in our output is highly accurate. Maybe we should mention that in the result summary.}
% performs claim summarization and event prediction,  based on expert-provided or automatically generated topic queries. 
%We further develop evaluation metrics to benchmark the situation report generation task, including human expert edit distance and time efficiency comparisons. 
 Our proposed framework automatically detects real-time event-related strategic questions, which are more directed than manually-crafted analyst questions, which tend to be too complex, hard to parse, vague and high-level. 
Results from thorough qualitative evaluations show that %intelligence analysts find 
roughly 82\% of the questions in Smartbook have strategic importance, with at least 93\% of the sections in the report being tactically useful.
%Further, SmartBook outperforms a web search $+$ large language model based generation approach by up to 9\% in terms of relevance and strategicness of information presented. 
Further, experiments show that expert analysts tend to add more information into the SmartBook reports, with only 2.3\% of the existing tokens being deleted, meaning SmartBook can serve as a useful foundation for analysts to build upon when creating intelligence reports.}\footnote{We deeply regret that one of our project contributors, Paul, passed away before the publication of this paper. His contributions to this research were invaluable, and the loss is felt deeply by all of us who had the privilege of working with him. We honor the memory and express our gratitude for his enduring commitment to the pursuit of knowledge.}
%Results show that the token overlap between generated and post-edited summaries is high, with a BLEU score of 59.0\% and a Rouge-2 score of 74.1\%.
%\heng{TODO: update results summary}
