
\begin{abstract}
Current point cloud segmentation architectures suffer from limited long-range feature modeling, as they mostly rely on aggregating information with local neighborhoods.
%
Furthermore, in order to learn point features at multiple scales, most methods utilize a data-agnostic sampling approach to decrease the number of points after each stage. Such sampling methods, however, often discard points for small objects in the early stages, leading to inadequate feature learning.
%
We believe these issues can be mitigated by introducing explicit geometry clues as guidance.
% 
To this end, we propose \textbf{GeoSpark}, a Plug-in module that incorporates \textbf{Geo}metry clue into the network to \textbf{Spark} up feature learning and downsampling. GeoSpark can be easily integrated into various backbones. For feature aggregation, it improves feature modeling by allowing the network to learn from both local points and neighboring geometry partitions, resulting in an enlarged data-tailored receptive field. Additionally, GeoSpark utilizes geometry partition information to guide the downsampling process, where points with unique features are preserved while redundant points are fused, resulting in better preservation of key points throughout the network. 
We observed consistent improvements after adding GeoSpark to various backbones including PointNet++, KPConv, and PointTransformer. Notably, when integrated with Point Transformer, our GeoSpark module achieves a 74.7\% mIoU on the ScanNetv2 dataset (4.1\% improvement) and 71.5\% mIoU on the S3DIS Area 5 dataset (1.1\% improvement), ranking top on both benchmarks. 
%
Code and models will be made publicly available.
\end{abstract}

