\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{amsthm}
\usepackage{xcolor}
\usepackage{bbding}
\usepackage{makecell}
\usepackage{algorithm}  
\usepackage{color}
\usepackage{multirow}
\usepackage{bm}
\usepackage{array}
\usepackage{booktabs}
\usepackage{tabularx,booktabs}
\usepackage{multicol}
\usepackage{cleveref}
\usepackage{balance}
\usepackage{lastpage}
\usepackage{tabulary}
\usepackage{subfigure}
\usepackage{etoolbox}
\usepackage{bbm}
\usepackage{enumitem}
\usepackage{mathrsfs}
\setlength{\columnwidth}{6.5in}
\usepackage{multicol}
\usepackage{amsfonts,amssymb}
\usepackage{ulem}
\usepackage{cancel}
\usepackage{setspace}
\usepackage{stackengine}
\usepackage{threeparttable}
\newcommand\xrowht[2][0]{\addstackgap[.5\dimexpr#2\relax]{\vphantom{#1}}}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

\usepackage{amsthm}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{theo}{Theorem}
\renewcommand{\proofname}{\textbf{Proof}}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
    \newcommand{\notered}[1]{\textcolor{red}{[{\bf #1}]}}
        \newcommand{\red}[1]{\textcolor{red}{[{#1}}]}
\newcommand{\noteorange}[1]{\textcolor{orange}{[{\bf #1}]}}
\newcommand{\noteblue}[1]{\textcolor{blue}{[{\bf #1}]}}
\newcommand{\blue}[1]{\textcolor{blue}{#1}}
\newcommand{\orange}[1]{\textcolor{orange}{ #1}}
\newcommand{\notegreen}[1]{\textcolor{green}{[{\bf #1}]}}
\newcommand{\cyan}[1]{\textcolor{cyan}{{ #1}}}

\newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}

%\pagestyle{plain}

\begin{document}

\bstctlcite{IEEEexample:BSTcontrol}

\title{%A Comprehensive Tutorial on Optimization Techniques for RIS-aided Future Wireless Communications: Model-based, Heuristic and Machine Learning Approaches\\
A Survey on Model-based, Heuristic, and Machine Learning Optimization Approaches in RIS-aided Wireless Networks\\
\thanks{
This work was supported in part by the Natural Sciences and Engineering Research Council of Canada (NSERC) Canadian Collaborative Research and Training Experience Program (CREATE) under Grant 497981, the Canada Research Chairs Program, and the U.S National Science Foundation under Grants CCF-1908308 and CNS-2128448.

H. Zhou and M. Erol-Kantarci are with the School of Electrical Engineering and Computer Science, University of Ottawa, Ottawa, ON K1N 6N5, Canada. (emails:\{hzhou098, melike.erolkantarci\}@uottawa.ca).

Yuanwei Liu are with the School of Electronic Engineering and Computer Science, Queen Mary University of London, London E1 4NS, U.K. (email:yuanwei.liu@qmul.ac.uk).

H. Vincent Poor is with the Department of Electrical and Computer Engineering,
Princeton University, Princeton, NJ 08544 USA (e-mail: poor@princeton.edu).} 

}

\author{\IEEEauthorblockN{Hao Zhou, Melike Erol-Kantarci, \IEEEmembership{Senior Member, IEEE}, Yuanwei Liu, \IEEEmembership{Senior Member, IEEE},\\ and H. Vincent Poor, \IEEEmembership{Life Fellow, IEEE}} }

\maketitle

\begin{abstract}
Reconfigurable intelligent surfaces (RISs) have received considerable attention as a key enabler for envisioned 6G networks, for the purpose of improving the network capacity, coverage, efficiency, and security with low energy consumption and low hardware cost. However, integrating RISs into the existing infrastructure greatly increases the network management complexity, especially for controlling a significant number of RIS elements. To unleash the full potential of RISs, efficient optimization approaches are of great importance. 
This work provides a comprehensive survey on optimization techniques for RIS-aided wireless communications, including model-based, heuristic, and machine learning (ML) algorithms. 
In particular, we first summarize the problem formulations in the literature with diverse objectives and constraints, e.g., sum-rate maximization, power minimization, and imperfect channel state information constraints. 
Then, we introduce model-based algorithms that have been used in the literature, such as alternating optimization, the majorization-minimization method, and successive convex approximation. Next, heuristic optimization is discussed, which applies heuristic rules for obtaining low-complexity solutions. Moreover, we present state-of-the-art ML algorithms and applications towards RISs, i.e., supervised and unsupervised learning, reinforcement learning, federated learning, graph learning, transfer learning, and hierarchical learning-based approaches. Model-based, heuristic, and ML approaches are compared in terms of stability, robustness, optimality and so on, providing a systematic understanding of these techniques. 
Finally, we highlight RIS-aided applications towards 6G networks and identify future challenges.   
\end{abstract}

\begin{IEEEkeywords}
Reconfigurable intelligent surfaces, optimization, model-based methods, heuristics, machine learning.
\end{IEEEkeywords}

\input{1_Introduction}
\input{2_RelatedWork}
\input{3_Background}
%\input{4_Channel}
\input{5_Model_based}
\input{5_Heuristic_based}
\input{6_Machine_learning}
\input{7_Applications_and_Challenges}
\input{8_Conclusion}
%\red{The ref papers have been checked and revised, including "Proc. " for conference papers, abbreviations for journal names, capitalization in titles, and so on.}


\normalem
\bibliographystyle{IEEEtran}
\bibliography{Reference}

\end{document}
