As hospitals move towards automating and integrating their computing systems, more fine-grained hospital operations data are becoming available.
These data include hospital architectural drawings, logs of interactions between patients and healthcare professionals, prescription data, procedures data, and data on patient admission, discharge, and transfers.
This has opened up many fascinating avenues for healthcare-related prediction tasks for improving patient care. 
However, in order to leverage off-the-shelf machine learning software for these tasks, one needs to learn structured representations of entities involved from heterogeneous, dynamic data streams.
Here, we propose \ourmethod, 
an auto-encoding heterogeneous co-evolving dynamic neural network,
% a novel approach 
for learning heterogeneous dynamic embeddings of patients, doctors, rooms, and medications from diverse data streams.
These embeddings capture similarities among doctors, rooms, patients, and medications based on static attributes and dynamic interactions.

\ourmethod enables several applications in healthcare prediction, such as 
predicting mortality risk and case severity of patients,
adverse events (e.g., transfer back into an intensive care unit),
and future healthcare-associated infections.
The results of using the learned patient embeddings in predictive modeling show that \ourmethod has a gain of
up to 48.1\% on the mortality risk prediction task,
12.6\% on the case severity prediction task,
6.4\% on the medical intensive care unit transfer task, 
and 3.8\% on the Clostridioides difficile (C.diff) Infection (CDI) prediction task
over the state-of-the-art baselines.
In addition, case studies on the learned doctor, medication, and room embeddings show that our approach learns meaningful and interpretable embeddings.

\begin{comment}
Representing patients based on their visits to hospitals is gaining attention recently because the representation learning can automate the feature engineering process by expressing the patients' medical information into lower-dimensional vectors.
We propose HIDEP, an approach that learns latent representations of patients, doctors, medications, and hospital rooms based on their visits.
HIDEP considers the longitudinal patients' inpatient visit records, including the patients' assigned physicians, procedures performed by the physician, patients' medication prescriptions, and patients' room transfer records.
These interactions are modeled as patients' dynamic trajectories and learned embeddings contain all the historical interactions.
We evaluate the learned patient embeddings by predicting severity, mortality, and Clostridioides difficile (C.diff) Infection (CDI) in patients' future visits with classifications.
Our results show that ... 
\end{comment}
