% \newpage

\vsacle
\begin{IEEEbiographynophoto}{Ziheng Chen}
received the B.A. degree in logistics
management from Shandong University, Jinan, China, and M.S. degree in computer science and technology from Jiangnan University, Wuxi, China. He is currently working toward the Ph.D.
degree with the Multimedia and Human Understanding Group (MHUG), University of Trento, Trento, Italy. His research interests are machine learning, geometric deep learning, matrix manifolds, and matrix Lie groups.
\end{IEEEbiographynophoto}
\vsacle
\begin{IEEEbiographynophoto}{Yue Song}
received the B.Sc. cum
laude from KU Leuven, Belgium and the joint M.S.
summa cum laude from the University of Trento,
Italy and KTH Royal Institute of Technology, Sweden. He is currently working toward the Ph.D.
degree with the Multimedia and Human Understanding Group (MHUG), University of Trento, Trento,
Italy. His research interests are computer vision,
deep learning, and numerical analysis and
optimization.
\end{IEEEbiographynophoto}
\vsacle
\begin{IEEEbiographynophoto}{Tianyang Xu}
received the B.Sc. degree in electronic
science and engineering from Nanjing University,
Nanjing, China, in 2011. He received his Ph.D. degree
at the School of Artificial Intelligence and Computer Science, Jiangnan University, Wuxi, China, in
2019. He is currently an Associate Professor at the
School of Artificial Intelligence and Computer Science, Jiangnan University, Wuxi, China. His research
interests include visual tracking and deep learning.
\end{IEEEbiographynophoto}
\vsacle
\begin{IEEEbiographynophoto}{Zhiwu Huang}
received the B.Sc. degree in computer
science and technology from Huaqiao University,
Quanzhou, Fujian, China, in 2007, and the M.S.
degree in computer software and theory from
Xiamen University, Xiamen, Fujian, China, in 2010,
and the Ph.D. degree in computer science and technology from the Institute of Computing Technology
(ICT), Chinese Academy of Sciences (CAS),
Beijing, China, in 2015. He is currently a Lecturer affiliated with the Vision, Learning, and Control (VLC) group in the School of Electronics and Computer Science (ECS) at the University of Southampton.
His research interests include
computer vision, Riemannian computing, metric learning, and deep learning.
\end{IEEEbiographynophoto}
\vsacle
\begin{IEEEbiographynophoto}{Xiao-Jun Wu}
received the B.Sc. degree in mathematics from Nanjing Normal University, Nanjing,
China, in 1991. He received the M.S. degree and the
Ph.D. degree in pattern recognition and intelligent
systems from Nanjing University of Science and
Technology, Nanjing, China, in 1996 and 2002, respectively. He is a Professor in artificial intelligence
and pattern recognition at the Jiangnan University,
Wuxi, China. His research interests include pattern
recognition, computer vision, fuzzy systems, neural
networks, and intelligent systems. He has won several
domestic and international awards because of his research achievements. He
served as an associate editor for several international journals. He is currently a
Fellow of IAPR and AAIA.
\end{IEEEbiographynophoto}
\vsacle
\begin{IEEEbiographynophoto}{Nicu Sebe}
is a professor
at the University of Trento, Italy, leading the
research in the areas of multimedia information
retrieval and human behavior understanding. He was the General Co-Chair of the IEEE FG Conference 2008 and ACM Multimedia 2013; the Program Chair of the International Conference on Image and Video Retrieval in 2007 and 2010, ACM Multimedia 2007 and 2011, and the ICCV 2017 and ECCV 2016; and the General Chair of ACM ICMR 2017. He is a fellow of the IAPR.
\end{IEEEbiographynophoto}




