\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{hyperref}
\usepackage{pgfplots,tikz}
\pgfplotsset{compat=1.17}
\usepackage{cleveref}
\usepackage[a4paper, total={6in, 8in}]{geometry}

\definecolor{hcorange}{RGB}{245, 130, 48}
\definecolor{hcnavy}{RGB}{0, 0, 128}
\definecolor{hcblue}{RGB}{0, 130, 200}
\definecolor{hcpink}{RGB}{250, 190, 190}
\definecolor{hcbrown}{RGB}{128, 0, 0}
\definecolor{hclavender}{RGB}{230, 190, 255}
\definecolor{hcgrey}{RGB}{128, 128, 128}
\definecolor{hcgreen}{RGB}{60, 180, 75}
\definecolor{hcred}{RGB}{230, 25, 75}

\newcommand{\rpy}[1]{{\color{red}{}#1}} % reply

\title{Response to referee 1}
\date{}

\begin{document}


\noindent Title: A NUMERICALLY STABLE COMMUNICATION AVOIDING S-STEP GMRES ALGORITHM

\noindent Journal: SIAM Journal on Matrix Analysis and Applications (SIMAX)

\noindent Manuscript Number: \#M157710

\noindent Date: \today

\vspace{0.2in}

\noindent Dear Editor and Reviewers,

\vspace{0.2in}
We would like to express our sincere gratitude to the Editor and the reviewers for their invaluable feedback and insightful comments on our manuscript, "A NUMERICALLY STABLE COMMUNICATION AVOIDING S-STEP
GMRES ALGORITHM" (Manuscript Number: \#M157710). We appreciate the time and effort devoted to the peer review process, and we have carefully considered each of the reviewers' comments in preparing this revised version of our manuscript. 

We would also like to extend our sincere appreciation to the Editor for graciously granting extensions to the submission deadlines. This extension has allowed us to regain access to the same cluster used in the original manuscript and given us valuable additional time to enhance the quality of our manuscript. We are genuinely thankful for this considerate accommodation.

Herein, we present our response to the comments provided by the reviewers. Since both reviewers have shared similar comments on benchmarking our algorithm in parallel settings, we would like to address that aspect first to both reviewers. Subsequently, we will provide point-to-point response to individual comments from each reviewer.

We submit this response and the revised manuscript for your consideration and look forward to any further guidance from the Editor and reviewers.

\vspace{0.2in}
Best regards,

\vspace{0.2in}

Zan Xu (Corresponding Author)

Stanford University




\end{document}