\newpage
\section{Notation, Wirtinger derivatives and special activation functions}
\subsection{Notation and Wirtinger derivatives}
\label{sec:notation_reordered}
Throughout the paper, multi-indices (i.e., elements of $\NN_0^n$) are denoted using boldface. For $\m \in \NN_0^n$ we have the usual notation $\vert \m \vert = \sum_{j=1}^n \m_j$. For a number $m \in \NN_0$ and another multi-index $\pp \in \NN_0^n$ we write $\m \leq m$ iff $\m_j \leq m$ for every $j \in \{1,...,n\}$ and $\m \leq \pp$ iff $\m_j \leq \pp_j$ for every $j \in \{1,...,n\}$. Furthermore we write
\begin{equation*}
    \binom{\pp}{\rr} \defeq \prod_{j = 1}^n \binom{\pp_j}{\rr_j}
\end{equation*}
for two multi-indices $\pp,  \rr \in \NN_0^n$ with $\rr \leq \pp$. For a complex vector $z \in \CC^n$ we write 
\begin{equation*}
    z^\m \defeq \prod_{j=1}^n z_j^{\m_j} \quad \text{and} \quad \overline{z}^\m \defeq \prod_{j=1}^n \overline{z_j}^{\m_j}.
\end{equation*}
For a point $x \in \RR^n$ and $r>0$ we define
\begin{equation*}
    B_r(x) \defeq \left\{ y \in \RR^n : \ \left\Vert x - y \right\Vert < r\right\}
\end{equation*}
with $\Vert \cdot \Vert$ denoting the usual Euclidean distance. This definition is analogously transferred to $\CC^n$. 


$\CC^n$ is canonically isomorphic to $\RR^{2n}$ by virtue of the isomorphism
\begin{equation} \label{isomorphism_intro}
    \varphi_n: \quad \RR^{2n} \to \CC^n, \quad \left(x_1, ..., x_n, y_1, ..., y_n\right) \mapsto \left(x_1 +iy_1, ..., x_n +iy_n\right).
\end{equation}

The Wirtinger derivatives defined in \Cref{sec:prelim} have the following properties that we are going to use, which can be found for example in \cite[E.1a]{kaup_holomorphic_1983}. Here, we assume that $U \subseteq \CC$ is open and $f \in C^1(U; \CC)$.
\begin{enumerate}
    \item $\wirt$ and $\wirtq$ are both $\CC$-linear operators on the set $C^1(U; \CC)$.
    \item $f$ is complex-differentiable in $z \in U$ iff $\wirtq f(z) = 0$ and in this case the equality
    \begin{equation*}
        \wirt f(z) = f'(z)
    \end{equation*}
    holds true, with $f'(z)$ denoting the complex derivative of $f$ at $z$. 
    \item We have the conjugation rules
    \begin{align*}
        \overline{\wirt f} = \wirtq \overline{f} \quad \text{and} \quad \overline{\wirtq f} = \wirt \overline{f}.
    \end{align*}
    \item If $g \in C^1(U; \CC)$, the following product rules for Wirtinger derivatives hold for every $z \in U$:
    \begin{align*}
        \wirt (f \cdot g)(z)&= \wirt f (z) \cdot g(z) + f(z) \cdot \wirt g(z), \\
        \wirtq (f \cdot g)(z)&= \wirtq f (z) \cdot g(z) + f(z) \cdot \wirtq g(z).
    \end{align*}
    This product rule is not explicitly stated in \cite{kaup_holomorphic_1983} but follows easily from the product rule for $\frac{\partial}{\partial x}$ and $\frac{\partial}{\partial y}$.
    \item If $V \subseteq \CC$ is an open set and $g \in C^1(V;\CC)$ with $g(V) \subseteq U$, then the following chain rules for Wirtinger derivatives hold true:
    \begin{align*}
        \wirt(f \circ g) &= \left[(\wirt f) \circ g\right]\cdot \wirt g + \left[\left(\wirtq f\right)\circ g\right]\cdot \wirt \overline{g}, \\
        \wirtq(f \circ g) &= \left[(\wirt f) \circ g\right]\cdot \wirtq g + \left[\left(\wirtq f\right)\circ g\right]\cdot \wirtq \overline{g}.
    \end{align*}
    \item \label{laplace_ident} If $f \in C^2(U; \CC)$ then we have
    \begin{equation*}
        \Delta f (z) = 4\left(\wirt \wirtq f \right) (z)
    \end{equation*}
    for every $z \in U$, with $\Delta$ denoting the usual Laplace-Operator $\Delta = \partial^{(2,0)} + \partial^{(0,2)}$ (cf. \cite[equation (1.7)]{balk_polyanalytic_1991}).
\end{enumerate}


For an open set $U \subseteq \CC^n$, a function $f \in C^k(U; \CC)$ and a multi-index $\elll \in \NN_0^n$ with $\vert \elll \vert \leq k$ we write $\wirt^{\elll} f$ and $\wirtq^{\elll} f$ for the iterated Wirtinger derivatives according to the multi-index $\elll$. 
\begin{proposition}
\label{wirtreal}
    Let $U \subseteq \CC^n$ be an open set and $f \in C^k(U; \CC)$. Then, identifying $f$ with the function $f \circ \varphi_n$ with $\varphi_n$ as in \eqref{isomorphism_intro}, for any multi-indices $\m, \elll \in \NN_0^{n}$ with $\vert \m + \elll \vert \leq k$ we have the representation
    \begin{equation*}
        \wirt^\m \wirtq^{\elll} f(a) = \underset{\pp' + \pp'' = \m + \elll}{\underset{\pp = (\pp', \pp'') \in \NN_0^{2n}}{\sum}} b_{\pp} \left(\partial^{\pp} f \right)(a) \quad \forall a \in U
    \end{equation*}
    with complex numbers $b_{\pp}  \in \CC$ only depending on $\pp, \m$ and $\elll$ and writing $\pp = (\pp', \pp'')$ for the concatenation of the multi-indices $\pp'$ and $\pp'' \in \NN_0^n$. In particular, the coefficients do not depend on $f$.
\end{proposition}
\begin{proof}
    The proof is by induction over $\m$ and $\elll$. We first assume $\m=0$ and show the claim for all $\elll \in \NN_0^n$ with $\vert \elll \vert \leq k$. In the case $\elll = 0$ there is nothing to show, so we assume the claim to be true for fixed $\elll \in \NN_0^n$ with $\vert \elll \vert < k$ and take $j \in \{1,...,n\}$ arbitrarily. Then we get
    \begin{align*}
        \wirtq^{\elll + e_j} f(a) &= \wirtq^{e_j} \wirtq ^{\elll} f(a) \overset{\text{IH}}{=} \underset{\pp' + \pp'' = \elll}{\sum_{\pp = (\pp', \pp'')\in \NN_0^{2n}}} b_{\pp}\wirtq^{e_j} \left(\partial^{\pp} f\right)(a) \\
&= \underset{\pp' + \pp'' = \elll}{\sum_{\pp= (\pp', \pp'') \in \NN_0^{2n}}} \frac{b_{\pp}}{2} \left(\partial^{(\pp' + e_j, \pp'')} f\right)(a) + \frac{ib_{\pp}}{2} \left(\partial^{(\pp', \pp'' + e_{j})}f\right)(a) \\
&=:\underset{\pp' + \pp'' = \elll + e_j}{\underset{\pp = (\pp', \pp'')\in \NN_0^{2n}}{\sum}} b_{\pp} \left(\partial^{\pp} f\right)(a) , 
    \end{align*}
    as was to be shown.

    Since we have shown the case $\m = 0$ we may assume the claim to be true for fixed $\m, \elll \in \NN_0^n$ with $\vert \m + \elll\vert < k$. Then we deduce
    \begin{align*}
        \wirt^{\m + e_j}\wirtq^{\elll} f (a) &= \wirt^{e_j} \wirt^\m \wirtq ^{\elll} f(a) \overset{\text{IH}}{=} \underset{\pp' + \pp'' = \m + \elll}{\sum_{\pp = (\pp', \pp'') \in \NN_0^{2n}}} b_{\pp}\wirt^{e_j} \left(\partial^{\pp} f\right)(a) \\
&= \underset{\pp' + \pp'' = \m + \elll}{\sum_{\pp = (\pp', \pp'') \in \NN_0^{2n}}} \frac{b_\pp}{2} \left(\partial^{(\pp' + e_j, \pp'')} f\right)(a) - \frac{ib_\pp}{2} \left(\partial^{(\pp', \pp'' + e_{j})}f\right)(a) \\
&=:\underset{\pp' + \pp'' = \m + \elll + e_j}{\underset{\pp = (\pp', \pp'') \in \NN_0^{2n}}{\sum}} b_{\pp} \left(\partial^{\pp} f\right)(a).
    \end{align*}
   Hence the claim follows using the principle of mathematical induction.
\end{proof}
\Cref{wirtreal} is technical but crucial: In the course of the paper we will need to approximate Wirtinger derivatives of certain functions. In fact, however, we will approximate real derivatives and take advantage of the fact that Wirtinger derivatives are linear combinations of these.

\input{concrete_activation_functions}