% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{booktabs}
\usepackage{ltablex}
\usepackage{xltabular}
\usepackage{pbox}
\usepackage{hyperref}

% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
\usepackage{color}
\renewcommand\UrlFont{\color{blue}\rmfamily}

%
\begin{document}
%
\title{Xplainer: From X-Ray Observations to Explainable Zero-Shot Diagnosis}% \thanks{Supported by organization x.}}

%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Chantal Pellegrini\inst{1}\thanks{These authors contributed equally.},
Matthias Keicher\inst{1,\star}, Ege Özsoy\inst{1,\star}, Petra Jiraskova\inst{2}, Rickmer Braren\inst{2}, Nassir Navab\inst{1} }
%
\authorrunning{Pellegrini, Keicher and Özsoy et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Computer Aided Medical Procedures, Technical University Munich, Germany \and Department of Diagnostic and Interventional Radiology, School of Medicine, Technical University of Munich, Germany}

%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Automated diagnosis prediction from medical images is a valuable resource to support clinical decision-making. However, such systems usually need to be trained on large amounts of annotated data, which often is scarce in the medical domain. Zero-shot methods address this challenge by allowing a flexible adaption to new settings with different clinical findings without relying on labeled data. Further, to integrate automated diagnosis in the clinical workflow, methods should be transparent and explainable, increasing medical professionals' trust and facilitating correctness verification. In this work, we introduce Xplainer, a novel framework for explainable zero-shot diagnosis in the clinical setting. Xplainer adapts the classification-by-description approach of contrastive vision-language models to the multi-label medical diagnosis task. Specifically, instead of directly predicting a diagnosis, we prompt the model to classify the existence of descriptive observations, which a radiologist would look for on an X-Ray scan, and use the descriptor probabilities to estimate the likelihood of a diagnosis. Our model is explainable by design, as the final diagnosis prediction is directly based on the prediction of the underlying descriptors. We evaluate Xplainer on two chest X-ray datasets, CheXpert and ChestX-ray14, and demonstrate its effectiveness in improving the performance and explainability of zero-shot diagnosis. Our results suggest that Xplainer provides a more detailed understanding of the decision-making process and can be a valuable tool for clinical diagnosis. Our code is available on github: \href{https://github.com/ChantalMP/Xplainer}{https://github.com/ChantalMP/Xplainer}
\keywords{Zero-Shot Diagnosis  \and Explainability \and Contrastive Learning}
\end{abstract}

\input{chapters/introduction.tex}
\input{chapters/method.tex}
\input{chapters/experiments.tex}
\input{chapters/conclusion.tex}

%\subsubsection{Acknowledgements} Please place your acknowledgments at
%the end of the paper, preceded by an unnumbered run-in heading (i.e.
%3rd-level heading).

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%

%\newpage

\bibliographystyle{splncs04}
\bibliography{refs}
\input{chapters/supplement_in.tex}
\end{document}
