\section{Comment Tracker (completed?)}

\heng{add a special footnote for Paul}


\heng{change intel report to situation report} \Yi{done}

\heng{the intro needs to be stronger: 1. emphasize any sort of application of mature AI techniques for intel analysis is near to zero; } \Yi{1-done}

\heng{don't over claim we are automating the whole intel report generation pipeline; machine needs to help human on generating report} \Yi{done}

\manling{I have addressed the comments via tracking changes.} \revanth{@heng: I have added my responses in brown to your comments. Feel free toƒ remove the comments for which you feel has been handled according to the response.}
\heng{A complete story: we need intel report for emergent situations, human analysts need to finish report within a few hours, so the reports tend to be incomplete and biased, hard to keep up to date, and cannot understand information in foreign languages, etc.. we developed a novel platform, leveraging SOTA NLP, and proposed new techniques, to automate intel report generation. the system knows how to ask good questions, extract and summarize related claims with evidence etc.}

This grounding of information element forms an interactive, multimedia knowledge graph enriched with relevant images. Additionally, our \textbf{SmartBook} framework extends the concept of schema induction and event prediction \cite{li-etal-2020-connecting} in the traditional ML/NLP research communities, to generate a natural language ``perspective" section, examining the probable future events, towards the end of the situation report. \revanth{Should we drip the preceding two sentences given we don't have multimedia/event prediction for now?} 