\documentclass[10pt,twocolumn]{config/asme2e}
\special{papersize=8.5in,11in}

\input{config/config}

\input{config/front}

\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{soul}
\sethlcolor{green}

%---------------------------------------------------------------------
\begin{document}
 \setlength{\parskip}{0pt}
 \setlength{\parsep}{0pt}
 \setlength{\headsep}{0pt}

%\setlength{\topskip}{0pt}
\setlength{\topsep}{0pt}
%\setlength{\partopsep}{0pt}

% equations
\abovedisplayshortskip=3pt
\belowdisplayshortskip=3pt
\abovedisplayskip=3pt
\belowdisplayskip=3pt

\titlespacing*{\section}{0pt}{18pt plus 1pt minus 1pt}{3pt plus 0.5pt minus 0.5pt}

\titlespacing*{\subsection}{0pt}{9pt plus 1pt minus 0.5pt}{1pt plus 0.5pt minus 0.5pt}

\titlespacing*{\subsubsection}{0pt}{9pt plus 1pt minus 0.5pt}{1pt plus 0.5pt minus 0.5pt}

\maketitle

%---------------
\begin{abstract}\noindent
% Engineers have applied machine learning techniques to their data for years. 
% There are many different ways to train a model when your data is a set of discrete and continuous values, which can be modeled in $n$-dimensional linear space. 
% But when systems become increasingly complex, the simple discrete or continuous form may not be enough to represent the system completely. 
% But when systems become increasingly complex, researchers have taken advantage of putting their data into a topological form such as graphs. 
\textit{Many complex engineering systems can be represented in a topological form, such as graphs.
This paper utilizes a machine learning technique called Geometric Deep Learning (GDL) to aid designers with challenging, graph-centric design problems. 
The strategy presented here is to take the graph data and apply GDL to seek the best realizable performing solution effectively and efficiently with lower computational costs. 
This case study used here is the synthesis of analog electrical circuits that attempt to match a specific frequency response within a particular frequency range.
Previous studies utilized an enumeration technique to generate 43,249 unique undirected graphs presenting valid potential circuits.
% in the form of undirected graphs. 
Unfortunately, determining the sizing and performance of many circuits can be too expensive.
% many circuit topologies using traditional techniques can take hours, if not days, especially since it is not a form where typical machine-learning techniques can help. 
% This is where GDL can be applied. 
To reduce computational costs with a quantified trade-off in accuracy, the fraction of the circuit graphs and their performance are used as input data to a classification-focused GDL model.
Then, the GDL model can be used to predict the remainder cheaply, thus, aiding decision-makers in the search for the best graph solutions.
The results discussed in this paper show that additional graph-based features are useful, favorable total set classification accuracy of 80\% in using only 10\% of the graphs, and iteratively-built GDL models can further subdivide the graphs into targeted groups with medians significantly closer to the best and containing 88.2 of the top 100 best-performing graphs on average.
}
\end{abstract}

\vspace{1ex}
\noindent Keywords: machine learning, geometric deep learning, graph classification, graph-based design, circuit synthesis

%---------------
\section{INTRODUCTION}
\input{input/intro.tex}

% \clearpage
\section{BACKGROUND}
\input{input/background/intro.tex}

% \clearpage
\section{METHODOLOGY}
\label{method}
\input{input/methods/intro.tex}

% \clearpage
\section{CASE STUDY: ELECTRIC CIRCUIT FREQUENCY RESPONSE GRAPH-DESIGN PROBLEM}
\label{case}
\input{input/case_study/intro.tex}

% \clearpage
\section{CASE STUDY EXPERIMENTS AND RESULTS}
\label{results}
\input{input/results/results.tex}

% \clearpage
\section{CONCLUSION}
\label{conclusion}
\input{input/conclusion.tex}
%--------------
%\clearpage
% \begin{acknowledgment}
% \blindtext[1]
% \end{acknowledgment}

%--------------------------
% \clearpage
\renewcommand{\refname}{REFERENCES}
\bibliographystyle{config/asmems4}
\begin{mySmall}
%\nocite{*} % remove later, displays all references
\bibliography{References}
\end{mySmall}

%--------------------------
% \clearpage
% \onecolumn
% \xneed{Will be removed in the final version.}
% % This will be removed in the final version.
% \tableofcontents
% \listoffigures
% \listoftables
% -----------

%---------------
%  \clearpage
% \input{input/working.tex}
% \clearpage
\appendix
\label{appa}
\input{input/appendix/tools}

\end{document}
