%% AASTeX (version 6.3) Template for submissions to AAS Journals (ApJ-AJ-ApJS-ApJL-PSJ-RNAAS)

%% two columns, 10 point font, single spaced, line numbers
\documentclass[twocolumn]{aastex631}
%\documentclass[linenumbers,twocolumn]{aastex631}

%% load packages
\input{packages.tex}

%% load figures
\graphicspath{{./}{figures/}}

\newcommand{\pv}[1]{\textcolor{orange}{{\bf PV:} #1}}


%% set page headers
\shorttitle{GRB\,221009A}
\shortauthors{Lesage et al.}

%% initialize document
\begin{document}

%% width of captions
\setlength{\LTcapwidth}{\textwidth}

%% title
% \title{Fermi-GBM Discovery of GRB 221009A:\\So Many Photons We Lost Count}
% \title{Fermi-GBM Discovery of GRB 221009A:\\An Extraordinarily Bright GRB with Distinctive Features}
\title{Fermi-GBM Discovery of GRB 221009A:\\An Extraordinarily Bright GRB from Onset to Afterglow}

%% 1st author info
\correspondingauthor{S. Lesage}
\email{stephen.lesage@uah.edu}

%% load definitions
\input{definitions.tex}

%% load affiliations
\input{affiliations.tex}

%% load authors
\input{authors.tex}

%%%%%%%%%%%%%%%%%%%%%%%%
%%%% BEGIN DOCUMENT %%%%
%%%%%%%%%%%%%%%%%%%%%%%%

%% abstract
\input{sections/00_abstract.tex}
\keywords{gamma rays: individual (221009A)}

%% introduction
\section{Introduction} \label{sec:introduction}
\input{sections/01_introduction.tex}

%% discovery
\section{Discovery} \label{sec:discovery}
\input{sections/02_discovery.tex}

%% data
\section{Fermi Data} \label{sec:data}
\input{sections/03_data}

%% temporal analysis
\section{Temporal Analysis} \label{sec:temporal_analysis}
\input{sections/04_temporal_analysis}

%% prompt emission phases
\section{Prompt Emission Phases} \label{sec:prompt_emission_phases}
\input{sections/05_prompt_emission_phases}

%% afterglow
\section{Afterglow} \label{sec:afterglow}
\input{sections/06_afterglow.tex}

%% energetics
\section{Energetics} \label{sec:energetics}
\input{sections/07_energetics.tex}

%% discussion
\section{Discussion} \label{sec:discussion}
\input{sections/08_discussion.tex}

%% summary
\section{Summary} \label{sec:summary}
\input{sections/09_summary.tex}

%% acknowledgments
\section{Acknowledgments} \label{sec:acknowledgments}
\input{sections/10_acknowledgments.tex}

%% appendix
\appendix
\section{Fermi Time-Resolved Interval Selection} \label{app:fermi_intervals}
\input{sections/11_appendix_fermi_intervals.tex}

%% references
%\bibliographystyle{aasjournal}
%\bibliography{references}

\begin{thebibliography}{}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
\providecommand{\url}[1]{\href{#1}{#1}}
\providecommand{\dodoi}[1]{doi:~\href{http://doi.org/#1}{\nolinkurl{#1}}}
\providecommand{\doeprint}[1]{\href{http://ascl.net/#1}{\nolinkurl{http://ascl.net/#1}}}
\providecommand{\doarXiv}[1]{\href{https://arxiv.org/abs/#1}{\nolinkurl{https://arxiv.org/abs/#1}}}

\bibitem[{Abbott {et~al.}(2017)Abbott, Abbott, Abbott, Acernese, Ackley, Adams,
  Adams, Addesso, \& etc.}]{Abbott2017a}
Abbott, B.~P., Abbott, R., Abbott, T.~D., {et~al.} 2017, \apj, 848, L13,
  \dodoi{10.3847/2041-8213/aa920c}

\bibitem[{Abdalla {et~al.}(2019)Abdalla, Adam, Aharonian, Benkhali, Angüner,
  Arakawa, Arcaro, Armand, Ashkar, Backes, Martins, Barnard, Becherini, Berge,
  Bernlöhr, Bissaldi, Blackwell, Böttcher, Boisson, Bolmont,
  {et~al.}}]{Abdalla2019}
Abdalla, H., Adam, R., Aharonian, F., {et~al.} 2019, Nature, 575, 464,
  \dodoi{10.1038/s41586-019-1743-9}

\bibitem[{Abdalla {et~al.}(2021)Abdalla, Aharonian, Benkhali, Angüner, Arcaro,
  Armand, Armstrong, Ashkar, Backes, Baghmanyan, Martins, Barnacka, Barnard,
  Becherini, Berge, Bernlöhr, Bi, Bissaldi, Böttcher, {et~al.}}]{Abdalla2021}
Abdalla, H., Aharonian, F., Benkhali, F.~A., {et~al.} 2021, Science, 372, 1081,
  \dodoi{10.1126/science.abe8560}

\bibitem[{Abdo {et~al.}(2009)Abdo, Ackermann, Ajello, Asano, Atwood, Axelsson,
  Baldini, Ballet, Barbiellini, Baring, Bastieri, Bechtol, Bellazzini, \&
  etc.}]{Abdo2009}
Abdo, A.~A., Ackermann, M., Ajello, M., {et~al.} 2009, \apj, 706, L138,
  \dodoi{10.1088/0004-637X/706/1/L138}

\bibitem[{Acciari {et~al.}(2019)Acciari, Ansoldi, Antonelli, Arbet~Engels,
  Baack, Babi\'c, Banerjee, Barres~de Almeida, Barrio, Becerra~Gonz\'alez,
  Bednarek, \& Bellizzi}]{Acciari2019}
Acciari, V.~A., Ansoldi, S., Antonelli, L.~A., {et~al.} 2019, \nat, 575, 455,
  \dodoi{10.1038/s41586-019-1750-x}

\bibitem[{{Acciari} {et~al.}(2021){Acciari}, {Ansoldi}, {Antonelli}, {Arbet
  Engels}, {Asano}, {Baack}, {Babi{\'c}}, {Baquero}, {Barres de Almeida},
  {Barrio}, {Becerra Gonz{\'a}lez}, {Bednarek}, {Bellizzi}, {Bernardini},
  {Bernardos}, {et~al.}}]{Acciari2021}
{Acciari}, V.~A., {Ansoldi}, S., {Antonelli}, L.~A., {et~al.} 2021, ApJ, 908,
  90, \dodoi{10.3847/1538-4357/abd249}

\bibitem[{Ackermann {et~al.}(2010)Ackermann, Asano, Atwood, Axelsson, Baldini,
  Ballet, Barbiellini, Baring, Bastieri, Bechtol, Bellazzini, Berenji, Bhat,
  Bissaldi, Blandford, Bloom, Bonamente, Borgland, Bouvier, Bregeon, Brez,
  Briggs, Brigida, Bruel, Buson, Caliandro, Cameron, Caraveo, Carrigan,
  Casandjian, Cecchi, Celik, Charles, Chiang, Ciprini, Claus, Cohen-Tanugi,
  Connaughton, Dermer, de~Palma, Dingus, do~Couto~e Silva, Drell, Dubois,
  Dumora, Farnier, Favuzzi, Fegan, Finke, Focke, Frailis, Fukazawa, Fusco,
  Gargano, Gasparrini, Gehrels, Germani, Giglietto, Giordano, Glanzman,
  Godfrey, Granot, Grenier, Grondin, Grove, Guiriec, Hadasch, Harding, Hays,
  Horan, Hughes, J{\'{o}}hannesson, Johnson, Kamae, Katagiri, Kataoka, Kawai,
  Kippen, Knödlseder, Kocevski, Kouveliotou, Kuss, Lande, Latronico,
  Lemoine-Goumard, Garde, Longo, Loparco, Lott, Lovellette, Lubrano, Makeev,
  Mazziotta, McEnery, McGlynn, Meegan, M{\'{e}}sz{\'{a}}ros, Michelson,
  Mitthumsiri, Mizuno, Moiseev, Monte, Monzani, Moretti, Morselli, Moskalenko,
  Murgia, Nakajima, Nakamori, Nolan, Norris, Nuss, Ohno, Ohsugi, Omodei,
  Orlando, Ormes, Ozaki, Paciesas, Paneque, Panetta, Parent, Pelassa, Pepe,
  Pesce-Rollins, Piron, Preece, Rain{\`{o}}, Rando, Razzano, Razzaque, Reimer,
  Ritz, Rodriguez, Roth, Ryde, Sadrozinski, Sander, Scargle, Schalk,
  Sgr{\`{o}}, Siskind, Smith, Spandre, Spinelli, Stamatikos, Stecker,
  Strickman, Suson, Tajima, Takahashi, Takahashi, Tanaka, Thayer, Thayer,
  Thompson, Toma, Torres, Tosti, Tramacere, Uchiyama, Uehara, Usher, van~der
  Horst, Vasileiou, Vilchez, Vitale, von Kienlin, Waite, Wang, Wilson-Hodge,
  Winer, Wu, Yamazaki, Yang, Ylinen, \& Ziegler}]{Ackermann_2010}
Ackermann, M., Asano, K., Atwood, W.~B., {et~al.} 2010, The Astrophysical
  Journal, 716, 1178, \dodoi{10.1088/0004-637x/716/2/1178}

\bibitem[{{Ackermann} {et~al.}(2011){Ackermann}, {Ajello}, {Asano}, {Axelsson},
  {Baldini}, {Ballet}, {Barbiellini}, {Baring}, {Bastieri}, {Bechtol},
  {Bellazzini}, {Berenji}, {Bhat}, {Bissaldi}, {Blandford}, {Bonamente},
  {Borgland}, {Bouvier}, {Bregeon}, {Brez}, {Briggs}, {Brigida}, {Bruel},
  {Buehler}, {Buson}, {Caliandro}, {Cameron}, {Caraveo}, {Carrigan},
  {Casandjian}, {Cecchi}, {Celik}, {Chaplin}, {Charles}, {Chekhtman}, {Chiang},
  {Ciprini}, {Claus}, {Cohen-Tanugi}, {Connaughton}, {Conrad}, {Cutini},
  {Dermer}, {de Angelis}, {de Palma}, {Dingus}, {Silva}, {Drell}, {Dubois},
  {Favuzzi}, {Fegan}, {Ferrara}, {Focke}, {Frailis}, {Fukazawa}, {Funk},
  {Fusco}, {Gargano}, {Gasparrini}, {Gehrels}, {Germani}, {Giglietto},
  {Giordano}, {Giroletti}, {Glanzman}, {Godfrey}, {Goldstein}, {Granot},
  {Greiner}, {Grenier}, {Grove}, {Guiriec}, {Hadasch}, {Hanabata}, {Harding},
  {Hayashi}, {Hayashida}, {Hays}, {Horan}, {Hughes}, {Itoh}, {J{\'o}hannesson},
  {Johnson}, {Johnson}, {Kamae}, {Katagiri}, {Kataoka}, {Kippen},
  {Kn{\"o}dlseder}, {Kocevski}, {Kouveliotou}, {Kuss}, {Lande}, {Latronico},
  {Lee}, {Llena Garde}, {Longo}, {Loparco}, {Lovellette}, {Lubrano}, {Makeev},
  {Mazziotta}, {McBreen}, {McEnery}, {McGlynn}, {Meegan}, {Mehault},
  {M{\'e}sz{\'a}ros}, {Michelson}, {Mizuno}, {Monte}, {Monzani}, {Moretti},
  {Morselli}, {Moskalenko}, {Murgia}, {Nakajima}, {Nakamori}, {Naumann-Godo},
  {Nishino}, {Nolan}, {Norris}, {Nuss}, {Ohno}, {Ohsugi}, {Okumura}, {Omodei},
  {Orlando}, {Ormes}, {Ozaki}, {Paciesas}, {Paneque}, {Panetta}, {Parent},
  {Pelassa}, {Pepe}, {Pesce-Rollins}, {Petrosian}, {Piron}, {Porter}, {Preece},
  {Racusin}, {Rain{\`o}}, {Rando}, {Rau}, {Razzano}, {Razzaque}, {Reimer},
  {Reimer}, {Reposeur}, {Reyes}, {Ripken}, {Ritz}, {Roth}, {Ryde},
  {Sadrozinski}, {Sander}, {Scargle}, {Schalk}, {Sgr{\`o}}, {Siskind}, {Smith},
  {Spandre}, {Spinelli}, {Stamatikos}, {Stecker}, {Strickman}, {Suson},
  {Tajima}, {Takahashi}, {Tanaka}, {Tanaka}, {Thayer}, {Thayer}, {Tibaldo},
  {Tierney}, {Toma}, {Torres}, {Tosti}, {Tramacere}, {Uchiyama}, {Uehara},
  {Usher}, {Vandenbroucke}, {van der Horst}, {Vasileiou}, {Vilchez}, {Vitale},
  {von Kienlin}, {Waite}, {Wang}, {Wilson-Hodge}, {Winer}, {Wood}, {Wu},
  {Yamazaki}, {Yang}, {Ylinen}, \& {Ziegler}}]{ackermann_2011}
{Ackermann}, M., {Ajello}, M., {Asano}, K., {et~al.} 2011, Astrophysical
  Journal Letters, 729, 114, \dodoi{10.1088/0004-637X/729/2/114}

\bibitem[{Ackermann {et~al.}(2014)Ackermann, Ajello, Asano, Atwood, Axelsson,
  Baldini, Ballet, Barbiellini, Baring, Bastieri, Bechtol, Bellazzini,
  Bissaldi, \& etc.}]{Ackermann2014}
Ackermann, M., Ajello, M., Asano, K., {et~al.} 2014, Science, 343, 42,
  \dodoi{10.1126/science.1242353}

\bibitem[{Ajello {et~al.}(2019)Ajello, Arimoto, Axelsson, Baldini, Barbiellini,
  Bastieri, Bellazzini, Bhat, Bissaldi, Blandford, Bonino, Bonnell, Bottacini,
  \& etc.}]{Ajello2019}
Ajello, M., Arimoto, M., Axelsson, M., {et~al.} 2019, \apj, 878, 52,
  \dodoi{10.3847/1538-4357/ab1d4e}

\bibitem[{Ajello {et~al.}(2020)Ajello, Arimoto, Axelsson, Baldini, Barbiellini,
  Bastieri, Bellazzini, Berretta, Bissaldi, Blandford, Bonino, Bottacini,
  Bregeon, Bruel, \& etc.}]{Ajello2020}
---. 2020, \apj, 890, 9, \dodoi{10.3847/1538-4357/ab5b05}

\bibitem[{An {et~al.}(2023)An, Antier, Bi, Bu, Cai, Cao, Camisasca, Chang,
  Chen, Chen, Chen, Chen, Chen, \& etc.}]{HTMX_GECAM-C_221009A}
An, Z.-H., Antier, S., Bi, X.-Z., {et~al.} 2023, Insight-HXMT and GECAM-C
  observations of the brightest-of-all-time GRB 221009A,  arXiv,
  \dodoi{10.48550/ARXIV.2303.01203}

\bibitem[{Arimoto {et~al.}(2020)Arimoto, Asano, Tachibana, \&
  Axelsson}]{Arimoto_2020}
Arimoto, M., Asano, K., Tachibana, Y., \& Axelsson, M. 2020, The Astrophysical
  Journal, 891, 106, \dodoi{10.3847/1538-4357/ab72f7}

\bibitem[{Atwood {et~al.}(2009)Atwood, Abdo, Ackermann, Althouse, Anderson,
  Axelsson, Baldini, Ballet, Band, Barbiellini, Bartelt, Bastieri, Baughman,
  Bechtol, B{\'{e}}d{\'{e}}r{\`{e}}de, Bellardi, Bellazzini, Berenji, Bignami,
  Bisello, Bissaldi, Blandford, Bloom, Bogart, Bonamente, Bonnell, Borgland,
  Bouvier, Bregeon, Brez, Brigida, Bruel, Burnett, Busetto, Caliandro, Cameron,
  Caraveo, Carius, Carlson, Casandjian, Cavazzuti, Ceccanti, Cecchi, Charles,
  Chekhtman, Cheung, Chiang, Chipaux, Cillis, Ciprini, Claus, Cohen-Tanugi,
  Condamoor, Conrad, Corbet, Corucci, Costamante, Cutini, Davis, Decotigny,
  DeKlotz, Dermer, de~Angelis, Digel, do~Couto~e Silva, Drell, Dubois, Dumora,
  Edmonds, Fabiani, Farnier, Favuzzi, Flath, Fleury, Focke, Funk, Fusco,
  Gargano, Gasparrini, Gehrels, Gentit, Germani, Giebels, Giglietto, Giommi,
  Giordano, Glanzman, Godfrey, Grenier, Grondin, Grove, Guillemot, Guiriec,
  Haller, Harding, Hart, Hays, Healey, Hirayama, Hjalmarsdotter, Horn, Hughes,
  J{\'{o}}hannesson, Johansson, Johnson, Johnson, Johnson, Johnson, Kamae,
  Katagiri, Kataoka, Kavelaars, Kawai, Kelly, Kerr, Klamra, Knödlseder,
  Kocian, Komin, Kuehn, Kuss, Landriu, Latronico, Lee, Lee, Lemoine-Goumard,
  Lionetto, Longo, Loparco, Lott, Lovellette, Lubrano, Madejski, Makeev,
  Marangelli, Massai, Mazziotta, McEnery, Menon, Meurer, Michelson, Minuti,
  Mirizzi, Mitthumsiri, Mizuno, Moiseev, Monte, Monzani, Moretti, Morselli,
  Moskalenko, Murgia, Nakamori, Nishino, Nolan, Norris, Nuss, Ohno, Ohsugi,
  Omodei, Orlando, Ormes, Paccagnella, Paneque, Panetta, Parent, Pearce, Pepe,
  Perazzo, Pesce-Rollins, Picozza, Pieri, Pinchera, Piron, Porter, Poupard,
  Rain{\`{o}}, Rando, Rapposelli, Razzano, Reimer, Reimer, Reposeur, Reyes,
  Ritz, Rochester, Rodriguez, Romani, Roth, Russell, Ryde, Sabatini,
  Sadrozinski, Sanchez, Sander, Sapozhnikov, Parkinson, Scargle, Schalk,
  Scolieri, Sgr{\`{o}}, Share, Shaw, Shimokawabe, Shrader, Sierpowska-Bartosik,
  Siskind, Smith, Smith, Spandre, Spinelli, Starck, Stephens, Strickman,
  Strong, Suson, Tajima, Takahashi, Takahashi, Tanaka, Tenze, Tether, Thayer,
  Thayer, Thompson, Tibaldo, Tibolla, Torres, Tosti, Tramacere, Turri, Usher,
  Vilchez, Vitale, Wang, Watters, Winer, Wood, Ylinen, \&
  Ziegler}]{Atwood_2009}
Atwood, W.~B., Abdo, A.~A., Ackermann, M., {et~al.} 2009, The Astrophysical
  Journal, 697, 1071, \dodoi{10.1088/0004-637x/697/2/1071}

\bibitem[{{Axelsson} {et~al.}(2012){Axelsson}, {Baldini}, {Barbiellini},
  {Baring}, {Bellazzini}, {Bregeon}, {Brigida}, {Bruel}, {Buehler},
  {Caliandro}, {Cameron}, {Caraveo}, {Cecchi}, {Chaves}, {Chekhtman}, {Chiang},
  {Claus}, {Conrad}, {Cutini}, {D'Ammando}, {de Palma}, {Dermer}, {Silva},
  {Drell}, {Favuzzi}, {Fegan}, {Ferrara}, {Focke}, {Fukazawa}, {Fusco},
  {Gargano}, {Gasparrini}, {Gehrels}, {Germani}, {Giglietto}, {Giroletti},
  {Godfrey}, {Guiriec}, {Hadasch}, {Hanabata}, {Hayashida}, {Hou}, {Iyyani},
  {Jackson}, {Kocevski}, {Kuss}, {Larsson}, {Larsson}, {Longo}, {Loparco},
  {Lundman}, {Mazziotta}, {McEnery}, {Mizuno}, {Monzani}, {Moretti},
  {Morselli}, {Murgia}, {Nuss}, {Nymark}, {Ohno}, {Omodei}, {Pesce-Rollins},
  {Piron}, {Pivato}, {Racusin}, {Rain{\`o}}, {Razzano}, {Razzaque}, {Reimer},
  {Roth}, {Ryde}, {Sanchez}, {Sgr{\`o}}, {Siskind}, {Spandre}, {Spinelli},
  {Stamatikos}, {Tibaldo}, {Tinivella}, {Usher}, {Vandenbroucke}, {Vasileiou},
  {Vianello}, {Vitale}, {Waite}, {Winer}, {Wood}, {Burgess}, {Bhat},
  {Bissaldi}, {Briggs}, {Connaughton}, {Fishman}, {Fitzpatrick}, {Foley},
  {Gruber}, {Kippen}, {Kouveliotou}, {Jenke}, {McBreen}, {McGlynn}, {Meegan},
  {Paciesas}, {Pelassa}, {Preece}, {Tierney}, {von Kienlin}, {Wilson-Hodge},
  {Xiong}, \& {Pe'er}}]{Axelsson2012}
{Axelsson}, M., {Baldini}, L., {Barbiellini}, G., {et~al.} 2012, \apjl, 757,
  L31, \dodoi{10.1088/2041-8205/757/2/L31}

\bibitem[{Band {et~al.}(1993)Band, Matteson, Ford, Schaefer, Palmer, Teegarden,
  Cline, Briggs, Paciesas, Pendleton, Fishman, Kouveliotou, Meegan, Wilson, \&
  Lestrade}]{Band1993}
Band, D., Matteson, J., Ford, L., {et~al.} 1993, \apj, 413, 281,
  \dodoi{10.1086/172995}

\bibitem[{Beniamini \& Piran(2013)}]{Beniamini2013}
Beniamini, P., \& Piran, T. 2013, The Astrophysical Journal, 769, 69,
  \dodoi{10.1088/0004-637X/769/1/69}

\bibitem[{{Bhat}(2013)}]{Bhat2013}
{Bhat}, N.~P. 2013, in EAS Publications Series, Vol.~61, EAS Publications
  Series, ed. A.~J. {Castro-Tirado}, J.~{Gorosabel}, \& I.~H. {Park}, 45--52,
  \dodoi{10.1051/eas/1361005}

\bibitem[{Bhat {et~al.}(2014)Bhat, Fishman, Briggs, Connaughton, Meegan,
  Paciesas, Wilson-Hodge, \& Xiong}]{Bhat2014}
Bhat, P.~N., Fishman, G.~J., Briggs, M.~S., {et~al.} 2014, \ea, 38, 331,
  \dodoi{10.1007/s10686-014-9424-z}

\bibitem[{{Bhat} {et~al.}(2012){Bhat}, {Briggs}, {Connaughton}, {Kouveliotou},
  {van der Horst}, {Paciesas}, {Meegan}, {Bissaldi}, {Burgess}, {Chaplin},
  {Diehl}, {Fishman}, {Fitzpatrick}, {Foley}, {Gibby}, {Giles}, {Goldstein},
  {Greiner}, {Gruber}, {Guiriec}, {von Kienlin}, {Kippen}, {McBreen}, {Preece},
  {Rau}, {Tierney}, \& {Wilson-Hodge}}]{Bhat2012}
{Bhat}, P.~N., {Briggs}, M.~S., {Connaughton}, V., {et~al.} 2012, \apj, 744,
  141, \dodoi{10.1088/0004-637X/744/2/141}

\bibitem[{Bissaldi {et~al.}(2022)Bissaldi, Omodei, \& (NRL)}]{gcn32637}
Bissaldi, E., Omodei, N., \& (NRL), M.~K. 2022, \gcn, 32637.
\newblock \url{https://gcn.gsfc.nasa.gov/gcn3/32637.gcn3}

\bibitem[{Blackburn {et~al.}(2015)Blackburn, Briggs, Camp, Christensen,
  Connaughton, Jenke, Remillard, \& Veitch}]{Blackburn2015}
Blackburn, L., Briggs, M.~S., Camp, J., {et~al.} 2015, \apjs, 217, 8,
  \dodoi{10.1088/0067-0049/217/1/8}

\bibitem[{Blanch {et~al.}(2020)Blanch, Gaug, Noda, Berti, Moretti, Miceli,
  Gliwny, Ubach, Schleicher, Cerruti, , \& Stamerra}]{gcn28659}
Blanch, O., Gaug, M., Noda, K., {et~al.} 2020, GRB Coordinates Network, 28659,
  1.
\newblock \url{https://gcn.gsfc.nasa.gov/gcn3/28659.gcn3}

\bibitem[{{Burgess} {et~al.}(2011){Burgess}, {Preece}, {Baring}, {Briggs},
  {Connaughton}, {Guiriec}, {Paciesas}, {Meegan}, {Bhat}, {Bissaldi},
  {Chaplin}, {Diehl}, {Fishman}, {Fitzpatrick}, {Foley}, {Gibby}, {Giles},
  {Goldstein}, {Greiner}, {Gruber}, {van der Horst}, {von Kienlin}, {Kippen},
  {Kouveliotou}, {McBreen}, {Rau}, {Tierney}, \& {Wilson-Hodge}}]{Burgess2011}
{Burgess}, J.~M., {Preece}, R.~D., {Baring}, M.~G., {et~al.} 2011, \apj, 741,
  24, \dodoi{10.1088/0004-637X/741/1/24}

\bibitem[{Cano {et~al.}(2017)Cano, Wang, Dai, \& Wu}]{cano2017observer}
Cano, Z., Wang, S.-Q., Dai, Z.-G., \& Wu, X.-F. 2017, Advances in Astronomy,
  2017

\bibitem[{Chaplin {et~al.}(2013)Chaplin, Bhat, Briggs, \&
  Connaughton}]{Chaplin2013}
Chaplin, V., Bhat, N., Briggs, M.~S., \& Connaughton, V. 2013,
  \nucinstrummethodsa, 717, 21,
  \dodoi{https://doi.org/10.1016/j.nima.2013.03.067}

\bibitem[{Chirenti {et~al.}(2023)Chirenti, Dichiara, Lien, Miller, \&
  Preece}]{Chirenti2023}
Chirenti, C., Dichiara, S., Lien, A., Miller, M.~C., \& Preece, R. 2023,
  Nature, 613, 253, \dodoi{10.1038/s41586-022-05497-0}

\bibitem[{{Connaughton}(2002)}]{connaughton02afterglow}
{Connaughton}, V. 2002, \apj, 567, 1028, \dodoi{10.1086/338695}

\bibitem[{Crowther(2007)}]{Crowther2007}
Crowther, P.~A. 2007, Annual Review of Astronomy and Astrophysics, 45, 177,
  \dodoi{10.1146/annurev.astro.45.051806.110615}

\bibitem[{{de Ugarte Postigo} {et~al.}(2022{\natexlab{a}}){de Ugarte Postigo},
  {Izzo}, {Thoene}, {Fynbo}, {Kann}, {Agui Fernandez}, \& {Tanvir}}]{gcn32800}
{de Ugarte Postigo}, A., {Izzo}, L., {Thoene}, C.~C., {et~al.}
  2022{\natexlab{a}}, GRB Coordinates Network, 32800, 1

\bibitem[{{de Ugarte Postigo} {et~al.}(2022{\natexlab{b}}){de Ugarte Postigo},
  {Izzo}, {Pugliese}, {Xu}, {Schneider}, {Fynbo}, {Tanvir}, {Malesani},
  {Saccardi}, {Kann}, {Wiersema}, {Gompertz}, {Thoene}, {Levan}, \& {Stargate
  Collaboration}}]{gcn32648}
{de Ugarte Postigo}, A., {Izzo}, L., {Pugliese}, G., {et~al.}
  2022{\natexlab{b}}, GRB Coordinates Network, 32648, 1

\bibitem[{Dichiara {et~al.}(2022)Dichiara, Gropp, Kennea, Kuin, Lien, Marshall,
  Tohuvavohu, \& Williams}]{gcn32632}
Dichiara, S., Gropp, J., Kennea, J.~A., {et~al.} 2022, \gcn, 32632.
\newblock \url{https://gcn.gsfc.nasa.gov/gcn3/32632.gcn3}

\bibitem[{Eichler {et~al.}(1989)Eichler, Livio, Piran, \&
  Schramm}]{Eichler1989}
Eichler, D., Livio, M., Piran, T., \& Schramm, D.~N. 1989, Nature, 340, 126

\bibitem[{Fitzpatrick {et~al.}(2011)Fitzpatrick, Connaughton, McBreen, \&
  Tierney}]{Fitzpatrick2011}
Fitzpatrick, G., Connaughton, V., McBreen, S., \& Tierney, D. 2011, \arxive,
  \dodoi{10.48550/ARXIV.1111.3779}

\bibitem[{Frederiks {et~al.}(2023)Frederiks, Svinkin, Lysenko, Molkov,
  Tsvetkova, Ulanov, Ridnaia, Lutovinov, Lapshov, Tkachenko, \&
  Levin}]{Konus_221009A}
Frederiks, D., Svinkin, D., Lysenko, A.~L., {et~al.} 2023, Properties of the
  extremely energetic GRB~221009A from Konus-\textit{WIND} and
  \textit{SRG}/ART-XC observations,  arXiv, \dodoi{10.48550/ARXIV.2302.13383}

\bibitem[{Fukami {et~al.}(2021)Fukami, Berti, Loporchio, Suda, Nava, Noda,
  Bosnjak, Asano, Longo, Acciari, Ansoldi, Antonelli, Arbet~Engels, Artero,
  Baack, {et~al.}}]{Fukami2021}
Fukami, S., Berti, A., Loporchio, S., {et~al.} 2021, in Proceedings of 37th
  International Cosmic Ray Conference {\textemdash} PoS(ICRC2021), Vol. 395,
  788, \dodoi{10.22323/1.395.0788}

\bibitem[{Fulton {et~al.}(2023)Fulton, Smartt, Rhodes, Huber, Villar, Moore,
  Srivastav, Schultz, Chambers, Izzo, Hjorth, Chen, Nicholl, Foley, Rest, \&
  etc.}]{fulton_2023}
Fulton, M.~D., Smartt, S.~J., Rhodes, L., {et~al.} 2023, The optical light
  curve of GRB 221009A: the afterglow and detection of the emerging supernova
  SN 2022xiw,  arXiv, \dodoi{10.48550/ARXIV.2301.11170}

\bibitem[{{Ghirlanda} {et~al.}(2018){Ghirlanda}, {Nappo}, {Ghisellini},
  {Melandri}, {Marcarini}, {Nava}, {Salafia}, {Campana}, \&
  {Salvaterra}}]{Ghirlanda+18Lorentz}
{Ghirlanda}, G., {Nappo}, F., {Ghisellini}, G., {et~al.} 2018, \aap, 609, A112,
  \dodoi{10.1051/0004-6361/201731598}

\bibitem[{{Giblin} {et~al.}(1999){Giblin}, {van Paradijs}, {Kouveliotou},
  {Connaughton}, {Wijers}, {Briggs}, {Preece}, \&
  {Fishman}}]{Giblin+99afterglow}
{Giblin}, T.~W., {van Paradijs}, J., {Kouveliotou}, C., {et~al.} 1999, \apjl,
  524, L47, \dodoi{10.1086/312285}

\bibitem[{Gill \& Granot(2018)}]{Gill_2018}
Gill, R., \& Granot, J. 2018, Monthly Notices of the Royal Astronomical
  Society, 478, 4128, \dodoi{10.1093/mnras/sty1214}

\bibitem[{Goldstein {et~al.}(2016)Goldstein, Burns, Hamburg, Connaughton,
  Veres, Briggs, Hui, \& Collaboration}]{Goldstein2016}
Goldstein, A., Burns, E., Hamburg, R., {et~al.} 2016, \arxive,
  \dodoi{10.48550/arxiv.1612.02395}

\bibitem[{Goldstein {et~al.}(2022)Goldstein, Cleveland, \&
  Kocevski}]{GbmDataTools}
Goldstein, A., Cleveland, W.~H., \& Kocevski, D. 2022, Fermi GBM Data Tools:
  v1.1.1.
\newblock \url{https://fermi.gsfc.nasa.gov/ssc/data/analysis/gbm}

\bibitem[{Goldstein {et~al.}(2012)Goldstein, Burgess, Preece, Briggs, Guiriec,
  van~der Horst, Connaughton, Wilson-Hodge, Paciesas, Meegan, von Kienlin,
  Bhat, Bissaldi, \& etc.}]{Goldstein2012}
Goldstein, A., Burgess, J.~M., Preece, R.~D., {et~al.} 2012, \apjs, 199, 19,
  \dodoi{10.1088/0067-0049/199/1/19}

\bibitem[{Goodman(1986)}]{Goodman1986}
Goodman, J. 1986, The Astrophysical Journal, 308, L47

\bibitem[{{Granot} \& {Sari}(2002)}]{Granot2002}
{Granot}, J., \& {Sari}, R. 2002, \apj, 568, 820, \dodoi{10.1086/338966}

\bibitem[{Gruber {et~al.}(2014)Gruber, Goldstein, von Ahlefeld, Bhat, Bissaldi,
  Briggs, Byrne, Cleveland, Connaughton, Diehl, Fishman, Fitzpatrick, Foley,
  Gibby, Giles, Greiner, Guiriec, van~der Horst, von Kienlin, Kouveliotou,
  Layden, Lin, Meegan, McGlynn, Paciesas, Pelassa, Preece, Rau, Wilson-Hodge,
  Xiong, Younes, \& Yu}]{Gruber2014}
Gruber, D., Goldstein, A., von Ahlefeld, V.~W., {et~al.} 2014, \apjs, 211, 12,
  \dodoi{10.1088/0067-0049/211/1/12}

\bibitem[{{Grupe} {et~al.}(2013){Grupe}, {Nousek}, {Veres}, {Zhang}, \&
  {Gehrels}}]{Grupe+13swiftcat}
{Grupe}, D., {Nousek}, J.~A., {Veres}, P., {Zhang}, B.-B., \& {Gehrels}, N.
  2013, \apjs, 209, 20, \dodoi{10.1088/0067-0049/209/2/20}

\bibitem[{Guha \& Nicholson(2022)}]{gcn32745}
Guha, A., \& Nicholson, P. 2022, \gcn, 32745.
\newblock \url{https://gcn.gsfc.nasa.gov/gcn3/32745.gcn3}

\bibitem[{{Guiriec} {et~al.}(2015){Guiriec}, {Mochkovitch}, {Piran}, {Daigne},
  {Kouveliotou}, {Racusin}, {Gehrels}, \& {McEnery}}]{Guiriec2015}
{Guiriec}, S., {Mochkovitch}, R., {Piran}, T., {et~al.} 2015, \apj, 814, 10,
  \dodoi{10.1088/0004-637X/814/1/10}

\bibitem[{{Guiriec} {et~al.}(2011){Guiriec}, {Connaughton}, {Briggs},
  {Burgess}, {Ryde}, {Daigne}, {M{\'e}sz{\'a}ros}, {Goldstein}, {McEnery},
  {Omodei}, {Bhat}, {Bissaldi}, {Camero-Arranz}, {Chaplin}, {Diehl}, {Fishman},
  {Foley}, {Gibby}, {Giles}, {Greiner}, {Gruber}, {von Kienlin}, {Kippen},
  {Kouveliotou}, {McBreen}, {Meegan}, {Paciesas}, {Preece}, {Rau}, {Tierney},
  {van der Horst}, \& {Wilson-Hodge}}]{Guiriec2011}
{Guiriec}, S., {Connaughton}, V., {Briggs}, M.~S., {et~al.} 2011, \apjl, 727,
  L33, \dodoi{10.1088/2041-8205/727/2/L33}

\bibitem[{{Hasco{\"e}t} {et~al.}(2012){Hasco{\"e}t}, {Daigne}, {Mochkovitch},
  \& {Vennin}}]{Hascoet+12gamgam}
{Hasco{\"e}t}, R., {Daigne}, F., {Mochkovitch}, R., \& {Vennin}, V. 2012,
  \mnras, 421, 525, \dodoi{10.1111/j.1365-2966.2011.20332.x}

\bibitem[{Hou {et~al.}(2018)Hou, Zhang, Meng, Wu, Liang, Lü, Liu, Liang, Lin,
  jing Lu, Huang, \& Zhang}]{Hou2018}
Hou, S.-J., Zhang, B.-B., Meng, Y.-Z., {et~al.} 2018, \apj, 866, 13,
  \dodoi{10.3847/1538-4357/aadc07}

\bibitem[{{Huang} {et~al.}(2022){Huang}, {Hu}, {Chen}, {Zha}, {Liu}, {Yao},
  {Cao}, \& {Experiment}}]{gcn32677}
{Huang}, Y., {Hu}, S., {Chen}, S., {et~al.} 2022, GRB Coordinates Network,
  32677, 1

\bibitem[{{H{\"u}bner} {et~al.}(2022){H{\"u}bner}, {Huppenkothen}, {Lasky},
  {Inglis}, {Ick}, \& {Hogg}}]{huebner2022}
{H{\"u}bner}, M., {Huppenkothen}, D., {Lasky}, P.~D., {et~al.} 2022, \apj, 936,
  17, \dodoi{10.3847/1538-4357/ac7959}

\bibitem[{Kennea \& Williams(2022)}]{gcn32635}
Kennea, J.~A., \& Williams, M. 2022, \gcn, 32635.
\newblock \url{https://gcn.gsfc.nasa.gov/gcn3/32635.gcn3}

\bibitem[{{KM3NeT Collaboration}(2022)}]{gcn32741}
{KM3NeT Collaboration}. 2022, \gcn, 32741.
\newblock \url{https://gcn.gsfc.nasa.gov/gcn3/32741.gcn3}

\bibitem[{Knoll(2010)}]{Knoll2010}
Knoll, G.~F. 2010, Radiation detection and measurement (John Wiley \& Sons)

\bibitem[{\lat(2023)}]{grb221009a_fermi_lat_collaboration_2023}
\lat. 2023, remove221009a

\bibitem[{Lesage {et~al.}(2022)Lesage, Veres, Roberts, Burns, \&
  Bissaldi}]{gcn32642}
Lesage, S., Veres, P., Roberts, O., Burns, E., \& Bissaldi, E. 2022, \gcn,
  32642.
\newblock \url{https://gcn.gsfc.nasa.gov/gcn3/32642.gcn3}

\bibitem[{Levan {et~al.}(2022{\natexlab{a}})Levan, Barclay, Bhirombhakdi,
  Burns, Cenko, Chrimes, D’Avanzo, D’Elia, Valle, de~Ugarte~Postigo, Fong,
  Fruchter, Gompertz, Hartmann, Hedges, \& etc.}]{gcn32921}
Levan, A., Barclay, T., Bhirombhakdi, K., {et~al.} 2022{\natexlab{a}}, \gcn,
  32921.
\newblock \url{https://gcn.gsfc.nasa.gov/gcn3/32921.gcn3}

\bibitem[{Levan {et~al.}(2022{\natexlab{b}})Levan, Barclay, Burns, Cenko,
  Chrimes, D’Avanzo, D’Elia, Hedges, Heintz, Izzo, Kann, Kennea, Floc’h,
  Malesani, Melandri, \& etc.}]{gcn32821}
Levan, A., Barclay, T., Burns, E., {et~al.} 2022{\natexlab{b}}, \gcn, 32821.
\newblock \url{https://gcn.gsfc.nasa.gov/gcn3/32821.gcn3}

\bibitem[{Levan {et~al.}(2023)Levan, Lamb, Schneider, Hjorth, Zafar, Postigo,
  Sargent, Mullally, Izzo, D'Avanzo, Burns, Fernández, Barclay, Bernardini, \&
  etc.}]{JWST_221009A}
Levan, A.~J., Lamb, G.~P., Schneider, B., {et~al.} 2023, The first JWST
  spectrum of a GRB afterglow: No bright supernova in observations of the
  brightest GRB of all time, GRB 221009A,  arXiv,
  \dodoi{10.48550/ARXIV.2302.07761}

\bibitem[{{Lithwick} \& {Sari}(2001)}]{lithwick01}
{Lithwick}, Y., \& {Sari}, R. 2001, \apj, 555, 540, \dodoi{10.1086/321455}

\bibitem[{Lithwick \& Sari(2001)}]{Lithwick2001}
Lithwick, Y., \& Sari, R. 2001, The Astrophysical Journal, 555, 540,
  \dodoi{10.1086/321455}

\bibitem[{Lysenko {et~al.}(2019)Lysenko, Anfinogentov, Svinkin, Frederiks, \&
  Fleishman}]{Lysenko2019}
Lysenko, A.~L., Anfinogentov, S.~A., Svinkin, D.~S., Frederiks, D.~D., \&
  Fleishman, G.~D. 2019, \apj, 877, 145, \dodoi{10.3847/1538-4357/ab1be0}

\bibitem[{MacFadyen \& Woosley(1999)}]{MacFadyen1999}
MacFadyen, A.~I., \& Woosley, S.~E. 1999, The Astrophysical Journal, 524, 262,
  \dodoi{10.1086/307790}

\bibitem[{{MAGIC Collaboration} {et~al.}(2019){MAGIC Collaboration}, {Acciari},
  {Ansoldi}, {Antonelli}, {Engels}, {Baack}, {Babi{\'c}}, {Banerjee}, {Barres
  de Almeida}, {Barrio}, \& et~al.}]{MAGIC+21ssc}
{MAGIC Collaboration}, {Acciari}, V.~A., {Ansoldi}, S., {et~al.} 2019, \nat,
  575, 459, \dodoi{10.1038/s41586-019-1754-6}

\bibitem[{Mailyan {et~al.}(2019)Mailyan, Xu, Celestin, Briggs, Dwyer, Cramer,
  Roberts, \& Stanbro}]{Mailyan2019}
Mailyan, B.~G., Xu, W., Celestin, S., {et~al.} 2019, Journal of Geophysical
  Research: Space Physics, 124, 7170,
  \dodoi{https://doi.org/10.1029/2019JA026912}

\bibitem[{Mailyan {et~al.}(2016)Mailyan, Briggs, Cramer, Fitzpatrick, Roberts,
  Stanbro, Connaughton, McBreen, Bhat, \& Dwyer}]{Mailyan2016}
Mailyan, B.~G., Briggs, M.~S., Cramer, E.~S., {et~al.} 2016, Journal of
  Geophysical Research: Space Physics, 121, 11,346,
  \dodoi{https://doi.org/10.1002/2016JA022702}

\bibitem[{{Maiorano} {et~al.}(2022){Maiorano}, {Palazzi}, {Rossi},
  {et~al.}}]{gcn32850}
{Maiorano}, E., {Palazzi}, E., {Rossi}, A., {et~al.} 2022, GRB Coordinates
  Network, 32850, 1.
\newblock \url{https://gcn.gsfc.nasa.gov/gcn3/32850.gcn3}

\bibitem[{Mazets {et~al.}(1999)Mazets, Cline, Aptekar, Butterworth, Frederiks,
  Golenetskii, Il'inskii, \& Pal'shin}]{Mazets1999}
Mazets, E.~P., Cline, T.~L., Aptekar, R.~L., {et~al.} 1999, \apj, 25, 628.
\newblock \doarXiv{astro-ph/9905196}

\bibitem[{Meegan {et~al.}(2009)Meegan, Lichti, Bhat, Bissaldi, Briggs,
  Connaughton, Diehl, Fishman, Greiner, Hoover, van~der Horst, von Kienlin,
  Kippen, Kouveliotou, McBreen, Paciesas, Preece, Steinle, Wallace, Wilson, \&
  Wilson-Hodge}]{Meegan2009}
Meegan, C., Lichti, G., Bhat, P.~N., {et~al.} 2009, \apj, 702, 791,
  \dodoi{10.1088/0004-637x/702/1/791}

\bibitem[{{M{\'e}sz{\'a}ros} \& {Rees}(1993)}]{Meszaros1993}
{M{\'e}sz{\'a}ros}, P., \& {Rees}, M.~J. 1993, ApJ, 405, 278,
  \dodoi{10.1086/172360}

\bibitem[{{M{\'e}sz{\'a}ros} \& {Rees}(1997)}]{Meszaros+97ag}
---. 1997, \apj, 476, 232, \dodoi{10.1086/303625}

\bibitem[{{Mitchell} {et~al.}(2022){Mitchell}, {Phlips}, \&
  {Johnson}}]{gcn32746}
{Mitchell}, L.~J., {Phlips}, B.~F., \& {Johnson}, W.~N. 2022, GRB Coordinates
  Network, 32746, 1

\bibitem[{{Nappo} {et~al.}(2014){Nappo}, {Ghisellini}, {Ghirlanda}, {Melandri},
  {Nava}, \& {Burlon}}]{GammaNappo}
{Nappo}, F., {Ghisellini}, G., {Ghirlanda}, G., {et~al.} 2014, \mnras, 445,
  1625, \dodoi{10.1093/mnras/stu1832}

\bibitem[{Narayan {et~al.}(1992)Narayan, Paczynski, \& Piran}]{Narayan1992}
Narayan, R., Paczynski, B., \& Piran, T. 1992, The Astrophysical Journal, 395,
  L83, \dodoi{10.1086/186493}

\bibitem[{Negro {et~al.}(2022{\natexlab{a}})Negro, Manfreda, \&
  Omodei}]{gcn32690}
Negro, M., Manfreda, A., \& Omodei, N. 2022{\natexlab{a}}, \gcn, 32690.
\newblock \url{https://gcn.gsfc.nasa.gov/gcn3/32690.gcn3}

\bibitem[{Negro {et~al.}(2022{\natexlab{b}})Negro, Manfreda, Omodei, \&
  Muleri}]{gcn32754}
Negro, M., Manfreda, A., Omodei, N., \& Muleri, F. 2022{\natexlab{b}}, \gcn,
  32754.
\newblock \url{https://gcn.gsfc.nasa.gov/gcn3/32754.gcn3}

\bibitem[{Negro {et~al.}(2023)Negro, Di~Lalla, Omodei, Veres, Silvestri,
  Manfreda, Burns, Baldini, Costa, Ehlert, Kennea, Liodakis, Marshall, \&
  etc.}]{Negro_2023}
Negro, M., Di~Lalla, N., Omodei, N., {et~al.} 2023, The IXPE view of GRB
  221009A,  arXiv, \dodoi{10.48550/ARXIV.2301.01798}

\bibitem[{Norris {et~al.}(2005)Norris, Bonnell, Kazanas, Scargle, Hakkila, \&
  Giblin}]{Norris2005}
Norris, J.~P., Bonnell, J.~T., Kazanas, D., {et~al.} 2005, \apj, 627, 324,
  \dodoi{10.1086/430294}

\bibitem[{Oganesyan {et~al.}(2017)Oganesyan, Nava, Ghirlanda, \&
  Celotti}]{Oganesyan2017}
Oganesyan, G., Nava, L., Ghirlanda, G., \& Celotti, A. 2017, The Astrophysical
  Journal, 846, 137, \dodoi{10.3847/1538-4357/aa831e}

\bibitem[{Omodei {et~al.}(2022{\natexlab{a}})Omodei, Bruel, Bregeon,
  Pesce-Rollins, Horan, Bissaldi, \& Pillera}]{gcn32760}
Omodei, N., Bruel, P., Bregeon, J., {et~al.} 2022{\natexlab{a}}, \gcn, 32760.
\newblock \url{https://gcn.gsfc.nasa.gov/gcn3/32760.gcn3}

\bibitem[{Omodei {et~al.}(2022{\natexlab{b}})Omodei, Bruel, Bregeon,
  Pesce-Rollins, Horan, Bissaldi, \& Pillera}]{gcn32916}
---. 2022{\natexlab{b}}, \gcn, 32916.
\newblock \url{https://gcn.gsfc.nasa.gov/gcn3/32916.gcn3}

\bibitem[{Paczynski(1986)}]{Paczynski1986}
Paczynski, B. 1986, The Astrophysical Journal, 308, L43

\bibitem[{Pelassa {et~al.}(2010)Pelassa, Preece, Piron, Omodei, \&
  Guiriec}]{Pelassa2010}
Pelassa, V., Preece, R., Piron, F., Omodei, N., \& Guiriec, S. 2010, \arxive,
  \dodoi{10.48550/ARXIV.1002.2617}

\bibitem[{Pillera {et~al.}(2022)Pillera, Bissaldi, Omodei, Mura, \&
  Longo}]{gcn32658}
Pillera, R., Bissaldi, E., Omodei, N., Mura, G.~L., \& Longo, F. 2022, \gcn,
  32658.
\newblock \url{https://gcn.gsfc.nasa.gov/gcn3/32658.gcn3}

\bibitem[{Poolakkil {et~al.}(2021)Poolakkil, Preece, Fletcher, Goldstein, Bhat,
  Bissaldi, Briggs, Burns, Cleveland, Giles, Hui, Kocevski, Lesage, Mailyan,
  Malacaria, Paciesas, Roberts, Veres, von Kienlin, \&
  Wilson-Hodge}]{Poolakkil2021}
Poolakkil, S., Preece, R., Fletcher, C., {et~al.} 2021, \apj, 913, 60,
  \dodoi{10.3847/1538-4357/abf24d}

\bibitem[{Preece {et~al.}(1998)Preece, Briggs, Mallozzi, Pendleton, Paciesas,
  \& Band}]{Preece1998}
Preece, R.~D., Briggs, M.~S., Mallozzi, R.~S., {et~al.} 1998, The Astrophysical
  Journal, 506, L23, \dodoi{10.1086/311644}

\bibitem[{Ravasio {et~al.}(2018)Ravasio, Oganesyan, Ghirlanda, Nava,
  Ghisellini, Pescalli, \& Celotti}]{Ravasio2018}
Ravasio, M., Oganesyan, G., Ghirlanda, G., {et~al.} 2018, \aa, 613, 11,
  \dodoi{10.1051/0004-6361/201732245}

\bibitem[{Rees \& {M{\'e}sz{\'a}ros}(1994)}]{Rees1994}
Rees, M.~J., \& {M{\'e}sz{\'a}ros}, P. 1994, The Astrophysical Journal, 430,
  L93, \dodoi{10.1086/187446}

\bibitem[{{Ripa} {et~al.}(2022){Ripa}, {Pal}, {Werner}, {Ohno}, {Takahashi},
  {M{\'e}sz{\'a}ros}, {Csak}, {Dafcikova}, {Munz}, {Husarikova}, {Breuer},
  {Topinka}, {Hroch}, {Urbanec}, {Kasal}, {Povalac}, {Hudec}, {Kapus}, {Frajt},
  {Laszlo}, {Koleda}, {Smelko}, {Hanak}, {Lipovsky}, {Galgoczi}, {Uchida},
  {Poon}, {Matake}, {Uchida}, {Bozoki}, {Dalya}, {Enoto}, {Frei}, {Friss},
  {Fukazawa}, {Hirose}, {Hisadomi}, {Ichinohe}, {Kapas}, {Kiss}, {Mizuno},
  {Nakazawa}, {Odaka}, {Takatsy}, {Torigoe}, {Kogiso}, {Yoneyama}, {Moritaki},
  {Kano}, \& {GRBAlpha Collaboration.}}]{gcn32685}
{Ripa}, J., {Pal}, A., {Werner}, N., {et~al.} 2022, GRB Coordinates Network,
  32685, 1

\bibitem[{Ripa {et~al.}(2023)Ripa, Takahashi, Fukazawa, Werner, Munz, Pal,
  Ohno, Dafcikova, {M{\'e}sz{\'a}ros}, Csak, Husarikova, Kolar, Galgoczi, \&
  etc.}]{GRBAplha_221009A}
Ripa, J., Takahashi, H., Fukazawa, Y., {et~al.} 2023, The peak-flux of GRB
  221009A measured with GRBAlpha,  arXiv, \dodoi{10.48550/ARXIV.2302.10047}

\bibitem[{{Ryde} {et~al.}(2011){Ryde}, {Pe'er}, {Nymark}, {Axelsson},
  {Moretti}, {Lundman}, {Battelino}, {Bissaldi}, {Chiang}, {Jackson},
  {Larsson}, {Longo}, {McGlynn}, \& {Omodei}}]{Ryde2011}
{Ryde}, F., {Pe'er}, A., {Nymark}, T., {et~al.} 2011, \mnras, 415, 3693,
  \dodoi{10.1111/j.1365-2966.2011.18985.x}

\bibitem[{Sari {et~al.}(1998)Sari, Piran, \& Narayan}]{Sari1998}
Sari, R., Piran, T., \& Narayan, R. 1998, The Astrophysical Journal, 497, L17,
  \dodoi{10.1086/311269}

\bibitem[{Schnoor {et~al.}(2022)Schnoor, Nicholson, \& Welch}]{gcn32744}
Schnoor, P.~W., Nicholson, P., \& Welch, D.~L. 2022, \gcn, 32744.
\newblock \url{https://gcn.gsfc.nasa.gov/gcn3/32744.gcn3}

\bibitem[{Svinkin {et~al.}(2022)Svinkin, Frederiks, Ridnaia, Lysenko, Cline,
  Team, von Kienlin, Zhang, Rau, Savchenko, Bozzo, Ferrigno, Team, Goldstein,
  Briggs, Wilson-Hodge, Team, Barthelmy, Cummings, Krimm, Palmer, Tohuvavohu,
  \& Team}]{gcn32641}
Svinkin, D., Frederiks, D., Ridnaia, A., {et~al.} 2022, \gcn, 32641.
\newblock \url{https://gcn.gsfc.nasa.gov/gcn3/32641.gcn3}

\bibitem[{{The IceCube Collaboration}(2022)}]{gcn32665}
{The IceCube Collaboration}. 2022, \gcn, 32665.
\newblock \url{https://gcn.gsfc.nasa.gov/gcn3/32665.gcn3}

\bibitem[{{Tiengo} {et~al.}(2022){Tiengo}, {Pintore}, {Mereghetti}, \&
  {Salvaterra}}]{atel15661}
{Tiengo}, A., {Pintore}, F., {Mereghetti}, S., \& {Salvaterra}, R. 2022, The
  Astronomer's Telegram, 15661, 1

\bibitem[{van~der Klis(1989)}]{vanderklis1989}
van~der Klis, M. 1989, Fourier Techniques in X-Ray Timing, Vol. 324 (Dordrecht:
  Springer Netherlands), 27--69, \dodoi{10.1007/978-94-009-2273-0_3}

\bibitem[{Veres {et~al.}(2022)Veres, Burns, Bissaldi, Lesage, \&
  Roberts}]{gcn32636}
Veres, P., Burns, E., Bissaldi, E., Lesage, S., \& Roberts, O. 2022, \gcn,
  32636.
\newblock \url{https://gcn.gsfc.nasa.gov/gcn3/32636.gcn3}

\bibitem[{Vianello {et~al.}(2018)Vianello, Gill, Granot, Omodei, Cohen-Tanugi,
  \& Longo}]{Vianello_2018}
Vianello, G., Gill, R., Granot, J., {et~al.} 2018, The Astrophysical Journal,
  864, 163, \dodoi{10.3847/1538-4357/aad6ea}

\bibitem[{von Kienlin {et~al.}(2020)von Kienlin, Meegan, Paciesas, Bhat,
  Bissaldi, Briggs, Burns, Cleveland, Gibby, Giles, Goldstein, Hamburg, Hui,
  Kocevski, Mailyan, Malacaria, Poolakkil, Preece, Roberts, Veres, \&
  Wilson-Hodge}]{vonKienlin2020}
von Kienlin, A., Meegan, C.~A., Paciesas, W.~S., {et~al.} 2020, \apj, 893, 46,
  \dodoi{10.3847/1538-4357/ab7a18}

\bibitem[{Williams(2023)}]{gcn33305}
Williams, M. 2023, GRB Coordinates Network, 33305, 1.
\newblock \url{https://gcn.gsfc.nasa.gov/gcn3/33305.gcn3}

\bibitem[{Williams {et~al.}(2023)Williams, Kennea, Dichiara, Kobayashi,
  Iwakiri, Beardmore, Evans, Heinz, Lien, Oates, Negoro, Cenko, Buisson,
  Hartmann, Jaisawal, Kuin, Lesage, Page, Parsotan, Pasham, Sbarufatti, Siegel,
  Sugita, Younes, Ambrosi, Arzoumanian, Bernardini, Campana, Capalbi, Caputo,
  D'Ai, D'Avanzo, D'Elia, De~Pasquale, Eyles-Ferris, Ferrara, Gendreau, Gropp,
  Kawai, Klingler, Laha, Melandri, Mihara, Moss, O'Brien, Osborne, Palmer,
  Perri, Serino, Sonbas, Stamatikos, Starling, Tagliaferri, Tohuvavohu, Zane,
  \& Ziaeepour}]{Williams2023}
Williams, M.~A., Kennea, J.~A., Dichiara, S., {et~al.} 2023, GRB 221009A:
  Discovery of an Exceptionally Rare Nearby and Energetic Gamma-Ray Burst,
  arXiv, \dodoi{10.48550/ARXIV.2302.03642}

\bibitem[{Wilson-Hodge {et~al.}(2012)Wilson-Hodge, Case, Cherry, Rodi,
  Camero-Arranz, Jenke, Chaplin, Beklen, Finger, Bhat, Briggs, Connaughton,
  Greiner, Kippen, Meegan, Paciesas, Preece, \& von Kienlin}]{WilsonHodge2012}
Wilson-Hodge, C.~A., Case, G.~L., Cherry, M.~L., {et~al.} 2012, \apjs, 201, 33,
  \dodoi{10.1088/0067-0049/201/2/33}

\bibitem[{{Woosley}(1993)}]{Woosley1993}
{Woosley}, S.~E. 1993, Astrophysical Journal, 405, 273, \dodoi{10.1086/172359}

\bibitem[{{Xiao} {et~al.}(2022{\natexlab{a}}){Xiao}, {Krucker}, {Daniel}, \&
  {STIX Team}}]{gcn32661}
{Xiao}, H., {Krucker}, S., {Daniel}, R., \& {STIX Team}. 2022{\natexlab{a}},
  GRB Coordinates Network, 32661, 1.
\newblock \url{https://gcn.gsfc.nasa.gov/gcn3/32661.gcn3}

\bibitem[{{Xiao} {et~al.}(2022{\natexlab{b}}){Xiao}, {Zhang}, {Zhu}, {Xiong},
  {Gao}, {Xu}, {Zhang}, {Peng}, {Li}, {Zhang}, {Lu}, {Lin}, {Liu}, {Zhang},
  {Ge}, {Tuo}, {Xue}, {Fu}, {Liu}, {Li}, {Wang}, {Zheng}, {Wang}, {Jiang},
  {Li}, {Liu}, {Cao}, {Cai}, {Yi}, {Zhao}, {Xie}, {Li}, {Luo}, {Liao}, {Song},
  {Zhang}, {Qu}, {Liu}, {Li}, {Xu}, \& {Li}}]{xiao2022_qpo}
{Xiao}, S., {Zhang}, Y.-Q., {Zhu}, Z.-P., {et~al.} 2022{\natexlab{b}}, arXiv
  e-prints, arXiv:2205.02186, \dodoi{10.48550/arXiv.2205.02186}

\bibitem[{Zhang \& Yan(2010)}]{Zhang2010}
Zhang, B., \& Yan, H. 2010, The Astrophysical Journal, 726, 90,
  \dodoi{10.1088/0004-637x/726/2/90}

\bibitem[{Zhang {et~al.}(2016)Zhang, Uhm, Connaughton, Briggs, \&
  Zhang}]{Zhang2016}
Zhang, B.-B., Uhm, Z.~L., Connaughton, V., Briggs, M.~S., \& Zhang, B. 2016,
  \apj, 816, 72, \dodoi{10.3847/0004-637X/816/2/72}

\bibitem[{Zhang {et~al.}(2018)Zhang, Zhang, Castro-Tirado, Dai, Tam, Wang, Hu,
  Karpov, Pozanenko, Zhang, Mazaeva, Minaev, Volnova, \& etc.}]{Zhang2018}
Zhang, B.~B., Zhang, B., Castro-Tirado, A.~J., {et~al.} 2018, \nat, 2, 69,
  \dodoi{10.1038/s41550-017-0309-8}

\end{thebibliography}




%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% END DOCUMENT %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}




