

\documentclass{article} % For LaTeX2e
\usepackage{iclr2023_conference,times}

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{mathtools}
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{float}
% \usepackage[moderate]{savetrees}


\title{Deep Declarative Dynamic Time Warping for End-to-End Learning of Alignment Paths}

% Authors must not appear in the submitted version. They should be hidden
% as long as the \iclrfinalcopy macro remains commented out below.
% Non-anonymous submissions will be rejected without review.

\author{Ming Xu$^{1, 2}$ \quad Sourav Garg\textsuperscript{1} \quad Michael Milford$^{1}$ \quad Stephen Gould$^{2}$ \\
  $^{1}$Queensland University of Technology \quad $^{2}$Australian National University \\
  \texttt{\{mingda.xu, stephen.gould\}@anu.edu.au} \\
  \texttt{\{s.garg, michael.milford\}@qut.edu.au}
}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
\begin{document}


\maketitle

\input{tex/0-abstract}
\input{tex/1-introduction}
\input{tex/2-relatedworks}
\input{tex/3-method}
\input{tex/4-experiments}
\input{tex/5-discussion}

\subsubsection*{Acknowledgments}

S. Garg and M. Milford are with the QUT Centre for Robotics, School of Electrical Engineering and Robotics at the Queensland University of Technology. M. Xu and S. Gould are with the School of Computing, College of Engineering, Computing and Cybernetics at the Australian National University. The majority of the work was completed while M. Xu was at the QUT Centre for Robotics. M. Xu was supported by an Australian Government Research Training Program (RTP) Scholarship as well as by the QUT Centre for Robotics. M. Milford is supported by funding from ARC Laureate Fellowship (FL210100156) funded by the Australian Government. S. Gould is the recipient of an ARC Future Fellowship (FT200100421) funded by the Australian Government. Finally, we thank the reviewers and the area chair for their insightful and constructive comments during the discussion period.

\subsubsection*{Reproducibility Statement}

To facilitate reproducibility, we provide a reference implementation for our method, including code to reproduce all results across both of the experiments presented in the paper. Our code provides the full training and evaluation pipeline for all methods. In addition, we provide detailed instructions for setting up the datasets for training and evaluation, again for both experiments, as per the descriptions provided in the Appendix. Furthermore, we make publicly available the model checkpoint for the pre-trained single-image baseline network used for sequence fine-tuning in the VPR experiments.

\bibliography{iclr2023_conference}
\bibliographystyle{iclr2023_conference}

\appendix
\input{tex/6-appendix}

\end{document}
