\begin{thebibliography}{8}
\bibitem{ref_Kaggle}
  https://www.kaggle.com/datasets
\bibitem{ref_HuggingFaceHub}
  {https://huggingface.co/datasets}
\bibitem{ref_RDCL2019}
{Christian Clausner, RDCL2019 Competition Dataset (Recognition of Documents with Complex Layouts) (RDCL2019) ,1,ID:RDCL2019\_1,URL:https://tc11.cvc.uab.es/datasets/RDCL2019_1}

\bibitem{ref_Tobacco800}
{David Doermann, Tobacco 800 Dataset (Tobacco800) ,1,ID:Tobacco800_1,URL:https://tc11.cvc.uab.es/datasets/Tobacco800_1}

\bibitem{ref_icdar}
{Harold Mouchère, ICDAR 2019 Competition on Recognition of Handwritten Mathematical Expressions and Typeset Formula Detection (ICDAR2019-CROHME-TDF) ,1,ID:ICDAR2019-CROHME-TDF\_1,URL:https://tc11.cvc.uab.es/datasets/ICDAR2019-CROHME-TDF_1}

\bibitem{ref_NoisyOffice}
{Castro-Bleda, MJ.; España Boquera, S.; Pastor Pellicer, J.; Zamora Martínez, FJ. (2020). The NoisyOffice Database: A Corpus To Train Supervised Machine Learning Filters For Image Processing. The Computer Journal. 63(11):1658-1667. https://doi.org/10.1093/comjnl/bxz098}

\bibitem{ref_RVL-CDIP}
  @article{DBLP:journals/corr/HarleyUD15,
  author    = {Adam W. Harley and
               Alex Ufkes and
               Konstantinos G. Derpanis},
  title     = {Evaluation of Deep Convolutional Nets for Document Image Classification
               and Retrieval},
  journal   = {CoRR},
  volume    = {abs/1502.07058},
  year      = {2015},
  url       = {http://arxiv.org/abs/1502.07058},
  eprinttype = {arXiv},
  eprint    = {1502.07058},
  timestamp = {Mon, 13 Aug 2018 16:48:54 +0200},
  biburl    = {https://dblp.org/rec/journals/corr/HarleyUD15.bib},
  bibsource = {dblp computer science bibliography, https://dblp.org}
}

\bibitem{ref_NoisyOfficeDatabase}
{F. Zamora-Martinez, S. España-Boquera and M. J. Castro-Bleda, Behaviour-based Clustering of Neural Networks applied to Document Enhancement, in: Computational and Ambient Intelligence, pages 144-151, Springer, 2007.}

\bibitem{ref_UCIMLR}
{Dua, D. and Graff, C. (2019). UCI Machine Learning Repository [http://archive.ics.uci.edu/ml]. Irvine, CA: University of California, School of Information and Computer Science.}

\bibitem{ref_DocCreator}
  {Journet Nicholas, Visani Muriel, Mansencal Boris, Van-Cuong Kieu, Billy Antoine, DocCreator: A New Software for Creating Synthetic Ground-Truthed Document Images. J. Imaging 2017, 3, 62.}
\bibitem{ref_goldmann}
  {Pau Riba, Anjan Dutta, Lutz Goldmann, Alicia Fornes, Oriol Ramos, Josep LLados: "Table Detection in Invoice Documents by Graph Neural Networks", ICDAR, 2019.}
\bibitem{ref_zenodo}
  {Layout Analysis Groundtruth for the RVL-CDIP Dataset. Goldmann, Lutz. 10.5281/zenodo.3257319}
\bibitem{ref_tobacco800gt1}
  {Guangyu Zhu, Yefeng Zheng, David Doermann,and Stefan Jaeger. Multi-scale Structural Saliency for Signature Detection. In Proc. IEEE Conf. Computer Vision and Pattern Recognition (CVPR 2007), pp. 1‐8, 2007.}
\bibitem{ref_tobacco800gt2}
  {Guangyu Zhu and David Doermann. Automatic Document Logo Detection. In Proc. 9th Int. Conf. Document Analysis and Recognition (ICDAR 2007), pp. 864‐868, 2007.}