\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}              

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{dsfont}
\usepackage{booktabs}

\usepackage{times}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{tabu}
\usepackage{multirow}
\usepackage{color}
\usepackage[abs]{overpic}
\usepackage{comment}
\usepackage{textcomp}
\usepackage[accsupp]{axessibility} 

\def\eg{\emph{e.g.},}
\def\etal{\emph{et al.}}
\def\ie{\emph{i.e.},}
\def\etc{\emph{etc.}}
\def\wrt{w.r.t.}
\def\vs{\emph{vs.}}
\definecolor{mypink}{RGB}{236, 2, 141}


\usepackage[pagebackref,breaklinks,colorlinks]{hyperref}


\usepackage[capitalize]{cleveref}
\crefname{section}{Sec.}{Secs.}
\Crefname{section}{Section}{Sections}
\Crefname{table}{Table}{Tables}
\crefname{table}{Tab.}{Tabs.}

\newcommand{\peicomment}[1]{\textcolor[rgb]{1,0,0} {#1}}
\newcommand*{\affaddr}[1]{#1} 
\newcommand*{\affmark}[1][*]{\textsuperscript{#1}}
\newcommand*{\email}[1]{\small{\texttt{#1}}}

\begin{document}

\title{Joint Visual Grounding and Tracking with Natural Language Specification}

\author{Li Zhou\affmark[1], Zikun Zhou\affmark[2,1*], Kaige Mao\affmark[1], and Zhenyu He\affmark[1,*]\\\affaddr{\affmark[1]Harbin Institute of Technology, Shenzhen}\quad\affaddr{\affmark[2]Peng Cheng Laboratory}\\
\email{lizhou.hit@gmail.com\quad zhouzikunhit@gmail.com\quad maokaige.hit@gmail.com\quad zhenyuhe@hit.edu.cn}\\
}

\maketitle
\renewcommand{\thefootnote}{\fnsymbol{footnote}} 
\footnotetext{$^{*}$Corresponding authors: Zikun Zhou and Zhenyu He.}

\begin{abstract}
\input{abstract}
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
\input{introduction}

 
\section{Related work}
\input{related_work}

\section{Method}
\input{method}


\section{Experiments}
\input{experiments}

\section{Conclusion}
\input{conclusion}

\vspace{1mm}
\noindent\textbf{Acknowledgement.}
This study was supported in part by the National Natural Science Foundation of China (No. 62172126), the Shenzhen Research Council (No. JCYJ20210324120202006), and the Key Research Project of Peng Cheng Laboratory (No. PCL2021A07).

{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}

\end{document}
