\subsection{Coordinate frames}
\label{sec:supp-coord-frames}

\input{sections/figs/coordinate.tex}

\Cref{fig:coor} illustrates the difference between the different coordinate frames.
\citet{jiang2022opd}'s dataset contained images with only a single object (see \Cref{fig:coor} left).
When a scene contains only one object, the object coordinate is the same as the global scene coordinate.
In contrast, when there are multiple objects, the global scene coordinates and the object coordinate frame can be different.
The object coordinate frame ($\mathbf{O_A}$ and $\mathbf{O_B}$ for objects $\mathbf{A}$ and $\mathbf{B}$ in \Cref{fig:coor}) for each object are centered at the center of each object, with the axes aligned to the bounding box of the object (with +Z as front, and +Y as up), while the global scene coordinate is a single coordinate frame at the center of the scene.
The camera coordinate frame is used for projecting the 3D scene onto the image plane and has +Z facing into the camera, and +Y as up. 

\input{sections/figs/pose_vis.tex}

\subsection{Object pose for training}
\label{sec:supp-object-pose}

\Cref{fig:pose_vis} shows an example kitchen scene in our dataset containing multiple objects with openable parts.
In such scenarios, some care has to be taken to construct appropriate single global pose and multiple object poses information to train each of the architecture variants.

\mypara{Single global pose}.
Since \ourdatamulti images contain an arbitrary number of objects, there is no notion of a single global object pose.
Therefore, we train with the scene coordinates defining a global pose, and transform from camera coordinates to these scene coordinates.
All relevant motion parameters are also transformed to the scene coordinates.

\mypara{Multiple object poses}.
In this case, the object pose is defined by the transformation between camera coordinates and canonical object coordinates, using a consistently defined front and up orientation for each object pose.
See \Cref{fig:pose_vis} bottom right for example object coordinate frames.

