\section{Statistics on the BlurHand dataset}
\label{sec:detail_blurhand}
% 

In Table~\ref{table:blurhand_detail}, we report the detailed number of training samples.
We note that the right and left hands are evenly distributed in the BlurHand.
% 
In \figref{motion_blur_strength_statistics}, we further report additional measurements, namely joint motion magnitude, to present the statistics on the blur strength of our BlurHand.
% 
% Specifically, we first measure 2D joint displacements between neighboring frames from five sharp frames, which constructs the blurry frame.
In detail, we first prepare five sequential sharp frames, which construct a single blurry frame in our BlurHand.
% 
Then we calculate the 2D joint distance between two adjacent sharp frames using the GT joint positions.
% 
Finally, we add all distances for each joint, which we denote as joint motion magnitude.
% 
We note that the large joint motion magnitude means a strong blur exists in hand.
% 
Our BlurHand contains samples with various joint motion magnitude in both the train and test sets.
% 

\section{Results from various deblurring methods}
\label{sec_supp:deblurring}
% In Tables~\textcolor{red}{2} and \textcolor{red}{3} in our main manuscript, we compared our BlurHandNet with the combination of state-of-the-art 3D hand mesh estimation methods~\cite{moon2022accurate, lin2021end, moon2020i2l} and off-the-shelf deblurring method~\cite{chen2022simple}.
In Tables~\textcolor{red}{2} and \textcolor{red}{3} in our main manuscript, we compared our BlurHandNet with the combination of state-of-the-art 3D hand mesh estimation methods~[\fakeref{16}, \fakeref{21}, \fakeref{22}] and off-the-shelf deblurring method~[\fakeref{3}].
% 
% In Table~\ref{sup_table:deblurring}, we additionally compare the results from another widely used deblurring method, DeepDeblur~\cite{nah2017deep}, as the final mesh estimation results might be dependent on the performance of deblurring methods.
% In Table~\ref{sup_table:deblurring}, we additionally compare the results from another widely used deblurring method, DeepDeblur~\cite{nah2017deep}, as the final mesh estimation results might be dependent on the performance of deblurring methods.
In Table~\ref{sup_table:deblurring}, we additionally compare the results from another widely used deblurring method, DeepDeblur~[\fakeref{25}], as the final mesh estimation results might be dependent on the performance of deblurring methods.
% Please note that NAFNet~\cite{chen2022simple} is a deblurring method that we used in the main manuscript.
Please note that NAFNet~[\fakeref{3}] is a deblurring method that we used in the main manuscript.
% 
%As shown in Table~\ref{sup_table:deblurring},
% Our BlurHandNet still outperforms the case when we use DeepDeblur~\cite{nah2017deep} as the deblurring method.
Our BlurHandNet still outperforms the case when we use DeepDeblur~[\fakeref{25}] as the deblurring method.
% 
The results again demonstrate that utilizing temporal information is useful rather than simply adopting deblurring methods.
% 


\input{latex/supple/tables/statistics}
\input{latex/supple/figures/statistics/motion_blur_strength_statistics}
\input{latex/supple/tables/deblurring}