\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{iccv}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{algorithmic}
\usepackage{multirow}

\usepackage[linesnumbered,boxed,ruled,commentsnumbered]{algorithm2e}
\newcommand\sanbao[1]{\textcolor{blue}{Sanbao: #1}}
\newcommand\hsy[1]{\textcolor{red}{Songyang: #1}}
\newcommand\hsh[1]{\textcolor{red}{Sihong: #1}}
% Following added by Songyang
\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{prop}{Proposition}
\newtheorem{defi}{Definition}
\newtheorem{lemma}[theorem]{Lemma}
% \theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newenvironment{claim}[1]{\par\noindent\underline{Claim:}\space#1}{}
\newenvironment{claimproof}[1]{\par\noindent\underline{Proof:}\space#1}{\hfill $\blacksquare$}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}


\usepackage{hyperref}
\hypersetup{
colorlinks=true,
linkcolor=blue,
filecolor=blue,      
urlcolor=blue,
citecolor=[RGB]{119,185,0},
}

\iccvfinalcopy % *** Uncomment this line for the final submission

\def\iccvPaperID{****} % *** Enter the ICCV Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ificcvfinal\pagestyle{empty}\fi

\begin{document}

%%%%%%%%% TITLE
\title{Collaborative Multi-Object Tracking with Conformal Uncertainty Propagation}

\author{Sanbao Su\\
University of Connecticut\\
{\tt\small sanbao.su@uconn.edu}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Songyang Han\\
University of Connecticut\\
{\tt\small songyang.han@uconn.edu}
\and
Yiming Li\\
New York University\\
{\tt\small yimingli@nyu.edu}
\and
Zhili Zhang\\
University of Connecticut\\
{\tt\small zhili.zhang@uconn.edu}
\and
Chen Feng\\
New York University\\
{\tt\small cfeng@nyu.edu}
\and
Caiwen Ding\\
University of Connecticut\\
{\tt\small caiwen.ding@uconn.edu}
\and
Fei Miao\\
University of Connecticut\\
{\tt\small fei.miao@uconn.edu}
}

\maketitle
% Remove page # from the first page of camera-ready.
\ificcvfinal\thispagestyle{empty}\fi

%%%%%%%%% ABSTRACT
\begin{abstract}
   Object detection and multiple object tracking (MOT) are essential components of self-driving systems. Accurate detection and uncertainty quantification are both critical for onboard modules, such as perception, prediction, and planning, to improve the safety and robustness of autonomous vehicles. Collaborative object detection (COD) has been proposed to improve detection accuracy and reduce uncertainty by leveraging the viewpoints of multiple agents. However, little attention has been paid on how to leverage the uncertainty quantification from COD to enhance MOT performance. In this paper, as the first attempt, we design the uncertainty propagation framework to address this challenge, called MOT-CUP. Our framework first quantifies the uncertainty of COD through direct modeling and conformal prediction, and propogates this uncertainty information during the motion prediction and association steps. MOT-CUP is designed to work with different collaborative object detectors and baseline MOT algorithms. We evaluate MOT-CUP on V2X-Sim,  a comprehensive collaborative perception dataset, and demonstrate a $2\%$ improvement in accuracy and a $2.67\times$ reduction in uncertainty compared to the baselines, \eg, SORT and ByteTrack. MOT-CUP demonstrates the importance of uncertainty quantification in both COD and MOT, and provides the first attempt to improve the accuracy and reduce the uncertainty in MOT based on COD through uncertainty propogation. %ongoing efforts toward achieving safer and more robust autonomous systems.
\end{abstract}

%%%%%%%%% BODY TEXT
\input{introduction}

\input{relatedwork}

\input{approach}

\input{experiment}

\input{conclusion}

{\small
\bibliographystyle{ieee_fullname}
\bibliography{uncertainty}
}

\input{appendix}
\end{document}
