%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%23456789012345678901234567890123456789012345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8         9         10        11       12

\newcommand{\thetitle}{Robustified Empirical Risk Minimization with Law-Invariant, Coherent Risk Measures}

\documentclass[todo=false, usebiblatex=false, pub=true, color=true]{kulconf}                       % Comment this line out if you need a4paper
\configuretemplate{P. Coppens}{\thetitle}

\usepackage[arxiv=true]{arxivix}
\usepackage{tikzutils}
\usepackage{booktabs, multirow, tabularx}
\usepackage{array}
\usepackage[ruled, linesnumbered]{algorithm2e}

% bibliography
% \addbibresource{IEEEabrv.bib}
\addbibresource{bibliography.bib}

%In case you encounter the following error:
%Error 1010 The PDF file may be corrupt (unable to open PDF file) OR
%Error 1000 An error occurred while parsing a contents stream. Unable to analyze the PDF file.
%This is a known problem with pdfLaTeX conversion filter. The file cannot be opened with acrobat reader
%Please use one of the alternatives below to circumvent this error by uncommenting one or the other
%\pdfobjcompresslevel=0
% \pdfminorversion=4

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document


\title{\thetitle}
\author{Peter Coppens and Panagiotis Patrinos$^\dagger$
\thanks{$^\dagger$P. Coppens and P. Patrinos are with the Department of Electrical
Engineering (ESAT-STADIUS), KU Leuven, Kasteelpark Arenberg
10, 3001 Leuven, Belgium.
        {Email: \tt\footnotesize peter.coppens@kuleuven.be, panos.patrinos@kuleuven.be}}%
\thanks{This work was supported by: the Research Foundation
Flanders (FWO) PhD grant 11E5520N and research projects G0A0920N, G086518N and G086318N;
Research Council KU Leuven C1 project No. C14/18/068; Fonds de la Recherche 
Scientifique - FNRS and the FWO - Vlaanderen under 
EOS project no 30468160 (SeLMA); EU's Horizon 2020 research and innovation programme: Marie Skłodowska-Curie grant No. 953348.}%
}%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% notation

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
    In this work we consider law-invariant, coherent risk measures as a proxy-cost for data-driven expected risk 
    minimization. We show how such risks serve as point-wise high-confidence upper bounds of the expected risk. 
    The confidence level can be determined tightly for any number of samples. Conversely we also illustrate how to 
    calibrate risk measures to act as a high-confidence upper bound with some user specified confidence. Numerical 
    experiments then illustrate how the resulting proxy-cost both generalizes better and is less sensitive to tuning 
    parameters compared to the usual empirical risk minimization approach. 
\end{abstract}


\begin{pub}
\begin{IEEEkeywords}
\todo*{Placeholder keywords.}
\end{IEEEkeywords}
\end{pub}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{content/intro.tex}
\input{content/statistics.tex}
\input{content/distortion.tex}
\input{content/calibration.tex}
\input{content/cases.tex}

\printbibliography{}
\appendices
\input{content/appendix/monotone.tex}
\input{content/appendix/statistics.tex}
\input{content/appendix/distortion.tex}
\input{content/appendix/calibration.tex}
\input{content/appendix/tractable.tex}
\input{content/appendix/svm.tex}

\end{document}

