%% Time-stamp: <2023-11-01 16:11:24 sglass>
\begingroup
\pretolerance=200 
\tolerance=1800  
%%%%%% leave next line empty and set first mark there


%1%Achdou Buera Lasry Lions Moll 2014
    \brefitem[Achdou et al$.$ (2014)]{ABLLM14}
    \aut{Achdou, Yves, Francisco J.\ Buera, Jean-Michel Lasry, Pierre-Louis Lions, and Benjamin Moll}
    \anno{2014} 
    \jtitle{Partial differential equations in macroeconomics}
    \journal{Philosohpical Transactions of the Royal Society of London} {A372} 20130397.
%2%


%1%Achdou Camilli Capuzzo-Dolcetta 2013
    \brefitem[Achdou et al$.$ (2013)]{ACD13}
    \aut{Achdou, Yves, Fabio Camilli, and Italo Capuzzo-Dolcetta}
    \anno{2013} 
    \jtitle{Mean field games: convergence of a finite difference method}
    \journal{Siam Journal on Numerical Analysis} {51} 2585-\nobreak2612.
%2%


%1%Achdou Capuzzo-Dolcetta 2010
    \brefitem[Achdou and Capuzzo-Dolcetta (2010)]{AD10}
    \aut{Achdou, Yves, and Italo Capuzzo-Dolcetta}
    \anno{2010} 
    \jtitle{Mean field games: numerical methods}
    \journal{Siam Journal on Numerical Analysis} {48} 1136-\nobreak1162.
%2%



%1%Achdou Carlier Petit Tonon 2023
         \brefitem[Achdou et al$.$ (2023)]{ACPT23}
         \aut{Achdou, Yves, Guillaume Carlier, Quentin Petit, Daniela Tonon}
	 \anno{2023} 
	 \btitle{A mean field model for the interactions between firms on the markets of their inputs}
         \journal{Mathematics and Financial Economics} (to appear).
%2%


%1%Achdou Han Lasry Lions Moll 2022
    \brefitem[Achdou et al$.$ (2022a)]{AHLLM17}
    \aut{Achdou, Yves, Jiequn Han, Jean-Michel Lasry, Pierre-Louis Lions, and Benjamin Moll}
    \anno{2022} 
    \jtitle{Income and wealth distribution in macroeconomics: a continuous-time approach}
    \journal{Review of Economic Studies} {89} 45-\nobreak86.
%2%



%1%Achdou Lasry Lions 2022
         \brefitem[Achdou et al$.$ (2022b)]{ALL22}
         \aut{Achdou, Yves, Jean-Michel Lasry, and Pierre-Louis Lions}
	 \anno{2022} 
	 \btitle{Simulating nu\-me\-ri\-cally the Krusell-Smith model with neural networks} 
\book{\href{https://doi.org/10.48550/arXiv.2211.07698}{DOI: 10.48550 / arXiv.2211.07698}}.
%2%


%1%Achdou Porretta 2016
    \brefitem[Achdou and Porretta (2016)]{AP16}
    \aut{Achdou, Yves, and Alessio Porretta}
    \anno{2016} 
    \jtitle{Convergence of a finite difference scheme to weak solutions of the system of partial differential equation arising in mean field games}
    \journal{Siam Journal on Numerical Analysis} {54} 161-\nobreak186.
%2%


%1%Acikgoz 2018
    \brefitem[Açıkgöz (2018)]{Aci18}
    \aut{Açıkgöz, Ömer T}
    \anno{2018} 
    \jtitle{On the existence and uniqueness of stationary equilibrium in Bewley economies with production}
    \journal{Journal of Economic Theory} {173} 18-\nobreak55.
%2%


%1%Ahn Kaplan Moll Winberry Wolf 2018
    \brefitem[Ahn et al$.$ (2018)]{AKMWW18}
    \aut{Ahn, SeHyoun, Greg Kaplan, Benjamin Moll, Thomas Winberry, and Christian Wolf}
    \anno{2018} 
\jtitle{When inequality matters for macro and macro matters for inequality}
\book{In: Eichenbaum, M., Hurst, E., and Parker, J.~A.~(Eds.), {\it NBER Macroeconomics Annual 2017, vol.~32\/}. Chicago, IL: University of Chicago Press, pp.~1-75}.
%2%


%1%Aiyagari 1993
    \brefitem[Aiyagari (1993)]{Aiya93}
    \aut{Aiyagari, S.~Rao}
    \anno{1993} 
\jtitle{Uninsured idiosyncratic risk and aggregate saving}
\book{\it Working paper 502, Federal Reseve Bank of Minneapolis}.
%2%


%1%Aiyagari 1994
    \brefitem[Aiyagari (1994)]{Aiya94}
    \aut{Aiyagari, S.~Rao}
    \anno{1994} 
\jtitle{Uninsured idiosyncratic risk and aggregate saving}
\journal{The Quarterly Journal of Economics} 109 659-\nobreak684.
%2%


%1%Aiyagari 1995
    \brefitem[Aiyagari (1995)]{Aiya95}
    \aut{Aiyagari, S.~Rao}
    \anno{1995} 
    \jtitle{Optimal capital income taxation with incomplete markets, borrowing constraints and constant discounting}
    \journal{Journal of Political Economy} {6} 1158-\nobreak1175.
%2%


%1%Algan Allais DenHaan 2010
    \brefitem[Algan et al$.$ (2010)]{AAD10}
    \aut{Algan, Yann, Olivier Allais, and Wouter J.~Den Haan}
    \anno{2010} 
    \jtitle{Solving the incomplete markets model with aggregate uncertainty using parameterized cross-sectional distributions}
    \journal{Journal of Economic Dynamics \& Control} {34} 59-\nobreak68.
%2%


%1%Aumann 1964
    \brefitem[Aumann (1964)]{Aum64}
    \aut{Aumann, Robert J}
    \anno{1964} 
    \jtitle{Markets with a continuum of traders}
    \journal{Econometrica} {32} 39-\nobreak50.
%2%


%1%Aumann 1966
    \brefitem[Aumann (1966)]{Aum66}
    \aut{Aumann, Robert J}
    \anno{1966} 
    \jtitle{Existence of competitive equilibria in markets with a continuum of traders}
    \journal{Econometrica} {34} 1-\nobreak17.
%2%



%1%Bayer Luetticke 2020
    \brefitem[Bayer and Luetticke (2020)]{BL20}
    \aut{Bayer, Christian, and Ralph Luetticke}
    \anno{2020} 
    \jtitle{Solving discrete time heterogeneous agent models with aggregate risk and many idiosyncratic states by perturbation}
    \journal{Quantitative Economics} {11} 1253-\nobreak1288.
%2%



%1%Benamou Brenier 2000
    \brefitem[Benamou and Brenier (2000)]{BB00}
    \aut{Benamou, Jean-David, and Yann Brenier}
    \anno{2000} 
\jtitle{A computational fluid mechanics solution to the Monge-Kantorovich mass transfer problem}
\journal{Numerische Mathematik} {84} 375-\nobreak393.
%2%



%1%Benamou Carlier Santambrogio 2017
    \brefitem[Benamou et al$.$ (2017)]{BCS17}
    \aut{Benamou, Jean-David, Guillaume Carlier, and Filippo Santambrogio}
    \anno{2017} 
\jtitle{Variational Mean Field Games}
\book{In: Bellomo, N., Degond, P., and Tadmor, E.~(Eds.), {\it Active Particles, Volume 1\/}. Cham, CH: Springer International, pp.~141-171}.
%2%



%1%Bensoussan Frehse Yam 2013
         \brefitem[Bensoussan et al$.$  (2013)]{BFY13}
         \aut{Bensoussan, Alain, Jens Frehse, and Phillip Yam}
	 \anno{2013} 
	 \btitle{Mean Field Games and Mean Field Type Control Theory} 
         \book{New York, NY: Springer}.
%2%


%1%Bertoin 1996
           \brefitem[Bertoin (1996)]{Ber96}
           \aut{Bertoin, Jean}
	   \anno{1996}
           \btitle{Lévy Processes}
           \book{Cambridge, UK: Cambridge University Press}.
%2%


%1%Bewley 1977
    \brefitem[Bewley (1977)]{Bew77}
    \aut{Bewley, Truman F}
    \anno{1977} 
    \jtitle{The permanent income hypothesis: a theoretical formulation}
    \journal{Journal of Economic Theory} {16} 252-\nobreak292.
%2%


%1%Bewley 1980
    \brefitem[Bewley (1980)]{Bew80}
    \aut{Bewley, Truman F}
    \anno{1980} 
\jtitle{The optimum quantity of money}
\book{In: Kareken, J.~H., Wallace, N.\ (Eds.), {\it Models of Monetary Economics\/}. Minneapolis, MI: Federal Reserve Bank of Minneapolis, pp.~169-210}.
%2%


%1%Bewley 1983
    \brefitem[Bewley (1983)]{Bew83}
    \aut{Bewley, Truman F}
    \anno{1983} 
\jtitle{A difficulty with the optimum quantity of money}
\journal{Econometrica} {16} 252-\nobreak292.
%2%



%1%Bewley 1986
    \brefitem[Bewley (1986)]{Bew86}
    \aut{Bewley, Truman F}
    \anno{1986} 
\jtitle{Stationary monetary equilibrium with a continuum of independently fluctuating consumers}
\book{In: Hildenbrand, W., Mas-Colell, A.\ (Eds.), {\it Contributions to Mathematical Economics in Honor of Gerard Debreu\/}. Amsterdam, NL: North Holland, pp.~79-102}.
%2%


%1%Bismut 1973
    \brefitem[Bismut (1973)]{Bis73}
    \aut{Bismut, Jean-Michel}
    \anno{1973} 
\jtitle{Conjugate convex functions in optimal stochastic control}
\journal{Journal of Mathematical Analysis and Applications} {44} 384-\nobreak404.
%2%


%1%Brumm Kryczka Kubler 2017
    \brefitem[Brumm et al$.$ (2017)]{BKK17}
    \aut{Brumm, Johannes, Dominika Kryczka, and Felix Kubler}
    \anno{2017} 
\jtitle{Recursive equilibria in dynamic economies with stochastic production}
\journal{Econometrica} {85} 1467-\nobreak1499.
%2%


%1%Cannarsa Capuani 2018
    \brefitem[Cannarsa and Capuani (2018)]{CanCap18}
    \aut{Cannarsa, Piermarco, and Rossana Capuani}
    \anno{2018} 
    \jtitle{Existence and uniqueness of mean field games with state constraints}
    \book{In: Cardaliaguet, P., Porretta, A., and Salvarani, F.~(Eds.), {\it PDE Models for Multi-Agent Phenomena\/}. Cham, CH: Springer Nature, pp.~49-71}.
%2%



%1%Cannarsa Capuani Cardaliaguet 2021
    \brefitem[Cannarsa et al$.$ (2021)]{CCC21}
    \aut{Cannarsa, Piermarco, Rossana Capuani, and Pierre Cardaliaguet}
    \anno{2021} 
    \jtitle{Mean field games with state constraints: from mild to pointwise solutions of the PDE system}
    \journal{Calculus of Variations and Partial Differential Equations} {60} 108.
%2%



%1%Cao 2020
    \brefitem[Cao (2020)]{Cao20}
    \aut{Cao, Dan}
    \anno{2020} 
    \jtitle{Recursive equilibrium in Krusell and Smith (1998)}
    \journal{Journal of Economic Theory} {186} \href{https://doi.org/10.1016/j.jet.2019.104978}{DOI: 10.1016 / j.jet.2019.104978}.
%2%



%1%Cardaliaguet Delarue Lasry Lions 2019
         \brefitem[Cardaliaguet et al$.$  (2019)]{CDLL19}
         \aut{Cardaliaguet, Pierre, Fran{\cc}ois Delarue, Jean-Michele Lasry, and Pierre-Louis Lions}
	 \anno{2019} 
	 \btitle{The Master Equation and the Convergence Problem in Mean Field Games} 
         \book{Princeton, NJ: Princeton University Press}.
%2%


%1%Carmona Delarue 2014
         \brefitem[Carmona and Delarue (2014)]{CD14}
         \aut{Carmona, Ren{\ea}, and Fran{\cc}ois Delarue}
	 \anno{2014} 
	 \btitle{The master equation for large population equilibriums} 
         \book{\href{https://doi.org/10.48550/arXiv.1404.4694}{DOI: 10.48550 / arXiv.1404.4694}}.
%2%



%1%Carmona Delarue 2018a
         \brefitem[Carmona and Delarue (2018a)]{CD18a}
         \aut{Carmona, Ren{\ea}, and Fran{\cc}ois Delarue}
	 \anno{2018a} 
	 \btitle{Probabilistic Theory of Mean Field Games with Applications~I: mean field FBSDEs, control, and games} 
         \book{Cham, CH: Springer}.
%2%



%1%Carmona Delarue 2018b
         \brefitem[Carmona and Delarue (2018b)]{CD18b}
         \aut{Carmona, Ren{\ea}, and Fran{\cc}ois Delarue}
	 \anno{2018b} 
	 \btitle{Probabilistic Theory of Mean Field Games with Applications~II: mean field games with common noise and master equations} 
         \book{Cham, CH: Springer}.
%2%



%1%Carmona Delarue 2018
         \brefitem[Carmona and Delarue (2018a)]{CD18}
         \aut{Carmona, Ren{\ea}, and Fran{\cc}ois Delarue}
	 \anno{2018} 
	 \btitle{Probabilistic Theory of Mean Field Games with Applications~I\ts\&\ts II} 
         \book{Cham, CH: Springer}.
%2%



%1%Carmona Delarue Lacker 2016
         \brefitem[Carmona et al$.$ (2016)]{CDL16}
         \aut{Carmona, Ren{\ea}, Fran{\cc}ois Delarue, and Daniel Lacker}
	 \anno{2016} 
	 \jtitle{Mean Field Games with Common Noise} 
         \journal{Annals of Applied Probability} {44} 3740-\nobreak3803.
%2%



%1%Cass Shell 1983
    \brefitem[Cass and Shell (1983)]{CS83}
    \aut{Cass, David, and Karl Shell}
    \anno{1983} 
    \jtitle{Do sunspots matter?}
    \journal{Journal of Political Economy} {91} 193-\nobreak227.
%2%



%1%Chassagneux Crisan Delarue 2014
    \brefitem[Chassagneux et al$.$ (2014)]{CCD14}
    \aut{Chassagneux, Jean-Fran{\cc}ois, Dan Crisan, and Fran{\cc}ois Delarue}
    \anno{2014} 
    \jtitle{Classical solutions to the master equation for large population equilibria}
    \book{\href{https://doi.org/10.48550/arXiv.1411.3009}{DOI: 10.48550 / arXiv:1411.3009}}.
%2%


%1%Cheridito Sagredo 2016a
    \brefitem[Cheridito and Sagredo (2016a)]{ChS16}
    \aut{Cheridito, Patrick, and Juan Sagredo}
    \anno{2016} 
\jtitle{Existence of sequential competitive equilibrium in Krusell-Smith type economies}
\book{\href{https://doi.org/10.2139/ssrn.2794629}{DOI: 10.2139 / ssrn.2794629}}. 
%2%



%1%Cheridito Sagredo 2016b
    \brefitem[Cheridito and Sagredo (2016b)]{ChS16b}
    \aut{Cheridito, Patrick, and Juan Sagredo}
    \anno{2016} 
\jtitle{Comment on ``Competitive equilibria of economies with a continuum of consumers and aggregate shocks'' by J. Miao}
\book{\href{https://doi.org/10.2139/ssrn.2815971}{DOI: 10.2139 / ssrn.2815971}}.
%2%


%1%Clarida 1990
    \brefitem[Clarida (1990)]{Cla90}
    \aut{Clarida, Richard H}
    \anno{1990} 
\jtitle{International lending and borrowing in a stochastic, stationary equilibrium}
\journal{International Economic Review} {31} 543-\nobreak558.
%2%



%1%Cociuba Prescott Ueberfeldt 2018
    \brefitem[Cociuba et al$.$ (2018)]{CPU18}
    \aut{Cociuba, Simona E., Edward C.~Prescott, and  Alexander Ueberfeldt}
    \anno{2018} 
\jtitle{US hours at work}
\journal{Economics Letters} {169}(C) 87-\nobreak90.
%2%



%1%Cogburn 1980
    \brefitem[Cogburn (1980)]{Cog80}
    \aut{Cogburn, Robert}
    \anno{1980} 
    \jtitle{Markov chains in random environment: the case of MArkovian environments}
    \journal{The Annals of Probability} {8} 908-\nobreak916.
%2%



%1%Constantinides 1990
    \brefitem[Constantinides (1990)]{Con90}
    \aut{Constantinides, George M}
    \anno{1990} 
\jtitle{Habit formation: a resolution of the equity premium puzzle}
\journal{Journal of Political Economy} {98} 519-\nobreak543.
%2%


%1%Constantinides Duffie 1996
    \brefitem[Constantinides and Duffie (1996)]{CD96}
    \aut{Constantinides, George M., and Darrell Duffie}
    \anno{1996} 
\jtitle{Asset pricing with heterogeneous consumers}
\journal{Journal of Political Economy} 104 219-\nobreak240.
%2%


%1%Deaton 1991
    \brefitem[Deaton (1991)]{Dea91}
    \aut{Deaton, Angus}
    \anno{1991} 
    \jtitle{Saving and liquidity constraints}
    \journal{Econometrica} {59} 1221-\nobreak1248.
%2%



%1%Delarue Lacker Ramanan 2018
    \brefitem[Delarue et al$.$ (2018)]{DLR18}
    \aut{Delarue, Fran{\cc}ois, Daniel Lacker, and Kavita Ramanan}
    \anno{2018} 
    \jtitle{From the master equation to mean field game limit theory: large deviations and concentration of measure}
    \book{\href{https://doi.org/10.48550/arXiv.1804.08550}{DOI: 10.48550 / arXiv:1804.08550}}. 
%2%



%1%Dellacherie 1972
           \brefitem[Dellacherie (1972)]{Dell72}
           \aut{Dellacherie, Claude}
	   \anno{1972}
           \btitle{Capacit{\ea}s et Processus Stochastique}
           \book{Berlin, DE: Springer}.
%2%



%1%Dellacherie 1980
    \brefitem[Dellacherie (1980))]{Dell80}
    \aut{Dellacherie, Claude}
    \anno{1980} 
\jtitle{Un survol de la theorie de l'integrale stochastique}
\journal{Stochastic Processes and Their Applications} {10} 115-\nobreak144.
%2%


%1%Dellacherie Meyer 1975
                 \brefitem[Dellacherie and Meyer (1975)]{DellMey78}
           \aut{Dellacherie, Claude, et Paul-Andr{\ea}~Meyer}
	   \anno{1978}
\btitle{Probabilities and Potential}
\book{Paris, FR: Hermann}.
%2%



%1%Dellacherie Meyer 1980
                 \brefitem[Dellacherie and Meyer (1980)]{DellMey80}
           \aut{Dellacherie, Claude, et Paul-Andr{\ea}~Meyer}
	   \anno{1980}
\btitle{Probabilit{\ea}s et Potentiel, Chapitres V {\ag} VIII: Th{\ea}orie des Martingales}
\book{Paris, FR: Hermann}.
%2%



%1%DenHaan 1996
    \brefitem[Den Hann (1996)]{DH96}
    \aut{Den Haan, Wouter J}
    \anno{1996} 
    \jtitle{Heterogeneity, aggregate uncertainty, and the short-term interest rate}
    \journal{Journal of Business \& Economic Statistics} {14} 399-\nobreak411.
%2%


%1%DenHaan 2010a
    \brefitem[Den Hann (2010a)]{DH10a}
    \aut{Den Haan, Wouter J}
    \anno{2010a} 
    \jtitle{Comparison of solutions to the incomplete markets model with aggregate uncertainty}
    \journal{Journal of Economic Dynamics \& Control} {34} 4-\nobreak27.
%2%



%1%DenHaan 2010b
    \brefitem[Den Hann (2010b)]{DH10b}
    \aut{Den Haan, Wouter J}
    \anno{2010} 
    \jtitle{Assessing the accuracy of the aggregate law of motion in models with heterogeneous agents}
    \journal{Journal of Economic Dynamics \& Control} {34} 79-\nobreak99.
%2%




%1%DenHaan Marcet 1990
    \brefitem[Den Hann and Marcet (1990)]{DM90}
    \aut{Den Haan, Wouter J., and Albert Marcet}
    \anno{1990} 
    \jtitle{Solving the stochastic growth model by parameterizing expectations}
    \journal{Journal of Business \& Economic Statistics} {8} 31-\nobreak34.
%2%




%1%Doleans-Dade 1970
          \brefitem[Dol{\ea}ans-Dade (1970)]{Dol70}
    \aut{Dol{\ea}ans-Dade, Catherine}
    \anno{1970} 
\jtitle{Quelques applications de la formule de changement de variables pour les semimartingales} 
\journal{Zeitschrift f{\uD}r Wahrscheinlichkeitstheorie und Verwandte Gebiete} 16 181--\nobreak194.
%2%






%1%Dudley 2002
          \brefitem[Dudley (2002)]{Dud02}
	  \aut{Dudley, Richard~M}
	  \anno{2002}
\btitle{Real Analysis and Probability}
\book{Cambridge, UK: Cambridge University Press}.
%2%



%1%Duffie Epstein 1992a
    \brefitem[Duffie and Epstein (1992a)]{DE92a}
    \aut{Duffie, Darrell, and Larry G.~Epstein}
    \anno{1992a} 
\jtitle{Stochastic differential utility}
\journal{Econometrica} {60} 353-\nobreak394.
%2%



%1%Duffie Epstein 1992b
    \brefitem[Duffie and Epstein (1992b)]{DE92b}
    \aut{Duffie, Darrell, and Larry G.~Epstein}
    \anno{1992b} 
\jtitle{Asset pricing with stochastic differential utility}
\journal{Review of Financial Studies} {5} 411-\nobreak436.
%2%



%1%Duffie Geanakoplos Mas-Colell McLennan 1994
    \brefitem[Duffie et al$.$ (1994)]{DGMM94}
    \aut{Duffie, Darrell, John Geanakoplos, Andreu Mas-Colell, and Andrew McLennan}
    \anno{1994} 
\jtitle{Stationary Markov equilibria}
\journal{Econometrica} {62} 745-\nobreak781.
%2%



%1%Duffie Qiao Sun 2019
    \brefitem[Duffie et al$.$ (2019)]{DQS19}
    \aut{Duffie, Darrell, Lei Qiao, and Yuneng Sun}
    \anno{2019} 
\jtitle{Continuous-time random matching}
\book{\it Working paper}.
%2%



%1%Duffie Sun 2012
    \brefitem[Duffie and Sun (2012)]{DS12}
    \aut{Duffie, Darrell, and Yuneng Sun}
    \anno{2012} 
\jtitle{The exact law of large numbers for independent random matching}
\journal{Journal of Economic Theory} {147} 1105-\nobreak1139.
%2%



%1%Duffie Zame 1989
    \brefitem[Duffie and Zame (1989)]{DZ89}
    \aut{Duffie, Darrell, and William Zame}
    \anno{1989} 
\jtitle{The consumption-based capital asset pricing model}
\journal{Econometrica} {57} 1279-\nobreak1297.
%2%




%1%Dumas 1989
    \brefitem[Dumas (1989)]{Dum89}
    \aut{Dumas, Bernard}
    \anno{1989} 
\jtitle{Two-person dynamic equilibrium in the capital market}
\journal{Review of Financial Studies} {2} 157-\nobreak188.
%2%


%1%Dumas Lyasoff 2012
    \brefitem[Dumas and Lyasoff (2012)]{DL12}
    \aut{Dumas, Bernard, and Andrew Lyasoff}
    \anno{2012} 
\jtitle{Incomplete-market equilibria solved recursively on an even tree}
\journal{Journal of Finance} {67} 1897-\nobreak1941.
%2%



%1%Dumas Savioz 2022
    \brefitem[Dumas and Savioz (2022)]{DS22}
    \aut{Dumas, Bernard, and Marcel Savioz}
    \anno{2022} 
\jtitle{A theory of the nominal character of stock securities}
\journal{Review of Finance,} { } forthcoming.
%2%



%1%Emery 1978
       \brefitem[Emery (1978)]{Eme78}
        \aut{Emery, Michel} 
	\anno{1978} 
        \jtitle{Stabilit{\ea} des solutions des {\ea}quations diff{\ea}rentielles stochastiques application aux int{\ea}grales multiplicatives stochastiques}
        \journal{Zeit\-schrift f{\uD}r Wahr\-schein\-lichkeitstheorie und Verwandte Gebiete} 41 241--\nobreak262.
%2%


%1%Emery 1979a
          \brefitem[Emery (1979)]{Eme79a}
	  \aut{Emery, Michel}
	  \anno{1979}
\jtitle{Une topologie sur l'espace des semimartingales}
\book{In: {\it S{\ea}minaire de Probabilit{\ea}s (Strasbourg) XIII\/}.  Lecture Notes in Mathematics 721. Berlin, DE: Springer, pp.~260--280}.
%2%




%1%Emery 1979b
          \brefitem[Emery (1979)]{Eme79b}
	  \aut{Emery, Michel}
	  \anno{1979}
          \jtitle{{\Ea}quations diff{\ea}rentielles stochastiques lipschitziennes: {\ea}tude de la stabilit{\ea}}
          \book{In: {\it S{\ea}minaire de Probabilit{\ea}s (Strasbourg) XIII\/}.  Lecture Notes in Mathematics 721. Berlin, DE: Springer, pp.~281--293}.
%2%


%1%Emoto Sunakawa 2021
         \brefitem[Emoto and Sunakawa (2021)]{ES21}
         \aut{Emoto, Masakuzi, and Takeki Sunakawa}
	 \anno{2021} 
	 \jtitle{Applying the explicit aggregation algorithm to heterogeneous agent models in continuous time} 
\journal{Economic Letters} {206} 109940.
%2%



%1%Epstein Zin 1991
    \brefitem[Epstein and Zin (1991)]{EZ91}
    \aut{Epstein, Larry G., and Stanley E.~Zin}
    \anno{1991} 
\jtitle{Substitution, risk aversion, and the temporal behavior of consumption and asset returns: an empirical analysis}
\journal{The Journal of Political Economy} {99} 263-\nobreak286.
%2%


%1%Feldman Gilles 1985
    \brefitem[Feldman and Gilles (1985)]{FG85}
    \aut{Feldman, Mark and Christian Gilles}
    \anno{1985} 
\jtitle{An expository note on individual risk without aggregate uncertainty}
\journal{Journal of Economic Theory} {35} 26-\nobreak32.
%2%




%1%Feng Nguyen 2012
    \brefitem[Feng and Nguyen (2012)]{FN12}
    \aut{Feng, Jin, and Truyen Nguyen}
    \anno{2012} 
    \jtitle{Hamilton-Jacobi equations in space of measures associated with a system of conservation laws}
    \journal{Journal de Mathématiques Pures et Appliquées} {97} 318-\nobreak390.
%2%



%1%Fernandez-Villaverde Hurtado Nuno 2020
    \brefitem[Fernández et al$.$ (2020)]{VHN20}
    \aut{Fernández-Villaverde, Jesús, Samuel Hurtado, and Galo Nuño}
    \anno{2020} 
    \jtitle{Financial frictions and the wealth distribution}
    \book{{\it CESifo Working Papers\/} \ No.~8482}. 
%2%



%1%Follmer 1994
    \brefitem[Föllmer (1994)]{Foll94}
    \aut{Föllmer, Hans}
    \anno{1994} 
    \jtitle{Stock price fluctuations as a diffusion in a random environment}
    \journal{Philosohpical Transactions of the Royal Society of London} {A347} 471-\nobreak483.
%2%



%1%Follmer Schweizer 1993
    \brefitem[Föllmer and Schweizer (1993)]{FS93}
    \aut{Föllmer, Hans, and Martin Schweizer}
    \anno{1993} 
    \jtitle{A microeconomic approach to diffusion models for stock prices}
    \journal{Mathematical Finance} {3} 1-\nobreak23.
%2%



%1%Galichon 2016
           \brefitem[Galichon (2016)]{Gal16}
           \aut{Galichon, Alfred}
	   \anno{2016}
           \btitle{Optimal Transport Methods in Economics}
           \book{Princeton, NJ: Princeton University Press}.
%2%



%1%Geanakoplos Karatzas Shubik Sudderth 2000
    \brefitem[Geanakoplos et al$.$ (2000)]{GKSS00}
    \aut{Geanakoplos, John, Ioannis Karatzas, Martin Shubik, and William D.\ Sudderth}
    \anno{2000} 
\jtitle{A strategic market game with active bankruptcy}
\journal{Journal of Mathematical Economics} {34} 359-\nobreak396.
%2%



%1%Glynn 2013
         \brefitem[Glynn (2013)]{Glynn13}
         \aut{Glynn, Peter W}
	 \anno{2013} 
	 \btitle{Harris recurrence} 
\book{Stanford University: Stochastic Systems Lecture Notes}.
%2%



%1%Gomes Mohr Souza 2010
    \brefitem[Gomes et al$.$ (2010)]{GMS10}
    \aut{Gomes, Diogo A., Joana Mohr, and Rafael Rigão Souza}
    \anno{2010} 
    \jtitle{Discrete time, finite state space mean field games}
    \journal{Journal de Math{\ea}matiques Pures et Apliqu{\ea}es} {93} 308-\nobreak328.
%2%


%1%Greenwald Lettau Ludvigson 2019
    \brefitem[Greenwald et al$.$ (2019)]{GLL19}
    \aut{Greenwald, Daniel L., Martin Lettau, and Sydney C.~Ludvigson}
    \anno{2019} 
\jtitle{How the wealth was won: factors shares as market fundamentals}
\book{\it NBER Working Paper\/} \ No.~25769. 
%2%



%1%Gueant 2009
    \brefitem[Guéant (2009)]{Gue09}
    \aut{Guéant, Olivier}
    \anno{2009} 
    \jtitle{A reference case for mean field games models}
    \journal{Journal de Mathématiques Pures et Apliquées} {92} 276-\nobreak294.
%2%


%1%Gueant 2009
    \brefitem[Gu{\ea}ant (2009)]{Gue09}
    \aut{Gu{\ea}ant, Olivier}
    \anno{2009} 
    \jtitle{A reference case for mean field games models}
    \journal{Journal de Math{\ea}matiques Pures et Apliqu{\ea}es} {92} 276-\nobreak294.
%2%


%1%Haan 1996
    \brefitem[Haan (1996)]{Haa96}
    \aut{Den Haan, Wouter J.}
    \anno{1996} 
\jtitle{Heterogeneity, aggregate uncertainty, and the short-term interest rate}
\journal{Journal of Business and Economic Statistics} {14} 399-\nobreak411.
%2%


%1%Haan Marcet 1990
    \brefitem[Haan and Marcet (1990)]{HM90}
    \aut{Den Haan, Wouter J., and Albert Marcet}
    \anno{1990} 
\jtitle{Solving the stochastic growth model by parameterizing expectations}
\journal{Journal of Business and Economic Statistics} {8} 31-\nobreak34.
%2%


%1%Hall 1978
    \brefitem[Hall (1978)]{Hall78}
    \aut{Hall, Robert E}
    \anno{1978} 
\jtitle{Stochastic implications for the life cycle--permanent income hypothesis: theory and evidence}
\journal{Journal of Political Economy} {86} 971-\nobreak987.
%2%


%1%Han Jentzen E 2017
    \brefitem[Han et al$.$ (2017)]{HJE17}
    \aut{Han, Jiequn, Arnulf Jentzen, and Weinan E}
    \anno{2017} 
\jtitle{Deep learning-based numerical methods for high-dimensional parabolic partial differential equations and backward stochastic differential equations}
\journal{Communications in Mathematics and Statistics} {5} 349-\nobreak380.
%2%


%1%Han Jentzen E 2018
    \brefitem[Han et al$.$ (2018)]{HJE18}
    \aut{Han, Jiequn, Arnulf Jentzen, and Weinan E}
    \anno{2018} 
\jtitle{Solving high-dimensional partial differential equations using deep learning}
\journal{Proceedings of the National Academy of Sciences of the USA} 115 8505-\nobreak8510.
%2%



%1%Hart Hildenbrand Kohlberg 1974
    \brefitem[Hart et al$.$ (1974)]{HHK74}
    \aut{Hart, Sergiu, Werner Hildenbrand, and Elon Kohlberg}
    \anno{1974} 
\jtitle{On equilibrium allocations as distributions on the commodity space}
\journal{Journal of Mathematical Economics} {1} 159-\nobreak167.
%2%


%1%Heaton 1995
    \brefitem[Heaton (1995)]{Hea95}
    \aut{Heaton, John}
    \anno{1995} 
\jtitle{An empirical investigation of asset pricing with temporally dependent preference specifications}
\journal{Econometrica} {63} 681-\nobreak717.
%2%


%1%Heaton Lucas 1995
    \brefitem[Heaton and Lucas (1995)]{HL95}
    \aut{Heaton, John, and Deborah Lucas}
    \anno{1995} 
\jtitle{The importance of investor heterogeneity and financial market imperfections for the behavior of asset prices}
\journal{Carnegie-Rochester Conference Series on Public Policy} {42} 1-\nobreak32.
%2%



%1%Heaton Lucas 1996
    \brefitem[Heaton and Lucas (1996)]{HL96}
    \aut{Heaton, John, and Deborah Lucas}
    \anno{1996} 
\jtitle{Evaluating the effects of incomplete markets on risk sharing and asset pricing}
\journal{Journal of Political Economy} {104} 443-\nobreak487.
%2%



%1%Hildenbrand 1974
         \brefitem[Hildenbrand (1974)]{Hil74}
         \aut{Hildenbrand, Werner}
	 \anno{1974} 
	 \btitle{Numerical Methods in Economics} 
\book{Princeton, NJ: Princeton University Press}.
%2%


%1%Holm 2018
    \brefitem[Holm (2018)]{Holm18}
    \aut{Holm, Martin Blomhoff}
    \anno{2018} 
    \jtitle{Consumption with liquidity constraints: an analytical characterization}
    \journal{Economics Letters} {167} 40-\nobreak42.
%2%



%1%Hopenhayn 1992
    \brefitem[Hopenhayn (1992)]{Hop92}
    \aut{Hopenhayn, Hugo A}
    \anno{1992} 
    \jtitle{Entry, exit, and firm dynamics in long run equilibrium}
    \journal{Econometrica} {32} 39-\nobreak50.
%2%



%1%Huang Malhame Caines 2006
    \brefitem[Huang et al$.$ (2006)]{HMC06}
    \aut{Huang, Minyi, Roland P.~Malham{\ea}, and Peter E.~Caines}
    \anno{2006} 
    \jtitle{Large population stochastic dynamic games: closed-loop McKean-Vlasov systems and the Nash certainty equivalence principle}
    \journal{Communications in Information and Systems} {6} 221-\nobreak252.
%2%



%1%Huggett 1993
    \brefitem[Huggett (1993)]{Hug93}
    \aut{Huggett, Mark}
    \anno{1993} 
\jtitle{The risk free rate in heterogeneous-agent, incomplete-insurance economies}
\journal{Journal of Economic Dynamics and Control} {17} 953-\nobreak969.
%2%


%1%Huggett 1997
    \brefitem[Huggett (1997)]{Hug97}
    \aut{Huggett, Mark}
    \anno{1997} 
\jtitle{The one-sector growth model with idiosyncratic shocks: steady states and dynamics}
\journal{Journal of Monetary Economics} {39} 385-\nobreak403.
%2%



%1%Huggett Ospina 2001
    \brefitem[Huggett and Ospina (2001)]{HO01}
    \aut{Huggett, Mark, and Sandra Ospina}
    \anno{1997} 
\jtitle{Aggregate precautionary savings: when is the third derivative irrelevant?}
\journal{Journal of Monetary Economics} {48} 373-\nobreak396.
%2%



%1%Imrohoroglu 1989
    \brefitem[İmrohoroğlu (1989)]{Imro89}
    \aut{{\rm İ}mrohoroğlu, Ayşe}
    \anno{1989} 
    \jtitle{Cost of business cycles with indivisibilities and liquidity constraints}
    \journal{Journal of Political Economy} {97} 1364-\nobreak1383.
%2%




%1%Jacod Shiryaev 2003
         \brefitem[Jacod and Shiryaev (2003)]{JacShir87}
           \aut{Jacod, Jean, and Albert N.~Shiryaev}
	   \anno{2003}
\btitle{Limit Theorems for Stochastic Processes}
\book{Berlin, DE: Springer}.
%2%



%1%Jovanovic Rosenthal 1988
    \brefitem[Jovanovic and Rosenthal (1988)]{JR88}
    \aut{Jovanovic, Boyan, and Robert W.~Rosenthal}
    \anno{1988} 
\jtitle{Anonymous sequential games}
\journal{Journal of Mathematical Economics} {17} 77-\nobreak97.
%2%



%1%Judd 1985
    \brefitem[Judd (1985)]{Judd85}
    \aut{Judd, Kenneth L}
    \anno{1985} 
\jtitle{The law of large numbers with a continuum of IID random variables}
\journal{Journal of Economic Theory} {35} 19-\nobreak25.
%2%


%1%Judd 1998
         \brefitem[Judd (1998)]{Judd98}
         \aut{Judd, Kenneth L}
	 \anno{1998} 
	 \btitle{Numerical Methods in Economics} 
\book{Cambridge, MA: MIT Press}.
%2%



%1%Judd Kubler Schmedders 2000
    \brefitem[Judd et al$.$ (2000)]{JKS00}
    \aut{Judd, Kenneth L., Felix Kubler, and Karl Schmedders}
    \anno{2000} 
\jtitle{Computing equilibria in infinite-horizon finance economies: the case of one asset}
\journal{Journal of Economic Dynamics and Control} {24} 1047-\nobreak1078.
%2%


%1%Judd Kubler Schmedders 2002
    \brefitem[Judd et al$.$ (2002)]{JKS02}
    \aut{Judd, Kenneth L., Felix Kubler, and Karl Schmedders}
    \anno{2002} 
\jtitle{A Solution Method for Incomplete Asset Markets With Heterogeneous Agents}
\book{\href{https://doi.org/10.2139/ssrn.900165}{DOI: 10.2139 / ssrn.900165}}.
%2%


%1%Kac 1976
         \brefitem[Kac (1976)]{Kac76}
         \aut{Kac, Mark}
	 \anno{1976} 
	 \btitle{Probability and Related Topics in Physical Sciences} 
\book{Providence, RY: American Mathematical Society}.
%2%


%1%Karatzas Lehoczky Shreve 1990a
    \brefitem[Karatzas et al$.$ (1990)]{KLS90a}
    \aut{Karatzas, Ioannis, John P.~Lehoczky, and Steven E.~Shreve}
    \anno{1990} 
\jtitle{Existence and uniqueness of multi-agent equilibrium in a stochastic, dynamic consumption/investment model}
\journal{Mathematics of Operations Research} {15} 80-\nobreak128.
%2%



%1%Karatzas Shubik Sudderth 1994
    \brefitem[Karatzas et al$.$ (1994)]{KSS94}
    \aut{Karatzas, Ioannis, Martin Shubik, and William D.\ Sudderth}
    \anno{1994} 
\jtitle{Construction of stationary Markov equilibria in a strategic market game}
\journal{Mathematics of Operations Research} {19} 975-\nobreak1006.
%2%



%1%Karatzas Shubik Sudderth 1997
    \brefitem[Karatzas et al$.$ (1997)]{KSS97}
    \aut{Karatzas, Ioannis, Martin Shubik, and William D.\ Sudderth}
    \anno{1997} 
\jtitle{A strategic market game with secured lending}
\journal{Journal of Mathematical Economics} {28} 207-\nobreak247.
%2%




%1%Karoui Peng Quenez 1997
    \brefitem[El Karoui et al$.$ (1997)]{EPQ97}
    \aut{El Karoui, Nicole, Shige G.~Peng, and Marie-Claire Quenez}
    \anno{1997} 
\jtitle{Backward stochastic differential equations in finance }
\journal{Mathematical Finance} {7} 1-\nobreak71.
%2%






%1%Khan Thomas 2008
    \brefitem[Khan and Thomas (2008)]{KT08}
    \aut{Khan, Aubhik, and Julia K.~Thomas}
    \anno{2008} 
\jtitle{Idiosyncratic Shocks and the Role of Nonconvexities in Plant And Aggregate Investment Dynamics}
\journal{Econometrica} {76} 395-\nobreak436.
%2%



%1%Kirby 2018
    \brefitem[Kirby (2018)]{Kir18}
    \aut{Kirby, Robert}
    \anno{2018} 
\jtitle{Bewley-Huggett-Aiyagari models: computation, simulation, and uniqueness of general equilibrium}
\book{\it Macroeconomic Dynamics\/}, forthcoming, published online. 
%2%




%1%Krusell Smith 1998
    \brefitem[Krusell and Smith (1998)]{KS98}
    \aut{Krusell, Per, and Anthony Smith}
    \anno{1998} 
\jtitle{Income and wealth heterogeneity in the macroeconomy}
\journal{Journal of Political Economy} {106} 867-\nobreak896.
%2%




%1%Kubler Schmedders 2002
    \brefitem[Kubler and Schmedders (2002)]{KS02}
    \aut{Kubler, Felix, and Karl Schmedders}
    \anno{2002} 
\jtitle{Recursive equilibria in economies with incomplete markets}
\journal{Macroeconomic Dynamics} {6} 284-\nobreak306.
%2%



%1%Kunita 2009
    \brefitem[Kunita (2009)]{Kun09}
    \aut{Kunita, Hiroshi}
    \anno{2009} 
\jtitle{Smooth density of canonical stochastic differential equation with jumps}
\journal{Astérisque} {327} 69-\nobreak91.
%2%

%1%Lasry Lions 2007
    \brefitem[Lasry and Lions (2007)]{LaLi07}
    \aut{Lasry, Jean-Michel, and Pierre-Louis Lions}
    \anno{2007} 
\jtitle{Mean field games}
\journal{Japanese Journal of Mathematics} {2} 229-\nobreak260.
%2%



%1%Lepingle-Memin 1970
          \brefitem[Lepingle and M{\ea}min (1978)]{LepMem78}
    \aut{Lepingle, Dominique, and Jean M{\ea}min}
    \anno{1978} 
\jtitle{Sur l'int{\ea}grabilit{\ea} uniforme des martingales exponentielles} 
\journal{Zeitschrift f{\uD}r Wahrscheinlichkeitstheorie und Verwandte Gebiete} 42 175--\nobreak203.
%2%



%1%Li Stachurski 2014
    \brefitem[Li and Stachurski (2014)]{LS14}
    \aut{Li, Huiyu, and John Stachurski}
    \anno{2014} 
\jtitle{Solving the income fluctuation problem with unbounded rewards }
\journal{Journal of Economic Dynamics and Control} {45} 353-\nobreak365.
%2%




%1%Light 2018
    \brefitem[Light (2018)]{Light18}
    \aut{Light, Bar}
    \anno{2018} 
\jtitle{Uniqueness of equilibrium in a Bewley-Aiyagari model}
\book{\it Economic Theory\/}, forthcoming, published online. 
%2%




%1%Lions Lasry 2007
    \brefitem[Lions and Lasry (2007)]{LL07}
    \aut{Lions, Pierre-Louis, and Jean-Michel Lasry}
    \anno{2007} 
\jtitle{Large investor trading impacts on volatility}
\book{In: {\it Paris-Princeton Lectures on Mathematical Finance 2004\/}. Lecture Notes in Mathematics, vol 1919, pp.~173-\nobreak190, Berlin: Springer}.
%2%






%1%Ljungqvist Sargent 2018
         \brefitem[Ljungqvist and Sargent (2018)]{LjunSar00}
         \aut{Ljungqvist, Lars, and Thomas J.~Sargent}
	 \anno{2018} 
	 \btitle{Recursive Macroeconomic Theory (4th Ed.)} 
\book{Cambridge, MA: MIT Press}.
%2%



%1%Lucas 1994
    \brefitem[Lucas (1994)]{Luc94}
    \aut{Lucas, Deborah J.}
    \anno{1994} 
\jtitle{Asset pricing with undiversifiable income risk and short sales constraints: deepening the equity premium puzzle}
\journalnt{Journal of Monetary Economics} {34} 325-\nobreak341.
%2%



%1%Lyasoff 2017
         \brefitem[Lyasoff (2017)]{Lya17}
         \aut{Lyasoff, Andrew}
	 \anno{2017} 
	 \btitle{Stochastic Methods in Asset Pricing} 
\book{Cambridge, MA: MIT Press}.
%2%



%1%Lyasoff 2019
    \brefitem[Lyasoff (2019)]{Lya19}
    \aut{Lyasoff, Andrew}
    \anno{2019} 
\jtitle{Bewley's incomplete market model revisited}
\book{\it \href{https://drive.google.com/file/d/1VXSzI6ayEqOE_wazXNA7dtS88SKBoDUf/view}{Working Paper}\/}.
%2%


%1%Lyasoff 2019a
    \brefitem[Lyasoff (2019a)]{Lya19aa}
    \aut{Lyasoff, Andrew}
    \anno{2019a} 
\jtitle{Bewley's incomplete market model revisited}
\book{\it Working Paper\/}.
%2%



%1%Lyasoff 2019b
    \brefitem[Lyasoff (2019)]{Lya19b}
    \aut{Lyasoff, Andrew}
    \anno{2019} 
\jtitle{A brief note on incomplete-market equilibria and their connection with mean field games and control}
\book{\it Working Paper\/}.
%2%



%1%Lyasoff 2019bb
    \brefitem[Lyasoff (2019b)]{Lya19bb}
    \aut{Lyasoff, Andrew}
    \anno{2019b} 
\jtitle{A brief note on incomplete-market equilibria and their connection with mean field games and control}
\book{\it Working Paper\/}.
%2%



%1%Lyasoff 2019c
    \brefitem[Lyasoff (2019)]{Lya19c}
    \aut{Lyasoff, Andrew}
    \anno{2019} 
\jtitle{A brief note on discrete mean field games and control}
\book{\it Working Paper\/}.
%2%




%1%Lyasoff 2019cc
    \brefitem[Lyasoff (2019c)]{Lya19cc}
    \aut{Lyasoff, Andrew}
    \anno{2019c} 
\jtitle{A brief note on discrete mean field games and control}
\book{\it Working Paper\/}.
%2%





%1%Ma Protter Yong 1994
    \brefitem[Ma et al$.$ (2013)]{MPY94}
    \aut{Ma, Jin, Philip Protter, and Jiongming Yong}
    \anno{1994} 
    \jtitle{Solving forward-backward stochastic differential equations explicitly~-- a fours step scheme}
    \journal{Probability Theory and Related Fields} {98} 339-\nobreak350.
%2%




%1%Ma Yong 2007
         \brefitem[Ma and Yong (2007)]{MY07}
         \aut{Ma, Jin, and Jiongmin Yong}
	 \anno{2007} 
	 \btitle{Forward-Backward Stochastic Differential Equations and Their Applications} 
\book{Berlin, DE: Springer}.
%2%




%1%Magill Quinzii 1996
         \brefitem[Magill and Quinzii (1996)]{MQ96}
         \aut{Magill, Michael, and Martine Quinzii}
	 \anno{1996} 
	 \btitle{Theory of Incomplete Markets} 
\book{Cambridge, MA: MIT Press}.
%2%



%1%Maliar Maliar Winant 2021
    \brefitem[Maliar et al$.$ (2021)]{MMW21}
    \aut{Maliar, Lilia, Serguei Maliar, and Pablo Wiant}
    \anno{2021} 
\jtitle{Deep learning for solving dynamic economic models}
\journal{Journal of Monetary Economics} {122} 76-\nobreak101.
%2%


%1%Malinvaud 1972
    \brefitem[Malinvaud (1972)]{Mal72}
    \aut{Malinvaud, Edmond}
    \anno{1972} 
\jtitle{The allocation of individual risks in large markets}
\journal{Journal of Economic Theory} {4} 312-\nobreak328.
%2%



%1%Marcet Singleton 1999
    \brefitem[Marcet and Singleton (1999)]{MS99}
    \aut{Marcet, Albert, and Kenneth J.~ Singleton}
    \anno{1999} 
\jtitle{Equilibrium asset prices and savings of heterogeneous agents in the presence of incomplete markets and portfolio constraints}
\journal{Macroeconomic Dynamics} {3} 243-\nobreak277.
%2%


%1%McKean 1966
    \brefitem[McKean (1966)]{McK66}
    \aut{McKean, Henry P., Jr}
    \anno{1966} 
\jtitle{A class of Markov processes associated with nonlinear parabolic equations}
\journal{Proceedings of the National Academy of Sciences of the USA} 56 1907-\nobreak1911.
%2%


%1%Mehra Prescott 1985
    \brefitem[Mehra and Prescott (1985)]{MP85}
    \aut{Mehra, Rajnish, and Edward C.~Prescott}
    \anno{1985} 
\jtitle{The equity premium: a puzzle}
\journal{Journal of Monetary Economics} {15} 145-\nobreak161.
%2%

%1%Mertens Judd (2018)
    \brefitem[Mertens and Judd (2018)]{MJ18}
    \aut{ Mertens, Thomas M., and Kenneth L.~Judd}
    \anno{2018} 
\jtitle{Solving an incomplete markets model with a large cross-section of agents}
\journal{Journal of Economic Dynamics and Control} {91} 349-\nobreak368.
%2%


%1%Meyer 1966
          \brefitem[Me\-yer (1966)]{Mey66}
	  \aut{Meyer, Paul A} 
	  \anno{1966}
	  \btitle{Probability and Potentials} 
\book{Waltham, MA: Blaisdell Publishing}.
%2%



%1%Miao 2002
    \brefitem[Miao (2002)]{Miao02}
    \aut{Miao, Jianjun}
    \anno{2002} 
\jtitle{Stationary equilibria of economies with a continuum of heterogeneous consumers}
\book{\it Mimeo\/}.
%2%



%1%Miao 2006
    \brefitem[Miao (2006)]{Miao06}
    \aut{Miao, Jianjun}
    \anno{2006} 
\jtitle{Competitive equilibria of economies with a continuum of consumers and aggregate shocks}
\journal{Journal of Economic Theory} {128} 274-\nobreak298.
%2%


%1%Pakes McGuire 2001
         \brefitem[Pakes and McGuire (2001)]{PM01}
         \aut{Pakes, Ariel, and Paul McGuire}
	 \anno{2001} 
	 \jtitle{Stochastic algorithms, symmetric Markov perfect equilibrium, and the `curse' of dimensionality} 
\journal{Econometrica} {69} 1261-\nobreak1281.
%2%


%1%Panageas 2019
    \brefitem[Panageas (2019)]{Pan19}
    \aut{Panageas, Stavros}
    \anno{2019} 
\jtitle{The implications of heterogeneity and inequality for asset pricing}
\book{\href{https://doi.org/10.2139/ssrn.3494558}{DOI: 10.2139 / ssrn.3494558}}. 
%2%



%1%Pardoux Peng 1990
    \brefitem[Pardoux and Peng (1990)]{PP90}
    \aut{Pardoux, {\Ea}tienne, and Shige G.~Peng}
    \anno{1990} 
\jtitle{Adapted solution of a backward stochastic differential equation}
\journal{Systems and Control Letters} {14} 55-\nobreak61.
%2%



%1%Peng 1990
    \brefitem[Peng (1990)]{Peng90}
    \aut{Peng, Shige G}
    \anno{1990} 
\jtitle{A general stochastic maximum principle for optimal control problems}
\journal{SIAM Journal of Control} {28} 966-\nobreak979.
%2%





%1%Pontryagin 1986
    \brefitem[Pontryagin (1986)]{P86}
    \aut{Pontryagin, Lev Semyonovich}
    \anno{1986} 
\btitle{The Mathematical Theory of Optimal Processes (selected works, Volume 4)}
\book{New York, NY: Gordon and Breach}.
%2%



%1%Prohl 2021
    \brefitem[Pröhl (2021)]{Pro21}
    \aut{Pröhl, Elisabeth}
    \anno{2021} 
\jtitle{Existence and uniqueness of recursive equilibria with aggregate and idiosyncratic risk}
\book{\href{https://doi.org/10.2139/ssrn.3250651}{DOI: 10.2139 / ssrn.3250651}}. 
%2%


%1%Protter 1978
       \brefitem[Protter (1978)]{Pro78}
        \aut{Protter, Philip} 
	\anno{1978} 
        \jtitle{${\scr H}^p$ Stability of Solutions of Stochastic Differential Equations}
        \journal{Zeitschrift f{\uD}r Wahrscheinlichkeitstheorie und Verwandte Gebiete} 44 337--\nobreak352.
%2%



%1%Reed Simon 1980
            \brefitem[Reed and Simon (1980)]{RS80}
            \aut{Reed, Michael, and Barry Simon}
	    \anno{1980}
\btitle{Methods of Modern Mathematical Physics I: Functional Analysis}
\book{New York, NY: Academic Press}.
%2%



%1%Revuz Yor 1999
            \brefitem[Revuz and Yor (1999)]{RevYor99}
            \aut{Revuz, Daniel, and Marc Yor}
	    \anno{1999}
\btitle{Continuous Martingales and Brownian Motion}
\book{Berlin, DE: Sprin\-ger-Ver\-lag}.
%2%




%1%Samuelson 1941
    \brefitem[Samuelson (1941)]{Sam41}
    \aut{Samuelson, Paul A}
    \anno{1941} 
\jtitle{The Stability of Equilibrium: Comparative Statics and Dynamics}
\journal{Econometrica} {9} 97-\nobreak120.
%2%




%1%Stokey Lucas 1989
         \brefitem[Stokey and Lucas (1989)]{SL89}
         \aut{Stokey, Nancy L., and Robert E.\ Lucas Jr}
	 \anno{1989} 
	 \btitle{Recursive Methods in Economic Dynamics} 
\book{Cambridge, MA: Harvard University Press}.
%2%




%1%Stroock 2014
         \brefitem[Stroock (2014)]{Str14}
         \aut{Stroock, Daniel W}
	 \anno{2014} 
	 \btitle{An Introduction to Markov Processes (2d Ed.)} 
\book{Berlin, DE: Sprin\-ger-Ver\-lag}.
%2%



%1%Stroock 2023
         \brefitem[Stroock (2023)]{Str23}
         \aut{Stroock, Daniel W}
	 \anno{2023} 
	 \btitle{Integral functionals of probability that depend only on mean values} 
\book{\href{https://doi.org/10.48550/arXiv.2301.01195}{DOI: 10.48550 / arXiv.2301.01195}}.
%2%



%1%Sun 2006
    \brefitem[Sun (2006)]{Sun06}
    \aut{Sun, Yuneng}
    \anno{2006} 
\jtitle{The exact law of large numbers via Fubini extension and characterization of insurable risks}
\journal{Journal of Economic Theory} {126} 31-\nobreak69.
%2%



%1%Sun Zhang 2009
    \brefitem[Sun and Zhang (2009)]{SZh09}
    \aut{Sun, Yuneng, and Yongchao Zhang}
    \anno{2009} 
\jtitle{Individual risk and Lebesgue extension without aggregate uncertainty}
\journal{Journal of Economic Theory} {144} 432-\nobreak443.
%2%



%1%Tauchen 1986
         \brefitem[Tauchen (1986)]{Tau86}
         \aut{Tauchen, George}
	 \anno{1986} 
	 \jtitle{Finite state Markov chain approximation to univariate and vector autoregressions} 
\journal{Economic Letters} {20} 177-\nobreak181.
%2%



%1%Telmer 1993
    \brefitem[Telmer (1993)]{Tel93}
    \aut{Telmer, Chris I.}
    \anno{1993} 
\jtitle{Asset-pricing puzzles and incomplete markets}
\journal{Journal of Finance} {48} 1803-\nobreak1832.
%2%



%1%Telmer Zin 2002
    \brefitem[Telmer and Zin (2002)]{TZ02}
    \aut{Telmer, Chris I., and Stanley E.~Zin}
    \anno{2002} 
\jtitle{Prices as factors: approximate aggregation with incomplete markets}
\journal{Journal of Economic Dynamics and Control} {26} 1127-\nobreak1157.
%2%



%1%Touzi 2019
         \brefitem[Touzi  (2013)]{Tou13}
         \aut{Touzi, Nizar}
	 \anno{2013} 
	 \btitle{Optimal Stochastic Control, Stochastic Target Problems, and Backward SDE} 
         \book{New York, NY: Springer}.
%2%



%1%Vayanos Vila 1999
    \brefitem[Vayanos and Vila (1999)]{VV99}
    \aut{Vayanos, Dimitri, and Jean-Luc Vila}
    \anno{1999} 
\jtitle{Equilibrium interest rate and liquidity premium with transaction costs}
\journal{Economic Theory} {13} 509-\nobreak539.
%2%


%1%Vilani 2003
         \brefitem[Villani (2003)]{Vil03}
         \aut{Villani, Cédric}
	 \anno{2003} 
	 \btitle{Topics in Optimal Transportation} 
\book{Providence, RI: American Methematical Society}.
%2%



%1%Vilani 2009
         \brefitem[Villani (2009)]{Vil09}
         \aut{Villani, Cédric}
	 \anno{2009} 
	 \btitle{Optimal Transport: Old and New} 
\book{Berlin, DE: Sprin\-ger-Ver\-lag}.
%2%



%1%Wang 2007
    \brefitem[Wang (2007)]{Wan07}
    \aut{Wang, Neng}
    \anno{2007} 
    \jtitle{An equilibrium model with wealth distribution}
    \journal{Journal of Monetary Economics} {54} 1882-\nobreak1904.
%2%


%1%Wang 2007
    \brefitem[Wang (2007)]{Wan07}
    \aut{Wang, Neng}
    \anno{2007} 
    \jtitle{An equilibrium model with wealth distribution}
    \journal{Journal of Monetary Economics} {54} 1882-\nobreak1904.
%2%


%1%Weil 1992
    \brefitem[Weil (1992)]{Wei92}
    \aut{Weil, Philippe}
    \anno{1992} 
\jtitle{Equilibrium asset prices with undiversifiable labor income risk}
\journal{Journal of Economic Dynamics and Control} {16} 769-\nobreak790.
%2%



%1%Wu Zhang 2019
    \brefitem[Wu and Zhang (2019)]{WZ19}
    \aut{Wu, Cong, and Jianfeng Zhang}
    \anno{2019} 
    \jtitle{Viscosity solutions to parabolic master equations and McKean-Vlasov SDEs with closed-loop controls}
    \journal{Annals of Applied Probability} (to appear).
%2%



%1%Zadeh 1970
    \brefitem[Zadeh (1970)]{Zad70}
    \aut{Zadeh, Norman}
    \anno{2016} 
    \jtitle{A Note on the cyclic coordinate ascent method}
    \journal{Management Science} {16} 642-\nobreak644.
%2%


%1%Zeldes 1989
    \brefitem[Zeldes (1989)]{Zel89}
    \aut{Zeldes, Stephen P}
    \anno{1989} 
    \jtitle{Optimal consumption with stochastic income: deviations from certainty equivalence}
    \journal{Quarterly Journal of Economics} {104} 275-\nobreak298.
%2%


%1%Zhang 2017
         \brefitem[Zhang (2017)]{Zha17}
         \aut{Zhang, Jianfeng}
	 \anno{2017} 
	 \btitle{Backward Stochastic Differential Equations: from linear to fully nonlinear theory} 
\book{New York, NY: Springer}.
%2%


%% last mark on the line before
\endgroup
\WriteRefTot

\endinput
