% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{stmaryrd}

\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\graphicspath{ {./images/} }
\usepackage{tikz}
\usepackage{siunitx,booktabs}
%\usepackage[center]{caption}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{hyperref}
\usepackage{subfig}

\usetikzlibrary{calc} 
\newcommand{\splitcell}[1]{%
  \begin{tabular}[t]{@{}c@{}}\strut#1\strut\end{tabular}}

\newcommand{\argmin}{\arg\!\min}
  
\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
  
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}


\newcommand\MyBox[1]{%
  \fbox{\parbox[c][1.7cm][c]{1.7cm}{\centering #1}}%
}
\newcommand\MyVBox[1]{%
  \parbox[c][1.7cm][c]{1cm}{\centering\bfseries #1}%
}  
\newcommand\MyHBox[2][\dimexpr1.7cm+2\fboxsep\relax]{%
  \parbox[c][1cm][c]{#1}{\centering\bfseries #2}%
}  
\newcommand\MyTBox[4]{%
  \MyVBox{#1}\MyBox{#2}\hspace*{-\fboxrule}%
  \MyBox{#3}\hspace*{-\fboxrule}%
  \MyBox{#4}\par\vspace{-\fboxrule}
}  


\begin{document}
%
\title{Smart-Tree: Neural Medial Axis Approximation of Point Clouds for 3D Tree Skeletonization \thanks{Supported by University of Canterbury, New Zealand.}}
%
\titlerunning{Smart-Tree: Neural Axis Approximation}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Harry Dobbs\inst{1}\orcidID{0000-0003-3685-940X}\and
Oliver Batchelor\inst{2}\orcidID{0000-0002-6542-1661}\and
Richard Green\inst{2}\orcidID{0000-0001-5149-722X} \and
James Atlas\inst{2}\orcidID{0000-0002-8030-6098}}

%
\authorrunning{H. Dobbs et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{UC Vision Research Lab, \\ University of Canterbury, \\ Christchurch 8041, New Zealand \\
\email{harry.dobbs@pg.canterbury.ac.nz} \\
\email{\{oliver.batchelor, richard.green, james.atlas\}@canterbury.ac.nz} \\ 
\url{https://ucvision.org.nz/}}
%\and
%Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
%\email{lncs@springer.com}\\
%\url{http://www.springer.com/gp/computer-science/lncs} \and
%ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
%\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
This paper introduces Smart-Tree, a supervised method for approximating the medial axes of branch skeletons from a tree point cloud. Smart-Tree uses a sparse voxel convolutional neural network to extract the radius and direction towards the medial axis of each input point. A greedy algorithm performs robust skeletonization using the estimated medial axis. Our proposed method provides robustness to complex tree structures and improves fidelity when dealing with self-occlusions, complex geometry, touching branches, and varying point densities. We evaluate Smart-Tree using a multi-species synthetic tree dataset and perform qualitative analysis on a real-world tree point cloud. Our experimentation with synthetic and real-world datasets demonstrates the robustness of our approach over the current state-of-the-art method. The dataset\footnote{\url{https://github.com/uc-vision/synthetic-trees}} and source code\footnote{\url{https://github.com/uc-vision/smart-tree}} are publicly available. 

\keywords{Tree Skeletonization \and  Point Cloud \and  Metric Extraction \and Neural Network.}
\end{abstract}

\input{intro}
\input{method}
\input{results}
\input{conclusion}






%\section*{Code Availability} \label{code_availability}

\section*{Acknowledgment}
This work was funded by the New Zealand Ministry of Business, Innovation and Employment under contract C09X1923 (Catalyst: Strategic Fund).
\newline
This research/project is supported by the National Research Foundation, Singapore under its Industry Alignment Fund – Pre-positioning (IAF-PP) Funding Initiative. Any opinions, findings and conclusions or recommendations expressed in this material are those of the author(s) and do not reflect the views of the National Research Foundation, Singapore.

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\bibliographystyle{splncs04}

\bibliography{ref}

\end{document}




