\section{Introduction}
\label{sec:intro}

Hadronic scattering processes in the high-energy region are of great
phenomenological interest. Prime examples include coupling
measurements in weak boson fusion and weak boson scattering.  To
suppress the background in these measurements, one typically requires
jets with large invariant masses and a large difference in
rapidity. These requirements strongly enhance the contribution from
the high-energy region, which is characterised by invariant masses
that are much larger than all transverse scales, or equivalently large
rapidity separations with no strong hierarchy between the transverse
momenta. In this kinematic regime, high-energy logarithms of the large ratio $\hat{s}
/p_\perp^2$ arise in perturbation theory, where $\hat{s}$ is
the square of the partonic centre-of-mass energy and $p_\perp$ the characteristic
transverse momentum scale. In the QCD component, these large
logarithms jeopardise the convergence of the perturbative series.

\HIGHEJ (\HEJ) is both a framework and a flexible Monte Carlo
generator for the all-order resummation of high-energy
logarithms~\cite{Andersen:2009nu,Andersen:2009he,Andersen:2011hs}. In
\HEJ 2~\cite{Andersen:2019yzo}, this high-energy resummation can
additionally be matched to leading-order predictions obtained using
conventional fixed-order generators~\cite{Andersen:2017kfc}. \HEJ has
been validated against data in experimental studies of pure multijet
production~\cite{ATLAS:2011yyh,CMS:2012rfo,CMS:2012xfg,ATLAS:2014lzu},
lepton pair production via a virtual W boson, photon, or Z boson in
association with two or more
jets~\cite{Andersen:2012gk,D0:2013gro,ATLAS:2014fjg,Andersen:2016vkp},
and Higgs boson production with jets~\cite{Andersen:2022zte}.

In the following, we present \HEJ 2.2. This new version implements
high-energy resummation for the production of two leptonically
decaying W bosons with the same charge in association with two or more
jets. Moreover, the existing implementation for the production of a Higgs boson
with jets has been extended to also cover Higgs boson production with
a single jet. Resummation for the production of a charged lepton pair
via a virtual photon or Z boson together with two or more jets is now
also supported for higher multiplicities where no fixed-order
prediction is available. Furthermore, new options have been added, for
instance to facilitate differential next-to-leading-order matching and
to separate events with soft jets. In section~\ref{sec:features}, we
briefly summarise \HIGHEJ and describe the various improvements in
version 2.2. We give examples for the use of the new features
in section~\ref{sec:usage} and conclude in
section~\ref{sec:conclusions}.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
