\section{Related Work}\label{sec:related_works}
% In this section, we present some work that is closely related to our proposed work. 
Our proposed stochastic optimization problem is mainly related to three major areas of work. The first major area is optimization with complementarity constraints. This topic has been well studied in optimization and robotics literature~\cite{posa2014direct, 9812069, 8740889, shirai_2022iros}. This approach has been shown to work well for generating trajectories for manipulation and locomotion problems. However, it cannot be trivially extended to stochastic complementarity systems to introduce robustness. More recently, contact-aware feedback controllers for contact-rich systems have been proposed \cite{9197568} for linear complementarity systems. However, it cannot also be extended to consider stochastic complementarity constraints to provide stochastic guarantees. 

Using stochastic complementarity constraints for planning robust manipulation is not so well understood in literature. Some of the recent work could be found in~\cite{drnach2021robust, shirai2022chance}. However, the problem with these approaches is that the uncertainty needs to be very small otherwise the optimization might be infeasible. Consequently, these approaches could fail to provide robust plans for uncertain contact systems. Furthermore, uncertainty propagation for stochastic complementarity systems is not properly modeled in these approaches. One of the reasons is the implicit relationship between contact and state variables in complementarity constraints. As a consequence, most of the known approaches (e.g., extended Kalman
filter \cite{thrun2002probabilistic}, unscented Kalman filter \cite{julier2004unscented},  moment-based \cite{wang2020fast, jasour2021moment}) for uncertainty propagation can not be used for stochastic complementarity systems.

% More recently, there has some to deal with long horizon planning for uncertain systems. 
Since open-loop CCO would lead to quite conservative solutions to satisfy chance constraints, 
  covariance steering methods have gained attention to deal with long-horizon planning for uncertain systems \cite{hotz1987covariance, okamoto2019optimal, ridderhof2019nonlinear}. Covariance steering methods are able to design feedforward and feedback gains simultaneously to satisfy chance constraints. However, these cannot be directly applied to contact-rich systems since they assume (in general) linear dynamics with Gaussian additive noises. 

In this paper, we present an approach for planning in stochastic contact-rich systems which formulates a robust controller design by considering covariance steering during planning. To understand uncertainty evolution in stochastic complementarity systems, we use particle-based control formulation~\cite{5477242, doi:10.1137/070702928, pagnoncelli2009sample, sehr2017particle} to get approximate uncertainty propagation. To the best of our knowledge, this is the first time that we have shown covariance steering with chance constraints for complementarity systems. 