\documentclass[lettersize,journal]{IEEEtran}
\input{Sections/customary_settings}

\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
% updated with editorial comments 8/9/2021

\begin{document}

\title{Adaptive Log-Euclidean Metrics for SPD Matrix Learning}

% \author{IEEE Publication Technology,~\IEEEmembership{Staff,~IEEE,}
%         % <-this % stops a space
% \thanks{This paper was produced by the IEEE Publication Technology Group. They are in Piscataway, NJ.}% <-this % stops a space
% \thanks{Manuscript received April 19, 2021; revised August 16, 2021.}}

% % The paper headers
\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2021}%
{Shell \MakeLowercase{\textit{et al.}}: A Sample Article Using IEEEtran.cls for IEEE Journals}

\author{Ziheng~Chen,
        Yue~Song\textsuperscript{*},
        Tianyang~Xu,
        Zhiwu~Huang,
        Xiao-Jun~Wu,
        and
        Nicu~Sebe
        \thanks{This work was partly supported by the MUR PNRR project FAIR (PE00000013) funded by the NextGenerationEU, the EU Horizon project ELIAS (No. 101120237), and a donation from Cisco. The authors also gratefully acknowledge the financial support from the China Scholarship Council
        (CSC).}
        \thanks{Ziheng Chen, Yue Song, and Nicu Sebe are with the Department
        of Information Engineering and Computer Science, University of Trento,
        Trento, Italy.
        E-mail: ziheng\_ch@163.com, songyue19960927@gmail.com, niculae.sebe@unitn.it.
        (Corresponding author: Yue Song)}
        \thanks{Tianyang~Xu and Xiao-Jun~Wu are with the School of Artificial Intelligence and Computer Science, Jiangnan University, Wuxi, China.
        E-mail: {tianyang.xu; wu\_xiaojun}@jiangnan.edu.cn.}
        \thanks{Zhiwu~Huang is with the School of Electronics and Computer Science, University of Southampton, Southampton, U.K.
        E-mail: zhiwu.huang@soton.ac.uk.}
        \thanks{This paper has supplementary downloadable material available at \url{http://ieeexplore.ieee.org}, provided by the authors. The material includes preliminaries, implementation details, and proofs.}
        }

% \IEEEpubid{0000--0000/00\$00.00~\copyright~2021 IEEE}
% Remember, if you use this you must call \IEEEpubidadjcol in the second
% column for its text to clear the IEEEpubid mark.

\maketitle


\input{Sections/Abstract}
\input{Sections/Intro}
\input{Sections/Preliminaries}
\input{Sections/ALEM}
\input{Sections/Properties}
\input{Sections/Applications}
\input{Sections/ParamLearning}
\input{Sections/Experiments}
\input{Sections/Other_applications}
\input{Sections/Limitations}
\input{Sections/Conclusion}

\bibliographystyle{IEEEtran}
\bibliography{Sections/ref}
\input{Sections/Biography}

\input{Sections/Appendix}

\end{document}


