
\documentclass{article} % For LaTeX2e
\usepackage{iclr2021_conference,times}

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

\usepackage{hyperref}
\usepackage{url}
\usepackage[pdftex]{graphicx}
\usepackage[capitalize,noabbrev]{cleveref}                                                      
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{tikz}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=0.5pt] (char) {#1};}}
\title{$R^2$: Range Regularization for Model Compression and Quantization}

% Authors must not appear in the submitted version. They should be hidden
% as long as the \iclrfinalcopy macro remains commented out below.
% Non-anonymous submissions will be rejected without review.

\author{Arnav Kundu$^*$
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Chungkuk Yoo$^*$
\and
Srijan Mishra$^*$
\and
Minsik Cho
\and
Saurabh Adya\\
Apple Inc.\\
\{a\_kundu, ckyoo, srijan, minsik, sadya\}@apple.com
}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}
\newcommand{\edit}[1]{\textcolor{blue}{#1}}
\newcommand{\remove}[1]{\textcolor{red}{#1}}
%\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
\begin{document}


\maketitle

\begin{abstract}
\edit{Weight range restriction techniques like L1 and L2 regularization helps is a widely used technique to improve generalization, but, it can also be used to shape the weight distributions for various purposes. } \remove{Model parameter regularization is a widely used technique to improve generalization, but, it can also be used to shape the weight distributions for various purposes. }
In this work, we propose range regularization ($R^2$) for building quantization and compression friendly models by removing outliers from weights during training. By effectively regulating range of weights, we mold the overall distribution into a tight shape to ensure high quantization bit resolution, therefore allowing model compression and quantization techniques can to utilize their limited numeric representation powers better. We introduce $L_\infty$ regularization, its extension margin regularization and a new soft-min-max regularization to be used as a regularization loss during full-precision model training. We show that this technique generalizes well for post training quantization, quantization aware training methods like EWGS and compression techniques like DKM. Coupled with state-of-the-art quantization and compression techniques, models trained with $R^2$ perform better on an average, specifically at lower bit weights with 16x compression ratio. Our results show that $R^2$ generates state of the art 2-bit quantized models for heavily parameter constrained models like MobileNet V1 and V2 when coupled with EWGS. Additionally, for high compression ratio (32x), models trained with $R^2$ significantly better than the ones trained without it.
% We also demonstrate that $R^2$ helps parameter constrained models like MobileNetV1 achieve significant absolute improvement of around 8\% for 2 bit quantization and 7\% for 1 bit compression.
\end{abstract}

\input{sections/1_introduction.tex}
\input{sections/4_related_work.tex}
\input{sections/2_range_loss.tex}
\input{sections/3_experiment.tex}

\input{sections/5_conclusion.tex}




\bibliography{iclr2021_conference}
\bibliographystyle{iclr2021_conference}

%\appendix
%\section{Appendix}
%You may include other additional sections here.

\end{document}
