% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{glossaries}
\usepackage[table,xcdraw]{xcolor}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{float}
\usepackage{hyperref}

% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\linespread{0.99}
\begin{document}
%
\input{0.acronyms}
% \title{Grammar-aware self-adaptive mutation operator}
% \title{Context is All You Need: Self-Adaptive Mutation for Grammars}
\title{Context Matters: Adaptive Mutation for Grammars}
% %
% %\titlerunning{Abbreviated paper title}
% % If the paper title is too long for the running head, you can set
% % an abbreviated paper title here
% %
\author{Pedro Carvalho\orcidID{0000-0003-3845-4617} \and
Jessica Mégane\orcidID{0000-0001-6697-5423} \and
Nuno Lourenço\orcidID{0000-0002-2154-0642} \and
Penousal Machado\orcidID{0000-0002-6308-6484}
}
% %
\authorrunning{P. Carvalho et al.}
% % First names are abbreviated in the running head.
% % If there are more than two authors, 'et al.' is used.
% %
\institute{University of Coimbra, Centre for Informatics and Systems of the University of Coimbra, Department of Informatics Engineering
\email{\{pfcarvalho,jessicac,naml,machado\}@dei.uc.pt}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
This work proposes Adaptive Facilitated Mutation, a self-adaptive mutation method for Structured Grammatical Evolution (SGE), biologically inspired by the theory of facilitated variation. 
In SGE, the genotype of individuals contains a list for each non-terminal of the grammar that defines the search space. 
In our proposed mutation, each individual contains an array with a different, self-adaptive mutation rate for each non-terminal.
We also propose Function Grouped Grammars, a grammar design procedure to enhance the benefits of the propose mutation.
Experiments were conducted on three symbolic regression benchmarks using Probabilistic Structured Grammatical Evolution (PSGE), a variant of SGE. 
Results show our approach is similar or better when compared with the standard grammar and mutation.

\keywords{Adaptive Mutation \and Grammar-design \and Grammar-based Genetic Programming.}
\end{abstract}



\section{Introduction}
\input{1.introduction.tex}

\input{2.background.tex}

\section{Adaptive Facilitated Mutation}
\label{sec:mutation_levels}
\input{3.mutation}

\section{Experimental Setup}
\label{sec:experimental_setup}
\input{4.experimental_setup}

\section{Results}
\label{sec:results}
\input{5.results}

\section{Conclusion}
\label{sec:conc}
\input{6.conclusions}

\section*{Acknowledgments}
This work was funded by FEDER funds through the Operational Programme Competitiveness Factors - COMPETE and national funds by FCT - Foundation for Science and Technology (POCI-01-0145-FEDER-029297, CISUC - UID/CEC/00326/2020) and within the scope of the project A4A: Audiology for All (CENTRO-01-0247-FEDER-047083) financed by the Operational Program for Competitiveness and Internationalisation of PORTUGAL 2020 through the European Regional Development Fund. The first author is funded by FCT, Portugal, under the grant UI/BD/151053/2021 and the second under the grant 2022.10174.BD.

% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\bibliographystyle{splncs04}
\bibliography{bibliography}
% \begin{thebibliography}{8}
% \bibitem{ref_article1}
% Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

% \bibitem{ref_lncs1}
% Author, F., Author, S.: Title of a proceedings paper. In: Editor,
% F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
% Springer, Heidelberg (2016). \doi{10.10007/1234567890}

% \bibitem{ref_book1}
% Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
% Location (1999)

% \bibitem{ref_proc1}
% Author, A.-B.: Contribution title. In: 9th International Proceedings
% on Proceedings, pp. 1--2. Publisher, Location (2010)

% \bibitem{ref_url1}
% LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
% Oct 2017
% \end{thebibliography}
\end{document}
