\documentclass[a4paper,11pt,sans]{letter}
\usepackage[scale=0.75, top=1cm, bottom=1cm]{geometry}
\longindentation=0pt    

% Name of sender
\name{Yuhan Bao}

% Signature of sender
% \signature{Joe Fox}

% Address of sender
\address{
    Zhejiang University, P.R. China
}

\begin{document}

% Name and address of receiver
\begin{letter}{
    % Name and address of receiver
}

% Opening statement
\opening{Dear Editor,}
We are writing to submit our manuscript entitled "Improving Fast Auto-Focus with Event Polarity" to your distinguished journal Optics Express for consideration of publication. 


% In the past, achieving fast camera autofocus in dark as well as dynamic scenes has been a problem.
Historically, fast camera autofocus in low-light and dynamic scenes has been problematic.
In this study, we present an algorithm for high-speed autofocus utilizing event cameras, which can attain autofocus in low-light and rapidly changing environments with an error of less than 1 depth-of-focus and a speed of less than 4 ms.
Our proposed algorithm not only offers a reliable autofocus solution for event cameras but also introduces a novel approach to autofocus for traditional cameras in challenging scenarios, as demonstrated through our custom-built platform combining both types of cameras.



Specifically, We derive an event-based focus evaluation function by leveraging the symmetrical relationship between event polarities in the focusing process, grounded in the principles of event cameras and the imaging model.
We believe that our approach has the potential to revolutionize camera focusing and inspire novel ideas in various applications utilizing the depth-from-focus technique.

% In our opinion, our method will not only bring innovation to camera focusing itself but also enlighten new ideas in a range of applications based on the depth-from-focus method. 

% Optics Express is a well-known journal in the field of optics, and our work starts from the imaging principles of the focusing process and incorporates the latest dynamic vision sensor technology, solving the long-standing focusing problem in the field of optics. So we feel that our work is suitable for Optics Express.

Given that our study builds upon the fundamental principles of the focusing process and integrates the latest dynamic vision sensor technology, we believe that it addresses a longstanding challenge in the field of optics and is well-suited for publication in Optics Express, a reputable journal in the optics community.


No conflict of interest exists in the submission of this manuscript. All authors have approved the manuscript and have contributed significantly to the paper.

We appreciate your consideration of our manuscript.


\closing{Yours sincerely,}

\end{letter}
\end{document}