\section{Ablation Studies}\label{sec:ablation}
We run several ablation studies on our network architecture design. Table~\ref{tab:ablation} lists key design variables in DefGraspNets, with our selected conditions in bold. We compare our baseline model with 5 other trained models, each of which differ from baseline by exactly one condition.  We compare performance on a fixed test set and report the Kendall's $\tau$ metric for mean $\vec{d}$ and $\vec{\sigma}$. % over $50$ training epochs. 
We address the following questions:
\begin{itemize}[leftmargin=2ex]
    \item Does jointly predicting stress and deformation outperform using two separate networks to predict these quantities? (Ans: The $\tau$ metric is comparable in both cases, likely because stress and deformation are coupled through the equations of elasticity. Thus, training two networks would be strictly disadvantageous computationally, c.f. V1.)
    \item Does one-step prediction outperform multi-step prediction? (Ans: Yes, when predicting deformation. Otherwise, both are comparable when predicting stress, c.f. V2. In MeshGraphNets, multi-step prediction does not accumulate significant deformation errors  because the trajectory of the actuators is exactly controlled. In DefGraspNets, gripper force is commanded; the positions of \textit{both} $M_o$ and $M_g$ are predicted and subject to accumulating errors.) 
    \item Should $F_g$ be normalized by the number of contact edges? (Ans: Yes. This aligns with simulation, in which the total force is the sum of forces at all contact points, c.f. V3.)
    \item Should force features $F_g^C$ be assigned to contact edges or to gripper nodes? (Ans: The network is able to incorporate this information equally well, c.f. V4.)
\end{itemize}



\begin{table}[!htp]\centering
\caption{Ablation study variables and conditions. Our DefGraspNets network conditions are in bold. Best conditions are in gray.}\label{tab:ablation}
\scriptsize
\begin{tabular}{lrrrr}\toprule
\textbf{Variable} &\textbf{Condition} &\textbf{$\tau_d$↑} &\textbf{$\tau_s$↑} \\\midrule
\multirow{3}{*}{V1. Num. outputs} &\textbf{Def. and stress} &\cellcolor[HTML]{efefef}0.61 &0.82 \\
&Def. only &0.57 & \\
&Stress only & &\cellcolor[HTML]{efefef}0.84 \\ \midrule
\multirow{2}{*}{V2. Prediction type} &\textbf{One-step predictions} &\cellcolor[HTML]{efefef}0.61 &\cellcolor[HTML]{efefef}0.82 \\
&Multi-step &0.37 &0.70 \\ \midrule
\multirow{2}{*}{V3. Value of $F_g^W$} &\textbf{Distributed, $\mathbf{\sfrac{F_g}{|E^W|}}$} &\cellcolor[HTML]{efefef}0.61 &\cellcolor[HTML]{efefef}0.82 \\
&Non-distributed $F_g$ &0.33 &0.51 \\ \midrule
\multirow{2}{*}{V4. Assignment of $F_g$} &\textbf{On world edges $E^W$} &\cellcolor[HTML]{efefef}0.61 &\cellcolor[HTML]{efefef}0.82 \\
&On all nodes $V$ &0.58 &0.74 \\
\bottomrule
\end{tabular}
\vspace{-14pt}
\end{table}

