%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper
% \documentclass[letterpaper, 10 pt, conference]{IEEEtran}

% \documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

% \overrideIEEEmargins   
% Needed to meet printer requirements.

%\usepackage[numbers]{natbib}
% Allows citations like [1]--[3] instead of [1],[2],[3]
\usepackage[noadjust]{cite}
\def\citepunct{,}
\def\citedash{--}




% The following packages can be found on http:\\www.ctan.org
\usepackage{graphicx} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{float}
\usepackage{hyperref}
\usepackage{color}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{subcaption}
\usepackage{xfrac}


\usepackage{booktabs, multirow} % for borders and merged ranges
\usepackage{soul}% for underlines
\let\labelindent\relax
\usepackage{enumitem}

\usepackage[table]{xcolor} % for cell colors
\usepackage{changepage,threeparttable} % for wide tables
%If the table is too wide, replace \begin{table}[!htp]...\end{table} with
%\begin{adjustwidth}{-2.5 cm}{-2.5 cm}\centering\begin{threeparttable}[!htb]...\end{threeparttable}\end{adjustwidth}
% \pagenumbering{arabic}
\definecolor{international_orange}{RGB}{240, 74, 0}
\newcommand{\IH}[1]{
 {\textcolor{magenta}{#1}}}

\newcommand{\YN}[1]{
 {\textcolor{blue}{\textbf{[#1 --YN]}}}}
 
\newcommand{\CE}[1]{
 {\textcolor{YellowOrange}{\textbf{[#1 --CE]}}}}
 
\newcommand{\BS}[1]{
 {\textcolor{green}{\textbf{[#1 --BS]}}}}

\newcommand{\tucker}[1]{
 {\textcolor{international_orange}{\textbf{[#1 --TRH]}}}}

\newcommand{\NB}[1]{
 {\textcolor{magenta}{#1}}}
 
 \newcommand{\MM}[1]{
 {\textcolor{BlueViolet}{\textbf{[#1 --MM]}}}}
 
  \newcommand{\DF}[1]{
 {\textcolor{red}{\textbf{[#1 --DF]}}}}
 
  \newcommand{\FR}[1]{
 {\textcolor{cyan}{\textbf{[#1 --FR]}}}}
 
 
\newcommand{\units}[1]{\text{#1}}
 
\title{\LARGE \bf
DefGraspNets: Grasp Planning on 3D Fields with Graph Neural Nets 
}


\author{Isabella Huang$^{1}$, Yashraj Narang$^{2}$, Ruzena Bajcsy$^{1}$, Fabio Ramos$^{2,3}$, Tucker Hermans$^{2,4}$, Dieter Fox$^{2,5}$% <-this % stops a space
\thanks{$^{1}$Department of Electrical Engineering and Computer Sciences, University of California, Berkeley, USA ;$^{2}$NVIDIA Corporation, Seattle, USA;$^{3}$School of Computer Science, University of Sydney, Sydney, Australia;$^{4}$School of Computing, University of Utah, Salt Lake City, USA;$^{5}$Paul G. Allen School of Computer Science \& Engineering, University of Washington, Seattle, USA}}
\frenchspacing
\usepackage[skip=1pt,font=small,labelfont=bf]{caption}
\begin{document}



\maketitle
\thispagestyle{empty} 
\pagestyle{empty} 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  Robotic grasping of 3D deformable objects is critical for real-world applications such as food handling and robotic surgery. Unlike rigid and articulated objects, 3D deformable objects have infinite degrees of freedom. Fully defining their state requires 3D  deformation and stress fields, which are exceptionally difficult to analytically compute or experimentally measure. Thus, evaluating grasp candidates for grasp planning typically requires accurate, but slow 3D finite element method (FEM) simulation. Sampling-based grasp planning is often impractical, as it requires evaluation of a large number of grasp candidates. Gradient-based grasp planning can be more efficient, but requires a differentiable model to synthesize optimal grasps from initial candidates.
  Differentiable FEM simulators may fill this role, but are typically no faster than standard FEM. In this work, we propose learning a predictive graph neural network (GNN), DefGraspNets, to act as our differentiable model.
  We train DefGraspNets to predict 3D stress and deformation fields based on FEM-based grasp simulations.
  DefGraspNets not only runs up to $1500$x faster than the FEM simulator, 
  but also enables fast gradient-based grasp optimization over 3D stress and deformation metrics. We design DefGraspNets to align with real-world grasp planning practices and demonstrate generalization across multiple test sets, including real-world experiments.
\end{abstract}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{1_introduction}
\input{2_related_work}
\input{3_model}
\input{4_training}
\input{5_grasp_planning}
\input{6_prediction_results}
\input{7_grasp_planning_results}
\input{8_ablation}
\input{10_discussion}


\clearpage
\newpage
\bibliographystyle{unsrt}
\bibliography{references}  % .bib

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End: