\section{Related Work}

% \weikai{The current related work is a bit long.  We should shrink it. Ideally, the methodology section should end before 6th page (or at most 6.5 pages), leaving the rest 3 (2.5) pages for experiments + conclusion.}

\paragraph{3D Geometric Representation}
A 3D surface can be represented explicitly with voxels~\cite{shapenet2015,voxnet,7410471,3dr2n2,li2022voxsurf}, point clouds~\cite{8099747,mandikal20183dlmnet,lin2018learning,FoldingNet,achlioptas2018learning}, and meshes~\cite{pixel2mesh,atlasnet,pixel2mesh++}, or can be represented implicitly with neural implicit functions, which have gained popularity for their continuity and the arbitrary-resolution property. 
% We divide the implicit representations into two categories: implicit representation for watertight surfaces and implicit representation for arbitrary surfaces.
Watertight surfaces could be represented by occupancy functions~\cite{occnet, sdf0, pifuSHNMKL19}, signed distance functions~\cite{deepsdf,michalkiewicz2019implicit,disn}, or other signed implicits~\cite{Atzmon_2020_CVPR,genova2018unsupervised}. These approaches are limited to closed surfaces as they require the space to be represented as ``inside" and ``outside."
To lift the limitation, unsigned distance function (UDF)~\cite{Venkatesh_2021_ICCV, chibane2020ndf, venkatesh2020dude} is proposed to represent a much broader class of shapes containing open surfaces. However, the signless property of UDF prevents itself from applying the classic field-to-mesh conversion techniques~\cite{marching_cubes}. Instead, these UDF approaches support exporting open surfaces by applying the Ball-Pivoting algorithm~\cite{BPA}, meshUDF~\cite{guillard2021meshudf}, and Neural Dual Contouring~\cite{chen2022ndc}, which are prone to disconnected surface patches with inconsistent normals and coherence artifacts.
% Neural Dual Contouring (NDC)~\cite{chen2022ndc} supports exporting open surfaces from UDF by using a neural network to predict the vertex locations and edge crossings. However, NDC is not completely invariant to orientation: it occasionally generates coherence artifacts on sharp edges.
GIFS~\cite{Ye_2022_CVPR} represents non-watertight shapes by encoding whether two points are separated by any surface instead of dividing a 3D space into predefined inside/outside regions.
Three-pole signed distance function (3PSDF) ~\cite{chen_2022_3psdf} introduces the \textit{null} sign in addition to the conventional \textit{in} and \textit{out} labels. 
The \textit{null} sign stops the formation of closed isosurfaces, thus enabling the representation of both watertight- and open-surfaces. 
However, 3PSDF~\cite{chen_2022_3psdf} and GIFS~\cite{Ye_2022_CVPR} model the reconstruction of open surfaces as a classification problem, thus preventing these implicit representations from being differentiable. As a result, these methods do not support differentiable downstream tasks like differentiable rendering.
Inspired by the \textit{null} sign of 3PSDF, we propose to represent an open surface as a signed distance function with a validity branch to estimate the surface existence probability at the query positions, which bypasses its limitation of non-differentiability while keeping its capability of modeling arbitrary shapes.


% \weikai{GIFS~\cite{Ye_2022_CVPR} is also a new implicit representation that can represent non-watertight surfaces. We should add it. Neural Dual Contouring~\cite{chen2022ndc} can convert UDF to open surfaces. We should mention it as well.}
\vspace{-1em}
\paragraph{Implicit Surfaces Reconstruction from Multi-view Images}
It is well-known that a 3D database is more challenging to acquire than a 2D database. As such, learning shapes from 2D supervision is important and necessary.
Multiple differentiable rendering (DR) techniques have been proposed to circumvent the difficulty of explicit correspondence matching in 3D reconstruction.
Two popular types of DR are differentiable rasterization~\cite{kato2018neural,NEURIPS2019_f5ac21cd,softras,8578972} and differentiable ray casting.
% which could be coupled with the implicit representations to reconstruct 3D shapes from multi-view images. We concentrate on introducing the recent advances in differentiable ray casting since the proposed work falls into this category.\brandon{It is better to say the reason of choosing ray casting way, such as better performance valided by Nerf or Neus like works.}
A popular branch of differentiable ray casting is surface rendering~\cite{jiang2020sdfdiff, dvr, yariv2020idr, dist, liu2019learning}, which assumes that the ray's color only relies on the color of the intersection point. Surface rendering methods represent the geometry as an implicit function and learn the surface representation from 2D images via differentiable rendering techniques. 
% Surface rendering methods represent the geometry as an implicit function defined over a volumetric grid or implicit neural representation and learn the surface representation in 3D space from 2D images via differentiable rendering techniques. 
NeRF~\cite{mildenhall2020nerf} and follow-up volume rendering methods assume that the ray's color relies on all the sampled points along the ray. 
UNISURF~\cite{oechsle2021unisurf} improves the reconstruction quality by shrinking the sample region of volume rendering during optimization. 
{
NeuS~\cite{wang2021neus}, VolSDF~\cite{yariv2021volume} and HF-NeuS~\cite{wang2022hfneus} develop volume density functions for watertight surfaces applied to SDFs, which combine the advantages of surface rendering-based and volume rendering-based methods.
However, as the above methods all rely on the representation of the signed distance function or occupancy field, they can only reconstruct watertight shapes. NeuralUDF~\cite{long2023neuraludf} and NeUDF~\cite{liu2023neudf}, two concurrent works, propose to represent arbitrary surfaces as a UDF and develop unbiased density functions that correlate the property of UDF with the volume rendering scheme. However, converting UDF to a mesh typically suffer from artifacts, inconsistent normals, and large computational costs. Compared with the UDF-based approaches, our method represents the scene by a signed distance function with a validity branch,
and thus is compatible with easy field-to-mesh conversion methods, such as the classic Marching Cubes algorithm, ensuring high-fidelity and normal-consistent meshing results from the implicit field.
}
% NeuS~\cite{wang2021neus} develops an unbiased and occlusion-aware volume rendering method, which combines the advantages of surface rendering-based and volume rendering based-methods.
% Our method differs from the above reconstruction approaches in that we represent the scene by a signed distance function with a validity branch, thus supporting the reconstruction of arbitrary surfaces.
