Existing methods for open set action recognition focus on novelty detection that assumes video clips show a single action, which is unrealistic in the real world.
We propose a new method for open set action recognition and novelty detection via \textbf{MU}lti-\textbf{L}abel \textbf{E}vidential learning (\sysname{}), that goes beyond previous novel action detection methods by addressing the more general problems of single or multiple actors in the same scene, with simultaneous action(s) by any actor. 
Our Beta Evidential Neural Network estimates multi-action uncertainty with Beta densities based on actor-context-object relation representations. An evidence debiasing constraint is added to the objective function for optimization to reduce the static bias of video representations, which can incorrectly correlate predictions and static cues. We develop a learning algorithm based on a primal-dual average scheme update to optimize the proposed problem. Theoretical analysis of the optimization algorithm demonstrates the convergence of the primal solution sequence and bounds for both the loss function and the debiasing constraint. Uncertainty and belief-based novelty estimation mechanisms are formulated to detect novel actions.
%and re-split two video datasets for a fair comparison.
%To evaluate our system, we formalize the multi-actor/multi-action novelty detection problem and enhance multiple single-actor/single-action novelty detection approaches to work within the new paradigm to provide strong baselines.
Extensive experiments on two real-world video datasets show that our proposed approach achieves promising performance in single/multi-actor, single/multi-action settings.