\documentclass[conference,letterpaper]{IEEEtran}
\IEEEoverridecommandlockouts%
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
% \overrideIEEEmargins 
\usepackage{cite}
\usepackage[para]{footmisc}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
%\usepackage{enumitem}
\usepackage{graphicx}
\graphicspath{{./img/}}
\usepackage{textcomp}
\usepackage[table,xcdraw]{xcolor}
\usepackage{diagbox}
\usepackage{colortbl}
\setlength{\marginparwidth}{2cm}
\usepackage{todonotes}
\usepackage{multirow}
\usepackage{url}
\usepackage{nohyperref} %%For export activate for no hyperlinks.
%\usepackage{hyperref} %%Activate for hyperlinks.
\usepackage[per-mode=symbol,group-separator={,},group-minimum-digits={3}]{siunitx}
\sisetup{detect-weight=true, detect-family=true}
%\usepackage{subfig}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[nohyperlinks,nolist]{acronym} %\ac{} ausgabe, \acl{} langausgabe, \acf{} zweites erstes mal, \acp plural
\usepackage[]{algorithm2e}
\usepackage{tikz}
\usepackage{tikz-layers}
\usetikzlibrary{calc}
\usepackage{tabularx}
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\newcolumntype{L}{>{\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
\usepackage{booktabs}
\usepackage[absolute,showboxes]{textpos}
\usetikzlibrary{patterns}
\usetikzlibrary{spy}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{fit}
\usepackage{pgfplots}
\pgfplotsset{compat=newest}
\usepgfplotslibrary{units}
\usepgfplotslibrary{groupplots}
\usepgfplotslibrary{statistics}
\makeatletter
\pgfplotsset{
 unit code/.code 2 args=
   \begingroup
   \protected@edef\x{\endgroup\si{#2}}\x
}
\makeatother
\usetikzlibrary{matrix}
\usetikzlibrary{shapes.misc}

% colors from topology image.
\definecolor{CoreGray}{HTML}{BFBFBF}
\definecolor{CoreBlack}{HTML}{333333}
\definecolor{CoreBlue}{HTML}{002E7D}
\definecolor{CoreGreen}{HTML}{6AAC8E}
\definecolor{CoreRed}{HTML}{C80000}
\definecolor{CoreYellow}{HTML}{E6AC00}
\definecolor{CoreWhite}{HTML}{FFFFFF}
\definecolor{CoreMiddleGray}{HTML}{e5e5e5}
% Light colors from topology image.
\colorlet{LightCoreGray}{CoreGray!20}
\colorlet{LightCoreBlack}{CoreBlack!20}
\definecolor{CoreLightBlue}{HTML}{8BBDEB}
\colorlet{LightCoreGreen}{CoreGreen!30}
\colorlet{LightCoreRed}{CoreRed!20}
\colorlet{LightCoreYellow}{CoreYellow!20}
\colorlet{LightCoreWhite}{CoreWhite!20}

\newcommand\codeword[1]{\mbox{\texttt{\textcolor{CoreBlack}{#1}}}}

\usepackage[absolute,showboxes]{textpos}

\makeatletter
\newcommand\footnoteref[1]{\protected@xdef\@thefnmark{\ref{#1}}\@footnotemark}
\makeatother

\begin{document}

% Automatically shrink down the bib entries:
\bstctlcite{my:BSTcontrol}

\title{
    Authenticated and Secure Automotive Service Discovery with DNSSEC and DANE
    % \thanks{}
}
\author{\IEEEauthorblockN{Mehmet Mueller}\IEEEauthorblockA{\href{http://www.haw-hamburg.de/ti-i}{\textit{Dept. Computer Science}},
\href{http://www.haw-hamburg.de/ti-i}{\textit{Hamburg University of Applied Sciences}}, Germany \\
\{\href{mailto:mehmet.mueller@haw-hamburg.de}{mehmet.mueller}\}@haw-hamburg.de}
}
\author{\IEEEauthorblockN{Mehmet Mueller, Timo H\"ackel, Philipp Meyer, Franz Korf, and Thomas C. Schmidt}%
\IEEEauthorblockA{\href{http://www.haw-hamburg.de/ti-i}{\textit{Dept. Computer Science}},
\href{http://www.haw-hamburg.de/ti-i}{\textit{Hamburg University of Applied Sciences}}, Germany \\
\{\href{mailto:mehmet.mueller@haw-hamburg.de}{mehmet.mueller}, %
\href{mailto:timo.haeckel@haw-hamburg.de}{timo.haeckel}, %
\href{mailto:philipp.meyer@haw-hamburg.de}{philipp.meyer}, %
\href{mailto:franz.korf@haw-hamburg.de}{franz.korf}, %
\href{mailto:t.schmidt@haw-hamburg.de}{t.schmidt}\}@haw-hamburg.de} %
}

\maketitle

\setlength{\TPHorizModule}{\paperwidth}
\setlength{\TPVertModule}{\paperheight}
\TPMargin{5pt}
\begin{textblock}{0.8}(0.1,0.02)
     \noindent
     \footnotesize
     If you cite this paper, please use the original reference:
     Mehmet Mueller, Timo H\"ackel, Philipp Meyer, Franz Korf, and Thomas C. Schmidt. 
     ``Authenticated and Secure Automotive Service Discovery with DNSSEC and DANE,'' In: \emph{Proceedings of the 14th IEEE Vehicular Networking Conference (VNC)}. IEEE, April 2023.
\end{textblock}

\begin{abstract}
    Automotive softwarization is progressing and future cars are expected to operate a \acl{SOA} on multipurpose compute units, which are interconnected via a high-speed Ethernet backbone. The AUTOSAR architecture foresees a universal middleware called \acs{SOME/IP} that provides the service primitives, interfaces, and application  protocols on top of Ethernet and IP. \acs{SOME/IP} lacks a robust security architecture, even though security is an essential in future Internet-connected vehicles. 
	In this paper, we augment the \acs{SOME/IP} service discovery with an authentication and certificate management scheme based on DNSSEC and DANE. We argue that the deployment of well-proven, widely tested standard protocols should serve as an appropriate basis for a robust and reliable security infrastructure in cars. Our solution enables on-demand service authentication in offline scenarios, easy online updates, and remains free of attestation collisions. We evaluate our extension of the common \textit{vsomeip} stack and find performance values that fully comply with car operations. 
\end{abstract}

\begin{IEEEkeywords}
    Automotive security, authentication, attestation, service orientation, SOME/IP, AUTOSAR, standards
\end{IEEEkeywords}


%%%% 	Acronyms    %%%%
\input{tex/0_acronyms}

%%%%	Document    %%%%
\input{tex/1_intro}
\input{tex/2_background}
\input{tex/3_concept}
\input{tex/4_evaluation}
\input{tex/5_conclusion}
%\newpage

%%%% 	BibTeX		%%%%
%\bibliographystyle{plain}
\bibliographystyle{IEEEtran}
\bibliography{bibtex/HTML-Export/all_generated,bib/own,bib/security,bib/rfcs,bib/literature,bib/bibliography}

\end{document}
