\bibliographystyle{alpha}
\begin{thebibliography}{DDG$^+$15}
\bibitem[Ban22]{Ban}
        I.~M.~Banfield: {\em The maximum Levine-Tristram signature of torus knots} (2022), preprint available at \url{http://arxiv.org/abs/2212.09604}.

\bibitem[BBL20]{BBL}
	S.~Baader, I.~Banfield, L.~Lewark: {\em Untwisting $3$-strand torus knots}, Bull. Lond. Math. Soc. \textbf{52} (2020), no.~3, 429--436.

\bibitem[Ben83]{bennequin}
	D.~Bennequin: {\em Entrelacements et {\'e}quations de {P}faff}, Third {S}chnepfenried geometry conference, {V}ol. 1 ({S}chnepfenried, 1982), volume \textbf{107} of Ast{\'e}risque, Soc. Math. France, Paris (1983), 87--161.

\bibitem[BKL98]{BKL}
        J.~S.~Birman, K.~H.~Ko, S.~J.~Lee: {\em A new approach to the word and conjugacy problems in the braid groups}, Adv. Math. \textbf{139} (1998), no. 2, 322--353.

\bibitem[BM93]{BM1}
        J.~S.~Birman, W.~W.~Menasco: {\em Studying links via closed braids. III. Classifying links which are closed 3-braids}, Pacific J. Math. \textbf{161} (1993), no. 1, 25--113.

\bibitem[BM08]{BM2}
        \bysame: {\em A note on closed $3$-braids}, Commun. Contemp. Math. \textbf{10} (2008), suppl.~1, 1033--1047. 
        
\bibitem[DDG$^+$15]{DDGKM}
        P.~Dehornoy, F.~Digne, E.~Godelle, D.~Krammer, J.~Michel: {\em Foundations of Garside theory.},
        EMS Tracts in Mathematics, \textbf{22}. European Mathematical Society (EMS), Z\"urich, 2015. xviii+691 pp.

\bibitem[Erl99]{E}
        D.~Erle: {\em Calculation of the signature of a $3$-braid link}, Kobe J. Math. \textbf{16} (1999), no.~2, 161--175. 

\bibitem[FL18]{FL}
        P.~Feller, L.~Lewark: {\em On classical upper bounds for slice genera}, Selecta Math. (N.S.) \textbf{24} (2018), no. 5, 4885--4916.

\bibitem[Fre82]{F}
	M.~H.~Freedman: {\em The topology of four-dimensional manifolds}, J.~Differential Geom. \textbf{17} (1982), no.~3, 357--453.

\bibitem[FQ90]{FQ}
        M.~H.~Freedman, F.~Quinn: {\em Topology of 4-manifolds}, Princeton Mathematical Series, \textbf{39}. Princeton University Press, Princeton, NJ, 1990. viii+259 pp.

\bibitem[Gar69]{G}
        F.~A.~Garside: {\em The braid group and other groups}, Quart. J. Math. Oxford Ser. (2) \textbf{20} (1969), 235--254.

\bibitem[GG05]{GG}
	J.-M.~Gambaudo, \'E.~Ghys: {\em Braids and Signatures}, Bull. Soc. Math. France \textbf{133} (2005), no.~4, 541--579.

\bibitem[Inc16]{I}
	K.~Ince: {\em The untwisting number of a knot}, Pacific J.~Math. \textbf{283} (2016), no.~1, 139--156.

\bibitem[KT76]{KT}
	L.~H.~Kauffman, L.~R.~Taylor: {\em Signature of links}, Trans. Amer. Math. Soc. \textbf{216} (1976), 351--365.
	
\bibitem[Lev69]{Lev}
	J.~Levine, {\em Knot cobordism groups in codimension two}, Comment. Math. Helv. \textbf{44} (1969), 229--244.

\bibitem[Lew23]{Lew}
        L.~Lewark: {\em galg-computations} (2023), computer program available at \url{https://github.com/LLewark/galg-computations}.

\bibitem[Lie16]{L}
	L.~Liechti: {\em Positive braid knots of maximal topological $4$-genus}, Math.~Proc. Cambridge Philos.~Soc. \textbf{161} (2016), no.~3, 559--568.

\bibitem[Lit79]{Lit}
	R.~A.~Litherland: {\em Signatures of iterated torus knots}, Topology of low-dimensional manifolds (Proc. Second Sussex Conf., Chelwood Gate, 1977) Lecture Notes in Math. \textbf{722} (Springer, Berlin, 1979), 71--84.

\bibitem[Liv04]{Liv}
        C.~Livingston, {\em Computations of the Ozsv\'ath-Szab\'o knot concordance invariant}, Geom. Topol. \textbf{8} (2004), 735--742.

\bibitem[LL13]{LL}
	E.-K.~Lee, S.-J.~Lee: {\em Unknotting number and genus of $3$-braid knots}, J. Knot Theory Ramifications \textbf{22} (2013), no.~9, 1350047, 18 pp.

\bibitem[LM]{knotinfo}
        C.~Livingston and A.~H.~Moore: \emph{KnotInfo: Table of Knot Invariants}, \url{https://knotinfo.math.indiana.edu}, retrieved April 17, 2023. 

\bibitem[McC19]{McC}
	D.~McCoy: {\em Null-homologous twisting and the algebraic genus}, 2019--20 MATRIX annals, 147--165, MATRIX Book Ser., \textbf{4}, Springer, Cham.

\bibitem[Mur65]{M1}
	K.~Murasugi: {\em On a certain numerical invariant of link types}, Trans. Amer. Math. Soc. \textbf{117} (1965), 387--422.

\bibitem[Mur74]{M2}
	\bysame: {\em On closed $3$-braids}, Memoirs of the American Mathematical Society, no.~151. American Mathematical Society, Providence, R.I., 1974. vi+114 pp.

\bibitem[Pow17]{P}
	M.~Powell: {\em The four-genus of a link, Levine-Tristram signatures and satellites}, J.~Knot Theory Ramifications \textbf{26} (2017), no.~2, 1740008, 28 pp.

\bibitem[Ras10]{Ras}
	J.~Rasmussen: {\em Khovanov homology and the slice genus}, Invent. Math. \textbf{182} (2010), no.~2, 419--447.

\bibitem[Rud83]{R1}
        L.~Rudolph: {\em Braided surfaces and Seifert ribbons for closed braids}, Comment.  Math. Helvetici \textbf{58}, no.~1, (1983) 1--37.

\bibitem[Rud90]{R2}
        \bysame: {\em A congruence between link polynomials}, Math. Proc. Cambridge Philos. Soc. \textbf{107} (1990), no.~2, 319--327. 

\bibitem[Sag23]{Sage}
        The Sage Developers: {\em Sagemath, the Sage Mathematics Software System (Version 10.1)} (2023), \url{http://www.sagemath.org}.

\bibitem[Shu07]{Shu}
	A.~N.~Shumakovitch: {\em Rasmussen invariant, slice-Bennequin inequality, and sliceness of knots}, J.~Knot Theory Ramifications \textbf{16} (2007), no.~10, 1403--1412.

\bibitem[Sto17]{S}
        A.~Stoimenow: {\em Properties of closed $3$-braids and braid representations of links}, SpringerBriefs in Mathematics. Springer, Cham, 2017. x+110~pp.
        
\bibitem[Tri69]{Tri}
        A.~G.~Tristram: {\em Some cobordism invariants for links}, Proc. Cambridge Philos. Soc. \textbf{66} (1969), 251--264.

\bibitem[Tru23]{T}
        P.~Tru\"ol: {\em The upsilon invariant at $1$ of $3$-braid knots}, Algebr. Geom. Topol. \textbf{8} (2023), 3763--3804.       
        
\bibitem[Xu92]{Xu}
        P.~J.~Xu: {\em The genus of closed 3-braids}, J. Knot Theory Ramifications \textbf{1} (1992), no.~3, 303--326. 
\end{thebibliography}
