%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Notes on multigranular formalism
%%% Stephen J. Hegner
%%% Section 8
%%% 22 October 2018
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



 \section{Conclusions and Further Directions}\label{sec:cfd}



    In this paper, two main contributions have been made.

 \baxblkc

   \axitem{\textsc{Single-use proof system
                          for binary granule constraints:}}
    A sound and com-
 \preformat{\linebreak}
 plete proof system for the predicates of subsumption and disjunction
of granules,
 \preformat{\linebreak}
 $\bininfpos{G}$, has been developed.  This result builds
upon the earlier work in \mycite{AtzeniPa88_dke}, adding critical new
features, such as modelling of the bottom granule $\botgrsch{G}$ and
top granule $\topgrsch{G}$, and the requirement that all granules
other than $\botgrsch{G}$ have nonempty semantics.  It furthermore
provides single-use proofs, which are necessary for extension to a
proof system that involves the negations of these predicates as well.

   \axitem{\textsc{Proof system augmentation to negative constraints}}
   A general method has been developed to extend any sound and
complete single-use inference system over an Armstrong context
$\armctxt{C}$ to one which is sound and complete on the assertions in
$\armctxt{C}$ together with their negations.  This methods as then
applied to the inference system $\bininfpos{G}$ to obtain the sound
and complete inference $\bininf{G}$ system on all binary predicates of
an SMAS, both positive and negative.

 \eaxblk

  \noindent
  The immediate further direction is the following.

 \baxblkc

   \axitem{\textsc{Extend to granules with boundary:}}
    In spatial modelling, it is often advantageous or even necessary
to be able to work with granules with boundary.  Work is currently
underway to extend the notion of SMAS of this paper to such granules.
This requires replacing the single disjunction predicate
$\disjrulep{g_1}{g_2}$, with two, the first $\disjruleip{g_1}{g_2}$
for interiors and the second $\disjrulebp{g_1}{g_2}$ for boundaries.
The resulting framework can be shown to be an Armstrong context, with
a sound and complete single-use inference system which extends
$\bininfpos{G}$ naturally.  The methods of Sec.\ 6 of this paper apply
to this new framework as well, providing an inference system for both
positive and negative constraints for binary predicates with boundary.
The modelling power of this framework is equivalent to that of the
four-intersection model \mycite{EgenhoferFr91_ijgis} and RCC8
\mycite{Stell04_amai}.

 \eaxblk
