% CVPR 2022 Paper Template
% based on the CVPR template provided by Ming-Ming Cheng (https://github.com/MCG-NKU/CVPR_Template)
% modified and extended by Stefan Roth (stefan.roth@NOSPAMtu-darmstadt.de)

\documentclass[10pt,twocolumn,letterpaper]{article}

%%%%%%%%% PAPER TYPE  - PLEASE UPDATE FOR FINAL VERSION
%\usepackage[review]{cvpr}      % To produce the REVIEW version
\usepackage{cvpr}              % To produce the CAMERA-READY version
%\usepackage[pagenumbers]{cvpr} % To force page numbers, e.g. for an arXiv version

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage[accsupp]{axessibility}


% It is strongly recommended to use hyperref, especially for the review version.
% hyperref with option pagebackref eases the reviewers' job.
% Please disable hyperref *only* if you encounter grave issues, e.g. with the
% file validation for the camera-ready version.
%
% If you comment hyperref and then uncomment it, you should delete
% ReviewTempalte.aux before re-running LaTeX.
% (Or just hit 'q' on the first LaTeX run, let it finish, and you
%  should be clear).
\usepackage[pagebackref,breaklinks,colorlinks]{hyperref}


% Support for easy cross-referencing
\usepackage[capitalize]{cleveref}
\crefname{section}{Sec.}{Secs.}
\Crefname{section}{Section}{Sections}
\Crefname{table}{Table}{Tables}
\crefname{table}{Tab.}{Tabs.}


%\usepackage{multicol}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{adjustbox}

\usepackage{color}

\usepackage[normalem]{ulem}


\definecolor{ben}{rgb}{0.9,0.,0.5}
\newcommand{\ben}[1]{\textcolor{ben}{\emph{Ben:~{#1}}}}

\definecolor{pat}{rgb}{0.6,0.2,0.1}
\newcommand{\pat}[1]{\textcolor{pat}{\emph{Pat:~{#1}}}}

\definecolor{GY}{rgb}{0.4,0.1,0.9}
\newcommand{\gy}[1]{\textcolor{GY}{\emph{GY:~{#1}}}}

\newcommand{\mycomment}[1]{}

% custom commands
\newlength\savewidth\newcommand\shline{\noalign{\global\savewidth\arrayrulewidth
  \global\arrayrulewidth 1pt}\hline\noalign{\global\arrayrulewidth\savewidth}}


%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{9363} % *** Enter the CVPR Paper ID here
\def\confName{CVPR}
\def\confYear{2023}


\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{On the Importance of Accurate Geometry Data for Dense 3D Vision Tasks}


\author{
\hspace{-20pt}
HyunJun Jung$^{\ast 1}$,
Patrick Ruhkamp$^{\ast 1,2}$,
Guangyao Zhai$^{1}$,
Nikolas Brasch$^{1}$,
Yitong Li$^{1}$,\\
Yannick Verdie$^{1,3}$,
Jifei Song$^{3}$,
Yiren Zhou$^{3}$,
Anil Armagan$^{3}$,
Slobodan Ilic$^{1,4}$,\\
Ales Leonardis$^{3}$,
Nassir Navab$^{1}$,
Benjamin Busam$^{1,2}$
\\
\\
\small
$^1$ Technical University of Munich,
$^2$ 3Dwe.ai,
$^3$ Huawei Noah's Ark Lab,
$^4$ Siemens AG,
$^*$ Equal Contribution
\\ \footnotesize{\fontfamily{qcr}\selectfont
hyunjun.jung@tum.de, p.ruhkamp@tum.de, guangyao.zhai@tum.de, b.busam@tum.de
}
}

\maketitle


%%%%%%%%% ABSTRACT
\begin{abstract}

Learning-based methods to solve dense 3D vision problems typically train on 3D sensor data. The respectively used principle of measuring distances provides advantages and drawbacks. These are typically not compared nor discussed in the literature due to a lack of multi-modal datasets. Texture-less regions are problematic for structure from motion and stereo, reflective material poses issues for active sensing, and distances for translucent objects are intricate to measure with existing hardware. Training on inaccurate or corrupt data induces model bias and hampers generalisation capabilities. These effects remain unnoticed if the sensor measurement is considered as ground truth during the evaluation. This paper investigates the effect of sensor errors for the dense 3D vision tasks of depth estimation and reconstruction. We rigorously show the significant impact of sensor characteristics on the learned predictions and notice generalisation issues arising from various technologies in everyday household environments. For evaluation, we introduce a carefully designed dataset\footnote{dataset available at https://github.com/Junggy/HAMMER-dataset} comprising measurements from commodity sensors, namely D-ToF, I-ToF, passive/active stereo, and monocular RGB+P. Our study quantifies the considerable sensor noise impact and paves the way to improved dense vision estimates and targeted data fusion.

\end{abstract}

%%%%%%%%% BODY TEXT

\input{sections/1_introduction}
\input{sections/2_relatedwork}
\input{sections/3_dataset}
\input{sections/4_methods}
\input{sections/5_experiments}
\input{sections/6_discussion.tex}

\clearpage
\newpage
%%%%%%%%% REFERENCES
{\small
\bibliographystyle{ieee_fullname}
\bibliography{PaperForReview}
}

\end{document}
