\section{Conclusion and Limitation}

In this paper, we proposed a novel and practical weakly semi-supervised instance segmentation scheme leveraging point labels as weak supervision for cost-efficient and high-performance instance segmentation.
We motivated that the main performance bottleneck of modern instance segmentation frameworks arises from the instance proposal extraction.
To this end, we proposed a method that can effectively exploit the budget-friendly point labels as weak supervision to resolve the bottleneck.
Moreover, we presented the MaskRefineNet to deal with hard learning scenarios where the amount of fully labeled data is extremely limited.
Owing to the effectiveness of the proposed method, we can generate high-quality pseudo instance masks, achieving promising instance segmentation results.
Despite our remarkable results driven by cost-efficient point labels, we have a limit to straightforwardly exploiting the tremendous amount of unlabeled image pools, such as web-crawling images without any annotations.
Our future direction may involve incorporating unlabeled images in our framework to extend its application to semi-supervised learning scenarios.

\paragraph{Acknowledgment.} We thank Youngjoon Yoo and ImageVision team members for valuable discussions and feedback. This work was supported by the Engineering Research Center Program through the National Research Foundation of Korea (NRF) funded by the Korean Government MSIT (NRF-2018R1A5A1059921) and Institute of Information \& communications Technology Planning \& Evaluation (IITP) grant funded by the Korea government (MSIT) (No.2019-0-00075, Artificial Intelligence Graduate School Program (KAIST)).
