\section{Larger $k$}
For the majority of this paper, we have set $k=1$. In this section, we will look at larger $k$ and see if anything can be said about them before delving into similar calculations that can be time consuming.

Beforehand, let us discuss some properties on how these axes act on this regular $4k$-gon. We denote the axes in $X(4k)$ by $a_i$  for $i \in \Z /4k\Z=:N$. Before identifying opposite vertices in an orbit to produce a skew axet, it would be useful to formularise how the Miyamoto involution of one axis affect the others. For $i,j\in N$, we have
\[ a_i^{\tu{a_j}}= a_{2j-i}.\]
\subsection{Odd $k$}
We will now present a result that McInroy suggested.
\begin{prop}\label{odd k}
Let $k$ be odd. For axet $X'(k+2k)$, there exists a subaxet isomorphic $X'(1+2)$. 
\proof We have for $i\in N$, $a_{2i}=a_{2(k+i)}$. As $k$ is odd, $a_k$ is in the odd orbit and  $ a_0^{\tu{a_k}}= a_{2k-0}=a_0$. Therefore $a_0$ is fixed by $a_k$. We have that  $a_k^{\tu{a_0}}= a_{0-k}=a_{-k}$. Therefore the set $Y=\{a_0,a_k,a_{-k}\}=\GenG{a_0,a_k}$ is a skew axet and is isomorphic to $X'(1+2)$. \qed
\end{prop}
\begin{cor}
    Let $k>1$ be odd and $(A,X)$ be a $2$-generated primitive $\mon{\al,\bt}$-axial algebra of skew axet $X'(k+2k)$. Then $\al+\bt=1$. Further, either $A$ has a subalgebra of $3C(\al,1-\al)$ or $(\al,\bt)=(\frac{1}{3},\frac{2}{3})$ and $A$ has a subalgebra of $Q_2(\frac{1}{3})$.
    \proof  By the above theorem, $X$ must contain a subaxet, $Y$, isomorphic to $X'(1+2)$. Let $B=\GenA{a_0,a_k}$ be the $2$-generated axial algebra of Monster type with axet $Y$. Let $m=\frac{k-1}{2}$ and notice $a_k^{\tu{m}}=a_1$. Hence primitivitiy of $a_1$ implies that $a_k$ is too. Further $a_0$ has a $\bt$-eigenspace and as $a_k$ is a $\jor{\al}$-axis in $B$, then $a_1$ has a $\al$-eigenspace. Hence $\al+\bt=1$ and the rest follows. \qed
\end{cor}
With these statements, the method for odd $k>1$ involves looking at the subalgebra $B=\GenA{a_{-1},a_1}$ that acts on $X(2k)$. Further, $B$ will be symmetric as we can take the flip to be $\tu{0}$. Using classification of $2$-generated symmetric axial algebras of Monster type in \cite{yabe2023classification}, \cite{franchi2022classifying} and \cite{franchi2022quotients}, we will have a short list for possible options for $B$. We will go into much further detail in a second paper, which we will extend the classification to when $k$ is odd and we will start to look into skew axets when $k$ is even.