%LATEX TEMPLATE FOR PROGRESS IN PARTICLE AND NUCLEAR PHYSICS - October 2021
\documentclass[review]{elsarticle}

%For line numbers
% \usepackage{lineno}
% \modulolinenumbers[5]
\usepackage{enumitem}
\usepackage[colorlinks,citecolor=blue,linktoc=all,linkcolor=cyan]{hyperref}
\usepackage{graphicx}
\usepackage{bm}
% Fonts
\usepackage[T1]{fontenc}
\usepackage{dsfont}               % use mathds instead of mathbb for outline fonts
\usepackage{mathrsfs}             % provides mathscr without overwriting mathcal
\usepackage{slashed}              % For Dirac slash notation.
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{amsfonts}
\usepackage{amsfonts}
\usepackage{bbm}
\numberwithin{equation}{section}
\numberwithin{table}{section}
\numberwithin{figure}{section}

%\journal{Progress in Particle and Nuclear Physics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% JPPNP customization of the margins: 
\topmargin-2.8cm
\oddsidemargin-1cm
\evensidemargin-1cm
\textwidth18.5cm
\textheight25.0cm

% JPPNP customization of the headings: 
\usepackage{titlesec}
\usepackage{sectsty}
\titleformat{\section}{\normalfont\Large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\normalfont\large\bfseries}{\thesubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\normalsize\bfseries}{\thesubsubsection}{1em}{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\graphicspath{{figures/}}

\usepackage{xcolor}
\newcommand{\kz}[1]{{\color{red}\textit{KZ Note: #1}}}
\newcommand{\ssz}[1]{{\color{orange}\textit{SS Note: #1}}}
\newcommand{\lw}[1]{{\color{blue}\textit{LW Note: #1}}}
\newcommand{\plg}[1]{{\color{purple}\textit{LG Note: #1}}}

%%%%%%%%%%%%%%%%%%%%%%%
%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
\biboptions{numbers,sort&compress} % make the refs more concise
% \bibliographystyle{abbrv}
%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
	\begin{frontmatter}
		%\title{Studying High Energy Nuclear Physics with Machine Learning}
            \title{Exploring QCD matter in extreme conditions with Machine Learning}
		%authors, affiliations, corresponding author mention 
	    \author[fias]{Kai Zhou\corref{mycorrespondingauthor}}
            \cortext[mycorrespondingauthor]{Corresponding authors}
            \ead{zhou@fias.uni-frankfurt.de}
        
	    \author[fias]{Lingxiao Wang\corref{mycorrespondingauthor}}
            \ead{lwang@fias.uni-frankfurt.de}
        
        \author[ccnu]{Long-Gang Pang\corref{mycorrespondingauthor}}
            \ead{lgpang@ccnu.edu.cn}
        
        %\author[thu,sbu]{Shuzhe Shi\corref{mycorrespondingauthor}}
        \author[sbu]{Shuzhe Shi\corref{mycorrespondingauthor}}
	       \ead{shuzhe.shi@stonybrook.edu}		
            
		\address[fias]{Frankfurt Institute for Advanced Studies (FIAS), D-60438 Frankfurt am Main, Germany.}
  		\address[ccnu]{Institute of Particle Physics and Key Laboratory of Quark and Lepton Physics (MOE), Central China Normal University, Wuhan, 430079, China.}
        %\address[thu]{Department of Physics, Tsinghua University, Beijing 100084, China.}
		\address[sbu]{Center for Nuclear Physics, Department of Physics and Astronomy, Stony Brook University, Stony Brook, NY 11794-3800, USA.}

        
		\begin{abstract}
            In recent years, machine learning has emerged as a powerful computational tool and novel problem-solving perspective for physics, offering new avenues for studying strongly interacting QCD matter properties under extreme conditions. This review article aims to provide an overview of the current state of this intersection of fields, focusing on the application of machine learning to theoretical studies in high energy nuclear physics. It covers diverse aspects, including heavy ion collisions, lattice field theory, and neutron stars, and discuss how machine learning can be used to explore and facilitate the physics goals of understanding QCD matter. The review also provides a commonality overview from a methodology perspective, from data-driven perspective to physics-driven perspective. We conclude by discussing the challenges and future prospects of machine learning applications in high energy nuclear physics, also underscoring the importance of incorporating physics priors into the purely data-driven learning toolbox. This review highlights the critical role of machine learning as a valuable computational paradigm for advancing physics exploration in high energy nuclear physics.

			% We review recent progresses for high energy nuclear physics theoretical studies with machine learning paradigms utilized. Over the recent years, machine learning techniques have emerged as a powerful numerical tool and novel computational mindset in high energy nuclear physics, opening up brand-new avenues for studying strongly interacting QCD matter properties at extreme temperatures and densities. The purpose of this review article is to provide an overview of the current state of this intersection direction, which focuses on the application of machine learning paradigms to theoretical studies in high energy nuclear physics. From several different aspects including heavy ion collisions, lattice field theory study and neutron star sector, we discuss the utilization of machine learning for exploring and facilitating the physics aim within high energy nuclear physics. A comprehensive commonality from methodology perspective for the field is conducted as well. The article concludes with a discussion of the challenges and fugure prospects of machine learning in high energy nuclear physics, highlighting the importance of making detailed understanding in applying the machine learning paradigms for physics research, to which the incorporation of physics priors into the pure data-driven learning toolbox is promising. Overall, this review provides an overview of the interaction of high energy nuclear physics and machine learning, and underscores the critical role of machine learning as a valuable computational paradigm for advancing our physics exploration of high energy nuclear physics.
		\end{abstract}
		
		\begin{keyword}
			machine learning\sep heavy ion collisions\sep lattice QCD \sep neutron star \sep inverse problem
		\end{keyword}
		
	\end{frontmatter}
 
	\newpage
	\thispagestyle{empty}
	\tableofcontents
	%to begin the line numbers: 
	%\linenumbers
	
	%beginning of the core of the manuscript
	\input{1.intro}
	\newpage
	\input{2.hic}
	\newpage
    \input{3.lattice}
	\newpage
    \input{4.astrophy}
	\newpage
    \input{5.new}
    \newpage
    \input{6.sum}
	\newpage
	\section*{Acknowledgements}  
	We express our sincere gratitude to all collaborators who have made invaluable contributions to our research projects. \\
	This work was supported by the Germany BMBF under the ErUM-Data project (KZ), the AI grant of SAMSON AG, Frankfurt (LW and KZ), Xidian-FIAS International Joint Research Center (LW), Huawei Technologies Co., Ltd and the National Natural Science Foundation of China under contract No. 12075098 (LP), and U.S. Department of Energy, Office of Science, Office of Nuclear Physics, grant No. DE-FG88ER40388 (SS).
	
    \bibliography{reviews}
	
	\newpage
	\appendix
	\renewcommand*{\thesection}{\Alph{section}}
\end{document}