\documentclass{article}

\usepackage{arxiv}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{natbib}
% \usepackage{lineno}
\usepackage{xcolor}
\usepackage[toc, page]{appendix}
% \linenumbers
\usetikzlibrary{external}
\tikzexternalize[prefix=tikz/]
% \setlength{\parindent}{0em}
% \setlength{\parskip}{1ex}
\newcommand{\Kuu}{\mathbf K_{uu}}
\newcommand{\Kuf}{\mathbf K_{uf}}
\newcommand{\Kfu}{\mathbf K_{uf}^\top}
\newcommand{\Kff}{\mathbf K_{ff}}
\renewcommand{\u}{\mathbf u}
\newcommand\given{\,|\,}
\newcommand{\m}{\mathbf m}
\newcommand{\bmu}{\mathbf \mu}
\renewcommand{\S}{\mathbf{S}}
\newcommand{\zero}{\mathbf 0}
\newcommand{\half}{\tfrac{1}{2}}
\newcommand{\tr}{\textrm{tr}}
\renewcommand{\L}{\mathbf L}
\newcommand{\R}{\mathbf R}
\newcommand{\I}{\mathbf{I}}
\newcommand{\A}{\mathbf A}
\newcommand{\B}{\mathbf B}
\newcommand{\F}{\mathbf F}
\renewcommand\vec{\textrm{vec}}
\renewcommand{\d}{\textrm{d}}
\newcommand{\KL}{\textsc{KL}}
\newcommand{\Yml}{\phi_\ell^m}
\newcommand{\Ymlp}{\phi_{\ell^\prime}^{m^\prime}}
\newcommand{\uml}{u_\ell^m}
\newcommand{\fml}{\hat{f}_{\ell,m}}
\newcommand{\Nld}{N(\ell,d)}
\newcommand{\diff}{\mathop{}\!\mathrm{d}}
\newcommand{\james}[1]{{gt\color{red}JH:#1}}


\title{Sparse Gaussian Processes with Spherical Harmonic Features Revisited}
\author{%
  Stefanos Eleftheriadis\thanks{Amazon.com}%
  \And Dominic Richards\footnotemark[1]%
  \And James Hensman\thanks{Work done while at Amazon; currently with Microsoft Research}%
  }


\begin{document}
\maketitle

\begin{abstract}
We revisit the Gaussian process model with spherical harmonic features and study connections between the associated RKHS, its eigenstructure, and deep models.
Based on this, we introduce a new class of kernels which correspond to deep models of continuous depth. 
In our formulation, depth can be estimated as a kernel hyper-parameter by optimizing the evidence lower bound. 
Further, we introduce sparseness in the eigenbasis by variational learning of the spherical harmonic phases.
This enables scaling to larger input dimensions than previously, while also allowing for learning of high frequency variations.
We validate our approach on machine learning benchmark datasets.
\end{abstract}

\section{Introduction}
\input{intro.tex}

\section{Deep learning with kernels on the sphere}
\input{deep_kernel.tex}

\section{Introduction to spherical harmonics}
\input{sh_intro.tex}

\section{Continuous depth kernels}
\input{cont_depth.tex}

\section{Spherical harmonics as features for GPs}
\input{sh_gps.tex}


\section{Experiments}
\input{experiments.tex}

\section{Conclusions}
In this work we revisited the prior work on sparse Gaussian processes with spherical harmonics 
to solidify the understanding of the connection between deep models and spherical functions.
Specifically, we introduced a new kernel which corresponds to deep models of continuous depth and we further proposed to variationally learn the phases of spherical harmonic features, which results in
a more efficient set of global descriptors with high frequency components.
Our experimental evaluations on standard machine learning benchmarks verify the efficacy of the proposed approach.

\bibliographystyle{apalike}
\bibliography{refs}

\end{document}
