
In this section, we introduce our experimental setup,
which includes implementation details of EL methods we investigated (\Cref{sec:methods}) and datasets we create for investigating partial KB inference (\Cref{sec:datasets}).

\begin{table*}[th]
\small 
\centering
\setlength{\tabcolsep}{1.5mm}{
\begin{tabular}{p{1mm}ll|ccc|ccc|ccc}
\toprule
& \multicolumn{2}{c}{Target KB.}& \multicolumn{3}{c}{EntQA} & \multicolumn{3}{c}{GENRE}& \multicolumn{3}{c}{KeBioLM+CODER} \\
& Train KB & Eval KB &Precision & Recall & F1&Precision & Recall & F1&Precision & Recall & F1 \\ 
\hline
\cellcolor{blue!10}& UMLS & UMLS  & 45.99&23.68&31.27&42.44&43.69&43.05&33.58&34.94&34.25\\
\cellcolor{blue!10}&&\SNOMEDint  & 46.04&27.01&34.05&34.40&49.40&40.56&28.19&48.28&35.59\\
\cellcolor{blue!10}&&\SNOMEDext  & 
36.75 & 23.12 & 28.38 & 19.82 & 39.28 & 26.35 & 14.18 & 37.54 & 20.59 \\
\cellcolor{blue!10}&&\TAint  & 41.52&31.56&35.86&17.26&49.53&25.60&9.78&50.28&16.37\\
\cellcolor{blue!10}&&\TAext  & 
43.43 & 23.24 & 30.28 & 34.97 & 42.45 & 38.35 & 26.52 & 34.59 & 30.02 \\
\cellcolor{blue!10}& &\TBint  & 30.01&25.56&27.61&7.69&36.06&12.68&4.76&41.51&8.54\\
\cellcolor{blue!10}\multirow{-7}{*}{\rotatebox[origin=c]{90}{\textit{MedMentions}}} &&\TBext  & 
 46.02 & 24.34 & 31.84 & 40.45 & 44.76 & 42.50 & 31.95 & 37.74 & 34.61 \\
\hline
\multicolumn{3}{c}{Avg. Drop}\vline & 5.36 & -2.13 & -0.7 & 16.68 & 0.11 & 12.04 & 14.35 & -6.71 & 9.96 \\
\hline
\cellcolor{blue!10}&MeSH&MeSH & 83.59 & 66.48 & 74.06 &70.92&68.71&69.80&72.21&74.84&73.5 \\
\cellcolor{blue!10}&&\MEDICint  & 81.92&70.45&75.75&31.53&68.19&43.12&29.24&68.38&40.96\\
\cellcolor{blue!10}\multirow{-3}{*}{\rotatebox[origin=c]{90}{\textit{BC5.}}}&&\MEDICext & 
87.10 & 66.92 & 75.69 & 37.55 & 65.33 & 47.69 & 42.57 & 80.67 & 55.73 \\
\hline
\multicolumn{3}{c}{Avg. Drop}\vline & -0.92 & -2.21 & -1.66 & 36.38 & 1.95 & 24.40 & 36.31 & 0.32 & 25.16 \\
\bottomrule
\end{tabular}}
\caption{Results for entitly linking in parital KB inference. The first section shows results on MedMentions with UMLS as training KB. The last section shows results on BC5CDR with MeSH as training KB. Eval KB represents different partial KBs for inference. 
% The first row of each section are evaluated using training KBs. 
% And others are results that we evaluate models on subsets of training KB in zero-shot setting. 
The average drops are averaged among metrics between full evaluation (first row in each section) and partial KB evaluation (other rows).}
\label{tab:main_end-to-end_result}
\small 
\vspace{-1em}
\end{table*}



\subsection{Direct Partial KB Inference}\label{sec:methods}
\input{setting.tex}

\subsection{Datasets}\label{sec:datasets}

We conduct experiments on two widely-used biomedical EL datasets and select several partial KBs used as inference.
Selection biases of partial KBs may be introduced into our setting because different partial KBs may result in different target distributions of mention-concept annotations, as this may lead to different difficulties in EL due to different KB sizes, the semantics of entities, and entity occurrence frequencies in the training set.
% This might prejudice our empirical findings.
To eliminate this effect as much as possible, we not only evaluate on partial KBs mentioned above but also their complement KBs to the training KBs.
We add $\complement$ to indicate the complements. 
The detailed statistics of datasets are listed in \Cref{tab:stats} of \Cref{app:data_stat}.

\textbf{BC5CDR}~\cite{li2016biocreative} is a dataset that annotates 1,500 PubMed abstracts with 4,409 chemicals, 5818 disease entities, and 3,116 chemical-disease interactions. 
All annotated mentions are linked to concepts in the target knowledge base MeSH.
We use MeSH as the training KB and we consider a smaller KB \textit{MEDIC} \cite{davis2012medic} as the partial KB for inference.
MEDIC is a manually curated KB composed of 9,700 selected disease concepts mainly from MeSH.
% To meet the assumption that MEDIC forms a subset of MeSH, we ditch the concepts in MEDIC that do not exist in MeSH.

\textbf{MedMentions} \cite{medmentions} is a large-scale biomedical entity linking datasets curated from annotated PubMed abstracts.
We use the \textit{st21pv} subset which comprises 4,392 PubMed abstracts, and over 350,000 annotated mentions linked to concepts of 21 selected semantic types in UMLS \cite{bodenreider2004unified}.
We use UMLS as the training KB and we select three representative partial KBs which are concepts from semantic types \textit{T038 (Biologic Function)} and \textit{T058 (Health Care Activity)} in UMLS and \textit{SNOMED}.
% To meet the assumption that the partial KBs do not contain concepts out of training KB, we ditch the concepts in partial KBs that do not exist in UMLS. 


% \subsection{Metrics}\label{sec:metrics}

