\section{Conclusions}
\label{sec:conclusions}

Extracting entities and relations from CTI reports becomes more challenging as the number of classes increases. This paper presents STIXnet, the first solution for automatically extracting all STIX entities and relationships in unstructured Cyber Threat Intelligence reports. Our contribution uses rule-based, NLP, and DL techniques to retrieve all STIX entities and relationships in a report automatically. We also resort to regular expression rules and an extensible Knowledge Base to effectively create an infrastructure for cyber threat analysts to consult and gather all their data and resources. The proposed pipeline enforces a modular approach to be more flexible on the user and their demands, thus separating the different tasks into different modules. The formal definition of the interaction between the sub-modules allows researchers and organizations to use our framework by adding, swapping, and removing sub-modules at will. This is particularly useful in specific scenarios where threat analysts might want to focus on specific entity classes, thus fine-tuning the framework to their needs.

In future works, we would like to explore the text extraction module of STIXnet further to enhance its results. Indeed, being the first module in the pipeline, accurate extraction and efficient artifact removal could improve the precision of the subsequent modules. Furthermore, STIX Domain Objects have many fields that vary depending on the entity types we are considering. All these fields can be filled with information that can be extracted from the sentences. Thus, it could be possible to extend the scope of our processing and provide additional intelligence when present.