%% The first command in your LaTeX source must be the \documentclass command.
%%
%% Options:
%% twocolumn : Two column layout.
%% hf: enable header and footer.
\documentclass[
twocolumn,
% hf,
]{ceurart}

%%
%% One can fix some overfulls
\sloppy

%%
%% Minted listings support 
%% Need pygment <http://pygments.org/> <http://pypi.python.org/pypi/Pygments>
\usepackage{listings}
%% auto break lines
\lstset{breaklines=true}

% For theorems and such
\usepackage{amsmath, amssymb, amsthm}
\usepackage{mathtools, bm, bbm, thm-restate}
% Recommended, but optional, packages for figures and better typesetting:
\usepackage[skip=2pt]{caption}
\usepackage[skip=2pt]{subcaption}
\usepackage{microtype, nicefrac}
\usepackage{graphicx, wrapfig}
\usepackage{booktabs, adjustbox, multirow}
\usepackage{xcolor, colortbl}
\usepackage{tikz, float}
\usetikzlibrary{shapes,arrows}
\usepackage{threeparttable}
% if you use cleveref..
\usepackage[capitalize,noabbrev]{cleveref}

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\DeclareMathOperator{\argmaxinline}{arg\,max}
\DeclareMathOperator{\argmininline}{arg\,min}
\newcommand{\set}[1]{\mathcal{#1}}
\newcommand{\prob}{\mathbb{P}}
\renewcommand{\vec}[1]{\mathbf{#1}}
\newcommand{\symvec}[1]{\bm{#1}}

\newcommand\eqdef{\stackrel{\mathclap{\scriptsize\mbox{def}}}{=}}
\newcommand{\gray}[1]{\textcolor{gray}{#1}}
\def\rowgray{\rowcolor{lightgray!20}}
%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% Rights management information.
%% CC-BY is default license.
\copyrightyear{2023}
\copyrightclause{Copyright for this paper by its authors.
  Use permitted under Creative Commons License Attribution 4.0
  International (CC BY 4.0).}

%%
%% This command is for the conference information
\conference{AISafety-SafeRL 2023 Workshop (IJCAI), August 19–21, 2023, Macao, SAR, China}

%%
%% The "title" command
\title{Diffusion Denoised Smoothing for Certified and Adversarial Robust Out-Of-Distribution Detection}

\tnotemark[1]
\tnotetext[1]{This  work  was  funded  by  the  Bavarian  Ministry  for  Economic  Affairs,  Regional  Development  and  Energy.}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
\author[1]{Nicola Franco}[%
% orcid=0000-0002-0877-7063,
email=nicola.franco@iks.fraunhofer.de,
% url=https://yamadharma.github.io/,
]
\cormark[1]
% \fnmark[1]
\address[1]{Fraunhofer Institute for Cognitive Systems IKS, Munich, Germany}
\address[2]{Dept. of Computer Science \& Munich Data Science Institute, Technical Univ. of Munich, Germany}

\author[1]{Daniel Korth}[email=daniel.korth@iks.fraunhofer.de]
\author[1]{Jeanette Miriam Lorenz}[email=jeanette.miriam.lorenz@iks.fraunhofer.de]
\author[1]{Karsten Roscher}[email=karsten.roscher@iks.fraunhofer.de]
\author[2]{Stephan G{\"u}nnemann}[email=s.guennemann@tum.de]

%% Footnotes
\cortext[1]{Corresponding author.}
% \fntext[1]{These authors contributed equally.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
    As the use of machine learning continues to expand, the importance of ensuring its safety cannot be overstated. 
    A key concern in this regard is the ability to identify whether a given sample is from the training distribution, or is an "Out-Of-Distribution" (OOD) sample.
    In addition, adversaries can manipulate OOD samples in ways that lead a classifier to make a confident prediction.
    In this study, we present a novel approach for certifying the robustness of OOD detection within a $\ell_2$-norm around the input, regardless of network architecture and without the need for specific components or additional training.
    Further, we improve current techniques for detecting adversarial attacks on OOD samples, while providing high levels of certified and adversarial robustness on in-distribution samples.
    The average of all OOD detection metrics on CIFAR10/100 shows an increase of $\sim 13 \% / 5\%$ relative to previous approaches.
    Code: \url{https://github.com/FraunhoferIKS/distro}
\end{abstract}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\begin{keywords}
    Robust Machine Learning \sep
    Robustness Certificates \sep 
    Out-Of-Distribution \sep 
    Randomized Smoothing
\end{keywords}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\input{sections/introduction}
\input{sections/background}
\input{sections/method}
\input{sections/distro}
\input{sections/results/setting}
\input{sections/results/experiments}
\input{sections/conslusion}


%%
%% Define the bibliography file to be used
\bibliography{references/certificates, references/plain_ood, references/robust_ood, references/miscellaneous, references/datasets}

%%
%% If your work has an appendix, this is the place to put it.
% \appendix

% \input{sections/appendix/proofs}
% \input{sections/appendix/settings}
% \input{sections/appendix/experiments}
% \input{sections/appendix/experiments_standardized}

\end{document}

%%
%% End of file
